### 2024-01-04 paper/main_sections/1_head.tex
move from MS word for clean up

Authors
Haoyu Yang, Juanli Zhao, Qiankun Wang, Bin Lin, Wei Luo, Ziqi Sun*, Ting Liao*

Title
Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO2 Reduction Reactions

### 2024-01-04 paper/main_sections/2_abstract.tex
move from MS word for clean up

Abstract
Single-atom catalysts (SACs) have emerged as pivotal frontiers for catalyzing a myriad of chemical reactions, yet the diverse combinations of active elements and support materials, the nature of coordination environments, elude traditional methodologies in searching optimal SAC systems with superior catalytic performance. Herein, by integrating multi-branch Convolutional Neural Network (CNN) analysis models to hybrid descriptor based activity volcano plot, two-dimensional (2D) SAC system composed of diverse metallic single atoms anchored on six type of 2D supports, including g-C3N4, nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, BN, and C2N, are screened for efficient CO2 reduction reaction (CO2RR). Starting from establishing a correlation map between the adsorption energies of intermediates and diverse electronic and elementary descriptors, sole singular descriptor lost magic to predict catalytic activity, including d-band center. Deep learning method utilizing multi-branch CNN model therefore was employed, using 2D electronic density of states (eDOS) as input to predict adsorption energies. Hybrid-descriptor enveloping both C- and O-types of CO2RR intermediates was introduced to construct volcano plots and limiting potential periodic table, aiming for intuitive screening of catalyst candidates for efficient CO2 reduction to CH4. The eDOS occlusion experiments were performed to unravel individual orbital contribution to adsorption energy. To explore the electronic scale principle governing practical engineering catalytic CO2RR activity, orbitalwise eDOS shifting experiments based on CNN model were employed. The study involves examining the adsorption energy and, consequently, catalytic activities while varying supported single atoms. This work offers a tangible framework to inform both theoretical screening and experimental synthesis, thereby paving the way for systematically designing efficient SACs.

### 2024-01-04 paper/main_sections/3_introduction.tex
move from MS word for clean up

Electrochemical CO2RR stands as a promising avenue for long-term seasonal energy storage [1] and mitigating excess CO2 in the atmosphere.

Despite decades of research, metallic copper remains a leading CO2RR electrocatalyst for hydrocarbon production [2], albeit burdened by substantial overpotential and low faradic efficiency and poor operational stability [3, 4]. In this regard, supported SACs have displayed remarkable activity and selectivity across various catalytic reactions [5, 6], leveraging their unique electronic properties and coordination environment. To date, experimental studies have primarily focused on two-electron reduction products due to the facile release of gaseous CO [7-9]. Consequently, there is a pressing need to modulate the electronic structure of single-atom sites to enable hydrocarbon production at reduced overpotentials.

The challenge towards effective catalysts design lies in understanding the reaction mechanisms. Experimental determination of these mechanisms remains challenging due to the complexity of in situ spectroscopic detection of reaction intermediates [10]. Computational modeling, particularly methods based on quantum mechanics (QM) such as density functional theory (DFT), allows for the profiling the energetics of intermediates and unveils structure-activity relationships for identified active sites [11, 12], contributing to understanding of reaction mechanisms. However, the high computational cost of QM methods restricts the accessible catalyst space [13-15].

In this context, researchers have explored descriptor-based methods to circumvent QM calculations and establish direct correlations between target properties and electronic factors, commonly referred to as descriptors or features. Traditional methods of crafting descriptors, as seen in the d-band model of Hammer and Nørskov [16], necessitate meticulous selection of chemical properties based on chemical knowledge and are inherently case-dependent [17]. Particularly in the case of SACs, the relationship is intricate, rendering manual crafting inadequate [18, 19]. To streamline this featurization process, we employed convolutional neural networks (CNNs), which autonomously derive a hierarchical representation directly from the electronic density of state (eDOS) [20-22]. This approach accurately maps to the activity space, negating the need for manual crafting of descriptors and providing a more efficient method to understand and establish the structure-mechanism-activity relationship for electrochemical reactions.

In this study, we introduced a catalyst performance analysis pipeline (Figure 1) integrating a customized CNN model and volcano plots. Our CNN model accurately estimated the adsorption energies, the activity descriptor, from the eDOS of 2D materials supported single metal catalysts. Evaluations on the adsorption energies of nine intermediates along CO2RR and competing hydrogen evolution reaction (HER) as well yielded prediction mean absolute errors (MAEs) at the level of 0.1 eV, which is well aligned with the precision of conventional DFT calculations [23-25]. This result validated the capability of current CNN model to accurately capture intricate spatial information from eDOS. Building on this, we introduced an orbital-wise eDOS occlusion experiment was adopted afterwards inspired from the occlusion technique widely used in computer vision and pattern recognition applications. Systematic eDOS experiment was performed to elucidate orbitalwise contributions to the adsorption energies at different energy levels, which produced consistent outcome from Crystal Orbital Hamilton Population (COHP) analysis and real-space wavefunction visualization. All these results justified the proficiency of CNN model on identifying the dominant orbitals for adsorbate-substrate interactions. Furthermore, orbital-wise eDOS shifting experiment, exploring the impact of orbital-wise eDOS shifting on the adsorption behavior of studied catalysts were performed.

Simultaneously, we incorporated the volcano plots into the catalysis performance analysis pipeline. Besides offering intuitive analysis of catalyst activities (represented by the elevation of volcanoes), volcano plots points to the directions on how effort can be exerted to identify promising catalyst candidates. Built upon scaling relations [26], we introduced a hybrid-descriptor scheme incorporating both C- and O-centered species. The scaling coefficient of determination (R2) was increased by 0.1387 using hybrid descriptor, which demonstrate an improved prediction accuracy compared to the well documented single descriptor based method.

In summary, we introduced a catalyst performance analysis pipeline by integrating CNN and volcano plot analysis, using CO2RR as an example proof of concept. The CNN, which correlates eDOS with activity descriptors, establishes a robust electronic structure-activity relationship. Notably, it is capable to predict the influence of eDOS disturbances, caused by either alloying, strain, or defects [27-29], to modulate the catalytic activity of materials, which will offer insights into the intrinsic mechanism for rationalized catalyst optimization strategies. Advancing the current volcano plot method, the involvement of CNN models in catalyst performance analysis pipeline holds enormous promise for advanced exploration of catalysts with superior performance.

### 2024-01-04 paper/main_sections/4.1_cnn_for_eads.tex
move from MS word for clean up

Adsorption energy prediction from electronic density of states with convolutional neural network.

Originating from the pioneering work of Hammer and Nørskov [30], the d-band center model has emerged as a successful paradigm for employing descriptor to understand and predict the adsorption behavior on transition metal surfaces. To investigate alternative electronic and elementary descriptors that may serve as more suitable substitutes for the d-band center model in the context of SACs, we performed Kendall rank correlation analysis to account for both linearity and non-linearity [31]. The correlation coefficient map, as presented in Figure 2a, highlighted the d-band center as the most informative descriptor with a Kendall’s τ coefficient of -0.33, and followed by the vacuum level and electronegativity. However, d-band center alone does not suffice for accurate predictions of intermediate adsorption energy as illustrated in the scatter plot Supplementary Figure 18, and therefore, refinements are imperative. Unlike bulk transition metal surfaces, where the variations in the d-band centre account for the majority of the adsorption energy variations [27, 32], the unique structure of SACs introduces more variables rather than d-band center that are intrinsically correlated with the variations of adsorption energy. This finding also interpreted that in some reported prior studies, indicating that depending solely on the d-band center may be insufficient for accurate adsorption energy predictions in the context of SACs [33-37]. As a result, the development of a method tailored specifically for catalysts like SACs becomes essential.

In our study, we employ CNN, a renowned deep learning method proficient in capturing spatial hierarchy from matrix-like data, such as the eDOS. Notably, CNN’s autonomy from prior knowledge and human intervention during feature extraction renders it more efficient than traditional machine-learning methods. Our approach harnesses the entire 2D eDOS with a multi-branch CNN model. Figure 2b and Figure 2c delineate the model and its branches. The workflow involves processing the entire 2D eDOS as input, segregating orbitals into branches, and directing the concatenated outputs through another convolutional block, which generates the adsorption energy prediction. Sharing learnable parameters across branches optimizes computational efficiency. By leveraging the CNN model, we predicted adsorption energies from the eDOS of supported single atoms, and validated through parity plots (Figure 2d-m). The model predicts adsorption energies across nine species within the CO2RR process and competing HER side reaction, attaining an averaged MAE of 0.06 eV. This MAE aligns with the established precision of DFT methods, which typically range between 0.1-0.2 eV concerning experimental measurement [25, 38, 39]. The full list of prediction errors is available in Supplementary Table 18. These results confirm the CNN model’s ability to predict adsorption energies from eDOS input. Moreover, they suggest the potential for predicting adsorption energies for SACs using eDOS, although this would demand more sophisticated feature engineering techniques.

In terms of adsorption energy prediction, the CNN model maintained consistency across diverse elemental compositions and varied adsorption strengths. It handled species containing oxygen, hydrogen, and carbon atoms equally well, spanning an adsorption energy range from 0 to 10 eV. Significantly, after pretraining the CNN model, making predictions (inference) scales only linearly with system size and demands considerably less computational resources compared to DFT calculations [40]. Conversely, unlike QM based methods, which could generate reasonably precise energy estimation for individual candidates, CNN relies on extensive datasets to ensure reliable predictions. In our case, the original dataset comprised 2052 samples, leading to a CNN model with a validation MAE of 0.3725 eV. In pursuit of enhanced prediction accuracy, we proposed a data augmentation method detailed in the Methods section. This augmentation resulted in an expanded dataset of 12312 samples, enhancing prediction performance with a reduced validation MAE of 0.1736 eV. Comparatively, our CNN model diverges from prior attempts, notably Fung’s pioneer work [41], by requiring only the eDOS of supported single metal atom alone and adsorbate. This revision eliminated the necessity for a complete set of substrate and adsorbate eDOS and significantly reduced computational cost. We foresee the potential in the applicability of our method to diverse species and electrocatalytic reactions, given the availability of comprehensive datasets. The strength of our CNN model lies in its freedom from element- or adsorbate-specific parameters, relying solely on eDOS as input. This adaptability opens up the possibility for its utilization in a wide array of electrocatalytic studies.

### 2024-01-04 paper/main_sections/4.2_volcano_plots.tex
move from MS word for clean up

Hybrid descriptors enabled volcano plot for catalyst analysis.

Catalyst activity volcano plots, built upon the scaling relations proposed by Peterson and Nørskov’s [26], goes beyond assessment of candidatures’ energetics only but to provide informative guidance on discovering catalysts candidates with superior performance [42, 43]. Our endeavor to improve the accuracy of volcano plots leads to the development of the hybrid-descriptor, which encompasses both C- and O- bonding types of CO2RR intermediates within the scaling relations. This adaptation arose from the intuition that most CO2RR intermediates are featured with both bonding types rather than any single one in dominance. By integrating both bonding featured descriptors into the hybrid approach, we found the coefficient of determination (R2) was increased by 0.1387. Detailed information about the scaling parameters and performance enhancements are provided in Supplementary Tables 13 and Supplementary Figure 10. This improvement to some extent underscored our premise that CO2RR intermediates typically exhibit chemical similarities encompassing both O- and C-type descriptors. After taking this dual nature into consideration, our hybrid-descriptor method can evaluate the intermediates adsorption energies more accurately. Importantly, the introduction of hybrid descriptors is computationally affordable compared to DFT methods, as it involves only a set of linear regressions to identify the optimal mixing ratio, as elaborated in the Methods section.

Expanding upon the revised scaling relations, we introduce an activity volcano plot and a rate-determining step (RDS) volcano plot for the CO2RR process, shown in Figure 3a and Supplementary Figure 11. Given that HER is a key competing reaction with CO2RR [44], we also incorporated a selectivity volcano plot, presented in Supplementary Figure 12, to offer a comprehensive analysis of catalyst candidates. In adherence to Peterson and Nørskov’s original framework [26], our choice of x and y axes descriptors aligned with Gads *CO and Gads *OH. Further elaboration on how the limiting potentials were evaluated across the volcano plot can be found in the Methods section. Among the candidatures explored, Ge@g-C3N4 emerged as the most promising catalyst, demonstrating theoretical activity at a limiting potential of -1.2126 eV. Notably, the observed selectivity trend paralleled the activity trend, suggesting that catalysts exhibiting high theoretical activity are also resistant to HER side reactions. The RDS volcano plot (Supplementary Figure 11) indicated protonation of *CO as the rate-determining step for nearly optimal candidates. Moreover, the activity volcano plot predicted an optimal catalyst featuring a theoretical limiting potential of -1.0516 V, at Gads *CO of 0.0589 eV and Gads *OH of -4.0075 eV, positioned at the right-center of the volcano plot. Results from RDS volcano plot indicate that protonation of *CO likely serves as the RDS for CO2RR. Consequently, it should be the focal point for future catalyst designs. The activity and selectivity volcano plots imply that enhancing theoretical activity could be achieved by decreasing CO affinity while increasing OH affinity with the catalysts. This result suggests a perspective: weak binding of CO to the catalyst surface might facilitate the rotation of C-O backbone from the “upright” configuration in *CO to the “horizontal” orientation in *CHO [45], and therefore facilitating dynamics and protonation of the *CO species.

The volcano plot offers an intuitive analysis of the reaction energetics and provides insights into the mechanisms of the reaction. While the volcano plot provides a broad overview, it lacks the ability to delve into lower-level explanations rooted in electronic structures, where detailed electronic interactions and specific bonding mechanisms remain beyond its scope. Despite its limitations, the volcano plot serves as a useful tool for identifying focal elementary steps in the reaction pathway that demand closer attention during catalyst design. It also highlights directions for further catalyst refinement, and can also be integrated with the shifting experiment discussed later to optimize existing catalysts.

Additionally, we mapped the theoretical limiting potentials of the analyzed catalyst candidates onto periodic tables, shown in Figure 3b and Supplementary Figure 13 to 17. Our analyses do not reveal consistent trends within groups or periods, nor did they exhibit evident patterns across substrates. These observations suggest intricate interactions between supported metal atoms and substrates. The absence of straightforward trends underscores the need for nuanced explorations in understanding these interactions like the CNN model.

### 2024-01-04 paper/main_sections/4.3_validation.tex
move from MS word for clean up

Validation of CNN predictions.

Historically, interpretability has posed challenges for deep learning methods, often rendering their inner workings akin to black boxes [46-48]. The occlusion technique, widely utilized in Computer Vision [49-51], involves systematically masking sections of the input matrix to assess their impact on the final prediction score. In our work, we introduce an orbitalwise occlusion method to discern individual orbital contribution to adsorption energy within the CNN model, drawing inspiration from Fung’s pioneer integration of this technique into eDOS analysis [41]. In this work, occlusion experiments involve orbitalwise masking specific eDOS, which are then fed into the CNN model to observe resulting disturbance in adsorption energy. A visual representation of this process can be found in Supplementary Figure 21. Conceptually, this experiment simulates the effect of shielding electronic states, allowing investigation of the potential contribution to adsorption energy from these states. Additionally, we attempted to extract the planewave coefficients of Kohn-Sham orbital for wavefunction visualization. This validation step was undertaken to confirm the spatial distribution of the orbitals pinpointed by the occlusion experiments.

To validate our method, we conducted occlusion experiments on Cr@g-C3N4, Co@g-C3N4 and Cu@g-C3N4. Each of these supported metals possesses 3d subshells with different electronic configurations: half-filled, partially filled and fully filled, allowing us to test the universality of our approach. The results of the occlusion experiment on the supported Cr single atom in Cr@g-C3N4 are given in Figure 4a. The d_(x^2-y^2 ) orbital emerges as dominant in CO interaction. Shielding electrons centered around -2 eV significantly alter the adsorption energy, indicating the potency of this orbital. The real-space wavefunction visualization in Figure 4d corroborates these findings, highlighting the interaction between the d_(x^2-y^2 ) orbital of single metal atom and the adsorbate. This suggests the d_(x^2-y^2 ) orbital of supported Co predominantly influence the interaction with CO, and thus shielding electrons from this orbital markedly disturb the adsorption energy. Additionally, occlusion experiments were performed on the Co d_xy orbital of Co@g-C3N4 (Figure 4b) and the Cu d_xy orbital of Cu@g-C3N4 (Figure 4c). In both cases, the d_xy orbital was identified as the dominant contributor. While identifying the dominant orbital is crucial, these findings also suggest that interactions with adsorbates occurring out-of-plane are influenced by in-plane orbitals as well. Importantly, it becomes evident that d orbitals do not universally impact interactions with adsorbates, emphasizing the need for case-specific discussions.

To validate the chemical relevance of predictions made by CNN model, we conducted COHP analysis, a theoretical bond-detecting tool used to identify bonding and anti-bonding contributions to band-structure energy [52]. In this research, interactions between the supported metal atom and atoms within a 5 Å radius were calculated to understand its bonding environment, as detailed in the Methods section. The results of the occlusion experiment on the Co d_xy orbital of Co@g-C3N4, identified as the dominant orbital via occlusion experiments, were compared with the COHP analysis, as shown in Figure 4g and Figure 4i. The occlusion experiment pinpointed strong metal-adsorbate interactions at energy levels of -1 eV and -6.3 eV, which were confirmed by the COHP analysis. We then investigated the non-dominant Co d_xz orbital, and the COHP analysis highlighted interactions at -1 eV and -6.5 eV, aligning with the findings from the occlusion experiments.

In summary, orbitalwise occlusion experiments provide chemical interpretations into deep learning models, enhancing their interpretability. Furthermore, these occlusion results are readily understandable to chemists, enabling the identification of orbitalwise contributions to the adsorption process.

### 2024-01-04 paper/main_sections/4.4_shifting_exp.tex
move from MS word for clean up

Shifting experiments for prediction of better catalysts.

While CNN models excel in prediction of the activity of catalyst candidates directly from eDOS, volcano plots point out directions leading to better catalysts. Exploring potential disturbances to adsorption energies and aiming to shift existing catalyst candidates closer to the peak of the activity volcano plot presents an intriguing avenue of investigation. In this work, we introduce an orbitalwise shifting experiment to explore the impact of orbitalwise eDOS shifting on adsorption behavior. The experiment involved shifting eDOS along the energy axis, and the CNN model was deployed to predict the resultant disturbance in adsorption energy for each shifting operation. Focusing on all Period 4 metal elements examined in this study, we analyzed the effects of eDOS shifting. To induce a moderate disturbance, we selected the energy range of -1 to 1 eV, and a shifting resolution of 0.005 eV/step was chosen to align with the eDOS calculation resolution.

Figure 5 illustrates that supported Ga and Ge, the sole p-block metals in our study, exhibited no response to d orbital shifting. This observation is consistent with their lack of d-electrons in their valence shells, reinforcing the reliability of our shifting experiments. We also investigated potential disturbance from p orbital shifting, as shown in Supplementary Figure 31 and found no significant response. This implies that Ge@g-C3N4 holds promise as a CO2RR electrocatalyst, given its high activity and resilience to electronic structure disturbances. Nevertheless, fine-tuning its performance through eDOS modulation might pose a challenge. In contrast, supported Fe, Cu and Zn display strong sensitivity to eDOS shifting. Interestingly, the adsorption energy consistently shifted towards more positive values, indicating a weakening of the catalyst-adsorbate interaction, regardless of the shifting direction within the investigated energy range. This underscores the intricate interplay between the supported metal atom and the substrate, emphasizing the necessity of a tool like the CNN model to predict such disturbances. Supported Cr exhibited a contrary response to eDOS shifting, strengthening the interaction with the CO adsorbate regardless of the shifting direction. Supported Ti, V, Co and Ni showed weak response to eDOS shifting, suggesting the need for alternative methods beyond manipulating their eDOS to regulate their interactions with CO adsorbate.

In summary, shifting experiments offer a valuable means to predict the potential disturbances in adsorption behavior resulting from eDOS shifting, a task that is challenging to accomplish directly within the DFT framework. However, it's important to note that achieving the predicted shifting in actual theoretical or experimental scenarios may not be easily accessible. Skillful manipulation of the electronic structure of catalyst candidates would be required, presenting a practical challenge. In contrast to prior studies on bulk metals [41], wherein the adsorption energy exhibits a continuous shift with eDOS variations, the response of SACs is notably discrete. These responses manifest as isolated peaks throughout the shifting range, attributed to the distinctive structure of SACs. Despite this challenge, having a tool that can predict the potential impact of eDOS shifting is advantageous for the theoretical design of SACs.

### 2024-01-04 paper/main_sections/5_method.tex
move from MS word for clean up

Methods
DFT calculations.
Spin-polarized density functional theory calculations were performed using the Vienna Ab initio Simulation Package (VASP) version 5.4.4 [53-55] to optimize geometries and determine the electronic structure. The Perdew-Burke-Ernzerhof (PBE) functional [53] within the generalized gradient approximation (GGA) [56] was utilized to describe the electron-ion interactions and electronic exchange correlations. Kohn-Shan equations were approached employing a plane-wave basis set with a cut-off energy of 440 eV. Geometry optimizations were performed using Γ-Centered K-point meshes of (2 × 2 × 1) until the force on each atom fell below 0.02 eV Å-1. Electronic structure calculations utilized denser K-point meshes of (3 × 3 × 1) and employed self-consistent field (SCF) methods.

Catalyst models.
Supported SACs were modelled by anchoring individual metal atoms onto various 2D substrates, including graphitic carbon nitride (g-C3N4), nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, boron nitride, and monolayer C2N. The specific single metal atoms studied are outlined in Supplementary Figure 1. To prevent interactions between adjacent images along the z-axis, vacuum layers of 15 Å were introduced.

CO2RR pathway.
The C1 production CO2RR pathway, as initially described by Peterson et al. [45] and later confirmed by Jiao et al. [57] for g-C3N4 based SACs, involves the following elementary steps. Asterisks (*) indicate species adsorbed on the SAC surfaces:
# TODO: check format
█(CO_2+ ^*+H^++e^- □(→┴(          ) )  ^* COOH#(1))
█( ^* COOH+H^++e^- □(→┴(          ) )  ^* CO+H_2 O#(2))
█( ^* CO+H^++e^- □(→┴(          ) )  ^* CHO#(3)######)
█( ^* CHO+H^++e^- □(→┴(          ) )  ^* CH_2 O#(4)##)
█( ^* CH_2 O+H^++e^- □(→┴(          ) )  ^* OCH_3#(5)#)
█( ^* OCH_3+H^++e^- □(→┴(          ) )  ^* O+CH_4#(6)#)
█( ^* O+H^++e^- □(→┴(          ) )  ^* OH#(7)#)
█( ^* OH+H^++e^- □(→┴(          ) )  ^*+H_2 O#(8)#)

Free energy calculations.
Free energies were computed from electronic energies by considering thermal corrections, incorporating normal mode analysis of all degrees of freedom of adsorbates. The free energy G was calculated using the formula:
# TODO: check format
█(G=E+ E_ZPE-TS#(9))
where G represents the free energy, E denotes electronic energy, EZPE is the zero-point energy, T represents temperature in Kevin, and S stands for entropy. Detailed information regarding these corrections can be found in Supplementary Section 1.3.

The computational hydrogen electrode (CHE) model [45, 58] was employed to introduce potential dependence. At the reference electrode surface, the reaction
# TODO: check format
█(1/2 H_2(g)   □(↔┴(           )  H^++ e^- )#(10))
is in equilibrium, allowing the calculation of the chemical potential of the electron-proton pair as:
█(μ(H^+)+μ(e^-)=1/2 μ(H_2(g) )-eU#(11))
For the external potential U applied, the change in free energy (ΔG) was determined using the equation:
█(∆G_n (U)= ∆G_n (U=0)+neU#(12))
Here, μ represents chemical potential, U signifies the external potential applied, n represents the number of proton-electron pairs transferred, and e denotes the elementary charge.

Hybrid descriptor for volcano plots.
Hybrid descriptors incorporate both descriptors within a single equation, enhancing the accuracy of scaling relationship with minimal computational overhead, as demonstrated in Supplementary Figure 10 and Supplementary Table 13. Comprehensive analyses are presented Supplementary Section 1.5. This leads to the formulation of the scaling relation:
# TODO: check format
█(G_ads Z=k[θ*G_ads CO+(1-θ)*G_ads OH]+c_Z#(13)##)
Here, θ represents the mixing ratio of the CO descriptor, Z denotes any adsorbate, and k and cZ are adsorbate-specific scaling parameters. The optimal mixing ratio θ is determined through iterative exploration across the range, utilizing a step length of 0.01.

Equation 14 could be simplified to a more general form:
# TODO: check format
█(G_ads Z=a_Z G_ads CO+b_Z G_ads OH+c_Z#(14)#)
Here, a_Z, b_Z, c_Z are adsorbate-specific parameters.

Consequently, the limiting potential UL is entirely determined by two descriptors through the following equation:
# TODO: check format
█(U_L=-max⁡{〖ΔG〗_i }/e#(15)#)
Where ∆Gi represents the free energy change of reaction step i.

This approach simplifies the theoretical performance assessment of any catalyst within the scope of our research to only two descriptors: G_ads CO and G_ads OH. This method offers a visual representation of the high-dimensional optimization challenge. To aid visualization, a 2D mesh grid is established, enabling vectorized assessments of limiting potentials across the descriptor value ranges. At each grid point, the limiting potential is computed using Equation 16.

CNN architecture and hyperparameter tuning.
We designed our CNN architecture drawing inspiration from its successful implementation in tasks involving electrocardiogram signal classification [59], as illustrated in Figure 2b and 2c. This multi-branched CNN comprises nine branches tailored to handle eDOS orbitals while ensuring a reduced memory footprint.

The effectiveness of neural network models is intricately tied to the choice of hyperparameters. To identify the optimal set of hyperparameters, we employed Hyperband [60], a modern and parallelizable bandit-based optimization algorithm. The search space for hyperparameters is detailed in Supplementary Table 16, and the resulting optimal hyperparameters are presented in Supplementary Table 17.

Data augmentation and CNN model training.
To enhance the generalizability and robustness of the our CNN model, and achieve comprehensive coverage of the chemical space [61], we applied data augmentation techniques to the initial dataset using the following procedures:
	In addition to the designated "initial state" of the adsorption process, where the adsorbate positioned 6.5 Å above the supported single metal atom, five intermediate images were interpolated. These images were distributed between the initial and final states at a spacing of 0.5 Å, starting from the initial state side.
	A diverse set of smearing techniques was employed to determine of partial occupancies fnk, including the tetrahedron method [62] and the Gaussian method. For the Gaussian method, the smearing width was varied within the range of 0.01 eV to 0.1 eV. This careful selection of methods was made to guarantee reliable and consistent predictions of adsorption energies from the model, regardless of the smearing technique used.
The augmented dataset comprises 12,312 samples, with adsorption energies having a standard deviation of 1.8117 and a variance of 3.2821. Twenty pecent of these samples were allocated to the validation set. Throughout the training process, a batch size of 64 was employed to ensure a balanced learning dynamic.

Occlusion experiments.
Supplementary Figure 21 visually illustrates the occlusion experiment methodology. To maintain consistent shapes, zero-padding was applied to the input eDOS arrays. Focusing on understanding the influence of metals on adsorption behavior, a masker with dimensions [width, 1, 1] was employed along the metal channel to eliminate cross-orbital interactions. Here, "width" denotes the masker width, and detailed explanations for determining the width are provided in Supplementary Section 2.6. Through recursive application of these maskers, variations in predicted adsorption energies from the CNN model were recorded, generating an occlusion array.

Shifting experiments.
Supplementary Figure 30 illustrates the implemented shifting experiment protocol. In this study, the initial electronic density of states underwent controlled shifting along the energy axis. This protocol ranges from -1 eV to 1 eV, with a step length of 0.005 eV per image. To maintain a uniform energy window, each image underwent cropping and padding procedures. The resulted output arrays took the form of [400, 1] arrays for simultaneous orbital shifting and [400, 9] arrays for individual orbital shifting. The energy range for shifting was chosen to induce a moderate disturbance to adsorption energy.

Chemical bond analysis and real-space wavefunction visualization.
COHP analysis was performed using the Local-Orbital Basis Suite Towards Electronic-Structure Reconstruction (LOBSTER) package  [52, 63-66] version 4.1.0, with the GGA-PBE wavefunctions fitted by S. Maintz [63, 67]. A Gaussian smearing for energy integration was employed with a broadening width of 0.05 eV. The quantification of bonding strength between the single metal atom and the substrate was achieved through the summation of interactions with neighboring atoms within a range of 0.5 Å to 5.0 Å from the single metal atom. Orbitals of interest were confirmed through band-structure analysis, and real-space wavefunctions were subsequently visualized using VASPKIT [68] and VESTA [69].

Machine learning and data analysis environment.
The CNN model was implemented using TensorFlow [70], and hyperparameter optimization was conducted using the Hyperband [60] algorithm via KerasTuner [71]. For a more detailed overview of our machine learning setup and data analysis environment, please refer to Supplementary Section 3.

### 2024-01-04 paper/main_sections/6_tail.tex
move from MS word for clean up

Data Availability
Essential source data required to replicate the study's results–including VASP input files, structure files of SACs, eDOS arrays and the pretrained CNN model–are available on GitHub at https://github.com/DanielYang59/cnn4dos or can be provided by the corresponding authors upon request. Due to their substantial size in terabytes, the complete source data is not currently hosted on publicly available repositories but can also be obtained from the corresponding authors upon request.

Code Availability
Associated computer code for this study can be accessed on GitHub at https://github.com/DanielYang59/cnn4dos or obtained from the corresponding authors upon request.

Acknowledgements
The QUT eResearch Office provided computational resources and services used in this work. This research was undertaken with the assistance of resources and services from the National Computational Infrastructure (NCI), supported by the Australian Government. It was also supported by resources provided by the Pawsey Supercomputing Research Centre with funding from the Australian Government and the Government of Western Australia. Insights into deep learning methodologies were contributed by Mr. Yanwei Guan from Chongqing University and Mr. Zhipeng He from Assoc. Prof. Chun Ouyang's team at QUT. The machine learning and data analysis implementation benefited from resources provided by the GitHub, TensorFlow and Stack Overflow communities. Dr. Ryky Nelson from RWTH Aachen University offered valuable guidance on Crystal Orbital Hamilton Population analysis.

Author Contributions
H.Y. performed DFT calculations, implemented Python code the machine learning methodologies and data analysis, and drafted and refined the manuscript. J.Z. engaged in valuable discussions on DFT calculations. Q.W. provided advice on the computer code revisions. W.L. facilitated resource acquisition and offered research supervision. B.L. provided guidance on DFT calculations and offered research supervision. Z.S. initiated the research concept, contributed to manuscript revisions, and supervised the overall research. T.L. guided DFT calculations and data analysis, offering continuous supervision throughout the research and manuscript drafting.

Competing interests
The authors declare no competing interests in relation to this research.

### 2024-01-04 paper/si_sections/2_ml.tex
move from MS word for clean up

Section 2 Additional details on machine learning method
Section 2.1 d-band center and adsorption energy relations

Supplementary Figure 18 | Scatter plot of d-Band Center and Adsorption Energy Relationships. This figure delineates the relationship between d-band center and adsorption energies for various species: (a) CO2, (b) COOH, (c) CO, (d) CHO, (e) CH2O, (f) OCH3, (g) O, and (h) OH. Data from all six substrates investigated in this study are included.

Section 2.2 Feature correlation analysis

Supplementary Figure 19 | Pairwise Plot of Adsorption Energy and Key Descriptors. This chart displays the pairwise relationships between CO adsorption energy and its four most correlated descriptors–d-band center (spin-up) δεd↑, lattice parameter γ, vacuum level Evac, and electronegativity on the Allen scale XAllen –as identified by Kendall rank correlation analysis. Data from all six substrates investigated in this study are incorporated.

Supplementary Table 15
Notations for elementary descriptors and electronic descriptors
Elementary Descriptors	Electronic Descriptors
R	atomic radius	α, β, γ	lattice parameters
Eea	electron affinity	ΦDFT	DFT calculated work function
Φ	work function	Evac	vacuum level
XAllen, ΧP, ΧRevP	electronegativity in Allen, Pauling and revised Pauling scales	Eg, Eg↑, Eg↓	average, spin-up and spin-down band gaps
Ar	relative atomic mass	ed	number of d-electrons
Ei	ionisation energy	δεd↑	d-band centre (spin-up)
G	group number	Wd	d-band width
P	period number	eBader	Bader charge
V	number of valence electrons

Section 2.3 Input pipeline construction
The format of the 2D array for the eDOS is naturally well-suited for use as neural network inputs. In this study, the array adopts a shape of [numSamplings, numOrbitals, numChannels], as illustrated in Supplementary Figure 20. Here, “numSamplings” represents the number of data points sampled across the energy spectrum, “numOrbitals” denotes the number of DOS orbitals, and “numChannels” indicates the number of atomic channels.

Supplementary Figure 20 | Schematic representation of the input eDOS data structure.

For practical purposes, certain spatial hierarchies are expected to remain invariant, such as the energy range over which the eDOS is sampled. In this work, we maintain a consistent energy range of -14 eV to 6 eV, sampled at a density of 50 points⋅eV-1. In addition to maintaining a fixed energy range, the following steps are taken to standardize the input eDOS data:
1.	For atoms lacking d-electrons, the eDOS is zero-padded.
2.	f-orbital eDOS data are excluded.
3.	The eDOS of adsorbates is zero-padded along the Channels axis to align with the adsorbate that contains the maximum number of atoms, which, in this study, is the *OCH3 species. This padded eDOS is then appended to the metal eDOS.

As a result of these preprocessing steps, the input eDOS arrays consistently have a shape of [4000, 9, 6]. This corresponds to 4000 sampling points across the energy range, 9 eDOS orbitals, and 6 atomic channels.

Section 2.4 Hyperparameter tuning for CNN

Supplementary Table 16
The hyperparameter searching space
Hyperparameter	Search space	Description
learningRate	[10-4, 10-2], logscale	Learning rate of Adam optimiser
dropoutRate	[0, 1]	Dropout rate
root_fc0	128, 256, 512	Output dimensionality of 1st fully connected layer in root
root_fc1	256, 512, 1024, 2048	Output dimensionality of 2nd fully connected layer in root
root_act	"tanh", "relu", "sigmoid"	Activation function of fully connected layers in root
kernelSize	[2, 32]	Width of convolution window
numFilters	[8, 64]	Number of filters in the convolution
numConvLayers	[1, 16]	Number of convolution layers
numConvBlocks	[1, 16]	Number of convolution blocks
br_fc0	16, 32, 64, 128, 256, 512	Output dimensionality of 1st fully connected layer in branch
br_fc1	8, 16, 32, 64, 128, 256	Output dimensionality of 2nd fully connected layer in branch
br_act	"tanh", "relu", "sigmoid"	Activation function of fully connected layers in branch

Supplementary Table 17
Optimal hyperparameters identified with Hyperband algorithm
Hyperparameter	Optimal value	Description
learningRate	10-3	Learning rate of Adam optimiser
dropoutRate	0.3	Dropout rate
root_fc0	256	Output dimensionality of 1st fully connected layer in root
root_fc1	512	Output dimensionality of 2nd fully connected layer in root
root_act	“relu”	Activation function of fully connected layers in root
kernelSize	10	Width of convolution window
numFilters	17	Number of filters in the convolution
numConvLayers	3	Number of convolution layers
numConvBlocks	1	Number of convolution blocks
br_fc0	256	Output dimensionality of 1st fully connected layer in branch
br_fc1	128	Output dimensionality of 2nd fully connected layer in branch
br_act	“tanh”	Activation function of fully connected layers in branch

Supplementary Table 18
Prediction mean absolute errors of the CNN model
Adsorbate	Original dataset (eV)	Augmented dataset (eV)
CO2	0.0447	0.0336
COOH	0.0436	0.0581
CO	0.0402	0.0402
CHO	0.0614	0.0778
CH2O	0.0553	0.0632
OCH3	0.0605	0.0636
O	0.1135	0.1081
OH	0.0547	0.0602
H	0.0703	0.0646
Note. The same CNN model, trained on the augmented dataset, was used for all predictions. The term “Original dataset” refers to evaluations conducted on the original dataset without any augmented data; it does not imply the use of a different CNN model trained solely on the original dataset. Similarly, “Augmented dataset” refers to evaluations on the dataset with both original data and augment data, not a distinct model.

Section 2.5 Occlusion experiment

Supplementary Figure 21 | Illustration of the occlusion experiment. This figure demonstrates the step-by-step process of the occlusion experiment. The input eDOS array first undergoes zero-padded, and then a masker of width “width” is applied, resulting in an occlusion array that preserves the shape of the input array.

Supplementary Figure 22 | Occlusion Experiment with a masker width of “1”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.

Supplementary Figure 23 | Occlusion Experiment with a masker width of “3”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.

Supplementary Figure 24 | Occlusion Experiment with a masker width of “5”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.

Supplementary Figure 25 | Occlusion Experiment with a masker width of “11”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.

Supplementary Figure 26 | Occlusion Experiment with a masker width of “21”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.

Supplementary Figure 27 | Occlusion Experiment with a masker width of “31”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.

Supplementary Figure 28 | Occlusion Experiment with a masker width of “41”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.

Supplementary Figure 29 | Occlusion Experiment with a masker width of “51”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.

Section 2.6 Shifting experiment

Supplementary Figure 30 | Illustration of the shifting experiment. This figure illustrates the sequential stages of the shifting experiment. Initially, the input eDOS array is shifted along the Energy axis. Subsequently, it undergoes zero-padding and cropping, ensuring a consistent shape based on the shifting direction, to match the input eDOS array. The resulting shifted array is then processed by the CNN model to assess the disturbance in adsorption energy caused by the shifting operation.

Supplementary Figure 31 | Shifting Experiment on p orbital. Effect of orbital shifting on CO adsorption energy, predicted by the CNN model, for single metal atom catalysts supported on g-C3N4. The perturbations caused by shifting of entire p orbital are presented. The shifting step size corresponds to the energy resolution of the eDOS, set at 0.005 eV in this study. A positive eDOS shift indicates a shift towards higher energy levels, and vice versa.

### 2024-01-04 paper/si_sections/3_others.tex
move from MS word for clean up

Section 3 Other additional information
Section 3.1 Additional information on machine learning environment.
The hyperparameter optimization for the proposed CNN model was performed using NVIDIA® V100 Tensor Core GPUs, courtesy of the Australian National Computational Infrastructure's (NCI) HPC Gadi system. The HyperBand algorithm [7], as implemented in KerasTuner [8] , facilitated the tuning process.

Supplementary Table 19
Core packages in deep learning environment
Name	Version	Build	Channel
conda	4.13.0	py39h06a4308_0	anaconda
cuda-nvcc	11.8.89	0	nvidia
cuda-toolkit	11.8.0	0	nvidia
cudatoolkit	11.6.0	habf752d_9	nvidia
ipykernel	6.9.1	py39h06a4308_0	anaconda
ipython	7.34.0	pypi_0	pypi
jupyter_client	7.2.2	py39h06a4308_0	anaconda
jupyterlab	3.4.4	py39h06a4308_0	anaconda
keras	2.9.0	pypi_0	pypi
keras-preprocessing	1.1.2	pypi_0	pypi
keras-tuner	1.3.5		pypi
matplotlib	3.5.1	py39h06a4308_1	anaconda
numpy	1.22.4	pypi_0	pypi
pandas	1.3.4	py39h8c16a72_0	anaconda
python	3.9.12	h12debd9_1	anaconda
scikit-learn	1.1.1	py39h6a678d5_0	anaconda
scipy	1.8.1	py39hddc5342_3	conda-forge
tensorboard	2.9.1	pypi_0	pypi
tensorflow	2.9.3	pypi_0	pypi
tensorflow-gpu	2.9.3	pypi_0	pypi
xlrd	2.0.1	pyhd3eb1b0_0	anaconda
yaml	0.2.5	h7b6447c_0	anaconda
Note. The complete list of packages is provided along with the source code.

Section 3.2 Additional information on data analysis and visualization environment.
Data analysis and visualization tasks were executed on an Apple MacBook Air featuring an octa-core M2 chip. For accuracy, the TensorFlow-Metal plugin for Mac-based GPU acceleration was deliberately excluded, as it could potentially yield erroneous CNN model predictions.

The illustrations of CNN architecture displayed in Figure 1 of the main text, as well as  Supplementary Figure 21 and Supplementary Figure 30, were obtained from the GitHub repository dair-ai/ml-visuals [9]. Blender was used to create and render the visual representation of the catalyst analysis pipeline shown in Figure 1 of the main text.

Supplementary Table 20
Core packages in data analysis and visualization environment
Name	Version	Build	Channel
bokeh	3.2.2	pypi_0	pypi
colorcet	3.0.1	pypi_0	pypi
heatmapz	0.0.4	pypi_0	pypi
keras	2.13.1	pypi_0	pypi
keras-tuner	1.3.5	pypi_0	pypi
matplotlib	3.7.2	pypi_0	pypi
numpy	1.24.3	pypi_0	pypi
pandas	2.0.3	pypi_0	pypi
python	3.11.4	hb885b13_0
pyyaml	6.0.1	pypi_0	pypi
scikit-learn	1.3.0	pypi_0	pypi
scipy	1.11.1	pypi_0	pypi
seaborn	0.12.2	pypi_0	pypi
tensorboard	2.13.0	pypi_0	pypi
tensorflow	2.13.0	pypi_0	pypi
tensorflow-macos	2.13.0	pypi_0	pypi
Note. The complete list of packages is provided along with the source code.

### 2024-01-04 paper/main_sections/4.1_cnn_for_eads.tex
clean up some signs

@@
 To investigate alternative electronic and elementary descriptors that may serve as more suitable substitutes for the d-band center model in the context of SACs, we performed Kendall rank correlation analysis to account for both linearity and non-linearity [31].
-The correlation coefficient map, as presented in Figure 2a, highlighted the d-band center as the most informative descriptor with a Kendall’s τ coefficient of -0.33, and followed by the vacuum level and electronegativity.
+The correlation coefficient map, as presented in Figure 2a, highlighted the d-band center as the most informative descriptor with a Kendall's τ coefficient of -0.33, and followed by the vacuum level and electronegativity.
 However, d-band center alone does not suffice for accurate predictions of intermediate adsorption energy as illustrated in the scatter plot Supplementary Figure 18, and therefore, refinements are imperative.
@@
 In our study, we employ CNN, a renowned deep learning method proficient in capturing spatial hierarchy from matrix-like data, such as the eDOS.
-Notably, CNN’s autonomy from prior knowledge and human intervention during feature extraction renders it more efficient than traditional machine-learning methods.
+Notably, CNN's autonomy from prior knowledge and human intervention during feature extraction renders it more efficient than traditional machine-learning methods.
 Our approach harnesses the entire 2D eDOS with a multi-branch CNN model.
@@
 The full list of prediction errors is available in Supplementary Table 18.
-These results confirm the CNN model’s ability to predict adsorption energies from eDOS input.
+These results confirm the CNN model's ability to predict adsorption energies from eDOS input.
 Moreover, they suggest the potential for predicting adsorption energies for SACs using eDOS, although this would demand more sophisticated feature engineering techniques.
@@
 This augmentation resulted in an expanded dataset of 12312 samples, enhancing prediction performance with a reduced validation MAE of 0.1736 eV.
-Comparatively, our CNN model diverges from prior attempts, notably Fung’s pioneer work [41], by requiring only the eDOS of supported single metal atom alone and adsorbate.
+Comparatively, our CNN model diverges from prior attempts, notably Fung's pioneer work [41], by requiring only the eDOS of supported single metal atom alone and adsorbate.
 This revision eliminated the necessity for a complete set of substrate and adsorbate eDOS and significantly reduced computational cost.

### 2024-01-04 paper/main_sections/4.2_volcano_plots.tex
clean up some signs

@@
 
-Catalyst activity volcano plots, built upon the scaling relations proposed by Peterson and Nørskov’s [26], goes beyond assessment of candidatures’ energetics only but to provide informative guidance on discovering catalysts candidates with superior performance [42, 43].
+Catalyst activity volcano plots, built upon the scaling relations proposed by Peterson and Nørskov's [26], goes beyond assessment of candidatures' energetics only but to provide informative guidance on discovering catalysts candidates with superior performance [42, 43].
 Our endeavor to improve the accuracy of volcano plots leads to the development of the hybrid-descriptor, which encompasses both C- and O- bonding types of CO2RR intermediates within the scaling relations.
@@
 Given that HER is a key competing reaction with CO2RR [44], we also incorporated a selectivity volcano plot, presented in Supplementary Figure 12, to offer a comprehensive analysis of catalyst candidates.
-In adherence to Peterson and Nørskov’s original framework [26], our choice of x and y axes descriptors aligned with Gads *CO and Gads *OH.
+In adherence to Peterson and Nørskov's original framework [26], our choice of x and y axes descriptors aligned with Gads *CO and Gads *OH.
 Further elaboration on how the limiting potentials were evaluated across the volcano plot can be found in the Methods section.

### 2024-01-04 paper/main_sections/4.3_validation.tex
clean up some signs

@@
 The occlusion technique, widely utilized in Computer Vision [49-51], involves systematically masking sections of the input matrix to assess their impact on the final prediction score.
-In our work, we introduce an orbitalwise occlusion method to discern individual orbital contribution to adsorption energy within the CNN model, drawing inspiration from Fung’s pioneer integration of this technique into eDOS analysis [41].
+In our work, we introduce an orbitalwise occlusion method to discern individual orbital contribution to adsorption energy within the CNN model, drawing inspiration from Fung's pioneer integration of this technique into eDOS analysis [41].
 In this work, occlusion experiments involve orbitalwise masking specific eDOS, which are then fed into the CNN model to observe resulting disturbance in adsorption energy.

### 2024-01-04 paper/main_sections/5_method.tex
clean up some signs

@@
 DFT calculations.
+# TODO: fix multiply sign (×)
 Spin-polarized density functional theory calculations were performed using the Vienna Ab initio Simulation Package (VASP) version 5.4.4 [53-55] to optimize geometries and determine the electronic structure.

### 2024-01-04 paper/main_sections/5_methods.tex
rename method to methods

--- 2024-01-04 paper/main_sections/5_method.tex
@@
 # TODO: check format
-█(CO_2+ ^*+H^++e^- □(→┴(          ) )  ^* COOH#(1))
-█( ^* COOH+H^++e^- □(→┴(          ) )  ^* CO+H_2 O#(2))
-█( ^* CO+H^++e^- □(→┴(          ) )  ^* CHO#(3)######)
-█( ^* CHO+H^++e^- □(→┴(          ) )  ^* CH_2 O#(4)##)
-█( ^* CH_2 O+H^++e^- □(→┴(          ) )  ^* OCH_3#(5)#)
-█( ^* OCH_3+H^++e^- □(→┴(          ) )  ^* O+CH_4#(6)#)
-█( ^* O+H^++e^- □(→┴(          ) )  ^* OH#(7)#)
-█( ^* OH+H^++e^- □(→┴(          ) )  ^*+H_2 O#(8)#)
+% (CO_2+ ^*+H^++e^- □(→┴(          ) )  ^* COOH#(1))
+% ( ^* COOH+H^++e^- □(→┴(          ) )  ^* CO+H_2 O#(2))
+% ( ^* CO+H^++e^- □(→┴(          ) )  ^* CHO#(3)######)
+% ( ^* CHO+H^++e^- □(→┴(          ) )  ^* CH_2 O#(4)##)
+% ( ^* CH_2 O+H^++e^- □(→┴(          ) )  ^* OCH_3#(5)#)
+% ( ^* OCH_3+H^++e^- □(→┴(          ) )  ^* O+CH_4#(6)#)
+% ( ^* O+H^++e^- □(→┴(          ) )  ^* OH#(7)#)
+% ( ^* OH+H^++e^- □(→┴(          ) )  ^*+H_2 O#(8)#)
 
@@
 # TODO: check format
-█(G=E+ E_ZPE-TS#(9))
+% (G=E+ E_ZPE-TS#(9))
 where G represents the free energy, E denotes electronic energy, EZPE is the zero-point energy, T represents temperature in Kevin, and S stands for entropy.
@@
 # TODO: check format
-█(1/2 H_2(g)   □(↔┴(           )  H^++ e^- )#(10))
+% (1/2 H_2(g)   □(↔┴(           )  H^++ e^- )#(10))
 is in equilibrium, allowing the calculation of the chemical potential of the electron-proton pair as:
-█(μ(H^+)+μ(e^-)=1/2 μ(H_2(g) )-eU#(11))
+% (μ(H^+)+μ(e^-)=1/2 μ(H_2(g) )-eU#(11))
 For the external potential U applied, the change in free energy (ΔG) was determined using the equation:
-█(∆G_n (U)= ∆G_n (U=0)+neU#(12))
+% (∆G_n (U)= ∆G_n (U=0)+neU#(12))
 Here, μ represents chemical potential, U signifies the external potential applied, n represents the number of proton-electron pairs transferred, and e denotes the elementary charge.
@@
 # TODO: check format
-█(G_ads Z=k[θ*G_ads CO+(1-θ)*G_ads OH]+c_Z#(13)##)
+(G_ads Z=k[θ*G_ads CO+(1-θ)*G_ads OH]+c_Z#(13)##)
 Here, θ represents the mixing ratio of the CO descriptor, Z denotes any adsorbate, and k and cZ are adsorbate-specific scaling parameters.
@@
 # TODO: check format
-█(G_ads Z=a_Z G_ads CO+b_Z G_ads OH+c_Z#(14)#)
+% (G_ads Z=a_Z G_ads CO+b_Z G_ads OH+c_Z#(14)#)
 Here, a_Z, b_Z, c_Z are adsorbate-specific parameters.
@@
 # TODO: check format
-█(U_L=-max⁡{〖ΔG〗_i }/e#(15)#)
+% (U_L=-max⁡{〖ΔG〗_i }/e#(15)#)
 Where ∆Gi represents the free energy change of reaction step i.

### 2024-01-04 paper/main_sections/1_head.tex
temp save: format cleanup

@@
-Authors
-Haoyu Yang, Juanli Zhao, Qiankun Wang, Bin Lin, Wei Luo, Ziqi Sun*, Ting Liao*
+% Title and Authors (Affiliations)
 
-Title
-Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO2 Reduction Reactions
+% Title
+\title{Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO$_2$ Reduction Reactions}
+
+% Authors and Affiliations
+\author[1]{Haoyu Yang}
+\author[3]{Juanli Zhao}
+\author[4]{Qiankun Wang}
+\author[5]{Bin Lin}
+\author[6]{Wei Luo}
+\author[1,*]{Ziqi Sun}
+\author[2,**]{Ting Liao}
+
+\affil[1]{School of Chemistry and Physics, Queensland University of Technology, George Street, Brisbane, QLD 4000, Australia}
+\affil[2]{School of Mechanical Medical and Process Engineering, Queensland University of Technology, George Street, Brisbane, QLD 4000, Australia}
+\affil[3]{School of Materials Science and Engineering, Shanghai University, Shanghai, China}
+\affil[4]{School of Computer Science and Engineering, Southeast University, Nanjing, China}
+\affil[5]{State Key Laboratory for Modification of Chemical Fibers and Polymer Materials, College of Materials Science and Engineering, Institute of Functional Materials, Donghua University, Shanghai, 201620 China}
+\affil[*]{Corresponding author: ziqi.sun@qut.edu.au}
+\affil[**]{Corresponding author: t3.liao@qut.edu.au}
+
+% Date (optional)
+\date{2024-01-04}
+
+% Make Title
+\maketitle

### 2024-01-04 paper/main_sections/2_abstract.tex
temp save: format cleanup

@@
-Abstract
+% Abstract
+
+% TODO: prevent words from being broken in the middle
+
+\newpage
+
+\begin{abstract}
 Single-atom catalysts (SACs) have emerged as pivotal frontiers for catalyzing a myriad of chemical reactions, yet the diverse combinations of active elements and support materials, the nature of coordination environments, elude traditional methodologies in searching optimal SAC systems with superior catalytic performance.
-Herein, by integrating multi-branch Convolutional Neural Network (CNN) analysis models to hybrid descriptor based activity volcano plot, two-dimensional (2D) SAC system composed of diverse metallic single atoms anchored on six type of 2D supports, including g-C3N4, nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, BN, and C2N, are screened for efficient CO2 reduction reaction (CO2RR).
+Herein, by integrating multi-branch Convolutional Neural Network (CNN) analysis models to hybrid descriptor based activity volcano plot, two-dimensional (2D) SAC system composed of diverse metallic single atoms anchored on six type of 2D supports, including g-C$_3$N$_4$, nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, BN, and C$_2$N, are screened for efficient CO$_2$ reduction reaction (CO$_2$RR).
 Starting from establishing a correlation map between the adsorption energies of intermediates and diverse electronic and elementary descriptors, sole singular descriptor lost magic to predict catalytic activity, including d-band center.
 Deep learning method utilizing multi-branch CNN model therefore was employed, using 2D electronic density of states (eDOS) as input to predict adsorption energies.
-Hybrid-descriptor enveloping both C- and O-types of CO2RR intermediates was introduced to construct volcano plots and limiting potential periodic table, aiming for intuitive screening of catalyst candidates for efficient CO2 reduction to CH4.
+Hybrid-descriptor enveloping both C- and O-types of CO$_2$RR intermediates was introduced to construct volcano plots and limiting potential periodic table, aiming for intuitive screening of catalyst candidates for efficient CO$_2$ reduction to CH$_4$.
 The eDOS occlusion experiments were performed to unravel individual orbital contribution to adsorption energy.
-To explore the electronic scale principle governing practical engineering catalytic CO2RR activity, orbitalwise eDOS shifting experiments based on CNN model were employed.
+To explore the electronic scale principle governing practical engineering catalytic CO$_2$RR activity, orbitalwise eDOS shifting experiments based on CNN model were employed.
 The study involves examining the adsorption energy and, consequently, catalytic activities while varying supported single atoms.
 This work offers a tangible framework to inform both theoretical screening and experimental synthesis, thereby paving the way for systematically designing efficient SACs.
+\end{abstract}

### 2024-01-04 paper/main_sections/3_introduction.tex
temp save: format cleanup

@@
-Electrochemical CO2RR stands as a promising avenue for long-term seasonal energy storage [1] and mitigating excess CO2 in the atmosphere.
+% Introduction
 
-Despite decades of research, metallic copper remains a leading CO2RR electrocatalyst for hydrocarbon production [2], albeit burdened by substantial overpotential and low faradic efficiency and poor operational stability [3, 4].
+\newpage
+
+\section{Introduction}
+Electrochemical CO$_2$RR stands as a promising avenue for long-term seasonal energy storage [1] and mitigating excess CO$_2$ in the atmosphere.
+
+Despite decades of research, metallic copper remains a leading CO$_2$RR electrocatalyst for hydrocarbon production [2], albeit burdened by substantial overpotential and low faradic efficiency and poor operational stability [3, 4].
 In this regard, supported SACs have displayed remarkable activity and selectivity across various catalytic reactions [5, 6], leveraging their unique electronic properties and coordination environment.
 To date, experimental studies have primarily focused on two-electron reduction products due to the facile release of gaseous CO [7-9].
-Consequently, there is a pressing need to modulate the electronic structure of single-atom sites to enable hydrocarbon production at reduced overpotentials.
+Consequently, there is a pressing need to modulate the electronic structure of single-atom sites to enable hydrocarbon production at reduced overpotential.
 
@@
 Our CNN model accurately estimated the adsorption energies, the activity descriptor, from the eDOS of 2D materials supported single metal catalysts.
-Evaluations on the adsorption energies of nine intermediates along CO2RR and competing hydrogen evolution reaction (HER) as well yielded prediction mean absolute errors (MAEs) at the level of 0.1 eV, which is well aligned with the precision of conventional DFT calculations [23-25].
+Evaluations on the adsorption energies of nine intermediates along CO$_2$RR and competing hydrogen evolution reaction (HER) as well yielded prediction mean absolute errors (MAEs) at the level of 0.1 eV, which is well aligned with the precision of conventional DFT calculations [23-25].
 This result validated the capability of current CNN model to accurately capture intricate spatial information from eDOS.
@@
 Built upon scaling relations [26], we introduced a hybrid-descriptor scheme incorporating both C- and O-centered species.
-The scaling coefficient of determination (R2) was increased by 0.1387 using hybrid descriptor, which demonstrate an improved prediction accuracy compared to the well documented single descriptor based method.
+The scaling coefficient of determination ($R^2$) was increased by 0.1387 using hybrid descriptor, which demonstrate an improved prediction accuracy compared to the well documented single descriptor based method.
 
-In summary, we introduced a catalyst performance analysis pipeline by integrating CNN and volcano plot analysis, using CO2RR as an example proof of concept.
+In summary, we introduced a catalyst performance analysis pipeline by integrating CNN and volcano plot analysis, using CO$_2$RR as an example proof of concept.
 The CNN, which correlates eDOS with activity descriptors, establishes a robust electronic structure-activity relationship.

### 2024-01-04 paper/main_sections/4.1_cnn_for_eads.tex
temp save: format cleanup

@@
-Adsorption energy prediction from electronic density of states with convolutional neural network.
+% Results and Discussion Part One: Adsorption energy prediction from eDOS with CNN
 
+\section{Adsorption energy prediction from electronic density of states with convolutional neural network}
 Originating from the pioneering work of Hammer and Nørskov [30], the d-band center model has emerged as a successful paradigm for employing descriptor to understand and predict the adsorption behavior on transition metal surfaces.
 To investigate alternative electronic and elementary descriptors that may serve as more suitable substitutes for the d-band center model in the context of SACs, we performed Kendall rank correlation analysis to account for both linearity and non-linearity [31].
-The correlation coefficient map, as presented in Figure 2a, highlighted the d-band center as the most informative descriptor with a Kendall's τ coefficient of -0.33, and followed by the vacuum level and electronegativity.
+The correlation coefficient map, as presented in Figure 2a, highlighted the d-band center as the most informative descriptor with a Kendall's \tau coefficient of -0.33, and followed by the vacuum level and electronegativity.
 However, d-band center alone does not suffice for accurate predictions of intermediate adsorption energy as illustrated in the scatter plot Supplementary Figure 18, and therefore, refinements are imperative.
@@
 By leveraging the CNN model, we predicted adsorption energies from the eDOS of supported single atoms, and validated through parity plots (Figure 2d-m).
-The model predicts adsorption energies across nine species within the CO2RR process and competing HER side reaction, attaining an averaged MAE of 0.06 eV.
+The model predicts adsorption energies across nine species within the CO$_2$RR process and competing HER side reaction, attaining an averaged MAE of 0.06 eV.
 This MAE aligns with the established precision of DFT methods, which typically range between 0.1-0.2 eV concerning experimental measurement [25, 38, 39].

### 2024-01-04 paper/main_sections/4.2_volcano_plots.tex
temp save: format cleanup

@@
-Hybrid descriptors enabled volcano plot for catalyst analysis.
+% Results and Discussion Part Two: Hybrid descriptors enabled volcano plot for catalyst analysis
 
+\section{Hybrid descriptors enabled volcano plot for catalyst analysis}
 Catalyst activity volcano plots, built upon the scaling relations proposed by Peterson and Nørskov's [26], goes beyond assessment of candidatures' energetics only but to provide informative guidance on discovering catalysts candidates with superior performance [42, 43].
-Our endeavor to improve the accuracy of volcano plots leads to the development of the hybrid-descriptor, which encompasses both C- and O- bonding types of CO2RR intermediates within the scaling relations.
-This adaptation arose from the intuition that most CO2RR intermediates are featured with both bonding types rather than any single one in dominance.
-By integrating both bonding featured descriptors into the hybrid approach, we found the coefficient of determination (R2) was increased by 0.1387.
+Our endeavor to improve the accuracy of volcano plots leads to the development of the hybrid-descriptor, which encompasses both C- and O- bonding types of CO$_2$RR intermediates within the scaling relations.
+This adaptation arose from the intuition that most CO$_2$RR intermediates are featured with both bonding types rather than any single one in dominance.
+By integrating both bonding featured descriptors into the hybrid approach, we found the coefficient of determination ($R^2$) was increased by 0.1387.
 Detailed information about the scaling parameters and performance enhancements are provided in Supplementary Tables 13 and Supplementary Figure 10.
-This improvement to some extent underscored our premise that CO2RR intermediates typically exhibit chemical similarities encompassing both O- and C-type descriptors.
+This improvement to some extent underscored our premise that CO$_2$RR intermediates typically exhibit chemical similarities encompassing both O- and C-type descriptors.
 After taking this dual nature into consideration, our hybrid-descriptor method can evaluate the intermediates adsorption energies more accurately.
@@
 
-Expanding upon the revised scaling relations, we introduce an activity volcano plot and a rate-determining step (RDS) volcano plot for the CO2RR process, shown in Figure 3a and Supplementary Figure 11.
-Given that HER is a key competing reaction with CO2RR [44], we also incorporated a selectivity volcano plot, presented in Supplementary Figure 12, to offer a comprehensive analysis of catalyst candidates.
+Expanding upon the revised scaling relations, we introduce an activity volcano plot and a rate-determining step (RDS) volcano plot for the CO$_2$RR process, shown in Figure 3a and Supplementary Figure 11.
+Given that HER is a key competing reaction with CO$_2$RR [44], we also incorporated a selectivity volcano plot, presented in Supplementary Figure 12, to offer a comprehensive analysis of catalyst candidates.
 In adherence to Peterson and Nørskov's original framework [26], our choice of x and y axes descriptors aligned with Gads *CO and Gads *OH.
@@
 Moreover, the activity volcano plot predicted an optimal catalyst featuring a theoretical limiting potential of -1.0516 V, at Gads *CO of 0.0589 eV and Gads *OH of -4.0075 eV, positioned at the right-center of the volcano plot.
-Results from RDS volcano plot indicate that protonation of *CO likely serves as the RDS for CO2RR.
+Results from RDS volcano plot indicate that protonation of *CO likely serves as the RDS for CO$_2$RR.
 Consequently, it should be the focal point for future catalyst designs.

### 2024-01-04 paper/main_sections/4.3_validation.tex
temp save: format cleanup

@@
-Validation of CNN predictions.
+% Results and Discussion Part Three: Validation of CNN predictions
 
+\section{Validation of CNN predictions}
 Historically, interpretability has posed challenges for deep learning methods, often rendering their inner workings akin to black boxes [46-48].
@@
 
-To validate our method, we conducted occlusion experiments on Cr@g-C3N4, Co@g-C3N4 and Cu@g-C3N4.
+To validate our method, we conducted occlusion experiments on Cr@g-C$_3$N$_4$, Co@g-C$_3$N$_4$ and Cu@g-C$_3$N$_4$.
 Each of these supported metals possesses 3d subshells with different electronic configurations: half-filled, partially filled and fully filled, allowing us to test the universality of our approach.
-The results of the occlusion experiment on the supported Cr single atom in Cr@g-C3N4 are given in Figure 4a.
+The results of the occlusion experiment on the supported Cr single atom in Cr@g-C$_3$N$_4$ are given in Figure 4a.
 The d_(x^2-y^2 ) orbital emerges as dominant in CO interaction.
 Shielding electrons centered around -2 eV significantly alter the adsorption energy, indicating the potency of this orbital.
-The real-space wavefunction visualization in Figure 4d corroborates these findings, highlighting the interaction between the d_(x^2-y^2 ) orbital of single metal atom and the adsorbate.
-This suggests the d_(x^2-y^2 ) orbital of supported Co predominantly influence the interaction with CO, and thus shielding electrons from this orbital markedly disturb the adsorption energy.
-Additionally, occlusion experiments were performed on the Co d_xy orbital of Co@g-C3N4 (Figure 4b) and the Cu d_xy orbital of Cu@g-C3N4 (Figure 4c).
+The real-space wavefunction visualization in Figure 4d corroborates these findings, highlighting the interaction between the d_(x^2-y^2) orbital of single metal atom and the adsorbate.
+This suggests the d_(x^2-y^2) orbital of supported Co predominantly influence the interaction with CO, and thus shielding electrons from this orbital markedly disturb the adsorption energy.
+Additionally, occlusion experiments were performed on the Co d_xy orbital of Co@g-C$_3$N$_4$ (Figure 4b) and the Cu d_xy orbital of Cu@g-C$_3$N$_4$ (Figure 4c).
 In both cases, the d_xy orbital was identified as the dominant contributor.
@@
 In this research, interactions between the supported metal atom and atoms within a 5 Å radius were calculated to understand its bonding environment, as detailed in the Methods section.
-The results of the occlusion experiment on the Co d_xy orbital of Co@g-C3N4, identified as the dominant orbital via occlusion experiments, were compared with the COHP analysis, as shown in Figure 4g and Figure 4i.
+The results of the occlusion experiment on the Co d_xy orbital of Co@g-C$_3$N$_4$, identified as the dominant orbital via occlusion experiments, were compared with the COHP analysis, as shown in Figure 4g and Figure 4i.
 The occlusion experiment pinpointed strong metal-adsorbate interactions at energy levels of -1 eV and -6.3 eV, which were confirmed by the COHP analysis.

### 2024-01-04 paper/main_sections/6_tail.tex
clean up some signs
temp save: format cleanup

@@
 Data Availability
-Essential source data required to replicate the study's results–including VASP input files, structure files of SACs, eDOS arrays and the pretrained CNN model–are available on GitHub at https://github.com/DanielYang59/cnn4dos or can be provided by the corresponding authors upon request.
+Essential source data required to replicate the study's results-including VASP input files,
+structure files of SACs, eDOS arrays and the pretrained CNN model-are available on GitHub
+at https://github.com/DanielYang59/cnn4dos or can be provided by the corresponding authors upon request.
 Due to their substantial size in terabytes, the complete source data is not currently hosted on publicly available repositories but can also be obtained from the corresponding authors upon request.
@@
 Code Availability
-Associated computer code for this study can be accessed on GitHub at https://github.com/DanielYang59/cnn4dos or obtained from the corresponding authors upon request.
+Associated computer code for this study can be accessed on GitHub at https://github.com/DanielYang59/cnn4dos,
+ or obtained from the corresponding authors upon request.
 
@@
 It was also supported by resources provided by the Pawsey Supercomputing Research Centre with funding from the Australian Government and the Government of Western Australia.
-Insights into deep learning methodologies were contributed by Mr.
-Yanwei Guan from Chongqing University and Mr.
-Zhipeng He from Assoc.
-Prof.
-Chun Ouyang's team at QUT.
+Insights into deep learning methodologies were contributed by Mr. Yanwei Guan from Chongqing University and Mr. Zhipeng He from Assoc. Prof. Chun Ouyang's team at QUT.
 The machine learning and data analysis implementation benefited from resources provided by the GitHub, TensorFlow and Stack Overflow communities.
-Dr.
-Ryky Nelson from RWTH Aachen University offered valuable guidance on Crystal Orbital Hamilton Population analysis.
+Dr. Ryky Nelson from RWTH Aachen University offered valuable guidance on Crystal Orbital Hamilton Population analysis.
 
 Author Contributions
-H.Y.
-performed DFT calculations, implemented Python code the machine learning methodologies and data analysis, and drafted and refined the manuscript.
-J.Z.
-engaged in valuable discussions on DFT calculations.
-Q.W.
-provided advice on the computer code revisions.
-W.L.
-facilitated resource acquisition and offered research supervision.
-B.L.
-provided guidance on DFT calculations and offered research supervision.
-Z.S.
-initiated the research concept, contributed to manuscript revisions, and supervised the overall research.
-T.L.
-guided DFT calculations and data analysis, offering continuous supervision throughout the research and manuscript drafting.
+H.Y. performed DFT calculations, implemented Python code the machine learning methodologies and data analysis, and drafted and refined the manuscript.
+J.Z. engaged in valuable discussions on DFT calculations.
+Q.W. provided advice on the computer code revisions.
+W.L. facilitated resource acquisition and offered research supervision.
+B.L. provided guidance on DFT calculations and offered research supervision.
+Z.S. initiated the research concept, contributed to manuscript revisions, and supervised the overall research.
+T.L. guided DFT calculations and data analysis, offering continuous supervision throughout the research and manuscript drafting.
 

### 2024-01-04 paper/main_sections/4.1_cnn_for_eads.tex
fix some broken symbols

@@
 To investigate alternative electronic and elementary descriptors that may serve as more suitable substitutes for the d-band center model in the context of SACs, we performed Kendall rank correlation analysis to account for both linearity and non-linearity [31].
-The correlation coefficient map, as presented in Figure 2a, highlighted the d-band center as the most informative descriptor with a Kendall's \tau coefficient of -0.33, and followed by the vacuum level and electronegativity.
+The correlation coefficient map, as presented in Figure 2a, highlighted the d-band center as the most informative descriptor with a Kendall's $\tau$ coefficient of -0.33, and followed by the vacuum level and electronegativity.
 However, d-band center alone does not suffice for accurate predictions of intermediate adsorption energy as illustrated in the scatter plot Supplementary Figure 18, and therefore, refinements are imperative.

### 2024-01-04 paper/main_sections/4.2_volcano_plots.tex
fix some broken symbols

@@
 Given that HER is a key competing reaction with CO$_2$RR [44], we also incorporated a selectivity volcano plot, presented in Supplementary Figure 12, to offer a comprehensive analysis of catalyst candidates.
-In adherence to Peterson and Nørskov's original framework [26], our choice of x and y axes descriptors aligned with Gads *CO and Gads *OH.
+In adherence to Peterson and Nørskov's original framework [26], our choice of x and y axes descriptors aligned with $\textit{G}_{\text{ads} \ast \text{CO}}$ and $\textit{G}_{\text{ads} \ast \text{OH}}$.
 Further elaboration on how the limiting potentials were evaluated across the volcano plot can be found in the Methods section.
@@
 The RDS volcano plot (Supplementary Figure 11) indicated protonation of *CO as the rate-determining step for nearly optimal candidates.
-Moreover, the activity volcano plot predicted an optimal catalyst featuring a theoretical limiting potential of -1.0516 V, at Gads *CO of 0.0589 eV and Gads *OH of -4.0075 eV, positioned at the right-center of the volcano plot.
+Moreover, the activity volcano plot predicted an optimal catalyst featuring a theoretical limiting potential of -1.0516 V, at $\textit{G}_{\text{ads} \ast \text{CO}}$ of 0.0589 eV and $\textit{G}_{\text{ads} \ast \text{OH}}$ of -4.0075 eV, positioned at the right-center of the volcano plot.
 Results from RDS volcano plot indicate that protonation of *CO likely serves as the RDS for CO$_2$RR.

### 2024-01-04 paper/main_sections/4.3_validation.tex
fix some broken symbols

@@
 The results of the occlusion experiment on the supported Cr single atom in Cr@g-C$_3$N$_4$ are given in Figure 4a.
-The d_(x^2-y^2 ) orbital emerges as dominant in CO interaction.
+The $d_{x^2-y^2}$ orbital emerges as dominant in CO interaction.
 Shielding electrons centered around -2 eV significantly alter the adsorption energy, indicating the potency of this orbital.
-The real-space wavefunction visualization in Figure 4d corroborates these findings, highlighting the interaction between the d_(x^2-y^2) orbital of single metal atom and the adsorbate.
-This suggests the d_(x^2-y^2) orbital of supported Co predominantly influence the interaction with CO, and thus shielding electrons from this orbital markedly disturb the adsorption energy.
-Additionally, occlusion experiments were performed on the Co d_xy orbital of Co@g-C$_3$N$_4$ (Figure 4b) and the Cu d_xy orbital of Cu@g-C$_3$N$_4$ (Figure 4c).
-In both cases, the d_xy orbital was identified as the dominant contributor.
+The real-space wavefunction visualization in Figure 4d corroborates these findings, highlighting the interaction between the $d_{x^2-y^2}$ orbital of single metal atom and the adsorbate.
+This suggests the $d_{x^2-y^2}$ orbital of supported Co predominantly influence the interaction with CO, and thus shielding electrons from this orbital markedly disturb the adsorption energy.
+Additionally, occlusion experiments were performed on the Co $d_xy$ orbital of Co@g-C$_3$N$_4$ (Figure 4b) and the $Cu d_xy$ orbital of Cu@g-C$_3$N$_4$ (Figure 4c).
+In both cases, the $d_xy$ orbital was identified as the dominant contributor.
 While identifying the dominant orbital is crucial, these findings also suggest that interactions with adsorbates occurring out-of-plane are influenced by in-plane orbitals as well.
@@
 To validate the chemical relevance of predictions made by CNN model, we conducted COHP analysis, a theoretical bond-detecting tool used to identify bonding and anti-bonding contributions to band-structure energy [52].
-In this research, interactions between the supported metal atom and atoms within a 5 Å radius were calculated to understand its bonding environment, as detailed in the Methods section.
-The results of the occlusion experiment on the Co d_xy orbital of Co@g-C$_3$N$_4$, identified as the dominant orbital via occlusion experiments, were compared with the COHP analysis, as shown in Figure 4g and Figure 4i.
+In this research, interactions between the supported metal atom and atoms within a 5 \AA(TODO: space missing) radius were calculated to understand its bonding environment, as detailed in the Methods section.
+The results of the occlusion experiment on the Co $d_xy$ orbital of Co@g-C$_3$N$_4$, identified as the dominant orbital via occlusion experiments, were compared with the COHP analysis, as shown in Figure 4g and Figure 4i.
 The occlusion experiment pinpointed strong metal-adsorbate interactions at energy levels of -1 eV and -6.3 eV, which were confirmed by the COHP analysis.
-We then investigated the non-dominant Co d_xz orbital, and the COHP analysis highlighted interactions at -1 eV and -6.5 eV, aligning with the findings from the occlusion experiments.
+We then investigated the non-dominant Co $d_xz$ orbital, and the COHP analysis highlighted interactions at -1 eV and -6.5 eV, aligning with the findings from the occlusion experiments.
 

### 2024-01-04 paper/main_sections/4.4_shifting_exp.tex
fix some broken symbols

@@
-Shifting experiments for prediction of better catalysts.
+% Results and Discussion Part Four: Shifting experiments for prediction of better catalysts
 
+\section{Validation of CNN predictions}
 While CNN models excel in prediction of the activity of catalyst candidates directly from eDOS, volcano plots point out directions leading to better catalysts.
@@
 We also investigated potential disturbance from p orbital shifting, as shown in Supplementary Figure 31 and found no significant response.
-This implies that Ge@g-C3N4 holds promise as a CO2RR electrocatalyst, given its high activity and resilience to electronic structure disturbances.
+This implies that Ge@g-C$_3$N$_4$ holds promise as a CO$_2$RR electrocatalyst, given its high activity and resilience to electronic structure disturbances.
 Nevertheless, fine-tuning its performance through eDOS modulation might pose a challenge.

### 2024-01-04 paper/main_sections/5_methods.tex
fix some broken symbols

@@
-Methods
-DFT calculations.
+% Methods
+
+\section{Methods}
+
+\subsection{DFT calculations}
 # TODO: fix multiply sign (×)
@@
 Kohn-Shan equations were approached employing a plane-wave basis set with a cut-off energy of 440 eV.
-Geometry optimizations were performed using Γ-Centered K-point meshes of (2 × 2 × 1) until the force on each atom fell below 0.02 eV Å-1.
+Geometry optimizations were performed using Γ-Centered K-point meshes of (2 × 2 × 1) until the force on each atom fell below 0.02 eV Å-1 (TODO:).
 Electronic structure calculations utilized denser K-point meshes of (3 × 3 × 1) and employed self-consistent field (SCF) methods.
 
-Catalyst models.
-Supported SACs were modelled by anchoring individual metal atoms onto various 2D substrates, including graphitic carbon nitride (g-C3N4), nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, boron nitride, and monolayer C2N.
+\subsection{Catalyst models}
+Supported SACs were modelled by anchoring individual metal atoms onto various 2D substrates, including graphitic carbon nitride (g-C$_3$N$_4$), nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, boron nitride, and monolayer C$_2$N.
 The specific single metal atoms studied are outlined in Supplementary Figure 1.
-To prevent interactions between adjacent images along the z-axis, vacuum layers of 15 Å were introduced.
+To prevent interactions between adjacent images along the z-axis, vacuum layers of 15 Å (TODO:) were introduced.
 
-CO2RR pathway.
-The C1 production CO2RR pathway, as initially described by Peterson et al.
-[45] and later confirmed by Jiao et al.
-[57] for g-C3N4 based SACs, involves the following elementary steps.
+\subsection{CO$_2$RR pathway}
+The C1 production CO$_2$RR pathway, as initially described by Peterson et al. [45] and later confirmed by Jiao et al. [57] for g-C$_3$N$_4$ based SACs, involves the following elementary steps.
 Asterisks (*) indicate species adsorbed on the SAC surfaces:
@@
 
-Free energy calculations.
+\subsection{Free energy calculations}
 Free energies were computed from electronic energies by considering thermal corrections, incorporating normal mode analysis of all degrees of freedom of adsorbates.
-The free energy G was calculated using the formula:
+The free energy $\textit{G}$ was calculated using the formula:
 # TODO: check format
 % (G=E+ E_ZPE-TS#(9))
-where G represents the free energy, E denotes electronic energy, EZPE is the zero-point energy, T represents temperature in Kevin, and S stands for entropy.
+where $\textit{G}$ represents the free energy, $\textit{E}$ denotes electronic energy, $\textit{E}_{\text{ZPE}}$ is the zero-point energy, $\textit{T}$ represents temperature in Kevin, and $\textit{S}$ stands for entropy.
 Detailed information regarding these corrections can be found in Supplementary Section 1.3.
 
-The computational hydrogen electrode (CHE) model [45, 58] was employed to introduce potential dependence. At the reference electrode surface, the reaction
+The computational hydrogen electrode (CHE) model [45, 58] was employed to introduce potential dependence.
+At the reference electrode surface, the reaction
 # TODO: check format
@@
 % (μ(H^+)+μ(e^-)=1/2 μ(H_2(g) )-eU#(11))
-For the external potential U applied, the change in free energy (ΔG) was determined using the equation:
+For the external potential $\textit{U}$ applied, the change in free energy ($\Delta \textit{G}$) was determined using the equation:
 % (∆G_n (U)= ∆G_n (U=0)+neU#(12))
-Here, μ represents chemical potential, U signifies the external potential applied, n represents the number of proton-electron pairs transferred, and e denotes the elementary charge.
+Here, $\mu$ represents chemical potential, $\textit{U}$ signifies the external potential applied, $\textit{n}$ represents the number of proton-electron pairs transferred, and $\textit{e}$ denotes the elementary charge.
 
-Hybrid descriptor for volcano plots.
+\subsection{Hybrid descriptor for volcano plots}
 Hybrid descriptors incorporate both descriptors within a single equation, enhancing the accuracy of scaling relationship with minimal computational overhead, as demonstrated in Supplementary Figure 10 and Supplementary Table 13.
-Comprehensive analyses are presented Supplementary Section 1.5.
-This leads to the formulation of the scaling relation:
+Comprehensive analyses are presented Supplementary Section 1.5. This leads to the formulation of the scaling relation:
 # TODO: check format
-(G_ads Z=k[θ*G_ads CO+(1-θ)*G_ads OH]+c_Z#(13)##)
-Here, θ represents the mixing ratio of the CO descriptor, Z denotes any adsorbate, and k and cZ are adsorbate-specific scaling parameters.
-The optimal mixing ratio θ is determined through iterative exploration across the range, utilizing a step length of 0.01.
+% (G_ads Z=k[θ*G_ads CO+(1-θ)*G_ads OH]+c_Z#(13)##)
+Here, $\theta$ represents the mixing ratio of the CO descriptor, $\textit{Z}$ denotes any adsorbate, and $\textit{k}$ and $\textit{c}_{Z}$ are adsorbate-specific scaling parameters.
+The optimal mixing ratio $\theta$ is determined through iterative exploration across the range, utilizing a step length of 0.01.
 
@@
 
-Consequently, the limiting potential UL is entirely determined by two descriptors through the following equation:
+Consequently, the limiting potential $\textit{U}_{L}$ is entirely determined by two descriptors through the following equation:
 # TODO: check format
@@
 
-This approach simplifies the theoretical performance assessment of any catalyst within the scope of our research to only two descriptors: G_ads CO and G_ads OH.
+This approach simplifies the theoretical performance assessment of any catalyst within the scope of our research to only two descriptors: $G_{\textit{ads} \, \textit{CO}}$ and $G_{\textit{ads} \, \textit{OH}}$.
 This method offers a visual representation of the high-dimensional optimization challenge.
@@
 
-CNN architecture and hyperparameter tuning.
+\subsection{CNN architecture and hyperparameter tuning}
 We designed our CNN architecture drawing inspiration from its successful implementation in tasks involving electrocardiogram signal classification [59], as illustrated in Figure 2b and 2c.
@@
 
-Data augmentation and CNN model training.
+\subsection{Data augmentation and CNN model training}
 To enhance the generalizability and robustness of the our CNN model, and achieve comprehensive coverage of the chemical space [61], we applied data augmentation techniques to the initial dataset using the following procedures:
-	In addition to the designated "initial state" of the adsorption process, where the adsorbate positioned 6.5 Å above the supported single metal atom, five intermediate images were interpolated.
-These images were distributed between the initial and final states at a spacing of 0.5 Å, starting from the initial state side.
-	A diverse set of smearing techniques was employed to determine of partial occupancies fnk, including the tetrahedron method [62] and the Gaussian method.
+	- In addition to the designated "initial state" of the adsorption process, where the adsorbate positioned 6.5 Å (TODO:) above the supported single metal atom, five intermediate images were interpolated.
+These images were distributed between the initial and final states at a spacing of 0.5 Å (TODO:), starting from the initial state side.
+	- A diverse set of smearing techniques was employed to determine of partial occupancies $f_{nk}$, including the tetrahedron method [62] and the Gaussian method.
 For the Gaussian method, the smearing width was varied within the range of 0.01 eV to 0.1 eV.
 This careful selection of methods was made to guarantee reliable and consistent predictions of adsorption energies from the model, regardless of the smearing technique used.
+
 The augmented dataset comprises 12,312 samples, with adsorption energies having a standard deviation of 1.8117 and a variance of 3.2821.
-Twenty pecent of these samples were allocated to the validation set.
-Throughout the training process, a batch size of 64 was employed to ensure a balanced learning dynamic.
+Twenty pecent of these samples were allocated to the validation set. Throughout the training process, a batch size of 64 was employed to ensure a balanced learning dynamic.
 
-Occlusion experiments.
-Supplementary Figure 21 visually illustrates the occlusion experiment methodology.
-To maintain consistent shapes, zero-padding was applied to the input eDOS arrays.
+\subsection{Occlusion experiments}
+Supplementary Figure 21 visually illustrates the occlusion experiment methodology. To maintain consistent shapes, zero-padding was applied to the input eDOS arrays.
 Focusing on understanding the influence of metals on adsorption behavior, a masker with dimensions [width, 1, 1] was employed along the metal channel to eliminate cross-orbital interactions.
@@
 
-Shifting experiments.
+\subsection{Shifting experiments}
 Supplementary Figure 30 illustrates the implemented shifting experiment protocol.
@@
 
-Chemical bond analysis and real-space wavefunction visualization.
+\subsection{Chemical bond analysis and real-space wavefunction visualization}
 COHP analysis was performed using the Local-Orbital Basis Suite Towards Electronic-Structure Reconstruction (LOBSTER) package  [52, 63-66] version 4.1.0, with the GGA-PBE wavefunctions fitted by S.
@@
 A Gaussian smearing for energy integration was employed with a broadening width of 0.05 eV.
-The quantification of bonding strength between the single metal atom and the substrate was achieved through the summation of interactions with neighboring atoms within a range of 0.5 Å to 5.0 Å from the single metal atom.
+The quantification of bonding strength between the single metal atom and the substrate was achieved through the summation of interactions with neighboring atoms within a range of 0.5 Å (TODO:) to 5.0 Å (TODO:) from the single metal atom.
 Orbitals of interest were confirmed through band-structure analysis, and real-space wavefunctions were subsequently visualized using VASPKIT [68] and VESTA [69].
 
-Machine learning and data analysis environment.
+\subsection{Machine learning and data analysis environment}
 The CNN model was implemented using TensorFlow [70], and hyperparameter optimization was conducted using the Hyperband [60] algorithm via KerasTuner [71].

### 2024-01-04 paper/main_sections/6_tail.tex
fix some broken symbols

--- 2024-01-04 paper/main_sections/6_tail.tex
@@
-Data Availability
-Essential source data required to replicate the study's results–including VASP input files, structure files of SACs, eDOS arrays and the pretrained CNN model–are available on GitHub at https://github.com/DanielYang59/cnn4dos or can be provided by the corresponding authors upon request.
+% Data/Code Availability, Acknowledgements, Author Contributions and Competing Interests
+
+\section{Tail}
+
+\subsection{Data Availability}
+Essential source data required to replicate the study's results-including VASP input files,
+structure files of SACs, eDOS arrays and the pretrained CNN model-are available on GitHub
+at https://github.com/DanielYang59/cnn4dos or can be provided by the corresponding authors upon request.
 Due to their substantial size in terabytes, the complete source data is not currently hosted on publicly available repositories but can also be obtained from the corresponding authors upon request.
 
-Code Availability
-Associated computer code for this study can be accessed on GitHub at https://github.com/DanielYang59/cnn4dos or obtained from the corresponding authors upon request.
+\subsection{Code Availability}
+Associated computer code for this study can be accessed on GitHub at https://github.com/DanielYang59/cnn4dos, or obtained from the corresponding authors upon request.
 
-Acknowledgements
+ \subsection{Acknowledgements}
 The QUT eResearch Office provided computational resources and services used in this work.
@@
 It was also supported by resources provided by the Pawsey Supercomputing Research Centre with funding from the Australian Government and the Government of Western Australia.
-Insights into deep learning methodologies were contributed by Mr.
-Yanwei Guan from Chongqing University and Mr.
-Zhipeng He from Assoc.
-Prof.
-Chun Ouyang's team at QUT.
+Insights into deep learning methodologies were contributed by Mr. Yanwei Guan from Chongqing University and Mr. Zhipeng He from Assoc. Prof. Chun Ouyang's team at QUT.
 The machine learning and data analysis implementation benefited from resources provided by the GitHub, TensorFlow and Stack Overflow communities.
-Dr.
-Ryky Nelson from RWTH Aachen University offered valuable guidance on Crystal Orbital Hamilton Population analysis.
+Dr. Ryky Nelson from RWTH Aachen University offered valuable guidance on Crystal Orbital Hamilton Population analysis.
 
-Author Contributions
-H.Y.
-performed DFT calculations, implemented Python code the machine learning methodologies and data analysis, and drafted and refined the manuscript.
-J.Z.
-engaged in valuable discussions on DFT calculations.
-Q.W.
-provided advice on the computer code revisions.
-W.L.
-facilitated resource acquisition and offered research supervision.
-B.L.
-provided guidance on DFT calculations and offered research supervision.
-Z.S.
-initiated the research concept, contributed to manuscript revisions, and supervised the overall research.
-T.L.
-guided DFT calculations and data analysis, offering continuous supervision throughout the research and manuscript drafting.
+\subsection{Author Contributions}
+H.Y. performed DFT calculations, implemented Python code the machine learning methodologies and data analysis, and drafted and refined the manuscript.
+J.Z. engaged in valuable discussions on DFT calculations.
+Q.W. provided advice on the computer code revisions.
+W.L. facilitated resource acquisition and offered research supervision.
+B.L. provided guidance on DFT calculations and offered research supervision.
+Z.S. initiated the research concept, contributed to manuscript revisions, and supervised the overall research.
+T.L. guided DFT calculations and data analysis, offering continuous supervision throughout the research and manuscript drafting.
 
-Competing interests
+\subsection{Competing Interests}
 The authors declare no competing interests in relation to this research.

### 2024-01-04 paper/main_sections/5_methods.tex
fix some symbols

@@
 \subsection{DFT calculations}
-# TODO: fix multiply sign (×)
+% TODO: fix multiply sign (×)
 Spin-polarized density functional theory calculations were performed using the Vienna Ab initio Simulation Package (VASP) version 5.4.4 [53-55] to optimize geometries and determine the electronic structure.
@@
 Kohn-Shan equations were approached employing a plane-wave basis set with a cut-off energy of 440 eV.
-Geometry optimizations were performed using Γ-Centered K-point meshes of (2 × 2 × 1) until the force on each atom fell below 0.02 eV Å-1 (TODO:).
+Geometry optimizations were performed using $\Gamma$-Centered K-point meshes of (2 × 2 × 1) until the force on each atom fell below 0.02 eV Å-1 (TODO:).
 Electronic structure calculations utilized denser K-point meshes of (3 × 3 × 1) and employed self-consistent field (SCF) methods.
@@
 Asterisks (*) indicate species adsorbed on the SAC surfaces:
-# TODO: check format
+% TODO: check format
 % (CO_2+ ^*+H^++e^- □(→┴(          ) )  ^* COOH#(1))
@@
 The free energy $\textit{G}$ was calculated using the formula:
-# TODO: check format
+% TODO: check format
 % (G=E+ E_ZPE-TS#(9))
@@
 At the reference electrode surface, the reaction
-# TODO: check format
+% TODO: check format
 % (1/2 H_2(g)   □(↔┴(           )  H^++ e^- )#(10))
@@
 Comprehensive analyses are presented Supplementary Section 1.5. This leads to the formulation of the scaling relation:
-# TODO: check format
+% TODO: check format
 % (G_ads Z=k[θ*G_ads CO+(1-θ)*G_ads OH]+c_Z#(13)##)
@@
 Equation 14 could be simplified to a more general form:
-# TODO: check format
+% TODO: check format
 % (G_ads Z=a_Z G_ads CO+b_Z G_ads OH+c_Z#(14)#)
-Here, a_Z, b_Z, c_Z are adsorbate-specific parameters.
+Here, $a_Z$, $b_Z$, $c_Z$ are adsorbate-specific parameters.
 
 Consequently, the limiting potential $\textit{U}_{L}$ is entirely determined by two descriptors through the following equation:
-# TODO: check format
+% TODO: check format
 % (U_L=-max⁡{〖ΔG〗_i }/e#(15)#)
-Where ∆Gi represents the free energy change of reaction step i.
+Where $\Delta G_{i}$ represents the free energy change of reaction step i.
 

### 2024-01-05 paper/main_sections/4.3_validation.tex
fix symbol format

@@
 To validate the chemical relevance of predictions made by CNN model, we conducted COHP analysis, a theoretical bond-detecting tool used to identify bonding and anti-bonding contributions to band-structure energy [52].
-In this research, interactions between the supported metal atom and atoms within a 5 \AA(TODO: space missing) radius were calculated to understand its bonding environment, as detailed in the Methods section.
+In this research, interactions between the supported metal atom and atoms within a 5 \text{\AA} radius were calculated to understand its bonding environment, as detailed in the Methods section.
 The results of the occlusion experiment on the Co $d_xy$ orbital of Co@g-C$_3$N$_4$, identified as the dominant orbital via occlusion experiments, were compared with the COHP analysis, as shown in Figure 4g and Figure 4i.

### 2024-01-05 paper/main_sections/5_methods.tex
fix symbol format

@@
 \subsection{DFT calculations}
-% TODO: fix multiply sign (×)
 Spin-polarized density functional theory calculations were performed using the Vienna Ab initio Simulation Package (VASP) version 5.4.4 [53-55] to optimize geometries and determine the electronic structure.
@@
 Kohn-Shan equations were approached employing a plane-wave basis set with a cut-off energy of 440 eV.
-Geometry optimizations were performed using $\Gamma$-Centered K-point meshes of (2 × 2 × 1) until the force on each atom fell below 0.02 eV Å-1 (TODO:).
-Electronic structure calculations utilized denser K-point meshes of (3 × 3 × 1) and employed self-consistent field (SCF) methods.
+Geometry optimizations were performed using $\Gamma$-Centered K-point meshes of ($2\times2\times1$) until the force on each atom fell below 0.02 eV/\(\mathrm{\AA}^{-1}\).
+Electronic structure calculations utilized denser K-point meshes of ($3\times3\times1$) and employed self-consistent field (SCF) methods.
 
@@
 The specific single metal atoms studied are outlined in Supplementary Figure 1.
-To prevent interactions between adjacent images along the z-axis, vacuum layers of 15 Å (TODO:) were introduced.
+To prevent interactions between adjacent images along the z-axis, vacuum layers of 15 \text{\AA} were introduced.
 
@@
 To enhance the generalizability and robustness of the our CNN model, and achieve comprehensive coverage of the chemical space [61], we applied data augmentation techniques to the initial dataset using the following procedures:
-	- In addition to the designated "initial state" of the adsorption process, where the adsorbate positioned 6.5 Å (TODO:) above the supported single metal atom, five intermediate images were interpolated.
-These images were distributed between the initial and final states at a spacing of 0.5 Å (TODO:), starting from the initial state side.
+	- In addition to the designated "initial state" of the adsorption process, where the adsorbate positioned 6.5 \text{\AA} above the supported single metal atom, five intermediate images were interpolated.
+These images were distributed between the initial and final states at a spacing of 0.5 \text{\AA}, starting from the initial state side.
 	- A diverse set of smearing techniques was employed to determine of partial occupancies $f_{nk}$, including the tetrahedron method [62] and the Gaussian method.
@@
 
-The augmented dataset comprises 12,312 samples, with adsorption energies having a standard deviation of 1.8117 and a variance of 3.2821.
-Twenty pecent of these samples were allocated to the validation set. Throughout the training process, a batch size of 64 was employed to ensure a balanced learning dynamic.
+The augmented dataset comprises 12,312 samples, with adsorption energies having a standard deviation of 1.8117 eV and a variance of 3.2821 $\mathrm{eV}^2$.
+Twenty percent of these samples were allocated to the validation set. Throughout the training process, a batch size of 64 was employed to ensure a balanced learning dynamic.
 
 \subsection{Occlusion experiments}
-Supplementary Figure 21 visually illustrates the occlusion experiment methodology. To maintain consistent shapes, zero-padding was applied to the input eDOS arrays.
+Supplementary Figure 21 visually illustrates the occlusion experiment methodology.
+To maintain consistent shapes, zero-padding was applied to the input eDOS arrays.
 Focusing on understanding the influence of metals on adsorption behavior, a masker with dimensions [width, 1, 1] was employed along the metal channel to eliminate cross-orbital interactions.
@@
 A Gaussian smearing for energy integration was employed with a broadening width of 0.05 eV.
-The quantification of bonding strength between the single metal atom and the substrate was achieved through the summation of interactions with neighboring atoms within a range of 0.5 Å (TODO:) to 5.0 Å (TODO:) from the single metal atom.
+The quantification of bonding strength between the single metal atom and the substrate was achieved through the summation of interactions with neighboring atoms within a range of 0.5 \text{\AA} to 5.0 \text{\AA} from the single metal atom.
 Orbitals of interest were confirmed through band-structure analysis, and real-space wavefunctions were subsequently visualized using VASPKIT [68] and VESTA [69].

### 2024-01-05 paper/main_sections/3_introduction.tex
fix some broken symbols
break long lines for readability

@@
 Experimental determination of these mechanisms remains challenging due to the complexity of in situ spectroscopic detection of reaction intermediates [10].
-Computational modeling, particularly methods based on quantum mechanics (QM) such as density functional theory (DFT), allows for the profiling the energetics of intermediates and unveils structure-activity relationships for identified active sites [11, 12], contributing to understanding of reaction mechanisms.
+Computational modeling, particularly methods based on quantum mechanics (QM) such as density functional theory (DFT),
+allows for the profiling the energetics of intermediates and unveils structure-activity relationships for identified active sites [11, 12], contributing to understanding of reaction mechanisms.
 However, the high computational cost of QM methods restricts the accessible catalyst space [13-15].
@@
 This result validated the capability of current CNN model to accurately capture intricate spatial information from eDOS.
-Building on this, we introduced an orbital-wise eDOS occlusion experiment was adopted afterwards inspired from the occlusion technique widely used in computer vision and pattern recognition applications.
+Building on this, we introduced an orbitalwise eDOS occlusion experiment was adopted afterwards inspired from the occlusion technique widely used in computer vision and pattern recognition applications.
 Systematic eDOS experiment was performed to elucidate orbitalwise contributions to the adsorption energies at different energy levels, which produced consistent outcome from Crystal Orbital Hamilton Population (COHP) analysis and real-space wavefunction visualization.

### 2024-01-05 paper/main_sections/4.1_cnn_for_eads.tex
break long lines for readability

@@
 It handled species containing oxygen, hydrogen, and carbon atoms equally well, spanning an adsorption energy range from 0 to 10 eV.
-Significantly, after pretraining the CNN model, making predictions (inference) scales only linearly with system size and demands considerably less computational resources compared to DFT calculations [40].
+Significantly, after training the CNN model, making predictions (inferences) scales only linearly with system size and demands considerably less computational resources compared to DFT calculations [40].
 Conversely, unlike QM based methods, which could generate reasonably precise energy estimation for individual candidates, CNN relies on extensive datasets to ensure reliable predictions.

### 2024-01-05 paper/main_sections/5_methods.tex
fix equation/formula format

@@
 Asterisks (*) indicate species adsorbed on the SAC surfaces:
-% TODO: check format
-% (CO_2+ ^*+H^++e^- □(→┴(          ) )  ^* COOH#(1))
-% ( ^* COOH+H^++e^- □(→┴(          ) )  ^* CO+H_2 O#(2))
-% ( ^* CO+H^++e^- □(→┴(          ) )  ^* CHO#(3)######)
-% ( ^* CHO+H^++e^- □(→┴(          ) )  ^* CH_2 O#(4)##)
-% ( ^* CH_2 O+H^++e^- □(→┴(          ) )  ^* OCH_3#(5)#)
-% ( ^* OCH_3+H^++e^- □(→┴(          ) )  ^* O+CH_4#(6)#)
-% ( ^* O+H^++e^- □(→┴(          ) )  ^* OH#(7)#)
-% ( ^* OH+H^++e^- □(→┴(          ) )  ^*+H_2 O#(8)#)
+
+\begin{equation*}
+\begin{aligned}
+\ce{CO2 + H+ + e- &-> \text{*}COOH} \\
+\ce{\text{*}COOH + H+ + e- &-> \text{*}CO + H2O} \\
+\ce{\text{*}CO + H+ + e- &-> \text{*}CHO} \\
+\ce{\text{*}CHO + H+ + e- &-> \text{*}CH2O} \\
+\ce{\text{*}CH2O + H+ + e- &-> \text{*}OCH3} \\
+\ce{\text{*}OCH3 + H+ + e- &-> \text{*}O + CH4} \\
+\ce{\text{*}O + H+ + e- &-> \text{*}OH} \\
+\ce{\text{*}OH + H+ + e- &-> \text{*} + H2O}
+\end{aligned}
+\end{equation*}
 
@@
 The free energy $\textit{G}$ was calculated using the formula:
-% TODO: check format
-% (G=E+ E_ZPE-TS#(9))
+\begin{equation*}
+G = E + E_{\text{ZPE}} - TS
+\end{equation*}
+
 where $\textit{G}$ represents the free energy, $\textit{E}$ denotes electronic energy, $\textit{E}_{\text{ZPE}}$ is the zero-point energy, $\textit{T}$ represents temperature in Kevin, and $\textit{S}$ stands for entropy.
@@
 At the reference electrode surface, the reaction
-% TODO: check format
-% (1/2 H_2(g)   □(↔┴(           )  H^++ e^- )#(10))
+\begin{equation*}
+\ce{1/2H2_{(g)}  <-> H+ + e-}
+\end{equation*}
 is in equilibrium, allowing the calculation of the chemical potential of the electron-proton pair as:
-% (μ(H^+)+μ(e^-)=1/2 μ(H_2(g) )-eU#(11))
+\begin{equation*}
+\mu(H^+) + \mu(e^-) = \frac{1}{2}\mu(H_{2(g)}) - eU
+\end{equation*}
 For the external potential $\textit{U}$ applied, the change in free energy ($\Delta \textit{G}$) was determined using the equation:
-% (∆G_n (U)= ∆G_n (U=0)+neU#(12))
+\begin{equation*}
+\Delta G_n(U) = \Delta G_n(U=0) + neU
+\end{equation*}
 Here, $\mu$ represents chemical potential, $\textit{U}$ signifies the external potential applied, $\textit{n}$ represents the number of proton-electron pairs transferred, and $\textit{e}$ denotes the elementary charge.
@@
 Comprehensive analyses are presented Supplementary Section 1.5. This leads to the formulation of the scaling relation:
-% TODO: check format
-% (G_ads Z=k[θ*G_ads CO+(1-θ)*G_ads OH]+c_Z#(13)##)
+\begin{equation*}
+G_{\text{ads}} Z = k[\theta^* G_{\text{ads}} \ce{CO} + (1-\theta^*) G_{\text{ads}} \ce{OH}] + c_Z
+\end{equation*}
 Here, $\theta$ represents the mixing ratio of the CO descriptor, $\textit{Z}$ denotes any adsorbate, and $\textit{k}$ and $\textit{c}_{Z}$ are adsorbate-specific scaling parameters.
@@
 Equation 14 could be simplified to a more general form:
-% TODO: check format
-% (G_ads Z=a_Z G_ads CO+b_Z G_ads OH+c_Z#(14)#)
+\begin{equation*}
+G_{\text{ads}} Z = a_Z G_{\text{ads}} \ce{CO} + b_Z G_{\text{ads}} \ce{OH} + c_Z
+\end{equation*}
 Here, $a_Z$, $b_Z$, $c_Z$ are adsorbate-specific parameters.
@@
 Consequently, the limiting potential $\textit{U}_{L}$ is entirely determined by two descriptors through the following equation:
-% TODO: check format
-% (U_L=-max⁡{〖ΔG〗_i }/e#(15)#)
+\begin{equation*}
+U_L = -\frac{\max\{ \Delta G_i \}}{e}
+\end{equation*}
 Where $\Delta G_{i}$ represents the free energy change of reaction step i.

### 2024-01-05 paper/main_sections/4.4_shifting_exp.tex
add figures

@@
 \section{Validation of CNN predictions}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\linewidth]{main_sections/figures/figure_5.JPG}
+    \caption{\textbf{Shifting Experiments.}
+    Impact of orbitalwise eDOS shifting on CO adsorption energy, as predicted by the CNN model, for single metal atom catalysts supported on g-$\mathrm{C_3N_4}$.
+    The disturbances caused by shifting of (a)entire $d$, (b)$d_{xy}$, (c)$d_{yz}$, (d)$d_{z^2}$, (e)$d_{xz}$ and (f)$d_{x^2-y^2}$ orbitals are illustrated.
+    The shifting step size corresponds to the energy resolution of the eDOS, which is 0.005 eV in this study.
+    A positive eDOS shift indicates a shift towards higher energy levels, and vice versa.}
+    \label{main_fig5:shifting}
+\end{figure}
+
 While CNN models excel in prediction of the activity of catalyst candidates directly from eDOS, volcano plots point out directions leading to better catalysts.

### 2024-01-05 paper/main_sections/3_introduction.tex
add figures

@@
 
-\newpage
+\section{Introduction}
 
-\section{Introduction}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\linewidth]{main_sections/figures/figure_1.png}
+    \caption{\textbf{Catalyst Performance Analysis Pipeline Integrating Volcano Plots and CNN.}
+    The figure demonstrates the integrated usage of volcano plots for predictive assessments of existing catalysts and the utility of CNNs to predict and modulate adsorption energies \(E_{\text{ads}}\) using eDOS as input.
+    Advanced occlusion and shifting experiments on eDOS are conducted to extract chemical meanings from CNN model.}
+    \label{main_fig1:pipeline}
+\end{figure}
+
 Electrochemical CO$_2$RR stands as a promising avenue for long-term seasonal energy storage [1] and mitigating excess CO$_2$ in the atmosphere.

### 2024-01-05 paper/main_sections/4.1_cnn_for_eads.tex
add figures

@@
 \section{Adsorption energy prediction from electronic density of states with convolutional neural network}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\linewidth]{main_sections/figures/figure_2.JPG}
+    \caption{\textbf{CNN for Electronic Density of States.}
+    a.
+Kendall rank correlation map illustrating the correlation between adsorption energy and some electronic and elementary descriptors.
+Definitions of the notations are provided in Supplementary Table 15.
+    b-c. Architectural of (b)the root and (c)each branch of the CNN model. The architecture remains consistent across individual branches.
+    d-m.
+Parity plots demonstrating the performance of the CNN model across nine adsorbates: (d)all adsorbates, (e) $\mathrm{CO_2}$, (f)COOH, (g)CO, (h)CHO, (i) $\mathrm{CH_2O}$, (j) $\mathrm{OCH_3}$, (k)O, (l)OH, and (m)H.
+    The augmentation data are not displayed in the plots nor included in MAE evaluations.
+    Kernel density estimate results are shown along the top and right sides of the main plot, representing DFT calculations and CNN model prediction distributions, respectively.}
+    \label{main_fig2:cnn_for_eads}
+\end{figure}
+
 Originating from the pioneering work of Hammer and Nørskov [30], the d-band center model has emerged as a successful paradigm for employing descriptor to understand and predict the adsorption behavior on transition metal surfaces.

### 2024-01-05 paper/main_sections/4.2_volcano_plots.tex
fix symbol format
break long lines for readability
add figures

@@
 \section{Hybrid descriptors enabled volcano plot for catalyst analysis}
-Catalyst activity volcano plots, built upon the scaling relations proposed by Peterson and Nørskov's [26], goes beyond assessment of candidatures' energetics only but to provide informative guidance on discovering catalysts candidates with superior performance [42, 43].
-Our endeavor to improve the accuracy of volcano plots leads to the development of the hybrid-descriptor, which encompasses both C- and O- bonding types of CO$_2$RR intermediates within the scaling relations.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\linewidth]{main_sections/figures/figure_3.JPG}
+    \caption{\textbf{Limiting Potential Volcano Plot and Periodic Table.}
+    a. Limiting potential volcano plot computed from hybrid-descriptor-based linear scaling relations at -0.17 V vs SHE.
+    In the plot, the circle, triangle, square, diamond, plus, and star symbols represent metals supported on g-$\mathrm{C_3N_4}$, nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, BN, and $\mathrm{C_2N}$, respectively.
+    Dotted purple lines delineate regions representing rate-determining steps (RDS), with roman numerals denoting the respective RDS for each region.
+    b. Limiting potential periodic table illustrating the theoretical activity of single atom catalysts, where metals are supported on g-$\mathrm{C_3N_4}$.}
+    \label{main_fig3:volcano}
+\end{figure}
+
+Catalyst activity volcano plots, built upon the scaling relations proposed by Peterson and Nørskov's [26],
+goes beyond assessment of candidatures' energetics only but to provide informative guidance on discovering catalysts candidates with superior performance [42, 43].
+Our endeavor to improve the accuracy of volcano plots leads to the development of the hybrid-descriptor,
+which encompasses both C- and O- bonding types of CO$_2$RR intermediates within the scaling relations.
 This adaptation arose from the intuition that most CO$_2$RR intermediates are featured with both bonding types rather than any single one in dominance.
@@
 After taking this dual nature into consideration, our hybrid-descriptor method can evaluate the intermediates adsorption energies more accurately.
-Importantly, the introduction of hybrid descriptors is computationally affordable compared to DFT methods, as it involves only a set of linear regressions to identify the optimal mixing ratio, as elaborated in the Methods section.
+Importantly, the introduction of hybrid descriptors is computationally affordable compared to DFT methods,
+as it involves only a set of linear regressions to identify the optimal mixing ratio, as elaborated in the Methods section.
 
@@
 The activity and selectivity volcano plots imply that enhancing theoretical activity could be achieved by decreasing CO affinity while increasing OH affinity with the catalysts.
-This result suggests a perspective: weak binding of CO to the catalyst surface might facilitate the rotation of C-O backbone from the “upright” configuration in *CO to the “horizontal” orientation in *CHO [45], and therefore facilitating dynamics and protonation of the *CO species.
+This result suggests a perspective: weak binding of CO to the catalyst surface might facilitate the rotation of C-O backbone from the “upright” configuration in *CO to the “horizontal” orientation in *CHO [45],
+and therefore facilitating dynamics and protonation of the *CO species.
 

### 2024-01-05 paper/main_sections/4.3_validation.tex
add figures

@@
 \section{Validation of CNN predictions}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\linewidth]{main_sections/figures/figure_4.JPG}
+    \caption{\textbf{Validation of CNN Predictions.}
+    a-c, The occlusion experiment results for (a)Cr $d_{x^2-y^2}$ orbital of Cr@g-$\mathrm{C_3N_4}$, (b)Co $d_{xy}$ orbital of Co@g-$\mathrm{C_3N_4}$ and (c)Cu $d_{xy}$ orbital of Cu@g-$\mathrm{C_3N_4}$.
+    Occlusion experiments were conducted on the initial states of CO adsorption process.
+    d-f, Real-space wavefunction visualization for (d)Cr $d_{x^2-y^2}$ orbital of Cr@g-$\mathrm{C_3N_4}$, (e)Co $d_{xy}$ orbital of Co@g-$\mathrm{C_3N_4}$ and (f)Cu $d_{xy}$ orbital of Cu@g-$\mathrm{C_3N_4}$.
+    Wavefunction visualizations were performed on the final states of CO adsorption process.
+    The yellow and aqua colors represent areas of positive and negative Kohn-Sham orbital coefficients, respectively.
+    g-j, Occlusion experiment results for (g)$d_{xy}$ orbital and (h)$d_{xz}$ orbital for Co of Co@g-$\mathrm{C_3N_4}$.
+    COHP analysis for (i)$d_{xy}$ orbital and (j)$d_{xz}$ orbital for Co of Co@g-$\mathrm{C_3N_4}$, performed between Co and all adsorbate atoms in the final states of CO adsorption process.}
+    \label{main_fig4:validation}
+\end{figure}
+
 Historically, interpretability has posed challenges for deep learning methods, often rendering their inner workings akin to black boxes [46-48].

### 2024-01-05 paper/main_sections/6_tail.tex
fix symbol format
adjust empty lines

@@
 structure files of SACs, eDOS arrays and the pretrained CNN model-are available on GitHub
-at https://github.com/DanielYang59/cnn4dos or can be provided by the corresponding authors upon request.
+at \url{https://github.com/DanielYang59/cnn4dos} or can be provided by the corresponding authors upon request.
 Due to their substantial size in terabytes, the complete source data is not currently hosted on publicly available repositories but can also be obtained from the corresponding authors upon request.
@@
 \subsection{Code Availability}
-Associated computer code for this study can be accessed on GitHub at https://github.com/DanielYang59/cnn4dos, or obtained from the corresponding authors upon request.
+Associated computer code for this study can be accessed on GitHub at \url{https://github.com/DanielYang59/cnn4dos},
+or obtained from the corresponding authors upon request.
 
@@
 \subsection{Author Contributions}
-H.Y. performed DFT calculations, implemented Python code the machine learning methodologies and data analysis, and drafted and refined the manuscript.
+H.Y. performed DFT calculations, implemented Python code for machine learning methodologies and data analysis,
+and drafted and refined the manuscript.
 J.Z. engaged in valuable discussions on DFT calculations.

### 2024-01-05 paper/main_sections/4.2_volcano_plots.tex
fix references

@@
 
-Catalyst activity volcano plots, built upon the scaling relations proposed by Peterson and Nørskov's [26],
-goes beyond assessment of candidatures' energetics only but to provide informative guidance on discovering catalysts candidates with superior performance [42, 43].
+Catalyst activity volcano plots, built upon the scaling relations proposed by Peterson and Nørskov's \cite{peterson2012activity},
+goes beyond assessment of candidatures' energetics only but to provide informative guidance on discovering catalysts candidates with superior performance \cite{balandin1969modern, deutschmann2000heterogeneous}.
 Our endeavor to improve the accuracy of volcano plots leads to the development of the hybrid-descriptor,
@@
 Expanding upon the revised scaling relations, we introduce an activity volcano plot and a rate-determining step (RDS) volcano plot for the CO$_2$RR process, shown in Figure 3a and Supplementary Figure 11.
-Given that HER is a key competing reaction with CO$_2$RR [44], we also incorporated a selectivity volcano plot, presented in Supplementary Figure 12, to offer a comprehensive analysis of catalyst candidates.
-In adherence to Peterson and Nørskov's original framework [26], our choice of x and y axes descriptors aligned with $\textit{G}_{\text{ads} \ast \text{CO}}$ and $\textit{G}_{\text{ads} \ast \text{OH}}$.
+Given that HER is a key competing reaction with CO$_2$RR \cite{goyal2020competition}, we also incorporated a selectivity volcano plot, presented in Supplementary Figure 12, to offer a comprehensive analysis of catalyst candidates.
+In adherence to Peterson and Nørskov's original framework \cite{peterson2012activity}, our choice of x and y axes descriptors aligned with $\textit{G}_{\text{ads} \ast \text{CO}}$ and $\textit{G}_{\text{ads} \ast \text{OH}}$.
 Further elaboration on how the limiting potentials were evaluated across the volcano plot can be found in the Methods section.
@@
 The activity and selectivity volcano plots imply that enhancing theoretical activity could be achieved by decreasing CO affinity while increasing OH affinity with the catalysts.
-This result suggests a perspective: weak binding of CO to the catalyst surface might facilitate the rotation of C-O backbone from the “upright” configuration in *CO to the “horizontal” orientation in *CHO [45],
+This result suggests a perspective: weak binding of CO to the catalyst surface might facilitate the rotation of C-O backbone from the “upright” configuration in *CO to the “horizontal” orientation in *CHO \cite{peterson2010copper},
 and therefore facilitating dynamics and protonation of the *CO species.

### 2024-01-05 paper/main_sections/4.3_validation.tex
fix references

@@
 
-Historically, interpretability has posed challenges for deep learning methods, often rendering their inner workings akin to black boxes [46-48].
-The occlusion technique, widely utilized in Computer Vision [49-51], involves systematically masking sections of the input matrix to assess their impact on the final prediction score.
-In our work, we introduce an orbitalwise occlusion method to discern individual orbital contribution to adsorption energy within the CNN model, drawing inspiration from Fung's pioneer integration of this technique into eDOS analysis [41].
+Historically, interpretability has posed challenges for deep learning methods, often rendering their inner workings akin to black boxes \cite{zhang2018interpretable, zhang2018visual, savage2022breaking}.
+The occlusion technique, widely utilized in Computer Vision \cite{zeiler2014visualizing, kortylewski2020combining, wang2020robust}, involves systematically masking sections of the input matrix to assess their impact on the final prediction score.
+In our work, we introduce an orbitalwise occlusion method to discern individual orbital contribution to adsorption energy within the CNN model, drawing inspiration from Fung's pioneer integration of this technique into eDOS analysis \cite{fung2021machine}.
 In this work, occlusion experiments involve orbitalwise masking specific eDOS, which are then fed into the CNN model to observe resulting disturbance in adsorption energy.
@@
 
-To validate the chemical relevance of predictions made by CNN model, we conducted COHP analysis, a theoretical bond-detecting tool used to identify bonding and anti-bonding contributions to band-structure energy [52].
+To validate the chemical relevance of predictions made by CNN model, we conducted COHP analysis, a theoretical bond-detecting tool used to identify bonding and anti-bonding contributions to band-structure energy \cite{deringer2011crystal}.
 In this research, interactions between the supported metal atom and atoms within a 5 \text{\AA} radius were calculated to understand its bonding environment, as detailed in the Methods section.

### 2024-01-05 paper/main_sections/4.4_shifting_exp.tex
fix references

@@
 Skillful manipulation of the electronic structure of catalyst candidates would be required, presenting a practical challenge.
-In contrast to prior studies on bulk metals [41], wherein the adsorption energy exhibits a continuous shift with eDOS variations, the response of SACs is notably discrete.
+In contrast to prior studies on bulk metals \cite{fung2021machine}, wherein the adsorption energy exhibits a continuous shift with eDOS variations, the response of SACs is notably discrete.
 These responses manifest as isolated peaks throughout the shifting range, attributed to the distinctive structure of SACs.

### 2024-01-05 paper/main_sections/3_introduction.tex
fix references

@@
 
-Electrochemical CO$_2$RR stands as a promising avenue for long-term seasonal energy storage [1] and mitigating excess CO$_2$ in the atmosphere.
+Electrochemical CO$_2$RR stands as a promising avenue for long-term seasonal energy storage \cite{dinh2018co2} and mitigating excess CO$_2$ in the atmosphere.
 
-Despite decades of research, metallic copper remains a leading CO$_2$RR electrocatalyst for hydrocarbon production [2], albeit burdened by substantial overpotential and low faradic efficiency and poor operational stability [3, 4].
-In this regard, supported SACs have displayed remarkable activity and selectivity across various catalytic reactions [5, 6], leveraging their unique electronic properties and coordination environment.
-To date, experimental studies have primarily focused on two-electron reduction products due to the facile release of gaseous CO [7-9].
+Despite decades of research, metallic copper remains a leading CO$_2$RR electrocatalyst for hydrocarbon production \cite{osella2023co2}, albeit burdened by substantial overpotential and low faradic efficiency and poor operational stability \cite{chen2019identifying, liu2021co2}.
+In this regard, supported SACs have displayed remarkable activity and selectivity across various catalytic reactions \cite{wang2018heterogeneous, yang2018atomically}, leveraging their unique electronic properties and coordination environment.
+To date, experimental studies have primarily focused on two-electron reduction products due to the facile release of gaseous CO \cite{cai2021insights, ju2017understanding, ren2019isolated}.
 Consequently, there is a pressing need to modulate the electronic structure of single-atom sites to enable hydrocarbon production at reduced overpotential.
@@
 The challenge towards effective catalysts design lies in understanding the reaction mechanisms.
-Experimental determination of these mechanisms remains challenging due to the complexity of in situ spectroscopic detection of reaction intermediates [10].
+Experimental determination of these mechanisms remains challenging due to the complexity of in situ spectroscopic detection of reaction intermediates \cite{zhao2021revisiting}.
 Computational modeling, particularly methods based on quantum mechanics (QM) such as density functional theory (DFT),
-allows for the profiling the energetics of intermediates and unveils structure-activity relationships for identified active sites [11, 12], contributing to understanding of reaction mechanisms.
-However, the high computational cost of QM methods restricts the accessible catalyst space [13-15].
+allows for the profiling the energetics of intermediates and unveils structure-activity relationships for identified active sites [feaster2017understanding, carter2008challenges], contributing to understanding of reaction mechanisms.
+However, the high computational cost of QM methods restricts the accessible catalyst space \cite{jinnouchi2017predicting, cuenya2015nanocatalysis, goldsmith2018machine}.
 
 In this context, researchers have explored descriptor-based methods to circumvent QM calculations and establish direct correlations between target properties and electronic factors, commonly referred to as descriptors or features.
-Traditional methods of crafting descriptors, as seen in the d-band model of Hammer and Nørskov [16], necessitate meticulous selection of chemical properties based on chemical knowledge and are inherently case-dependent [17].
-Particularly in the case of SACs, the relationship is intricate, rendering manual crafting inadequate [18, 19].
-To streamline this featurization process, we employed convolutional neural networks (CNNs), which autonomously derive a hierarchical representation directly from the electronic density of state (eDOS) [20-22].
+Traditional methods of crafting descriptors, as seen in the d-band model of Hammer and Nørskov \cite{hammer1995electronic}, necessitate meticulous selection of chemical properties based on chemical knowledge and are inherently case-dependent \cite{kajita2017universal}.
+Particularly in the case of SACs, the relationship is intricate, rendering manual crafting inadequate \cite{han2021single, thirumalai2018investigating}.
+To streamline this featurization process, we employed convolutional neural networks (CNNs), which autonomously derive a hierarchical representation directly from the electronic density of state (eDOS) \cite{tran2015learning, socher2012convolutional, krizhevsky2012imagenet}.
 This approach accurately maps to the activity space, negating the need for manual crafting of descriptors and providing a more efficient method to understand and establish the structure-mechanism-activity relationship for electrochemical reactions.
@@
 Our CNN model accurately estimated the adsorption energies, the activity descriptor, from the eDOS of 2D materials supported single metal catalysts.
-Evaluations on the adsorption energies of nine intermediates along CO$_2$RR and competing hydrogen evolution reaction (HER) as well yielded prediction mean absolute errors (MAEs) at the level of 0.1 eV, which is well aligned with the precision of conventional DFT calculations [23-25].
+Evaluations on the adsorption energies of nine intermediates along CO$_2$RR and competing hydrogen evolution reaction (HER) as well yielded prediction mean absolute errors (MAEs) at the level of 0.1 eV, which is well aligned with the precision of conventional DFT calculations \cite{kirklin2015open, lejaeghere2016reproducibility, wellendorff2015benchmark}.
 This result validated the capability of current CNN model to accurately capture intricate spatial information from eDOS.
@@
 Besides offering intuitive analysis of catalyst activities (represented by the elevation of volcanoes), volcano plots points to the directions on how effort can be exerted to identify promising catalyst candidates.
-Built upon scaling relations [26], we introduced a hybrid-descriptor scheme incorporating both C- and O-centered species.
+Built upon scaling relations \cite{peterson2012activity}, we introduced a hybrid-descriptor scheme incorporating both C- and O-centered species.
 The scaling coefficient of determination ($R^2$) was increased by 0.1387 using hybrid descriptor, which demonstrate an improved prediction accuracy compared to the well documented single descriptor based method.
@@
 The CNN, which correlates eDOS with activity descriptors, establishes a robust electronic structure-activity relationship.
-Notably, it is capable to predict the influence of eDOS disturbances, caused by either alloying, strain, or defects [27-29], to modulate the catalytic activity of materials, which will offer insights into the intrinsic mechanism for rationalized catalyst optimization strategies.
+Notably, it is capable to predict the influence of eDOS disturbances, caused by either alloying, strain, or defects \cite{norskov2011density, bera2017density, kusada2019emergence}, to modulate the catalytic activity of materials, which will offer insights into the intrinsic mechanism for rationalized catalyst optimization strategies.
 Advancing the current volcano plot method, the involvement of CNN models in catalyst performance analysis pipeline holds enormous promise for advanced exploration of catalysts with superior performance.

### 2024-01-05 paper/main_sections/4.1_cnn_for_eads.tex
fix references

@@
 
-Originating from the pioneering work of Hammer and Nørskov [30], the d-band center model has emerged as a successful paradigm for employing descriptor to understand and predict the adsorption behavior on transition metal surfaces.
-To investigate alternative electronic and elementary descriptors that may serve as more suitable substitutes for the d-band center model in the context of SACs, we performed Kendall rank correlation analysis to account for both linearity and non-linearity [31].
+Originating from the pioneering work of Hammer and Nørskov \cite{hammer2000theoretical}, the d-band center model has emerged as a successful paradigm for employing descriptor to understand and predict the adsorption behavior on transition metal surfaces.
+To investigate alternative electronic and elementary descriptors that may serve as more suitable substitutes for the d-band center model in the context of SACs, we performed Kendall rank correlation analysis to account for both linearity and non-linearity \cite{kendall1938new}.
 The correlation coefficient map, as presented in Figure 2a, highlighted the d-band center as the most informative descriptor with a Kendall's $\tau$ coefficient of -0.33, and followed by the vacuum level and electronegativity.
 However, d-band center alone does not suffice for accurate predictions of intermediate adsorption energy as illustrated in the scatter plot Supplementary Figure 18, and therefore, refinements are imperative.
-Unlike bulk transition metal surfaces, where the variations in the d-band centre account for the majority of the adsorption energy variations [27, 32], the unique structure of SACs introduces more variables rather than d-band center that are intrinsically correlated with the variations of adsorption energy.
-This finding also interpreted that in some reported prior studies, indicating that depending solely on the d-band center may be insufficient for accurate adsorption energy predictions in the context of SACs [33-37].
+Unlike bulk transition metal surfaces, where the variations in the d-band centre account for the majority of the adsorption energy variations \cite{norskov2011density, takigawa2016machine}, the unique structure of SACs introduces more variables rather than d-band center that are intrinsically correlated with the variations of adsorption energy.
+This finding also interpreted that in some reported prior studies, indicating that depending solely on the d-band center may be insufficient for accurate adsorption energy predictions in the context of SACs \cite{33-37sun2022going, fung2020descriptors, di2022universal, yuan2020descriptor, huang2020rational}.
 As a result, the development of a method tailored specifically for catalysts like SACs becomes essential.
@@
 The model predicts adsorption energies across nine species within the CO$_2$RR process and competing HER side reaction, attaining an averaged MAE of 0.06 eV.
-This MAE aligns with the established precision of DFT methods, which typically range between 0.1-0.2 eV concerning experimental measurement [25, 38, 39].
+This MAE aligns with the established precision of DFT methods, which typically range between 0.1-0.2 eV concerning experimental measurement \cite{wellendorff2015benchmark, kirklin2015open, lejaeghere2016reproducibility}.
 The full list of prediction errors is available in Supplementary Table 18.
@@
 It handled species containing oxygen, hydrogen, and carbon atoms equally well, spanning an adsorption energy range from 0 to 10 eV.
-Significantly, after training the CNN model, making predictions (inferences) scales only linearly with system size and demands considerably less computational resources compared to DFT calculations [40].
+Significantly, after training the CNN model, making predictions (inferences) scales only linearly with system size and demands considerably less computational resources compared to DFT calculations \cite{chandrasekaran2019solving}.
 Conversely, unlike QM based methods, which could generate reasonably precise energy estimation for individual candidates, CNN relies on extensive datasets to ensure reliable predictions.
@@
 This augmentation resulted in an expanded dataset of 12312 samples, enhancing prediction performance with a reduced validation MAE of 0.1736 eV.
-Comparatively, our CNN model diverges from prior attempts, notably Fung's pioneer work [41], by requiring only the eDOS of supported single metal atom alone and adsorbate.
+Comparatively, our CNN model diverges from prior attempts, notably Fung's pioneer work \cite{fung2021machine}, by requiring only the eDOS of supported single metal atom alone and adsorbate.
 This revision eliminated the necessity for a complete set of substrate and adsorbate eDOS and significantly reduced computational cost.

### 2024-01-05 paper/main_sections/5_methods.tex
fix references

@@
 \subsection{DFT calculations}
-Spin-polarized density functional theory calculations were performed using the Vienna Ab initio Simulation Package (VASP) version 5.4.4 [53-55] to optimize geometries and determine the electronic structure.
-The Perdew-Burke-Ernzerhof (PBE) functional [53] within the generalized gradient approximation (GGA) [56] was utilized to describe the electron-ion interactions and electronic exchange correlations.
+Spin-polarized density functional theory calculations were performed using the Vienna Ab initio Simulation Package (VASP) version 5.4.4 \cite{kresse1996efficient, kresse1996efficiency, kresse1993ab} to optimize geometries and determine the electronic structure.
+The Perdew-Burke-Ernzerhof (PBE) functional \cite{kresse1996efficient} within the generalized gradient approximation (GGA) \cite{perdew1996generalized} was utilized to describe the electron-ion interactions and electronic exchange correlations.
 Kohn-Shan equations were approached employing a plane-wave basis set with a cut-off energy of 440 eV.
@@
 \subsection{CO$_2$RR pathway}
-The C1 production CO$_2$RR pathway, as initially described by Peterson et al. [45] and later confirmed by Jiao et al. [57] for g-C$_3$N$_4$ based SACs, involves the following elementary steps.
+The C1 production CO$_2$RR pathway, as initially described by Peterson et al.
+\cite{peterson2010copper} and later confirmed by Jiao et al.
+\cite{jiao2017molecular} for g-C$_3$N$_4$ based SACs, involves the following elementary steps.
 Asterisks (*) indicate species adsorbed on the SAC surfaces:
@@
 
-The computational hydrogen electrode (CHE) model [45, 58] was employed to introduce potential dependence.
+The computational hydrogen electrode (CHE) model \cite{peterson2010copper, norskov2004origin} was employed to introduce potential dependence.
 At the reference electrode surface, the reaction
@@
 \subsection{CNN architecture and hyperparameter tuning}
-We designed our CNN architecture drawing inspiration from its successful implementation in tasks involving electrocardiogram signal classification [59], as illustrated in Figure 2b and 2c.
+We designed our CNN architecture drawing inspiration from its successful implementation in tasks involving electrocardiogram signal classification \cite{weimann2021transfer}, as illustrated in Figure 2b and 2c.
 This multi-branched CNN comprises nine branches tailored to handle eDOS orbitals while ensuring a reduced memory footprint.
@@
 The effectiveness of neural network models is intricately tied to the choice of hyperparameters.
-To identify the optimal set of hyperparameters, we employed Hyperband [60], a modern and parallelizable bandit-based optimization algorithm.
+To identify the optimal set of hyperparameters, we employed Hyperband \cite{li2018hyperband}, a modern and parallelizable bandit-based optimization algorithm.
 The search space for hyperparameters is detailed in Supplementary Table 16, and the resulting optimal hyperparameters are presented in Supplementary Table 17.
@@
 \subsection{Data augmentation and CNN model training}
-To enhance the generalizability and robustness of the our CNN model, and achieve comprehensive coverage of the chemical space [61], we applied data augmentation techniques to the initial dataset using the following procedures:
+To enhance the generalizability and robustness of the our CNN model, and achieve comprehensive coverage of the chemical space \cite{DBLP:journals/corr/abs-2112-12542}, we applied data augmentation techniques to the initial dataset using the following procedures:
 	- In addition to the designated "initial state" of the adsorption process, where the adsorbate positioned 6.5 \text{\AA} above the supported single metal atom, five intermediate images were interpolated.
 These images were distributed between the initial and final states at a spacing of 0.5 \text{\AA}, starting from the initial state side.
-	- A diverse set of smearing techniques was employed to determine of partial occupancies $f_{nk}$, including the tetrahedron method [62] and the Gaussian method.
+	- A diverse set of smearing techniques was employed to determine of partial occupancies $f_{nk}$, including the tetrahedron method \cite{blochl1994improved} and the Gaussian method.
 For the Gaussian method, the smearing width was varied within the range of 0.01 eV to 0.1 eV.
@@
 \subsection{Chemical bond analysis and real-space wavefunction visualization}
-COHP analysis was performed using the Local-Orbital Basis Suite Towards Electronic-Structure Reconstruction (LOBSTER) package  [52, 63-66] version 4.1.0, with the GGA-PBE wavefunctions fitted by S.
-Maintz [63, 67].
+COHP analysis was performed using the Local-Orbital Basis Suite Towards Electronic-Structure Reconstruction (LOBSTER) package  \cite{deringer2011crystal, koga1999analytical, nelson2020lobster, maintz2013analytic, dronskowski1993crystal} version 4.1.0, with the GGA-PBE wavefunctions fitted by S.
+Maintz \cite{koga1999analytical, maintz2016lobster}.
 A Gaussian smearing for energy integration was employed with a broadening width of 0.05 eV.
 The quantification of bonding strength between the single metal atom and the substrate was achieved through the summation of interactions with neighboring atoms within a range of 0.5 \text{\AA} to 5.0 \text{\AA} from the single metal atom.
-Orbitals of interest were confirmed through band-structure analysis, and real-space wavefunctions were subsequently visualized using VASPKIT [68] and VESTA [69].
+Orbitals of interest were confirmed through band-structure analysis, and real-space wavefunctions were subsequently visualized using VASPKIT \cite{wang2021vaspkit} and VESTA \cite{momma2008vesta}.
 
 \subsection{Machine learning and data analysis environment}
-The CNN model was implemented using TensorFlow [70], and hyperparameter optimization was conducted using the Hyperband [60] algorithm via KerasTuner [71].
+The CNN model was implemented using TensorFlow \cite{abadi2016tensorflow}, and hyperparameter optimization was conducted using the Hyperband \cite{li2018hyperband} algorithm via KerasTuner \cite{omalley2019kerastuner}.
 For a more detailed overview of our machine learning setup and data analysis environment, please refer to Supplementary Section 3.

### 2024-01-05 paper/main_sections/3_introduction.tex
fix missing formats

@@
 Computational modeling, particularly methods based on quantum mechanics (QM) such as density functional theory (DFT),
-allows for the profiling the energetics of intermediates and unveils structure-activity relationships for identified active sites [feaster2017understanding, carter2008challenges], contributing to understanding of reaction mechanisms.
+allows for the profiling the energetics of intermediates and unveils structure-activity relationships for identified active sites \cite{feaster2017understanding, carter2008challenges}, contributing to understanding of reaction mechanisms.
 However, the high computational cost of QM methods restricts the accessible catalyst space \cite{jinnouchi2017predicting, cuenya2015nanocatalysis, goldsmith2018machine}.

### 2024-01-05 paper/main_sections/4.2_volcano_plots.tex
fix missing formats

@@
 Further elaboration on how the limiting potentials were evaluated across the volcano plot can be found in the Methods section.
-Among the candidatures explored, Ge@g-C3N4 emerged as the most promising catalyst, demonstrating theoretical activity at a limiting potential of -1.2126 eV.
+Among the candidatures explored, Ge@g-C$_3$N$_4$ emerged as the most promising catalyst, demonstrating theoretical activity at a limiting potential of -1.2126 eV.
 Notably, the observed selectivity trend paralleled the activity trend, suggesting that catalysts exhibiting high theoretical activity are also resistant to HER side reactions.

### 2024-01-05 paper/si_sections/3_others.tex
add si references

@@
 The hyperparameter optimization for the proposed CNN model was performed using NVIDIA® V100 Tensor Core GPUs, courtesy of the Australian National Computational Infrastructure's (NCI) HPC Gadi system.
-The HyperBand algorithm [7], as implemented in KerasTuner [8] , facilitated the tuning process.
+The HyperBand algorithm \cite{li2018hyperband}, as implemented in KerasTuner \cite{omalley2019kerastuner} , facilitated the tuning process.
 
@@
 
-The illustrations of CNN architecture displayed in Figure 1 of the main text, as well as  Supplementary Figure 21 and Supplementary Figure 30, were obtained from the GitHub repository dair-ai/ml-visuals [9].
+The illustrations of CNN architecture displayed in Figure 1 of the main text, as well as  Supplementary Figure 21 and Supplementary Figure 30, were obtained from the GitHub repository dair-ai/ml-visuals \cite{Saravia_ML_Visuals_2021}.
 Blender was used to create and render the visual representation of the catalyst analysis pipeline shown in Figure 1 of the main text.

### 2024-01-05 paper/main_sections/4.1_cnn_for_eads.tex
add cross-ref in main text

@@
 To investigate alternative electronic and elementary descriptors that may serve as more suitable substitutes for the d-band center model in the context of SACs, we performed Kendall rank correlation analysis to account for both linearity and non-linearity \cite{kendall1938new}.
-The correlation coefficient map, as presented in Figure 2a, highlighted the d-band center as the most informative descriptor with a Kendall's $\tau$ coefficient of -0.33, and followed by the vacuum level and electronegativity.
-However, d-band center alone does not suffice for accurate predictions of intermediate adsorption energy as illustrated in the scatter plot Supplementary Figure 18, and therefore, refinements are imperative.
+The correlation coefficient map, as presented in \cref{main_fig2:cnn_for_eads}a, highlighted the d-band center as the most informative descriptor with a Kendall's $\tau$ coefficient of -0.33, and followed by the vacuum level and electronegativity.
+However, d-band center alone does not suffice for accurate predictions of intermediate adsorption energy as illustrated in the scatter plot Supplementary Figure 18 (TODO:), and therefore, refinements are imperative.
 Unlike bulk transition metal surfaces, where the variations in the d-band centre account for the majority of the adsorption energy variations \cite{norskov2011density, takigawa2016machine}, the unique structure of SACs introduces more variables rather than d-band center that are intrinsically correlated with the variations of adsorption energy.
-This finding also interpreted that in some reported prior studies, indicating that depending solely on the d-band center may be insufficient for accurate adsorption energy predictions in the context of SACs \cite{33-37sun2022going, fung2020descriptors, di2022universal, yuan2020descriptor, huang2020rational}.
+This finding also interpreted that in some reported prior studies, indicating that depending solely on the d-band center may be insufficient for accurate adsorption energy predictions in the context of SACs \cite{sun2022going, fung2020descriptors, di2022universal, yuan2020descriptor, huang2020rational}.
 As a result, the development of a method tailored specifically for catalysts like SACs becomes essential.
@@
 Our approach harnesses the entire 2D eDOS with a multi-branch CNN model.
-Figure 2b and Figure 2c delineate the model and its branches.
+\cref{main_fig2:cnn_for_eads}b and \cref{main_fig2:cnn_for_eads}c delineate the model and its branches.
 The workflow involves processing the entire 2D eDOS as input, segregating orbitals into branches, and directing the concatenated outputs through another convolutional block, which generates the adsorption energy prediction.
 Sharing learnable parameters across branches optimizes computational efficiency.
-By leveraging the CNN model, we predicted adsorption energies from the eDOS of supported single atoms, and validated through parity plots (Figure 2d-m).
+By leveraging the CNN model, we predicted adsorption energies from the eDOS of supported single atoms, and validated through parity plots (\cref{main_fig2:cnn_for_eads}d-m).
 The model predicts adsorption energies across nine species within the CO$_2$RR process and competing HER side reaction, attaining an averaged MAE of 0.06 eV.

### 2024-01-05 paper/main_sections/4.2_volcano_plots.tex
add cross-ref in main text

@@
 By integrating both bonding featured descriptors into the hybrid approach, we found the coefficient of determination ($R^2$) was increased by 0.1387.
-Detailed information about the scaling parameters and performance enhancements are provided in Supplementary Tables 13 and Supplementary Figure 10.
+Detailed information about the scaling parameters and performance enhancements are provided in Supplementary Tables 13 and Supplementary Figure 10 (TODO:).
 This improvement to some extent underscored our premise that CO$_2$RR intermediates typically exhibit chemical similarities encompassing both O- and C-type descriptors.
@@
 
-Expanding upon the revised scaling relations, we introduce an activity volcano plot and a rate-determining step (RDS) volcano plot for the CO$_2$RR process, shown in Figure 3a and Supplementary Figure 11.
-Given that HER is a key competing reaction with CO$_2$RR \cite{goyal2020competition}, we also incorporated a selectivity volcano plot, presented in Supplementary Figure 12, to offer a comprehensive analysis of catalyst candidates.
+Expanding upon the revised scaling relations, we introduce an activity volcano plot and a rate-determining step (RDS) volcano plot for the CO$_2$RR process, shown in \cref{main_fig3:volcano}a and Supplementary Figure 11 (TODO:).
+Given that HER is a key competing reaction with CO$_2$RR \cite{goyal2020competition}, we also incorporated a selectivity volcano plot, presented in Supplementary Figure 12 (TODO:), to offer a comprehensive analysis of catalyst candidates.
 In adherence to Peterson and Nørskov's original framework \cite{peterson2012activity}, our choice of x and y axes descriptors aligned with $\textit{G}_{\text{ads} \ast \text{CO}}$ and $\textit{G}_{\text{ads} \ast \text{OH}}$.
@@
 Notably, the observed selectivity trend paralleled the activity trend, suggesting that catalysts exhibiting high theoretical activity are also resistant to HER side reactions.
-The RDS volcano plot (Supplementary Figure 11) indicated protonation of *CO as the rate-determining step for nearly optimal candidates.
+The RDS volcano plot (Supplementary Figure 11 TODO:) indicated protonation of *CO as the rate-determining step for nearly optimal candidates.
 Moreover, the activity volcano plot predicted an optimal catalyst featuring a theoretical limiting potential of -1.0516 V, at $\textit{G}_{\text{ads} \ast \text{CO}}$ of 0.0589 eV and $\textit{G}_{\text{ads} \ast \text{OH}}$ of -4.0075 eV, positioned at the right-center of the volcano plot.
@@
 
-Additionally, we mapped the theoretical limiting potentials of the analyzed catalyst candidates onto periodic tables, shown in Figure 3b and Supplementary Figure 13 to 17.
+Additionally, we mapped the theoretical limiting potentials of the analyzed catalyst candidates onto periodic tables, shown in \cref{main_fig3:volcano}b and Supplementary Figure 13 to 17 (TODO:).
 Our analyses do not reveal consistent trends within groups or periods, nor did they exhibit evident patterns across substrates.

### 2024-01-05 paper/main_sections/4.3_validation.tex
add cross-ref in main text

@@
 In this work, occlusion experiments involve orbitalwise masking specific eDOS, which are then fed into the CNN model to observe resulting disturbance in adsorption energy.
-A visual representation of this process can be found in Supplementary Figure 21.
+A visual representation of this process can be found in Supplementary Figure 21 (TODO:).
 Conceptually, this experiment simulates the effect of shielding electronic states, allowing investigation of the potential contribution to adsorption energy from these states.
@@
 Each of these supported metals possesses 3d subshells with different electronic configurations: half-filled, partially filled and fully filled, allowing us to test the universality of our approach.
-The results of the occlusion experiment on the supported Cr single atom in Cr@g-C$_3$N$_4$ are given in Figure 4a.
+The results of the occlusion experiment on the supported Cr single atom in Cr@g-C$_3$N$_4$ are given in \cref{main_fig4:validation}a.
 The $d_{x^2-y^2}$ orbital emerges as dominant in CO interaction.
 Shielding electrons centered around -2 eV significantly alter the adsorption energy, indicating the potency of this orbital.
-The real-space wavefunction visualization in Figure 4d corroborates these findings, highlighting the interaction between the $d_{x^2-y^2}$ orbital of single metal atom and the adsorbate.
+The real-space wavefunction visualization in \cref{main_fig4:validation}d corroborates these findings, highlighting the interaction between the $d_{x^2-y^2}$ orbital of single metal atom and the adsorbate.
 This suggests the $d_{x^2-y^2}$ orbital of supported Co predominantly influence the interaction with CO, and thus shielding electrons from this orbital markedly disturb the adsorption energy.
-Additionally, occlusion experiments were performed on the Co $d_xy$ orbital of Co@g-C$_3$N$_4$ (Figure 4b) and the $Cu d_xy$ orbital of Cu@g-C$_3$N$_4$ (Figure 4c).
+Additionally, occlusion experiments were performed on the Co $d_xy$ orbital of Co@g-C$_3$N$_4$ (\cref{main_fig4:validation}b) and the $Cu d_xy$ orbital of Cu@g-C$_3$N$_4$ (\cref{main_fig4:validation}c).
 In both cases, the $d_xy$ orbital was identified as the dominant contributor.
@@
 In this research, interactions between the supported metal atom and atoms within a 5 \text{\AA} radius were calculated to understand its bonding environment, as detailed in the Methods section.
-The results of the occlusion experiment on the Co $d_xy$ orbital of Co@g-C$_3$N$_4$, identified as the dominant orbital via occlusion experiments, were compared with the COHP analysis, as shown in Figure 4g and Figure 4i.
+The results of the occlusion experiment on the Co $d_xy$ orbital of Co@g-C$_3$N$_4$, identified as the dominant orbital via occlusion experiments, were compared with the COHP analysis, as shown in \cref{main_fig4:validation}g and \cref{main_fig4:validation}i.
 The occlusion experiment pinpointed strong metal-adsorbate interactions at energy levels of -1 eV and -6.3 eV, which were confirmed by the COHP analysis.

### 2024-01-05 paper/main_sections/4.4_shifting_exp.tex
add cross-ref in main text

@@
 
-Figure 5 illustrates that supported Ga and Ge, the sole p-block metals in our study, exhibited no response to d orbital shifting.
+\cref{main_fig5:shifting} illustrates that supported Ga and Ge, the sole p-block metals in our study, exhibited no response to d orbital shifting.
 This observation is consistent with their lack of d-electrons in their valence shells, reinforcing the reliability of our shifting experiments.
-We also investigated potential disturbance from p orbital shifting, as shown in Supplementary Figure 31 and found no significant response.
+We also investigated potential disturbance from p orbital shifting, as shown in Supplementary Figure 31 (TODO:) and found no significant response.
 This implies that Ge@g-C$_3$N$_4$ holds promise as a CO$_2$RR electrocatalyst, given its high activity and resilience to electronic structure disturbances.

### 2024-01-05 paper/main_sections/5_methods.tex
add cross-ref in main text

@@
 Supported SACs were modelled by anchoring individual metal atoms onto various 2D substrates, including graphitic carbon nitride (g-C$_3$N$_4$), nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, boron nitride, and monolayer C$_2$N.
-The specific single metal atoms studied are outlined in Supplementary Figure 1.
+The specific single metal atoms studied are outlined in Supplementary Figure 1 (TODO:).
 To prevent interactions between adjacent images along the z-axis, vacuum layers of 15 \text{\AA} were introduced.
@@
 \subsection{Hybrid descriptor for volcano plots}
-Hybrid descriptors incorporate both descriptors within a single equation, enhancing the accuracy of scaling relationship with minimal computational overhead, as demonstrated in Supplementary Figure 10 and Supplementary Table 13.
+Hybrid descriptors incorporate both descriptors within a single equation, enhancing the accuracy of scaling relationship with minimal computational overhead, as demonstrated in Supplementary Figure 10 (TODO:) and Supplementary Table 13 (TODO:).
 Comprehensive analyses are presented Supplementary Section 1.5. This leads to the formulation of the scaling relation:
@@
 \subsection{CNN architecture and hyperparameter tuning}
-We designed our CNN architecture drawing inspiration from its successful implementation in tasks involving electrocardiogram signal classification \cite{weimann2021transfer}, as illustrated in Figure 2b and 2c.
+We designed our CNN architecture drawing inspiration from its successful implementation in tasks involving electrocardiogram signal classification \cite{weimann2021transfer}, as illustrated in \cref{main_fig2:cnn_for_eads}b and \cref{main_fig2:cnn_for_eads}c.
 This multi-branched CNN comprises nine branches tailored to handle eDOS orbitals while ensuring a reduced memory footprint.
@@
 \subsection{Occlusion experiments}
-Supplementary Figure 21 visually illustrates the occlusion experiment methodology.
+Supplementary Figure 21 (TODO:) visually illustrates the occlusion experiment methodology.
 To maintain consistent shapes, zero-padding was applied to the input eDOS arrays.
@@
 \subsection{Shifting experiments}
-Supplementary Figure 30 illustrates the implemented shifting experiment protocol.
+Supplementary Figure 30 (TODO:) illustrates the implemented shifting experiment protocol.
 In this study, the initial electronic density of states underwent controlled shifting along the energy axis.

### 2024-01-05 paper/si_sections/2_ml.tex
clean up some signs
add section headers

@@
-Section 2 Additional details on machine learning method
-Section 2.1 d-band center and adsorption energy relations
+% Supporting Information Section Two: Additional details on ML Methods
+
+\section{Additional details on machine learning method}
+
+\subsection{d-band center and adsorption energy relations}
 
@@
 
-Section 2.2 Feature correlation analysis
+\subsection{Feature correlation analysis}
 
@@
 
-Section 2.3 Input pipeline construction
+\subsection{Input pipeline construction}
 The format of the 2D array for the eDOS is naturally well-suited for use as neural network inputs.
@@
 
-Section 2.4 Hyperparameter tuning for CNN
+\subsection{Hyperparameter tuning for CNN}
 
@@
 
-Section 2.5 Occlusion experiment
+\subsection{Occlusion experiment}
 
@@
 
-Section 2.6 Shifting experiment
+\subsection{Shifting experiment}
 

### 2024-01-05 paper/si_sections/3_others.tex
add section headers

@@
-Section 3 Other additional information
-Section 3.1 Additional information on machine learning environment.
+% Supporting Information Section Three: Other Additional Information
+
+\section{Other additional information}
+
+\subsection{Additional information on machine learning environment}
+
 The hyperparameter optimization for the proposed CNN model was performed using NVIDIA® V100 Tensor Core GPUs, courtesy of the Australian National Computational Infrastructure's (NCI) HPC Gadi system.
@@
 
-Section 3.2 Additional information on data analysis and visualization environment.
+\subsection{Additional information on data analysis and visualization environment}
 Data analysis and visualization tasks were executed on an Apple MacBook Air featuring an octa-core M2 chip.

### 2024-01-05 paper/si_sections/2_ml.tex
get tables for cleaning up

@@
 Supplementary Figure 19 | Pairwise Plot of Adsorption Energy and Key Descriptors.
-This chart displays the pairwise relationships between CO adsorption energy and its four most correlated descriptors–d-band center (spin-up) δεd↑, lattice parameter γ, vacuum level Evac, and electronegativity on the Allen scale XAllen –as identified by Kendall rank correlation analysis.
+This chart displays the pairwise relationships between CO adsorption energy and its four most correlated descriptors-d-band center (spin-up) δεd↑, lattice parameter γ, vacuum level Evac, and electronegativity on the Allen scale XAllen -as identified by Kendall rank correlation analysis.
 Data from all six substrates investigated in this study are incorporated.
 
-Supplementary Table 15
-Notations for elementary descriptors and electronic descriptors
+% Supplementary Table 15
+\begin{table}[h]
+    \centering
+    \begin{tabular}{lr}
+      \hline
       Elementary Descriptors	Electronic Descriptors
+      \hline
       R	atomic radius	α, β, γ	lattice parameters
@@
       V	number of valence electrons
+      \hline
+    \end{tabular}
+    \caption{Notations for elementary descriptors and electronic descriptors}
+    \label{si_table15}
+\end{table}
 
@@
 
-Supplementary Table 16
-The hyperparameter searching space
+% Supplementary Table 16
+\begin{table}[h]
+    \centering
+    \begin{tabular}{lr}
+      \hline
       Hyperparameter	Search space	Description
+      \hline
       learningRate	[10-4, 10-2], logscale	Learning rate of Adam optimiser
@@
       br_act	"tanh", "relu", "sigmoid"	Activation function of fully connected layers in branch
+      \hline
+    \end{tabular}
+    \caption{The hyperparameter searching space}
+    \label{si_table16}
+\end{table}
 
-Supplementary Table 17
-Optimal hyperparameters identified with Hyperband algorithm
+% Supplementary Table 17
+\begin{table}[h]
+    \centering
+    \begin{tabular}{lr}
+      \hline
       Hyperparameter	Optimal value	Description
+      \hline
       learningRate	10-3	Learning rate of Adam optimiser
@@
       br_act	“tanh”	Activation function of fully connected layers in branch
+      \hline
+    \end{tabular}
+    \caption{Optimal hyperparameters identified with Hyperband algorithm}
+    \label{si_table17}
+\end{table}
 
-Supplementary Table 18
-Prediction mean absolute errors of the CNN model
+% Supplementary Table 18
+\begin{table}[h]
+    \centering
+    \begin{tabular}{lr}
+      \hline
       Adsorbate	Original dataset (eV)	Augmented dataset (eV)
+      \hline
       CO2	0.0447	0.0336
@@
       H	0.0703	0.0646
+      \hline
+    \end{tabular}
+    \caption{Prediction mean absolute errors of the CNN model}
+    \label{si_table18}
+\end{table}
 Note.
@@
 
-Supplementary Figure 22 | Occlusion Experiment with a masker width of “1”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.
+Supplementary Figure 22 | Occlusion Experiment with a masker width of “1”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
 
-Supplementary Figure 23 | Occlusion Experiment with a masker width of “3”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.
+Supplementary Figure 23 | Occlusion Experiment with a masker width of “3”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
 
-Supplementary Figure 24 | Occlusion Experiment with a masker width of “5”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.
+Supplementary Figure 24 | Occlusion Experiment with a masker width of “5”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
 
-Supplementary Figure 25 | Occlusion Experiment with a masker width of “11”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.
+Supplementary Figure 25 | Occlusion Experiment with a masker width of “11”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
 
-Supplementary Figure 26 | Occlusion Experiment with a masker width of “21”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.
+Supplementary Figure 26 | Occlusion Experiment with a masker width of “21”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
 
-Supplementary Figure 27 | Occlusion Experiment with a masker width of “31”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.
+Supplementary Figure 27 | Occlusion Experiment with a masker width of “31”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
 
-Supplementary Figure 28 | Occlusion Experiment with a masker width of “41”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.
+Supplementary Figure 28 | Occlusion Experiment with a masker width of “41”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
 
-Supplementary Figure 29 | Occlusion Experiment with a masker width of “51”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C3N4.
+Supplementary Figure 29 | Occlusion Experiment with a masker width of “51”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
 
@@
 Supplementary Figure 31 | Shifting Experiment on p orbital.
-Effect of orbital shifting on CO adsorption energy, predicted by the CNN model, for single metal atom catalysts supported on g-C3N4.
+Effect of orbital shifting on CO adsorption energy, predicted by the CNN model, for single metal atom catalysts supported on g-C$_3$N$_4$.
 The perturbations caused by shifting of entire p orbital are presented.

### 2024-01-05 paper/si_sections/3_others.tex
get tables for cleaning up

@@
 
-The hyperparameter optimization for the proposed CNN model was performed using NVIDIA® V100 Tensor Core GPUs, courtesy of the Australian National Computational Infrastructure's (NCI) HPC Gadi system.
+The hyperparameter optimization for the proposed CNN model was performed using NVIDIA$^{\textregistered}$ (TODO:) V100 Tensor Core GPUs, courtesy of the Australian National Computational Infrastructure's (NCI) HPC Gadi system.
 The HyperBand algorithm \cite{li2018hyperband}, as implemented in KerasTuner \cite{omalley2019kerastuner} , facilitated the tuning process.
 
-Supplementary Table 19
-Core packages in deep learning environment
+% Supplementary Table 19
+\begin{table}[h]
+    \centering
+    \begin{tabular}{lr}
+      \hline
       Name	Version	Build	Channel
+      \hline
       conda	4.13.0	py39h06a4308_0	anaconda
@@
       yaml	0.2.5	h7b6447c_0	anaconda
+      \hline
+    \end{tabular}
+    \caption{Core packages in deep learning environment}
+    \label{si_table19}
+\end{table}
 Note. The complete list of packages is provided along with the source code.
@@
 
-Supplementary Table 20
-Core packages in data analysis and visualization environment
+% Supplementary Table 20
+\begin{table}[h]
+    \centering
+    \begin{tabular}{lr}
+      \hline
       Name	Version	Build	Channel
+      \hline
       bokeh	3.2.2	pypi_0	pypi
@@
       tensorflow-macos	2.13.0	pypi_0	pypi
+      \hline
+    \end{tabular}
+    \caption{Core packages in data analysis and visualization environment}
+    \label{si_table20}
+\end{table}
 Note. The complete list of packages is provided along with the source code.

### 2024-01-05 paper/si_sections/2_ml.tex
fix table formats (to be finished)

@@
 % Supplementary Table 15
+% TODO: buggy format
 \begin{table}[h]
   \centering
-    \begin{tabular}{lr}
+  \begin{tabular}{p{3cm} p{11cm}}
     \hline
-      Elementary Descriptors	Electronic Descriptors
+    \textbf{Elementary Descriptors} & \textbf{Electronic Descriptors} \\
     \hline
-      R	atomic radius	α, β, γ	lattice parameters
-      Eea	electron affinity	ΦDFT	DFT calculated work function
-      Φ	work function	Evac	vacuum level
-      XAllen, ΧP, ΧRevP	electronegativity in Allen, Pauling and revised Pauling scales	Eg, Eg↑, Eg↓	average, spin-up and spin-down band gaps
-      Ar	relative atomic mass	ed	number of d-electrons
-      Ei	ionisation energy	δεd↑	d-band centre (spin-up)
-      G	group number	Wd	d-band width
-      P	period number	eBader	Bader charge
-      V	number of valence electrons
+    R                 & atomic radius \quad α, β, γ & lattice parameters \\
+    Eea               & electron affinity \quad ΦDFT & DFT-calculated work function \\
+    Φ                 & work function \quad Evac & vacuum level \\
+    XAllen, ΧP, ΧRevP & electronegativity in Allen, Pauling, and revised Pauling scales \quad Eg, Eg↑, Eg↓ & average, spin-up, and spin-down band gaps \\
+    Ar                & relative atomic mass \quad ed & number of d-electrons \\
+    Ei                & ionization energy \quad δεd↑ & d-band center (spin-up) \\
+    G                 & group number \quad Wd & d-band width \\
+    P                 & period number \quad eBader & Bader charge \\
+    V                 & number of valence electrons \\
     \hline
@@
   \centering
-    \begin{tabular}{lr}
+  \begin{tabular}{lrp{5.5cm}}
     \hline
-      Hyperparameter	Search space	Description
+    \textbf{Hyperparameter} & \textbf{Search Space}                             & \textbf{Description}            \\
     \hline
-      learningRate	[10-4, 10-2], logscale	Learning rate of Adam optimiser
-      dropoutRate	[0, 1]	Dropout rate
-      root_fc0	128, 256, 512	Output dimensionality of 1st fully connected layer in root
-      root_fc1	256, 512, 1024, 2048	Output dimensionality of 2nd fully connected layer in root
-      root_act	"tanh", "relu", "sigmoid"	Activation function of fully connected layers in root
-      kernelSize	[2, 32]	Width of convolution window
-      numFilters	[8, 64]	Number of filters in the convolution
-      numConvLayers	[1, 16]	Number of convolution layers
-      numConvBlocks	[1, 16]	Number of convolution blocks
-      br_fc0	16, 32, 64, 128, 256, 512	Output dimensionality of 1st fully connected layer in branch
-      br_fc1	8, 16, 32, 64, 128, 256	Output dimensionality of 2nd fully connected layer in branch
-      br_act	"tanh", "relu", "sigmoid"	Activation function of fully connected layers in branch
+    learningRate  & [10\textsuperscript{-4}, 10\textsuperscript{-2}], log scale & Learning rate of Adam optimizer \\
+    dropoutRate   & [0, 1]                    & Dropout rate                                                      \\
+    root\_fc0     & 128, 256, 512             & Output dimensionality of 1st fully connected layer in root        \\
+    root\_fc1     & 256, 512, 1024, 2048      & Output dimensionality of 2nd fully connected layer in root        \\
+    root\_act     & "tanh", "relu", "sigmoid" & Activation function of fully connected layers in root             \\
+    kernelSize    & [2, 32]                   & Width of the convolution window                                   \\
+    numFilters    & [8, 64]                   & Number of filters in the convolution                              \\
+    numConvLayers & [1, 16]                   & Number of convolution layers                                      \\
+    numConvBlocks & [1, 16]                   & Number of convolution blocks                                      \\
+    br\_fc0       & 16, 32, 64, 128, 256, 512 & Output dimensionality of 1st fully connected layer in branch      \\
+    br\_fc1       & 8, 16, 32, 64, 128, 256   & Output dimensionality of 2nd fully connected layer in branch      \\
+    br\_act       & "tanh", "relu", "sigmoid" & Activation function of fully connected layers in branch           \\
     \hline
   \end{tabular}
-    \caption{The hyperparameter searching space}
+  \caption{The hyperparameter search space}
   \label{si_table16}
@@
   \centering
-    \begin{tabular}{lr}
+  \begin{tabular}{lrp{5.5cm}}
     \hline
-      Hyperparameter	Optimal value	Description
+    \textbf{Hyperparameter}   & \textbf{Optimal Value} & \textbf{Description}                \\
     \hline
-      learningRate	10-3	Learning rate of Adam optimiser
-      dropoutRate	0.3	Dropout rate
-      root_fc0	256	Output dimensionality of 1st fully connected layer in root
-      root_fc1	512	Output dimensionality of 2nd fully connected layer in root
-      root_act	“relu”	Activation function of fully connected layers in root
-      kernelSize	10	Width of convolution window
-      numFilters	17	Number of filters in the convolution
-      numConvLayers	3	Number of convolution layers
-      numConvBlocks	1	Number of convolution blocks
-      br_fc0	256	Output dimensionality of 1st fully connected layer in branch
-      br_fc1	128	Output dimensionality of 2nd fully connected layer in branch
-      br_act	“tanh”	Activation function of fully connected layers in branch
+    learningRate  & $10^{-3}$ & Learning rate of Adam optimizer                              \\
+    dropoutRate   & 0.3       & Dropout rate                                                 \\
+    root\_fc0     & 256       & Output dimensionality of 1st fully connected layer in root   \\
+    root\_fc1     & 512       & Output dimensionality of 2nd fully connected layer in root   \\
+    root\_act     & "relu"    & Activation function of fully connected layers in root        \\
+    kernelSize    & 10        & Width of convolution window                                  \\
+    numFilters    & 17        & Number of filters in the convolution                         \\
+    numConvLayers & 3         & Number of convolution layers                                 \\
+    numConvBlocks & 1         & Number of convolution blocks                                 \\
+    br\_fc0       & 256       & Output dimensionality of 1st fully connected layer in branch \\
+    br\_fc1       & 128       & Output dimensionality of 2nd fully connected layer in branch \\
+    br\_act       & "tanh"    & Activation function of fully connected layers in branch      \\
     \hline
@@
   \centering
-    \begin{tabular}{lr}
+  \begin{tabular}{lrr}
     \hline
-      Adsorbate	Original dataset (eV)	Augmented dataset (eV)
+    \textbf{Adsorbate} & \textbf{Original dataset (eV)} & \textbf{Augmented dataset (eV)} \\
     \hline
-      CO2	0.0447	0.0336
-      COOH	0.0436	0.0581
-      CO	0.0402	0.0402
-      CHO	0.0614	0.0778
-      CH2O	0.0553	0.0632
-      OCH3	0.0605	0.0636
-      O	0.1135	0.1081
-      OH	0.0547	0.0602
-      H	0.0703	0.0646
+    CO$_2$  & 0.0447 & 0.0336 \\
+    COOH    & 0.0436 & 0.0581 \\
+    CO      & 0.0402 & 0.0402 \\
+    CHO     & 0.0614 & 0.0778 \\
+    CH$_2$O & 0.0553 & 0.0632 \\
+    OCH$_3$ & 0.0605 & 0.0636 \\
+    O       & 0.1135 & 0.1081 \\
+    OH      & 0.0547 & 0.0602 \\
+    H       & 0.0703 & 0.0646 \\
     \hline
@@
 \end{table}
+
 Note.

### 2024-01-05 paper/si_sections/3_others.tex
fix table formats (to be finished)

@@
   \centering
-    \begin{tabular}{lr}
+  \begin{tabular}{l l l l}
     \hline
-      Name	Version	Build	Channel
+    Name                & Version & Build          & Channel     \\
     \hline
-      conda	4.13.0	py39h06a4308_0	anaconda
-      cuda-nvcc	11.8.89	0	nvidia
-      cuda-toolkit	11.8.0	0	nvidia
-      cudatoolkit	11.6.0	habf752d_9	nvidia
-      ipykernel	6.9.1	py39h06a4308_0	anaconda
-      ipython	7.34.0	pypi_0	pypi
-      jupyter_client	7.2.2	py39h06a4308_0	anaconda
-      jupyterlab	3.4.4	py39h06a4308_0	anaconda
-      keras	2.9.0	pypi_0	pypi
-      keras-preprocessing	1.1.2	pypi_0	pypi
-      keras-tuner	1.3.5		pypi
-      matplotlib	3.5.1	py39h06a4308_1	anaconda
-      numpy	1.22.4	pypi_0	pypi
-      pandas	1.3.4	py39h8c16a72_0	anaconda
-      python	3.9.12	h12debd9_1	anaconda
-      scikit-learn	1.1.1	py39h6a678d5_0	anaconda
-      scipy	1.8.1	py39hddc5342_3	conda-forge
-      tensorboard	2.9.1	pypi_0	pypi
-      tensorflow	2.9.3	pypi_0	pypi
-      tensorflow-gpu	2.9.3	pypi_0	pypi
-      xlrd	2.0.1	pyhd3eb1b0_0	anaconda
-      yaml	0.2.5	h7b6447c_0	anaconda
+    conda               & 4.13.0  & py39h06a4308_0 & anaconda    \\
+    cuda-nvcc           & 11.8.89 & 0              & nvidia      \\
+    cuda-toolkit        & 11.8.0  & 0              & nvidia      \\
+    cudatoolkit         & 11.6.0  & habf752d_9     & nvidia      \\
+    ipykernel           & 6.9.1   & py39h06a4308_0 & anaconda    \\
+    ipython             & 7.34.0  & pypi_0         & pypi        \\
+    jupyter\_client     & 7.2.2   & py39h06a4308_0 & anaconda    \\
+    jupyterlab          & 3.4.4   & py39h06a4308_0 & anaconda    \\
+    keras               & 2.9.0   & pypi_0         & pypi        \\
+    keras-preprocessing & 1.1.2   & pypi_0         & pypi        \\
+    keras-tuner         & 1.3.5   &                & pypi        \\
+    matplotlib          & 3.5.1   & py39h06a4308_1 & anaconda    \\
+    numpy               & 1.22.4  & pypi_0         & pypi        \\
+    pandas              & 1.3.4   & py39h8c16a72_0 & anaconda    \\
+    python              & 3.9.12  & h12debd9_1     & anaconda    \\
+    scikit-learn        & 1.1.1   & py39h6a678d5_0 & anaconda    \\
+    scipy               & 1.8.1   & py39hddc5342_3 & conda-forge \\
+    tensorboard         & 2.9.1   & pypi_0         & pypi        \\
+    tensorflow          & 2.9.3   & pypi_0         & pypi        \\
+    tensorflow-gpu      & 2.9.3   & pypi_0         & pypi        \\
+    xlrd                & 2.0.1   & pyhd3eb1b0_0   & anaconda    \\
+    yaml                & 0.2.5   & h7b6447c_0     & anaconda    \\
     \hline
   \end{tabular}
-    \caption{Core packages in deep learning environment}
+  \caption{Core packages in the deep learning environment}
   \label{si_table19}
@@
   \centering
-    \begin{tabular}{lr}
+  \begin{tabular}{l l l l}
     \hline
-      Name	Version	Build	Channel
+    Name             & Version & Build      & Channel \\
     \hline
-      bokeh	3.2.2	pypi_0	pypi
-      colorcet	3.0.1	pypi_0	pypi
-      heatmapz	0.0.4	pypi_0	pypi
-      keras	2.13.1	pypi_0	pypi
-      keras-tuner	1.3.5	pypi_0	pypi
-      matplotlib	3.7.2	pypi_0	pypi
-      numpy	1.24.3	pypi_0	pypi
-      pandas	2.0.3	pypi_0	pypi
-      python	3.11.4	hb885b13_0
-      pyyaml	6.0.1	pypi_0	pypi
-      scikit-learn	1.3.0	pypi_0	pypi
-      scipy	1.11.1	pypi_0	pypi
-      seaborn	0.12.2	pypi_0	pypi
-      tensorboard	2.13.0	pypi_0	pypi
-      tensorflow	2.13.0	pypi_0	pypi
-      tensorflow-macos	2.13.0	pypi_0	pypi
+    bokeh            & 3.2.2   & pypi_0     & pypi    \\
+    colorcet         & 3.0.1   & pypi_0     & pypi    \\
+    heatmapz         & 0.0.4   & pypi_0     & pypi    \\
+    keras            & 2.13.1  & pypi_0     & pypi    \\
+    keras-tuner      & 1.3.5   & pypi_0     & pypi    \\
+    matplotlib       & 3.7.2   & pypi_0     & pypi    \\
+    numpy            & 1.24.3  & pypi_0     & pypi    \\
+    pandas           & 2.0.3   & pypi_0     & pypi    \\
+    python           & 3.11.4  & hb885b13_0 &         \\
+    pyyaml           & 6.0.1   & pypi_0     & pypi    \\
+    scikit-learn     & 1.3.0   & pypi_0     & pypi    \\
+    scipy            & 1.11.1  & pypi_0     & pypi    \\
+    seaborn          & 0.12.2  & pypi_0     & pypi    \\
+    tensorboard      & 2.13.0  & pypi_0     & pypi    \\
+    tensorflow       & 2.13.0  & pypi_0     & pypi    \\
+    tensorflow-macos & 2.13.0  & pypi_0     & pypi    \\
     \hline
   \end{tabular}
-    \caption{Core packages in data analysis and visualization environment}
+  \caption{Core packages in the data analysis and visualization environment}
   \label{si_table20}

### 2024-01-06 paper/main_sections/3_introduction.tex
add cross-ref in main text
revise fig names

@@
     \centering
-    \includegraphics[width=0.95\linewidth]{main_sections/figures/figure_1.png}
+    \includegraphics[width=0.95\linewidth]{main_sections/figures/main_fig1_pipeline.JPG}
     \caption{\textbf{Catalyst Performance Analysis Pipeline Integrating Volcano Plots and CNN.}
@@
 
-In this study, we introduced a catalyst performance analysis pipeline (Figure 1) integrating a customized CNN model and volcano plots.
+In this study, we introduced a catalyst performance analysis pipeline (\cref{main_fig1:pipeline}) integrating a customized CNN model and volcano plots.
 Our CNN model accurately estimated the adsorption energies, the activity descriptor, from the eDOS of 2D materials supported single metal catalysts.

### 2024-01-06 paper/si_sections/2_ml.tex
make all tables left aligned
break some long lines
fix symbol/table format

@@
 % Supplementary Table 15
-% TODO: buggy format
 \begin{table}[h]
   \centering
-  \begin{tabular}{p{3cm} p{11cm}}
+  \begin{tabular}{llll}
     \hline
-    \textbf{Elementary Descriptors} & \textbf{Electronic Descriptors} \\
+    \multicolumn{2}{c}{Elementary Descriptors}       & \multicolumn{2}{c}{Electronic Descriptors}            \\
     \hline
-    R                 & atomic radius \quad α, β, γ & lattice parameters \\
-    Eea               & electron affinity \quad ΦDFT & DFT-calculated work function \\
-    Φ                 & work function \quad Evac & vacuum level \\
-    XAllen, ΧP, ΧRevP & electronegativity in Allen, Pauling, and revised Pauling scales \quad Eg, Eg↑, Eg↓ & average, spin-up, and spin-down band gaps \\
-    Ar                & relative atomic mass \quad ed & number of d-electrons \\
-    Ei                & ionization energy \quad δεd↑ & d-band center (spin-up) \\
-    G                 & group number \quad Wd & d-band width \\
-    P                 & period number \quad eBader & Bader charge \\
-    V                 & number of valence electrons \\
+    $R$            & atomic radius                   & $\alpha$, $\beta$, $\gamma$  & lattice parameters     \\
+    $E_\text{ea}$  & electron affinity               & $\Phi_{\text{DFT}}$    & DFT calculated work function \\
+    $\Phi$         & work function                   & $E_\text{vac}$         & vacuum level                 \\
+    $\chi_\text{Allen}$, $\chi_\text{P}$, $\chi_\text{RevP}$
+    & \parbox[t]{4cm}{electronegativity in Allen, Pauling and revised Pauling scales}
+    & $E_\text{g}$, $E_\text{g}\uparrow$, $E_\text{g}\uparrow$
+    & \parbox[t]{4cm}{average, spin-up and spin-down band gaps} \\
+    $A_\text{r}$   & relative atomic mass            & $e_\text{d}$           & number of d-electrons        \\
+    $E_\text{i}$   & ionization energy & $\delta\epsilon_{\text{d}}\uparrow$  & d-band centre (spin-up)      \\
+    $G$            & group number                    & $W_\text{d}$           & d-band width                 \\
+    $P$            & period number                   & $e_{\text{Bader}}$     & Bader charge                 \\
+    $V$            & number of valence electrons     &                        &
     \hline
@@
 In this study, the array adopts a shape of [numSamplings, numOrbitals, numChannels], as illustrated in Supplementary Figure 20.
-Here, “numSamplings” represents the number of data points sampled across the energy spectrum, “numOrbitals” denotes the number of DOS orbitals, and “numChannels” indicates the number of atomic channels.
+Here, “numSamplings” represents the number of data points sampled across the energy spectrum,
+“numOrbitals” denotes the number of DOS orbitals,
+and “numChannels” indicates the number of atomic channels.
 
@@
 
-For practical purposes, certain spatial hierarchies are expected to remain invariant, such as the energy range over which the eDOS is sampled.
-In this work, we maintain a consistent energy range of -14 eV to 6 eV, sampled at a density of 50 points⋅eV-1.
-In addition to maintaining a fixed energy range, the following steps are taken to standardize the input eDOS data:
+For practical purposes, certain spatial hierarchies are expected to remain invariant,
+such as the energy range over which the eDOS is sampled.
+In this work, we maintain a consistent energy range of -14 eV to 6 eV,
+sampled at a density of 50 points⋅eV-1.
+In addition to maintaining a fixed energy range,
+the following steps are taken to standardize the input eDOS data:
   1.	For atoms lacking d-electrons, the eDOS is zero-padded.
@@
   \centering
-  \begin{tabular}{lrp{5.5cm}}
+  \begin{tabular}{lll}
     \hline
@@
   \centering
-  \begin{tabular}{lrr}
+  \begin{tabular}{lll}
     \hline

### 2024-01-06 paper/si_sections/3_others.tex
make all tables left aligned
break some long lines
fix symbol/table format

@@
 
-The hyperparameter optimization for the proposed CNN model was performed using NVIDIA$^{\textregistered}$ (TODO:) V100 Tensor Core GPUs, courtesy of the Australian National Computational Infrastructure's (NCI) HPC Gadi system.
+The hyperparameter optimization for the proposed CNN model was performed using NVIDIA\textsuperscript{\textregistered} V100 Tensor Core GPUs,
+courtesy of the Australian National Computational Infrastructure's (NCI) HPC Gadi system.
 The HyperBand algorithm \cite{li2018hyperband}, as implemented in KerasTuner \cite{omalley2019kerastuner} , facilitated the tuning process.
@@
   \centering
-  \begin{tabular}{l l l l}
+  \begin{tabular}{llll}
     \hline
@@
 Data analysis and visualization tasks were executed on an Apple MacBook Air featuring an octa-core M2 chip.
-For accuracy, the TensorFlow-Metal plugin for Mac-based GPU acceleration was deliberately excluded, as it could potentially yield erroneous CNN model predictions.
+For accuracy, the TensorFlow-Metal plugin for Mac-based GPU acceleration was deliberately excluded,
+as it could potentially yield erroneous CNN model predictions.
 
-The illustrations of CNN architecture displayed in Figure 1 of the main text, as well as  Supplementary Figure 21 and Supplementary Figure 30, were obtained from the GitHub repository dair-ai/ml-visuals \cite{Saravia_ML_Visuals_2021}.
+The illustrations of CNN architecture displayed in Figure 1 of the main text,
+as well as  Supplementary Figure 21 and Supplementary Figure 30,
+were obtained from the GitHub repository dair-ai/ml-visuals \cite{Saravia_ML_Visuals_2021}.
 Blender was used to create and render the visual representation of the catalyst analysis pipeline shown in Figure 1 of the main text.

### 2024-01-06 paper/si_sections/2_ml.tex
reposition table footnotes

@@
   \caption{Prediction mean absolute errors of the CNN model}
+  \tablefootnote{The same CNN model, trained on the augmented dataset, was used for all predictions.
+  The term “original dataset” refers to evaluations conducted on the original dataset without any augmented data;
+  it does not imply the use of a different CNN model trained solely on the original dataset.
+  Similarly, “augmented dataset” refers to evaluations on the dataset with both original data and augment data,
+  not a distinct model.}
   \label{si_table18}
 \end{table}
-
-Note.
-The same CNN model, trained on the augmented dataset, was used for all predictions.
-The term “Original dataset” refers to evaluations conducted on the original dataset without any augmented data; it does not imply the use of a different CNN model trained solely on the original dataset.
-Similarly, “Augmented dataset” refers to evaluations on the dataset with both original data and augment data, not a distinct model.
 

### 2024-01-06 paper/si_sections/2_ml.tex
more format fixes

@@
     $P$            & period number                   & $e_{\text{Bader}}$     & Bader charge                 \\
-    $V$            & number of valence electrons     &                        &
+    $V$            & number of valence electrons     &                        &                              \\
     \hline
@@
 In this work, we maintain a consistent energy range of -14 eV to 6 eV,
-sampled at a density of 50 points⋅eV-1.
+sampled at a density of 50 points * eV-1 (TODO: format).
 In addition to maintaining a fixed energy range,

### 2024-01-06 paper/si_sections/3_others.tex
reposition table footnotes
more format fixes

@@
     \hline
-    conda               & 4.13.0  & py39h06a4308_0 & anaconda    \\
+    conda               & 4.13.0  & py39h06a4308\textunderscore0 & anaconda    \\
     cuda-nvcc           & 11.8.89 & 0                            & nvidia      \\
     cuda-toolkit        & 11.8.0  & 0                            & nvidia      \\
-    cudatoolkit         & 11.6.0  & habf752d_9     & nvidia      \\
-    ipykernel           & 6.9.1   & py39h06a4308_0 & anaconda    \\
-    ipython             & 7.34.0  & pypi_0         & pypi        \\
-    jupyter\_client     & 7.2.2   & py39h06a4308_0 & anaconda    \\
-    jupyterlab          & 3.4.4   & py39h06a4308_0 & anaconda    \\
-    keras               & 2.9.0   & pypi_0         & pypi        \\
-    keras-preprocessing & 1.1.2   & pypi_0         & pypi        \\
+    cudatoolkit         & 11.6.0  & habf752d\textunderscore9     & nvidia      \\
+    ipykernel           & 6.9.1   & py39h06a4308\textunderscore0 & anaconda    \\
+    ipython             & 7.34.0  & pypi\textunderscore0         & pypi        \\
+    jupyter\_client     & 7.2.2   & py39h06a4308\textunderscore0 & anaconda    \\
+    jupyterlab          & 3.4.4   & py39h06a4308\textunderscore0 & anaconda    \\
+    keras               & 2.9.0   & pypi\textunderscore0         & pypi        \\
+    keras-preprocessing & 1.1.2   & pypi\textunderscore0         & pypi        \\
     keras-tuner         & 1.3.5   &                              & pypi        \\
-    matplotlib          & 3.5.1   & py39h06a4308_1 & anaconda    \\
-    numpy               & 1.22.4  & pypi_0         & pypi        \\
-    pandas              & 1.3.4   & py39h8c16a72_0 & anaconda    \\
-    python              & 3.9.12  & h12debd9_1     & anaconda    \\
-    scikit-learn        & 1.1.1   & py39h6a678d5_0 & anaconda    \\
-    scipy               & 1.8.1   & py39hddc5342_3 & conda-forge \\
-    tensorboard         & 2.9.1   & pypi_0         & pypi        \\
-    tensorflow          & 2.9.3   & pypi_0         & pypi        \\
-    tensorflow-gpu      & 2.9.3   & pypi_0         & pypi        \\
-    xlrd                & 2.0.1   & pyhd3eb1b0_0   & anaconda    \\
-    yaml                & 0.2.5   & h7b6447c_0     & anaconda    \\
+    matplotlib          & 3.5.1   & py39h06a4308\textunderscore1 & anaconda    \\
+    numpy               & 1.22.4  & pypi\textunderscore0         & pypi        \\
+    pandas              & 1.3.4   & py39h8c16a72\textunderscore0 & anaconda    \\
+    python              & 3.9.12  & h12debd9\textunderscore1     & anaconda    \\
+    scikit-learn        & 1.1.1   & py39h6a678d5\textunderscore0 & anaconda    \\
+    scipy               & 1.8.1   & py39hddc5342\textunderscore3 & conda-forge \\
+    tensorboard         & 2.9.1   & pypi\textunderscore0         & pypi        \\
+    tensorflow          & 2.9.3   & pypi\textunderscore0         & pypi        \\
+    tensorflow-gpu      & 2.9.3   & pypi\textunderscore0         & pypi        \\
+    xlrd                & 2.0.1   & pyhd3eb1b0\textunderscore0   & anaconda    \\
+    yaml                & 0.2.5   & h7b6447c\textunderscore0     & anaconda    \\
     \hline
@@
   \caption{Core packages in the deep learning environment}
+  \tablefootnote{The complete list of packages is provided along with the source code.}
   \label{si_table19}
 \end{table}
-Note. The complete list of packages is provided along with the source code.
 
@@
     \hline
-    bokeh            & 3.2.2   & pypi_0     & pypi    \\
-    colorcet         & 3.0.1   & pypi_0     & pypi    \\
-    heatmapz         & 0.0.4   & pypi_0     & pypi    \\
-    keras            & 2.13.1  & pypi_0     & pypi    \\
-    keras-tuner      & 1.3.5   & pypi_0     & pypi    \\
-    matplotlib       & 3.7.2   & pypi_0     & pypi    \\
-    numpy            & 1.24.3  & pypi_0     & pypi    \\
-    pandas           & 2.0.3   & pypi_0     & pypi    \\
-    python           & 3.11.4  & hb885b13_0 &         \\
-    pyyaml           & 6.0.1   & pypi_0     & pypi    \\
-    scikit-learn     & 1.3.0   & pypi_0     & pypi    \\
-    scipy            & 1.11.1  & pypi_0     & pypi    \\
-    seaborn          & 0.12.2  & pypi_0     & pypi    \\
-    tensorboard      & 2.13.0  & pypi_0     & pypi    \\
-    tensorflow       & 2.13.0  & pypi_0     & pypi    \\
-    tensorflow-macos & 2.13.0  & pypi_0     & pypi    \\
+    bokeh            & 3.2.2   & pypi\textunderscore0     & pypi    \\
+    colorcet         & 3.0.1   & pypi\textunderscore0     & pypi    \\
+    heatmapz         & 0.0.4   & pypi\textunderscore0     & pypi    \\
+    keras            & 2.13.1  & pypi\textunderscore0     & pypi    \\
+    keras-tuner      & 1.3.5   & pypi\textunderscore0     & pypi    \\
+    matplotlib       & 3.7.2   & pypi\textunderscore0     & pypi    \\
+    numpy            & 1.24.3  & pypi\textunderscore0     & pypi    \\
+    pandas           & 2.0.3   & pypi\textunderscore0     & pypi    \\
+    python           & 3.11.4  & hb885b13\textunderscore0 &         \\
+    pyyaml           & 6.0.1   & pypi\textunderscore0     & pypi    \\
+    scikit-learn     & 1.3.0   & pypi\textunderscore0     & pypi    \\
+    scipy            & 1.11.1  & pypi\textunderscore0     & pypi    \\
+    seaborn          & 0.12.2  & pypi\textunderscore0     & pypi    \\
+    tensorboard      & 2.13.0  & pypi\textunderscore0     & pypi    \\
+    tensorflow       & 2.13.0  & pypi\textunderscore0     & pypi    \\
+    tensorflow-macos & 2.13.0  & pypi\textunderscore0     & pypi    \\
     \hline
@@
   \caption{Core packages in the data analysis and visualization environment}
+  \tablefootnote{The complete list of packages is provided along with the source code.}
   \label{si_table20}
 \end{table}
-Note. The complete list of packages is provided along with the source code.

### 2024-01-07 paper/si_sections/2_ml.tex
prepare figure  headers

@@
 
+% SI Figure 18: d-band venter vs adsorption energy scatter plot
 Supplementary Figure 18 | Scatter plot of d-Band Center and Adsorption Energy Relationships.
@@
 
+% SI Figure 19: Pairwise plot of adsorption energy vs key descriptors
 Supplementary Figure 19 | Pairwise Plot of Adsorption Energy and Key Descriptors.
@@
 
-% Supplementary Table 15
+% Supplementary Table 15: TODO: revise header comment
 \begin{table}[h]
@@
 
+% SI Figure 20: Representation of the input eDOS data structure
 Supplementary Figure 20 | Schematic representation of the input eDOS data structure.
@@
 
-Supplementary Figure 21 | Illustration of the occlusion experiment.
+% SI Figure 21: Illustration of the eDOS occlusion experiment
+Supplementary Figure 21 | Illustration of the eDOS cclusion experiment.
 This figure demonstrates the step-by-step process of the occlusion experiment.
@@
 
+% SI Figure 22: Occlusion experiment with a masker width of 1
 Supplementary Figure 22 | Occlusion Experiment with a masker width of “1”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
 
+% SI Figure 23: Occlusion experiment with a masker width of 3
 Supplementary Figure 23 | Occlusion Experiment with a masker width of “3”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
 
+% SI Figure 24: Occlusion experiment with a masker width of 5
 Supplementary Figure 24 | Occlusion Experiment with a masker width of “5”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
 
+% SI Figure 25: Occlusion experiment with a masker width of 11
 Supplementary Figure 25 | Occlusion Experiment with a masker width of “11”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
 
+% SI Figure 26: Occlusion experiment with a masker width of 21
 Supplementary Figure 26 | Occlusion Experiment with a masker width of “21”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
 
+% SI Figure 27: Occlusion experiment with a masker width of 31
 Supplementary Figure 27 | Occlusion Experiment with a masker width of “31”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
 
+% SI Figure 28: Occlusion experiment with a masker width of 41
 Supplementary Figure 28 | Occlusion Experiment with a masker width of “41”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
 
+% SI Figure 29: Occlusion experiment with a masker width of 51
 Supplementary Figure 29 | Occlusion Experiment with a masker width of “51”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
@@
 
-Supplementary Figure 30 | Illustration of the shifting experiment.
+% SI Figure 30: Illustration of the eDOS shifting experiment
+Supplementary Figure 30 | Illustration of the eDOS shifting experiment.
 This figure illustrates the sequential stages of the shifting experiment.
@@
 
-Supplementary Figure 31 | Shifting Experiment on p orbital.
+% SI Figure 31: Shifting experiment on p orbital
+Supplementary Figure 31 | Shifting experiment on p orbital.
 Effect of orbital shifting on CO adsorption energy, predicted by the CNN model, for single metal atom catalysts supported on g-C$_3$N$_4$.

### 2024-01-07 paper/si_sections/2_ml.tex
insert SI figures

@@
 % SI Figure 18: d-band venter vs adsorption energy scatter plot
-Supplementary Figure 18 | Scatter plot of d-Band Center and Adsorption Energy Relationships.
-This figure delineates the relationship between d-band center and adsorption energies for various species: (a) CO2, (b) COOH, (c) CO, (d) CHO, (e) CH2O, (f) OCH3, (g) O, and (h) OH.
-Data from all six substrates investigated in this study are included.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig18_d-band_eads.png}
+  \caption{\textbf{Scatter plot of d-Band Center and Adsorption Energy Relationships.}
+  This figure delineates the relationship between d-band center and adsorption energies for
+  various species: (a) CO$_2$, (b) COOH, (c) CO, (d) CHO, (e) CH$_2$O, (f) OCH$_3$, (g) O, and (h) OH.
+  Data from all six substrates investigated in this study are included.}
+  \label{si_fig18:dband_vs_eads}
+\end{figure}
 
@@
 % SI Figure 19: Pairwise plot of adsorption energy vs key descriptors
-Supplementary Figure 19 | Pairwise Plot of Adsorption Energy and Key Descriptors.
-This chart displays the pairwise relationships between CO adsorption energy and its four most correlated descriptors-d-band center (spin-up) δεd↑, lattice parameter γ, vacuum level Evac, and electronegativity on the Allen scale XAllen -as identified by Kendall rank correlation analysis.
-Data from all six substrates investigated in this study are incorporated.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig19_pairwise_eads_des.png}
+  \caption{\textbf{Pairwise Plot of Adsorption Energy and Key Descriptors.}
+  This chart displays the pairwise relationships between CO adsorption energy and
+  its four most correlated descriptors: d-band center (spin-up) $\delta\epsilon_{\text{d}}\uparrow$,
+  lattice parameter $\gamma$, vacuum level $E_\text{vac}$, and electronegativity
+  on the Allen scale $\chi_\text{Allen}$, identified by Kendall rank correlation analysis.
+  Data from all six substrates investigated in this study are included.}
+  \label{si_fig19:pairwise_eads_des}
+\end{figure}
 
-% Supplementary Table 15: TODO: revise header comment
+% Supplementary Table 15: Notations for elementary descriptors and electronic descriptors
 \begin{table}[h]
@@
 % SI Figure 20: Representation of the input eDOS data structure
-Supplementary Figure 20 | Schematic representation of the input eDOS data structure.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig20_input_dos.png}
+  \caption{\textbf{Schematic representation of the input eDOS data structure.}}
+  \label{si_fig20:input_dos}
+\end{figure}
 
@@
 In this work, we maintain a consistent energy range of -14 eV to 6 eV,
-sampled at a density of 50 points * eV-1 (TODO: format).
+sampled at a density of 50 \si{\text{points} \cdot \text{eV}^{-1}}.
 In addition to maintaining a fixed energy range,
@@
   2.	f-orbital eDOS data are excluded.
-  3.	The eDOS of adsorbates is zero-padded along the Channels axis to align with the adsorbate that contains the maximum number of atoms, which, in this study, is the *OCH3 species.
+  3.	The eDOS of adsorbates is zero-padded along the Channels axis to align with the adsorbate that contains the maximum number of atoms, which, in this study, is the *OCH$_3$ species.
 This padded eDOS is then appended to the metal eDOS.
@@
 
-% Supplementary Table 16
+% Supplementary Table 16: The hyperparameter search space
 \begin{table}[h]
@@
 
-% Supplementary Table 17
+% Supplementary Table 17: Optimal hyperparameters identified with Hyperband algorithm
 \begin{table}[h]
@@
 
-% Supplementary Table 18
+% Supplementary Table 18: Prediction MAEs of the CNN model
 \begin{table}[h]
@@
 % SI Figure 21: Illustration of the eDOS occlusion experiment
-Supplementary Figure 21 | Illustration of the eDOS cclusion experiment.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig21_occlusion.png}
+  \caption{\textbf{Illustration of the eDOS occlusion experiment.}
   This figure demonstrates the step-by-step process of the occlusion experiment.
-The input eDOS array first undergoes zero-padded, and then a masker of width “width” is applied, resulting in an occlusion array that preserves the shape of the input array.
+  The input eDOS array first undergoes zero-padded, and then a masker of width “width” is applied,
+  resulting in an occlusion array that preserves the shape of the input array.}
+  \label{si_fig21:occlusion}
+\end{figure}
 
 % SI Figure 22: Occlusion experiment with a masker width of 1
-Supplementary Figure 22 | Occlusion Experiment with a masker width of “1”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig22_occl_wid1.png}
+  \caption{\textbf{Occlusion Experiment with a masker width of “1”.}
+  This figure shows an occlusion experiment on the Ge atom in
+  the initial state of CO adsorption on Ge@g-C$_3$N$_4$.}
+  \label{si_fig22:occl_wid1}
+\end{figure}
 
 % SI Figure 23: Occlusion experiment with a masker width of 3
-Supplementary Figure 23 | Occlusion Experiment with a masker width of “3”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig23_occl_wid3.png}
+  \caption{\textbf{Occlusion Experiment with a masker width of “3”.}
+  This figure shows an occlusion experiment on the Ge atom in
+  the initial state of CO adsorption on Ge@g-C$_3$N$_4$.}
+  \label{si_fig23:occl_wid3}
+\end{figure}
 
 % SI Figure 24: Occlusion experiment with a masker width of 5
-Supplementary Figure 24 | Occlusion Experiment with a masker width of “5”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig24_occl_wid5.png}
+  \caption{\textbf{Occlusion Experiment with a masker width of “5”.}
+  This figure shows an occlusion experiment on the Ge atom in
+  the initial state of CO adsorption on Ge@g-C$_3$N$_4$.}
+  \label{si_fig24:occl_wid5}
+\end{figure}
 
 % SI Figure 25: Occlusion experiment with a masker width of 11
-Supplementary Figure 25 | Occlusion Experiment with a masker width of “11”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig25_occl_wid11.png}
+  \caption{\textbf{Occlusion Experiment with a masker width of “11”.}
+  This figure shows an occlusion experiment on the Ge atom in
+  the initial state of CO adsorption on Ge@g-C$_3$N$_4$.}
+  \label{si_fig25:occl_wid11}
+\end{figure}
 
 % SI Figure 26: Occlusion experiment with a masker width of 21
-Supplementary Figure 26 | Occlusion Experiment with a masker width of “21”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig26_occl_wid21.png}
+  \caption{\textbf{Occlusion Experiment with a masker width of “21”.}
+  This figure shows an occlusion experiment on the Ge atom in
+  the initial state of CO adsorption on Ge@g-C$_3$N$_4$.}
+  \label{si_fig26:occl_wid21}
+\end{figure}
 
 % SI Figure 27: Occlusion experiment with a masker width of 31
-Supplementary Figure 27 | Occlusion Experiment with a masker width of “31”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig27_occl_wid31.png}
+  \caption{\textbf{Occlusion Experiment with a masker width of “31”.}
+  This figure shows an occlusion experiment on the Ge atom in
+  the initial state of CO adsorption on Ge@g-C$_3$N$_4$.}
+  \label{si_fig27:occl_wid31}
+\end{figure}
 
 % SI Figure 28: Occlusion experiment with a masker width of 41
-Supplementary Figure 28 | Occlusion Experiment with a masker width of “41”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig28_occl_wid41.png}
+  \caption{\textbf{Occlusion Experiment with a masker width of “41”.}
+  This figure shows an occlusion experiment on the Ge atom in
+  the initial state of CO adsorption on Ge@g-C$_3$N$_4$.}
+  \label{si_fig28:occl_wid41}
+\end{figure}
 
 % SI Figure 29: Occlusion experiment with a masker width of 51
-Supplementary Figure 29 | Occlusion Experiment with a masker width of “51”. This figure shows an occlusion experiment on the Ge atom in the initial state of CO adsorption on Ge@g-C$_3$N$_4$.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig29_occl_wid51.png}
+  \caption{\textbf{Occlusion Experiment with a masker width of “51”.}
+  This figure shows an occlusion experiment on the Ge atom in
+  the initial state of CO adsorption on Ge@g-C$_3$N$_4$.}
+  \label{si_fig29:occl_wid51}
+\end{figure}
 
@@
 % SI Figure 30: Illustration of the eDOS shifting experiment
-Supplementary Figure 30 | Illustration of the eDOS shifting experiment.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig30_shifting.png}
+  \caption{\textbf{Illustration of the eDOS shifting experiment.}
   This figure illustrates the sequential stages of the shifting experiment.
   Initially, the input eDOS array is shifted along the Energy axis.
-Subsequently, it undergoes zero-padding and cropping, ensuring a consistent shape based on the shifting direction, to match the input eDOS array.
-The resulting shifted array is then processed by the CNN model to assess the disturbance in adsorption energy caused by the shifting operation.
+  Subsequently, it undergoes zero-padding and cropping,
+  ensuring a consistent shape based on the shifting direction, to match the input eDOS array.
+  The resulting shifted array is then processed by the CNN model to
+  assess the disturbance in adsorption energy caused by the shifting operation.}
+  \label{si_fig30:shifting}
+\end{figure}
 
 % SI Figure 31: Shifting experiment on p orbital
-Supplementary Figure 31 | Shifting experiment on p orbital.
-Effect of orbital shifting on CO adsorption energy, predicted by the CNN model, for single metal atom catalysts supported on g-C$_3$N$_4$.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig31_p_shifting.png}
+  \caption{\textbf{Shifting experiment on p orbital.}
+  Effect of orbital shifting on CO adsorption energy, predicted by the CNN model,
+  for single metal atom catalysts supported on g-C$_3$N$_4$.
   The perturbations caused by shifting of entire p orbital are presented.
   The shifting step size corresponds to the energy resolution of the eDOS, set at 0.005 eV in this study.
-A positive eDOS shift indicates a shift towards higher energy levels, and vice versa.
+  A positive eDOS shift indicates a shift towards higher energy levels, and vice versa.}
+  \label{si_fig31:p_shifting}
+\end{figure}

### 2024-01-08 paper/si_sections/2_ml.tex
more table format fixes

@@
 % Supplementary Table 16: The hyperparameter search space
+% TODO: check adam citation
 \begin{table}[h]
@@
     \hline
-    learningRate  & [10\textsuperscript{-4}, 10\textsuperscript{-2}], log scale & Learning rate of Adam optimizer \\
+    learningRate  & [10\textsuperscript{-4}, 10\textsuperscript{-2}], log scale & Learning rate of Adam\cite{kingma2017adam} optimizer \\
     dropoutRate   & [0, 1]                    & Dropout rate                                                      \\
-    root\_fc0     & 128, 256, 512             & Output dimensionality of 1st fully connected layer in root        \\
-    root\_fc1     & 256, 512, 1024, 2048      & Output dimensionality of 2nd fully connected layer in root        \\
+    root\_fc0     & 128, 256, 512             & Output dimensionality of 1\textsuperscript{st} fully connected layer in root           \\
+    root\_fc1     & 256, 512, 1024, 2048      & Output dimensionality of 2\textsuperscript{nd} fully connected layer in root           \\
     root\_act     & "tanh", "relu", "sigmoid" & Activation function of fully connected layers in root             \\
@@
     numConvBlocks & [1, 16]                   & Number of convolution blocks                                      \\
-    br\_fc0       & 16, 32, 64, 128, 256, 512 & Output dimensionality of 1st fully connected layer in branch      \\
-    br\_fc1       & 8, 16, 32, 64, 128, 256   & Output dimensionality of 2nd fully connected layer in branch      \\
+    br\_fc0       & 16, 32, 64, 128, 256, 512 & Output dimensionality of 1\textsuperscript{st} fully connected layer in branch      \\
+    br\_fc1       & 8, 16, 32, 64, 128, 256   & Output dimensionality of 2\textsuperscript{nd} fully connected layer in branch      \\
     br\_act       & "tanh", "relu", "sigmoid" & Activation function of fully connected layers in branch           \\
@@
 % Supplementary Table 17: Optimal hyperparameters identified with Hyperband algorithm
+% TODO: check adam citation
 \begin{table}[h]
@@
     \hline
-    learningRate  & $10^{-3}$ & Learning rate of Adam optimizer                              \\
+    learningRate  & $10^{-3}$ & Learning rate of Adam\cite{kingma2017adam} optimizer                              \\
     dropoutRate   & 0.3       & Dropout rate                                                 \\
-    root\_fc0     & 256       & Output dimensionality of 1st fully connected layer in root   \\
-    root\_fc1     & 512       & Output dimensionality of 2nd fully connected layer in root   \\
+    root\_fc0     & 256       & Output dimensionality of 1\textsuperscript{st} fully connected layer in root   \\
+    root\_fc1     & 512       & Output dimensionality of 2\textsuperscript{nd} fully connected layer in root   \\
     root\_act     & "relu"    & Activation function of fully connected layers in root        \\
@@
     numConvBlocks & 1         & Number of convolution blocks                                 \\
-    br\_fc0       & 256       & Output dimensionality of 1st fully connected layer in branch \\
-    br\_fc1       & 128       & Output dimensionality of 2nd fully connected layer in branch \\
+    br\_fc0       & 256       & Output dimensionality of 1\textsuperscript{st} fully connected layer in branch \\
+    br\_fc1       & 128       & Output dimensionality of 2\textsuperscript{nd} fully connected layer in branch \\
     br\_act       & "tanh"    & Activation function of fully connected layers in branch      \\

### 2024-01-09 paper/main_sections/6_tail.tex
format tweaks

@@
 
-\section{Tail}
-
-\subsection{Data Availability}
+\section{Data Availability}
 Essential source data required to replicate the study's results-including VASP input files,
@@
 
-\subsection{Code Availability}
+\section{Code Availability}
 Associated computer code for this study can be accessed on GitHub at \url{https://github.com/DanielYang59/cnn4dos},
@@
 
- \subsection{Acknowledgements}
+\section{Acknowledgements}
 The QUT eResearch Office provided computational resources and services used in this work.
@@
 
-\subsection{Author Contributions}
+\section{Author Contributions}
 H.Y. performed DFT calculations, implemented Python code for machine learning methodologies and data analysis,
@@
 
-\subsection{Competing Interests}
+\section{Competing Interests}
 The authors declare no competing interests in relation to this research.

### 2024-01-09 paper/si_3_ml.tex
major cleanup: flat out dirs as per arxiv request

--- 2024-01-08 paper/si_sections/2_ml.tex
@@
-% Supporting Information Section Two: Additional details on ML Methods
+% SI Section Two: Additional details on Machine Learning
 
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig18_d-band_eads.png}
+  \includegraphics[width=0.8\linewidth]{si_fig18_d-band_eads.png}
   \caption{\textbf{Scatter plot of d-Band Center and Adsorption Energy Relationships.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig19_pairwise_eads_des.png}
+  \includegraphics[width=0.8\linewidth]{si_fig19_pairwise_eads_des.png}
   \caption{\textbf{Pairwise Plot of Adsorption Energy and Key Descriptors.}
@@
   \caption{Notations for elementary descriptors and electronic descriptors}
-  \label{si_table15}
+  \label{si_table15:descriptor_notations}
 \end{table}
@@
 The format of the 2D array for the eDOS is naturally well-suited for use as neural network inputs.
-In this study, the array adopts a shape of [numSamplings, numOrbitals, numChannels], as illustrated in Supplementary Figure 20.
+In this study, the array adopts a shape of [numSamplings, numOrbitals, numChannels], as illustrated in \cref{si_fig20:input_dos}.
 Here, “numSamplings” represents the number of data points sampled across the energy spectrum,
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig20_input_dos.png}
+  \includegraphics[width=0.8\linewidth]{si_fig20_input_dos.png}
   \caption{\textbf{Schematic representation of the input eDOS data structure.}}
@@
   \caption{The hyperparameter search space}
-  \label{si_table16}
+  \label{si_table16:hyperparam_space}
 \end{table}
@@
   \caption{Optimal hyperparameters identified with Hyperband algorithm}
-  \label{si_table17}
+  \label{si_table17:opt_hyperparam}
 \end{table}
@@
   not a distinct model.}
-  \label{si_table18}
+  \label{si_table18:cnn_mae}
 \end{table}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig21_occlusion.png}
+  \includegraphics[width=0.8\linewidth]{si_fig21_occlusion.png}
   \caption{\textbf{Illustration of the eDOS occlusion experiment.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig22_occl_wid1.png}
+  \includegraphics[width=0.8\linewidth]{si_fig22_occl_wid1.png}
   \caption{\textbf{Occlusion Experiment with a masker width of “1”.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig23_occl_wid3.png}
+  \includegraphics[width=0.8\linewidth]{si_fig23_occl_wid3.png}
   \caption{\textbf{Occlusion Experiment with a masker width of “3”.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig24_occl_wid5.png}
+  \includegraphics[width=0.8\linewidth]{si_fig24_occl_wid5.png}
   \caption{\textbf{Occlusion Experiment with a masker width of “5”.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig25_occl_wid11.png}
+  \includegraphics[width=0.8\linewidth]{si_fig25_occl_wid11.png}
   \caption{\textbf{Occlusion Experiment with a masker width of “11”.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig26_occl_wid21.png}
+  \includegraphics[width=0.8\linewidth]{si_fig26_occl_wid21.png}
   \caption{\textbf{Occlusion Experiment with a masker width of “21”.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig27_occl_wid31.png}
+  \includegraphics[width=0.8\linewidth]{si_fig27_occl_wid31.png}
   \caption{\textbf{Occlusion Experiment with a masker width of “31”.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig28_occl_wid41.png}
+  \includegraphics[width=0.8\linewidth]{si_fig28_occl_wid41.png}
   \caption{\textbf{Occlusion Experiment with a masker width of “41”.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig29_occl_wid51.png}
+  \includegraphics[width=0.8\linewidth]{si_fig29_occl_wid51.png}
   \caption{\textbf{Occlusion Experiment with a masker width of “51”.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig30_shifting.png}
+  \includegraphics[width=0.8\linewidth]{si_fig30_shifting.png}
   \caption{\textbf{Illustration of the eDOS shifting experiment.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_sections/si_figures/si_fig31_p_shifting.png}
+  \includegraphics[width=0.8\linewidth]{si_fig31_p_shifting.png}
   \caption{\textbf{Shifting experiment on p orbital.}

### 2024-01-09 paper/si_4_others.tex
major cleanup: flat out dirs as per arxiv request

--- 2024-01-06 paper/si_sections/3_others.tex
@@
-% Supporting Information Section Three: Other Additional Information
+% SI Section Three: Other Additional Information
 
@@
 
-% Supplementary Table 19
+% Supplementary Table 19: Packages in the DL env
 \begin{table}[h]
@@
   \tablefootnote{The complete list of packages is provided along with the source code.}
-  \label{si_table19}
+  \label{si_table19:pack_dl_env}
 \end{table}
@@
 The illustrations of CNN architecture displayed in Figure 1 of the main text,
-as well as  Supplementary Figure 21 and Supplementary Figure 30,
+as well as \cref{si_fig21:occlusion} and \cref{si_fig30:shifting},
 were obtained from the GitHub repository dair-ai/ml-visuals \cite{Saravia_ML_Visuals_2021}.
-Blender was used to create and render the visual representation of the catalyst analysis pipeline shown in Figure 1 of the main text.
+Blender was used to create and render the visual representation of the catalyst analysis pipeline shown in Figure 1 (TODO: cross-ref) of the main text.
 
-% Supplementary Table 20
+% Supplementary Table 20: Packages in data analysis and vis env
 \begin{table}[h]
@@
   \end{tabular}
-  \caption{Core packages in the data analysis and visualization environment}
+  \caption{Core packages in data analysis and visualization environment}
   \tablefootnote{The complete list of packages is provided along with the source code.}
-  \label{si_table20}
+  \label{si_table20:pack_vis_env}
 \end{table}

### 2024-01-09 paper/main_4.1_cnn_for_eads.tex
major cleanup: flat out dirs as per arxiv request
insert si cross-ref in main

--- 2024-01-05 paper/main_sections/4.1_cnn_for_eads.tex
@@
     \centering
-    \includegraphics[width=0.95\linewidth]{main_sections/figures/figure_2.JPG}
+    \includegraphics[width=0.95\linewidth]{main_fig2_cnn.JPG}
     \caption{\textbf{CNN for Electronic Density of States.}
@@
 Kendall rank correlation map illustrating the correlation between adsorption energy and some electronic and elementary descriptors.
-Definitions of the notations are provided in Supplementary Table 15.
+Definitions of the notations are provided in Supplementary \cref{si_table15:descriptor_notations}.
     b-c. Architectural of (b)the root and (c)each branch of the CNN model. The architecture remains consistent across individual branches.
@@
 The correlation coefficient map, as presented in \cref{main_fig2:cnn_for_eads}a, highlighted the d-band center as the most informative descriptor with a Kendall's $\tau$ coefficient of -0.33, and followed by the vacuum level and electronegativity.
-However, d-band center alone does not suffice for accurate predictions of intermediate adsorption energy as illustrated in the scatter plot Supplementary Figure 18 (TODO:), and therefore, refinements are imperative.
+However, d-band center alone does not suffice for accurate predictions of intermediate adsorption energy as illustrated in the scatter plot Supplementary \cref{si_fig18:dband_vs_eads}, and therefore, refinements are imperative.
 Unlike bulk transition metal surfaces, where the variations in the d-band centre account for the majority of the adsorption energy variations \cite{norskov2011density, takigawa2016machine}, the unique structure of SACs introduces more variables rather than d-band center that are intrinsically correlated with the variations of adsorption energy.
@@
 This MAE aligns with the established precision of DFT methods, which typically range between 0.1-0.2 eV concerning experimental measurement \cite{wellendorff2015benchmark, kirklin2015open, lejaeghere2016reproducibility}.
-The full list of prediction errors is available in Supplementary Table 18.
+The full list of prediction errors is available in Supplementary \cref{si_table18:cnn_mae}.
 These results confirm the CNN model's ability to predict adsorption energies from eDOS input.

### 2024-01-09 paper/main_4.2_volcano_plots.tex
major cleanup: flat out dirs as per arxiv request
insert si cross-ref in main

--- 2024-01-05 paper/main_sections/4.2_volcano_plots.tex
@@
     \centering
-    \includegraphics[width=0.95\linewidth]{main_sections/figures/figure_3.JPG}
+    \includegraphics[width=0.95\linewidth]{main_fig3_volcano.JPG}
     \caption{\textbf{Limiting Potential Volcano Plot and Periodic Table.}
@@
 By integrating both bonding featured descriptors into the hybrid approach, we found the coefficient of determination ($R^2$) was increased by 0.1387.
-Detailed information about the scaling parameters and performance enhancements are provided in Supplementary Tables 13 and Supplementary Figure 10.
+Detailed information about the scaling parameters and performance enhancements are provided in Supplementary \cref{si_table13:scaling_params} and Supplementary \cref{si_fig10:r2_hyb_des}.
 This improvement to some extent underscored our premise that CO$_2$RR intermediates typically exhibit chemical similarities encompassing both O- and C-type descriptors.
@@
 
-Expanding upon the revised scaling relations, we introduce an activity volcano plot and a rate-determining step (RDS) volcano plot for the CO$_2$RR process, shown in Figure 3a and Supplementary Figure 11.
-Given that HER is a key competing reaction with CO$_2$RR \cite{goyal2020competition}, we also incorporated a selectivity volcano plot, presented in Supplementary Figure 12, to offer a comprehensive analysis of catalyst candidates.
+Expanding upon the revised scaling relations, we introduce an activity volcano plot and a rate-determining step (RDS) volcano plot for the CO$_2$RR process, shown in \cref{main_fig3:volcano}a and Supplementary \cref{si_fig11:rds_volcano}.
+Given that HER is a key competing reaction with CO$_2$RR \cite{goyal2020competition}, we also incorporated a selectivity volcano plot, presented in Supplementary \cref{si_fig12:sel_volc}, to offer a comprehensive analysis of catalyst candidates.
 In adherence to Peterson and Nørskov's original framework \cite{peterson2012activity}, our choice of x and y axes descriptors aligned with $\textit{G}_{\text{ads} \ast \text{CO}}$ and $\textit{G}_{\text{ads} \ast \text{OH}}$.
@@
 Notably, the observed selectivity trend paralleled the activity trend, suggesting that catalysts exhibiting high theoretical activity are also resistant to HER side reactions.
-The RDS volcano plot (Supplementary Figure 11) indicated protonation of *CO as the rate-determining step for nearly optimal candidates.
+The RDS volcano plot (Supplementary \cref{si_fig11:rds_volcano}) indicated protonation of *CO as the rate-determining step for nearly optimal candidates.
 Moreover, the activity volcano plot predicted an optimal catalyst featuring a theoretical limiting potential of -1.0516 V, at $\textit{G}_{\text{ads} \ast \text{CO}}$ of 0.0589 eV and $\textit{G}_{\text{ads} \ast \text{OH}}$ of -4.0075 eV, positioned at the right-center of the volcano plot.
@@
 
-Additionally, we mapped the theoretical limiting potentials of the analyzed catalyst candidates onto periodic tables, shown in Figure 3b and Supplementary Figure 13 to 17.
+Additionally, we mapped the theoretical limiting potentials of the analyzed catalyst candidates onto periodic tables, shown in \cref{main_fig3:volcano}b and Supplementary \cref{si_fig13:n-gra_ptable} to \cref{si_fig17:C2N_ptable}.
 Our analyses do not reveal consistent trends within groups or periods, nor did they exhibit evident patterns across substrates.

### 2024-01-09 paper/si_4_others.tex
insert si cross-ref in main

@@
 % SI Section Three: Other Additional Information
+
+% TODO: fix main text figure cross-ref (search for main text/TODO)
 
@@
 
-The illustrations of CNN architecture displayed in Figure 1 of the main text,
+The illustrations of CNN architecture displayed in Figure 1 of the main text (TODO:),
 as well as \cref{si_fig21:occlusion} and \cref{si_fig30:shifting},
 were obtained from the GitHub repository dair-ai/ml-visuals \cite{Saravia_ML_Visuals_2021}.
-Blender was used to create and render the visual representation of the catalyst analysis pipeline shown in Figure 1 (TODO: cross-ref) of the main text.
+Blender was used to create and render the visual representation of the catalyst analysis pipeline shown in Figure 1 (TODO: cross-ref) of the main text (TODO:).
 

### 2024-01-09 paper/main_4.4_shifting_exp.tex
major cleanup: flat out dirs as per arxiv request
insert si cross-ref in main

--- 2024-01-05 paper/main_sections/4.4_shifting_exp.tex
@@
     \centering
-    \includegraphics[width=0.95\linewidth]{main_sections/figures/figure_5.JPG}
+    \includegraphics[width=0.95\linewidth]{main_fig5_shifting.JPG}
     \caption{\textbf{Shifting Experiments.}
@@
 This observation is consistent with their lack of d-electrons in their valence shells, reinforcing the reliability of our shifting experiments.
-We also investigated potential disturbance from p orbital shifting, as shown in Supplementary Figure 31 (TODO:) and found no significant response.
+We also investigated potential disturbance from p orbital shifting, as shown in Supplementary \cref{si_fig31:p_shifting} and found no significant response.
 This implies that Ge@g-C$_3$N$_4$ holds promise as a CO$_2$RR electrocatalyst, given its high activity and resilience to electronic structure disturbances.

### 2024-01-09 paper/main_5_methods.tex
major cleanup: flat out dirs as per arxiv request
insert si cross-ref in main

--- 2024-01-05 paper/main_sections/5_methods.tex
@@
 % Methods
+
+% TODO: line 47/70/117/139: cross-ref of section
 
@@
 Supported SACs were modelled by anchoring individual metal atoms onto various 2D substrates, including graphitic carbon nitride (g-C$_3$N$_4$), nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, boron nitride, and monolayer C$_2$N.
-The specific single metal atoms studied are outlined in Supplementary Figure 1 (TODO:).
+The specific single metal atoms studied are outlined in Supplementary \cref{si_fig1:ptable}.
 To prevent interactions between adjacent images along the z-axis, vacuum layers of 15 \text{\AA} were introduced.
@@
 where $\textit{G}$ represents the free energy, $\textit{E}$ denotes electronic energy, $\textit{E}_{\text{ZPE}}$ is the zero-point energy, $\textit{T}$ represents temperature in Kevin, and $\textit{S}$ stands for entropy.
-Detailed information regarding these corrections can be found in Supplementary Section 1.3.
+Detailed information regarding these corrections can be found in Supplementary Section 1.3 % TODO:.
 
@@
 \subsection{Hybrid descriptor for volcano plots}
-Hybrid descriptors incorporate both descriptors within a single equation, enhancing the accuracy of scaling relationship with minimal computational overhead, as demonstrated in Supplementary Figure 10 (TODO:) and Supplementary Table 13 (TODO:).
-Comprehensive analyses are presented Supplementary Section 1.5. This leads to the formulation of the scaling relation:
+Hybrid descriptors incorporate both descriptors within a single equation, enhancing the accuracy of scaling relationship with minimal computational overhead, as demonstrated in Supplementary \cref{si_fig10:r2_hyb_des} and Supplementary \cref{si_table13:scaling_params}.
+Comprehensive analyses are presented Supplementary Section 1.5 (TODO: fix this). This leads to the formulation of the scaling relation:
 \begin{equation*}
@@
 To identify the optimal set of hyperparameters, we employed Hyperband \cite{li2018hyperband}, a modern and parallelizable bandit-based optimization algorithm.
-The search space for hyperparameters is detailed in Supplementary Table 16, and the resulting optimal hyperparameters are presented in Supplementary Table 17.
+The search space for hyperparameters is detailed in Supplementary \cref{si_table16:hyperparam_space}, and the resulting optimal hyperparameters are presented in Supplementary \cref{si_table17:opt_hyperparam}.
 
@@
 \subsection{Occlusion experiments}
-Supplementary Figure 21 (TODO:) visually illustrates the occlusion experiment methodology.
+Supplementary \cref{si_fig21:occlusion} visually illustrates the occlusion experiment methodology.
 To maintain consistent shapes, zero-padding was applied to the input eDOS arrays.
 Focusing on understanding the influence of metals on adsorption behavior, a masker with dimensions [width, 1, 1] was employed along the metal channel to eliminate cross-orbital interactions.
-Here, "width" denotes the masker width, and detailed explanations for determining the width are provided in Supplementary Section 2.6.
+Here, "width" denotes the masker width, and detailed explanations for determining the width are provided in Supplementary Section 2.6 (TODO: fix).
 Through recursive application of these maskers, variations in predicted adsorption energies from the CNN model were recorded, generating an occlusion array.
@@
 \subsection{Shifting experiments}
-Supplementary Figure 30 (TODO:) illustrates the implemented shifting experiment protocol.
+Supplementary \cref{si_fig30:shifting} illustrates the implemented shifting experiment protocol.
 In this study, the initial electronic density of states underwent controlled shifting along the energy axis.
@@
 The CNN model was implemented using TensorFlow \cite{abadi2016tensorflow}, and hyperparameter optimization was conducted using the Hyperband \cite{li2018hyperband} algorithm via KerasTuner \cite{omalley2019kerastuner}.
-For a more detailed overview of our machine learning setup and data analysis environment, please refer to Supplementary Section 3.
+For a more detailed overview of our machine learning setup and data analysis environment, please refer to Supplementary Section 3 (TODO: fix).

### 2024-01-09 paper/main_5_methods.tex
add equation labels

@@
 
-% TODO: line 47/70/117/139: cross-ref of section
+% TODO: line 47/70/117/139: cross-ref of SI sections
 
@@
 
-\begin{equation*}
-\begin{aligned}
-\ce{CO2 + H+ + e- &-> \text{*}COOH} \\
-\ce{\text{*}COOH + H+ + e- &-> \text{*}CO + H2O} \\
-\ce{\text{*}CO + H+ + e- &-> \text{*}CHO} \\
-\ce{\text{*}CHO + H+ + e- &-> \text{*}CH2O} \\
-\ce{\text{*}CH2O + H+ + e- &-> \text{*}OCH3} \\
-\ce{\text{*}OCH3 + H+ + e- &-> \text{*}O + CH4} \\
-\ce{\text{*}O + H+ + e- &-> \text{*}OH} \\
-\ce{\text{*}OH + H+ + e- &-> \text{*} + H2O}
-\end{aligned}
-\end{equation*}
+\begin{align}
+\ce{CO2 + H+ + e-          &-> \text{*}COOH}      \label{main_eq1:co2rr1}    \\
+\ce{\text{*}CO + H+ + e-   &-> \text{*}CHO}       \label{main_eq3:co2rr3}    \\
+\ce{\text{*}COOH + H+ + e- &-> \text{*}CO + H2O}  \label{main_eq2:co2rr2}    \\
+\ce{\text{*}CHO + H+ + e-  &-> \text{*}CH2O}      \label{main_eq4:co2rr4}    \\
+\ce{\text{*}CH2O + H+ + e- &-> \text{*}OCH3}      \label{main_eq5:co2rr5}    \\
+\ce{\text{*}OCH3 + H+ + e- &-> \text{*}O + CH4}   \label{main_eq6:co2rr6}    \\
+\ce{\text{*}O + H+ + e-    &-> \text{*}OH}        \label{main_eq7:co2rr7}    \\
+\ce{\text{*}OH + H+ + e-   &-> \text{*} + H2O}    \label{main_eq8:co2rr8}
+\end{align}
 
@@
 The free energy $\textit{G}$ was calculated using the formula:
-\begin{equation*}
-G = E + E_{\text{ZPE}} - TS
-\end{equation*}
+\begin{align}
+G = E + E_{\text{ZPE}} - TS  \label{main_eq9:free_energy}
+\end{align}
 
@@
 At the reference electrode surface, the reaction
-\begin{equation*}
-\ce{1/2H2_{(g)}  <-> H+ + e-}
-\end{equation*}
+\begin{align}
+\ce{1/2H2_{(g)}  <-> H+ + e-}  \label{main_eq10:che}
+\end{align}
 is in equilibrium, allowing the calculation of the chemical potential of the electron-proton pair as:
-\begin{equation*}
-\mu(H^+) + \mu(e^-) = \frac{1}{2}\mu(H_{2(g)}) - eU
-\end{equation*}
+\begin{align}
+\mu(H^+) + \mu(e^-) = \frac{1}{2}\mu(H_{2(g)}) - eU  \label{main_eq11:che_potential}
+\end{align}
 For the external potential $\textit{U}$ applied, the change in free energy ($\Delta \textit{G}$) was determined using the equation:
-\begin{equation*}
-\Delta G_n(U) = \Delta G_n(U=0) + neU
-\end{equation*}
+\begin{align}
+\Delta G_n(U) = \Delta G_n(U=0) + neU  \label{main_eq12:ext_potential_che}
+\end{align}
 Here, $\mu$ represents chemical potential, $\textit{U}$ signifies the external potential applied, $\textit{n}$ represents the number of proton-electron pairs transferred, and $\textit{e}$ denotes the elementary charge.
@@
 Comprehensive analyses are presented Supplementary Section 1.5 (TODO: fix this). This leads to the formulation of the scaling relation:
-\begin{equation*}
-G_{\text{ads}} Z = k[\theta^* G_{\text{ads}} \ce{CO} + (1-\theta^*) G_{\text{ads}} \ce{OH}] + c_Z
-\end{equation*}
+\begin{align}
+G_{\text{ads}} Z =
+k[\theta^* G_{\text{ads}} \ce{CO} + (1-\theta^*) G_{\text{ads}} \ce{OH}] + c_Z  \label{main_eq13:scaling_relation}
+\end{align}
 Here, $\theta$ represents the mixing ratio of the CO descriptor, $\textit{Z}$ denotes any adsorbate, and $\textit{k}$ and $\textit{c}_{Z}$ are adsorbate-specific scaling parameters.
@@
 Equation 14 could be simplified to a more general form:
-\begin{equation*}
-G_{\text{ads}} Z = a_Z G_{\text{ads}} \ce{CO} + b_Z G_{\text{ads}} \ce{OH} + c_Z
-\end{equation*}
+\begin{align}
+G_{\text{ads}} Z =
+a_Z G_{\text{ads}} \ce{CO} + b_Z G_{\text{ads}} \ce{OH} + c_Z  \label{main_eq14:general_scaling_relation}
+\end{align}
 Here, $a_Z$, $b_Z$, $c_Z$ are adsorbate-specific parameters.
@@
 Consequently, the limiting potential $\textit{U}_{L}$ is entirely determined by two descriptors through the following equation:
-\begin{equation*}
-U_L = -\frac{\max\{ \Delta G_i \}}{e}
-\end{equation*}
+\begin{align}
+U_L = -\frac{\max\{ \Delta G_i \}}{e}  \label{main_eq14:limiting_potential}
+\end{align}
 Where $\Delta G_{i}$ represents the free energy change of reaction step i.
@@
 To aid visualization, a 2D mesh grid is established, enabling vectorized assessments of limiting potentials across the descriptor value ranges.
-At each grid point, the limiting potential is computed using Equation 16.
+At each grid point, the limiting potential is computed using Equation 16 (TODO:).
 

### 2024-01-09 paper/main_5_methods.tex
fix cross-ref to main in si

@@
 
-Equation 14 could be simplified to a more general form:
+\ref{main_eq13:scaling_relation} could be simplified to a more general form:
 \begin{align}
@@
 \begin{align}
-U_L = -\frac{\max\{ \Delta G_i \}}{e}  \label{main_eq14:limiting_potential}
+U_L = -\frac{\max\{ \Delta G_i \}}{e}  \label{main_eq15:limiting_potential}
 \end{align}
@@
 To aid visualization, a 2D mesh grid is established, enabling vectorized assessments of limiting potentials across the descriptor value ranges.
-At each grid point, the limiting potential is computed using Equation 16 (TODO:).
+At each grid point, the limiting potential is computed using \cref{main_eq15:limiting_potential}.
 

### 2024-01-09 paper/si_4_others.tex
fix cross-ref to main in si

--- 2024-01-09 paper/si_4_others.tex
@@
 
-The illustrations of CNN architecture displayed in Figure 1 of the main text,
+The illustrations of CNN architecture displayed in \cref{main_fig1:pipeline} of the main text,
 as well as \cref{si_fig21:occlusion} and \cref{si_fig30:shifting},
 were obtained from the GitHub repository dair-ai/ml-visuals \cite{Saravia_ML_Visuals_2021}.
-Blender was used to create and render the visual representation of the catalyst analysis pipeline shown in Figure 1 (TODO: cross-ref) of the main text.
+Blender was used to create and render the visual representation of the catalyst analysis pipeline shown in \cref{main_fig1:pipeline} of the main text.
 

### 2024-01-09 paper/main_4.2_volcano_plots.tex
main SI prefix in cross-ref

@@
 
-Additionally, we mapped the theoretical limiting potentials of the analyzed catalyst candidates onto periodic tables, shown in \cref{main_fig3:volcano}b and Supplementary \cref{si_fig13:n-gra_ptable} to \cref{si_fig17:C2N_ptable}.
+Additionally, we mapped the theoretical limiting potentials of the analyzed catalyst candidates onto periodic tables, shown in \cref{main_fig3:volcano}b and Supplementary \cref{si_fig13:n-gra_ptable} to Supplementary \cref{si_fig17:C2N_ptable}.
 Our analyses do not reveal consistent trends within groups or periods, nor did they exhibit evident patterns across substrates.

### 2024-01-09 paper/si_3_ml.tex
fix si section cross-ref

@@
 
-\subsection{d-band center and adsorption energy relations}
+\subsection{d-band center and adsorption energy relations}  \label{si_sec3.1_dband_eads}
 
@@
 
-\subsection{Feature correlation analysis}
+\subsection{Feature correlation analysis}  \label{si_sec3.2_feature_corr}
 
@@
 
-\subsection{Input pipeline construction}
+\subsection{Input pipeline construction}  \label{si_sec3.3_input_pipeline}
 The format of the 2D array for the eDOS is naturally well-suited for use as neural network inputs.
@@
 
-\subsection{Hyperparameter tuning for CNN}
+\subsection{Hyperparameter tuning for CNN}  \label{si_sec3.4_hyperparam}
 
@@
 
-\subsection{Occlusion experiment}
+\subsection{Occlusion experiment}  \label{si_sec3.5_occlusion}
 
@@
 
-\subsection{Shifting experiment}
+\subsection{Shifting experiment}  \label{si_sec3.6_shifting}
 

### 2024-01-09 paper/main_5_methods.tex
fix si section cross-ref

@@
 % Methods
-
-% TODO: line 47/70/117/139: cross-ref of SI sections
 
@@
 where $\textit{G}$ represents the free energy, $\textit{E}$ denotes electronic energy, $\textit{E}_{\text{ZPE}}$ is the zero-point energy, $\textit{T}$ represents temperature in Kevin, and $\textit{S}$ stands for entropy.
-Detailed information regarding these corrections can be found in Supplementary Section 1.3 % TODO:.
+Detailed information regarding these corrections can be found in Supplementary \cref{si_sec2.3_energies}.
 
@@
 Hybrid descriptors incorporate both descriptors within a single equation, enhancing the accuracy of scaling relationship with minimal computational overhead, as demonstrated in Supplementary \cref{si_fig10:r2_hyb_des} and Supplementary \cref{si_table13:scaling_params}.
-Comprehensive analyses are presented Supplementary Section 1.5 (TODO: fix this). This leads to the formulation of the scaling relation:
+Comprehensive analyses are presented Supplementary \cref{si_sec2.5_scaling}. This leads to the formulation of the scaling relation:
 \begin{align}
@@
 Focusing on understanding the influence of metals on adsorption behavior, a masker with dimensions [width, 1, 1] was employed along the metal channel to eliminate cross-orbital interactions.
-Here, "width" denotes the masker width, and detailed explanations for determining the width are provided in Supplementary Section 2.6 (TODO: fix).
+Here, "width" denotes the masker width, and detailed explanations for determining the width are provided in Supplementary \cref{si_sec3.5_occlusion}.
 Through recursive application of these maskers, variations in predicted adsorption energies from the CNN model were recorded, generating an occlusion array.
@@
 The CNN model was implemented using TensorFlow \cite{abadi2016tensorflow}, and hyperparameter optimization was conducted using the Hyperband \cite{li2018hyperband} algorithm via KerasTuner \cite{omalley2019kerastuner}.
-For a more detailed overview of our machine learning setup and data analysis environment, please refer to Supplementary Section 3 (TODO: fix).
+For a more detailed overview of our machine learning setup and data analysis environment, please refer to Supplementary \cref{si_sec4_env}.

### 2024-01-09 paper/si_4_others.tex
fix si section cross-ref

@@
 
-\section{Other additional information}
+\section{Other additional information}  \label{si_sec4_env}
 
-\subsection{Additional information on machine learning environment}
+\subsection{Additional information on machine learning environment}  \label{si_sec4.1_ml_env}
 
@@
 
-\subsection{Additional information on data analysis and visualization environment}
+\subsection{Additional information on data analysis and visualization environment}  \label{si_sec4.2_vis_env}
 Data analysis and visualization tasks were executed on an Apple MacBook Air featuring an octa-core M2 chip.

### 2024-01-09 paper/si_4_others.tex
put label in new lines

--- 2024-01-09 paper/si_4_others.tex
@@
 \section{Other additional information}
+\label{si_sec4_env}
 
-\subsection{Additional information on machine learning environment}
+\subsection{Additional information on machine learning environment}  \
+label{si_sec4.1_ml_env}
 
@@
 \subsection{Additional information on data analysis and visualization environment}
+\label{si_sec4.2_vis_env}
 Data analysis and visualization tasks were executed on an Apple MacBook Air featuring an octa-core M2 chip.

### 2024-01-09 paper/main_1_head.tex
replace math sub/subscript with text

--- 2024-01-04 paper/main_sections/1_head.tex
@@
 % Title
-\title{Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO$_2$ Reduction Reactions}
+\title{Convolutional Neural Networks and Volcano Plots:
+Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions}
 
-% Authors and Affiliations
+% Authors
 \author[1]{Haoyu Yang}
@@
 \author[4]{Qiankun Wang}
-\author[5]{Bin Lin}
-\author[6]{Wei Luo}
+\author[3]{Bin Liu}
+\author[5]{Wei Luo}
 \author[1,*]{Ziqi Sun}
@@
 
+% Affiliations
 \affil[1]{School of Chemistry and Physics, Queensland University of Technology, George Street, Brisbane, QLD 4000, Australia}
@@
 
-% Date (optional)
-\date{2024-01-04}
-
 % Make Title

### 2024-01-09 paper/main_4.1_cnn_for_eads.tex
adjust fig size
replace math sub/subscript with text

@@
     \centering
-    \includegraphics[width=0.95\linewidth]{main_fig2_cnn.JPG}
+    \includegraphics[width=0.7\linewidth]{main_fig2_cnn.JPG}
     \caption{\textbf{CNN for Electronic Density of States.}
-    a.
-Kendall rank correlation map illustrating the correlation between adsorption energy and some electronic and elementary descriptors.
+    a. Kendall rank correlation map illustrating the correlation between adsorption energy
+    and some electronic and elementary descriptors.
     Definitions of the notations are provided in Supplementary \cref{si_table15:descriptor_notations}.
-    b-c. Architectural of (b)the root and (c)each branch of the CNN model. The architecture remains consistent across individual branches.
-    d-m.
-Parity plots demonstrating the performance of the CNN model across nine adsorbates: (d)all adsorbates, (e) $\mathrm{CO_2}$, (f)COOH, (g)CO, (h)CHO, (i) $\mathrm{CH_2O}$, (j) $\mathrm{OCH_3}$, (k)O, (l)OH, and (m)H.
+    b-c. Architectural of (b)the root and (c)each branch of the CNN model.
+    The architecture remains consistent across individual branches.
+    d-m. Parity plots demonstrating the performance of the CNN model across nine adsorbates:
+    (d)all adsorbates, (e) CO\textsubscript{2}, (f)COOH, (g)CO, (h)CHO, (i) CH\textsubscript{2}O, (j) OCH\textsubscript{3}, (k)O, (l)OH, and (m)H.
     The augmentation data are not displayed in the plots nor included in MAE evaluations.
-    Kernel density estimate results are shown along the top and right sides of the main plot, representing DFT calculations and CNN model prediction distributions, respectively.}
+    Kernel density estimate results are shown along the top and right sides of the main plot,
+    representing DFT calculations and CNN model prediction distributions, respectively.}
     \label{main_fig2:cnn_for_eads}
@@
 By leveraging the CNN model, we predicted adsorption energies from the eDOS of supported single atoms, and validated through parity plots (\cref{main_fig2:cnn_for_eads}d-m).
-The model predicts adsorption energies across nine species within the CO$_2$RR process and competing HER side reaction, attaining an averaged MAE of 0.06 eV.
+The model predicts adsorption energies across nine species within the CO\textsubscript{2}RR process and competing HER side reaction, attaining an averaged MAE of 0.06 eV.
 This MAE aligns with the established precision of DFT methods, which typically range between 0.1-0.2 eV concerning experimental measurement \cite{wellendorff2015benchmark, kirklin2015open, lejaeghere2016reproducibility}.

### 2024-01-09 paper/main_4.4_shifting_exp.tex
replace math sub/subscript with text

@@
     \caption{\textbf{Shifting Experiments.}
-    Impact of orbitalwise eDOS shifting on CO adsorption energy, as predicted by the CNN model, for single metal atom catalysts supported on g-$\mathrm{C_3N_4}$.
+    Impact of orbitalwise eDOS shifting on CO adsorption energy, as predicted by the CNN model, for single metal atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.
     The disturbances caused by shifting of (a)entire $d$, (b)$d_{xy}$, (c)$d_{yz}$, (d)$d_{z^2}$, (e)$d_{xz}$ and (f)$d_{x^2-y^2}$ orbitals are illustrated.
@@
 We also investigated potential disturbance from p orbital shifting, as shown in Supplementary \cref{si_fig31:p_shifting} and found no significant response.
-This implies that Ge@g-C$_3$N$_4$ holds promise as a CO$_2$RR electrocatalyst, given its high activity and resilience to electronic structure disturbances.
+This implies that Ge@g-C\textsubscript{3}N\textsubscript{4} holds promise as a CO\textsubscript{2}RR electrocatalyst, given its high activity and resilience to electronic structure disturbances.
 Nevertheless, fine-tuning its performance through eDOS modulation might pose a challenge.

### 2024-01-09 paper/si_3_ml.tex
put label in new lines
replace math sub/subscript with text

--- 2024-01-09 paper/si_3_ml.tex
@@
 \subsection{d-band center and adsorption energy relations}
+\label{si_sec3.1_dband_eads}
 
@@
 \subsection{Feature correlation analysis}
+\label{si_sec3.2_feature_corr}
 
@@
 \subsection{Input pipeline construction}
+\label{si_sec3.3_input_pipeline}
 The format of the 2D array for the eDOS is naturally well-suited for use as neural network inputs.
@@
   2.	f-orbital eDOS data are excluded.
-  3.	The eDOS of adsorbates is zero-padded along the Channels axis to align with the adsorbate that contains the maximum number of atoms, which, in this study, is the *OCH$_3$ species.
+  3.	The eDOS of adsorbates is zero-padded along the Channels axis to align with the adsorbate that contains the maximum number of atoms, which, in this study, is the *OCH\textsubscript{3} species.
 This padded eDOS is then appended to the metal eDOS.
@@
 \subsection{Hyperparameter tuning for CNN}
+\label{si_sec3.4_hyperparam}
 
@@
 \subsection{Occlusion experiment}
+\label{si_sec3.5_occlusion}
 
@@
   This figure shows an occlusion experiment on the Ge atom in
-  the initial state of CO adsorption on Ge@g-C$_3$N$_4$.}
+  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
   \label{si_fig22:occl_wid1}
@@
   This figure shows an occlusion experiment on the Ge atom in
-  the initial state of CO adsorption on Ge@g-C$_3$N$_4$.}
+  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
   \label{si_fig23:occl_wid3}
@@
   This figure shows an occlusion experiment on the Ge atom in
-  the initial state of CO adsorption on Ge@g-C$_3$N$_4$.}
+  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
   \label{si_fig24:occl_wid5}
@@
   This figure shows an occlusion experiment on the Ge atom in
-  the initial state of CO adsorption on Ge@g-C$_3$N$_4$.}
+  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
   \label{si_fig25:occl_wid11}
@@
   This figure shows an occlusion experiment on the Ge atom in
-  the initial state of CO adsorption on Ge@g-C$_3$N$_4$.}
+  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
   \label{si_fig26:occl_wid21}
@@
   This figure shows an occlusion experiment on the Ge atom in
-  the initial state of CO adsorption on Ge@g-C$_3$N$_4$.}
+  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
   \label{si_fig27:occl_wid31}
@@
   This figure shows an occlusion experiment on the Ge atom in
-  the initial state of CO adsorption on Ge@g-C$_3$N$_4$.}
+  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
   \label{si_fig28:occl_wid41}
@@
   This figure shows an occlusion experiment on the Ge atom in
-  the initial state of CO adsorption on Ge@g-C$_3$N$_4$.}
+  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
   \label{si_fig29:occl_wid51}
@@
 \subsection{Shifting experiment}
+\label{si_sec3.6_shifting}
 
@@
   Effect of orbital shifting on CO adsorption energy, predicted by the CNN model,
-  for single metal atom catalysts supported on g-C$_3$N$_4$.
+  for single metal atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.
   The perturbations caused by shifting of entire p orbital are presented.

### 2024-01-09 paper/main_2_abstract.tex
replace math sub/subscript with text

--- 2024-01-04 paper/main_sections/2_abstract.tex
@@
 
-% TODO: prevent words from being broken in the middle
-
-\newpage
-
 \begin{abstract}
-Single-atom catalysts (SACs) have emerged as pivotal frontiers for catalyzing a myriad of chemical reactions, yet the diverse combinations of active elements and support materials, the nature of coordination environments, elude traditional methodologies in searching optimal SAC systems with superior catalytic performance.
-Herein, by integrating multi-branch Convolutional Neural Network (CNN) analysis models to hybrid descriptor based activity volcano plot, two-dimensional (2D) SAC system composed of diverse metallic single atoms anchored on six type of 2D supports, including g-C$_3$N$_4$, nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, BN, and C$_2$N, are screened for efficient CO$_2$ reduction reaction (CO$_2$RR).
+Single-atom catalysts (SACs) have emerged as pivotal frontiers for catalyzing a myriad of chemical reactions,
+yet the diverse combinations of active elements and support materials, the nature of coordination environments,
+elude traditional methodologies in searching optimal SAC systems with superior catalytic performance.
+Herein, by integrating multi-branch Convolutional Neural Network (CNN) analysis models to hybrid descriptor based activity volcano plot,
+two-dimensional (2D) SAC system composed of diverse metallic single atoms anchored on six type of 2D supports,
+including g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, BN, and C\textsubscript{2}N,
+are screened for efficient CO\textsubscript{2} reduction reaction (CO\textsubscript{2}RR).
 Starting from establishing a correlation map between the adsorption energies of intermediates and diverse electronic and elementary descriptors, sole singular descriptor lost magic to predict catalytic activity, including d-band center.
 Deep learning method utilizing multi-branch CNN model therefore was employed, using 2D electronic density of states (eDOS) as input to predict adsorption energies.
-Hybrid-descriptor enveloping both C- and O-types of CO$_2$RR intermediates was introduced to construct volcano plots and limiting potential periodic table, aiming for intuitive screening of catalyst candidates for efficient CO$_2$ reduction to CH$_4$.
+Hybrid-descriptor enveloping both C- and O-types of CO\textsubscript{2}RR intermediates was introduced to construct volcano plots and limiting potential periodic table,
+aiming for intuitive screening of catalyst candidates for efficient CO\textsubscript{2} reduction to CH\textsubscript{4}.
 The eDOS occlusion experiments were performed to unravel individual orbital contribution to adsorption energy.
-To explore the electronic scale principle governing practical engineering catalytic CO$_2$RR activity, orbitalwise eDOS shifting experiments based on CNN model were employed.
+To explore the electronic scale principle governing practical engineering catalytic CO\textsubscript{2}RR activity,
+orbitalwise eDOS shifting experiments based on CNN model were employed.
 The study involves examining the adsorption energy and, consequently, catalytic activities while varying supported single atoms.
-This work offers a tangible framework to inform both theoretical screening and experimental synthesis, thereby paving the way for systematically designing efficient SACs.
+This work offers a tangible framework to inform both theoretical screening and experimental synthesis,
+thereby paving the way for systematically designing efficient SACs.
 \end{abstract}

### 2024-01-09 paper/main_3_introduction.tex
major cleanup: flat out dirs as per arxiv request
replace math sub/subscript with text

--- 2024-01-06 paper/main_sections/3_introduction.tex
@@
     \centering
-    \includegraphics[width=0.95\linewidth]{main_sections/figures/main_fig1_pipeline.JPG}
+    \includegraphics[width=0.95\linewidth]{main_fig1_pipeline.JPG}
     \caption{\textbf{Catalyst Performance Analysis Pipeline Integrating Volcano Plots and CNN.}
@@
 
-Electrochemical CO$_2$RR stands as a promising avenue for long-term seasonal energy storage \cite{dinh2018co2} and mitigating excess CO$_2$ in the atmosphere.
+Electrochemical CO\textsubscript{2}RR stands as a promising avenue for long-term seasonal energy storage \cite{dinh2018co2} and mitigating excess CO\textsubscript{2} in the atmosphere.
 
-Despite decades of research, metallic copper remains a leading CO$_2$RR electrocatalyst for hydrocarbon production \cite{osella2023co2}, albeit burdened by substantial overpotential and low faradic efficiency and poor operational stability \cite{chen2019identifying, liu2021co2}.
+Despite decades of research, metallic copper remains a leading CO\textsubscript{2}RR electrocatalyst for hydrocarbon production \cite{osella2023co2}, albeit burdened by substantial overpotential and low faradic efficiency and poor operational stability \cite{chen2019identifying, liu2021co2}.
 In this regard, supported SACs have displayed remarkable activity and selectivity across various catalytic reactions \cite{wang2018heterogeneous, yang2018atomically}, leveraging their unique electronic properties and coordination environment.
@@
 Our CNN model accurately estimated the adsorption energies, the activity descriptor, from the eDOS of 2D materials supported single metal catalysts.
-Evaluations on the adsorption energies of nine intermediates along CO$_2$RR and competing hydrogen evolution reaction (HER) as well yielded prediction mean absolute errors (MAEs) at the level of 0.1 eV, which is well aligned with the precision of conventional DFT calculations \cite{kirklin2015open, lejaeghere2016reproducibility, wellendorff2015benchmark}.
+Evaluations on the adsorption energies of nine intermediates along CO\textsubscript{2}RR and competing hydrogen evolution reaction (HER) as well yielded prediction mean absolute errors (MAEs) at the level of 0.1 eV, which is well aligned with the precision of conventional DFT calculations \cite{kirklin2015open, lejaeghere2016reproducibility, wellendorff2015benchmark}.
 This result validated the capability of current CNN model to accurately capture intricate spatial information from eDOS.
@@
 
-In summary, we introduced a catalyst performance analysis pipeline by integrating CNN and volcano plot analysis, using CO$_2$RR as an example proof of concept.
+In summary, we introduced a catalyst performance analysis pipeline by integrating CNN and volcano plot analysis, using CO\textsubscript{2}RR as an example proof of concept.
 The CNN, which correlates eDOS with activity descriptors, establishes a robust electronic structure-activity relationship.

### 2024-01-09 paper/main_4.2_volcano_plots.tex
replace math sub/subscript with text

@@
     \centering
-    \includegraphics[width=0.95\linewidth]{main_fig3_volcano.JPG}
+    \includegraphics[width=0.75\linewidth]{main_fig3_volcano.JPG}
     \caption{\textbf{Limiting Potential Volcano Plot and Periodic Table.}
     a. Limiting potential volcano plot computed from hybrid-descriptor-based linear scaling relations at -0.17 V vs SHE.
-    In the plot, the circle, triangle, square, diamond, plus, and star symbols represent metals supported on g-$\mathrm{C_3N_4}$, nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, BN, and $\mathrm{C_2N}$, respectively.
+    In the plot, the circle, triangle, square, diamond, plus, and star symbols represent metals supported on g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, BN, and C\textsubscript{2}N, respectively.
     Dotted purple lines delineate regions representing rate-determining steps (RDS), with roman numerals denoting the respective RDS for each region.
-    b. Limiting potential periodic table illustrating the theoretical activity of single atom catalysts, where metals are supported on g-$\mathrm{C_3N_4}$.}
+    b. Limiting potential periodic table illustrating the theoretical activity of single atom catalysts, where metals are supported on g-C\textsubscript{3}N\textsubscript{4}.
     \label{main_fig3:volcano}
@@
 Our endeavor to improve the accuracy of volcano plots leads to the development of the hybrid-descriptor,
-which encompasses both C- and O- bonding types of CO$_2$RR intermediates within the scaling relations.
-This adaptation arose from the intuition that most CO$_2$RR intermediates are featured with both bonding types rather than any single one in dominance.
+which encompasses both C- and O- bonding types of CO\textsubscript{2}RR intermediates within the scaling relations.
+This adaptation arose from the intuition that most CO\textsubscript{2}RR intermediates are featured with both bonding types rather than any single one in dominance.
 By integrating both bonding featured descriptors into the hybrid approach, we found the coefficient of determination ($R^2$) was increased by 0.1387.
 Detailed information about the scaling parameters and performance enhancements are provided in Supplementary \cref{si_table13:scaling_params} and Supplementary \cref{si_fig10:r2_hyb_des}.
-This improvement to some extent underscored our premise that CO$_2$RR intermediates typically exhibit chemical similarities encompassing both O- and C-type descriptors.
+This improvement to some extent underscored our premise that CO\textsubscript{2}RR intermediates typically exhibit chemical similarities encompassing both O- and C-type descriptors.
 After taking this dual nature into consideration, our hybrid-descriptor method can evaluate the intermediates adsorption energies more accurately.
@@
 
-Expanding upon the revised scaling relations, we introduce an activity volcano plot and a rate-determining step (RDS) volcano plot for the CO$_2$RR process, shown in \cref{main_fig3:volcano}a and Supplementary \cref{si_fig11:rds_volcano}.
-Given that HER is a key competing reaction with CO$_2$RR \cite{goyal2020competition}, we also incorporated a selectivity volcano plot, presented in Supplementary \cref{si_fig12:sel_volc}, to offer a comprehensive analysis of catalyst candidates.
+Expanding upon the revised scaling relations, we introduce an activity volcano plot and a rate-determining step (RDS) volcano plot for the CO\textsubscript{2}RR process, shown in \cref{main_fig3:volcano}a and Supplementary \cref{si_fig11:rds_volcano}.
+Given that HER is a key competing reaction with CO\textsubscript{2}RR \cite{goyal2020competition}, we also incorporated a selectivity volcano plot, presented in Supplementary \cref{si_fig12:sel_volc}, to offer a comprehensive analysis of catalyst candidates.
 In adherence to Peterson and Nørskov's original framework \cite{peterson2012activity}, our choice of x and y axes descriptors aligned with $\textit{G}_{\text{ads} \ast \text{CO}}$ and $\textit{G}_{\text{ads} \ast \text{OH}}$.
 Further elaboration on how the limiting potentials were evaluated across the volcano plot can be found in the Methods section.
-Among the candidatures explored, Ge@g-C$_3$N$_4$ emerged as the most promising catalyst, demonstrating theoretical activity at a limiting potential of -1.2126 eV.
+Among the candidatures explored, Ge@g-C\textsubscript{3}N\textsubscript{4} emerged as the most promising catalyst, demonstrating theoretical activity at a limiting potential of -1.2126 eV.
 Notably, the observed selectivity trend paralleled the activity trend, suggesting that catalysts exhibiting high theoretical activity are also resistant to HER side reactions.
@@
 Moreover, the activity volcano plot predicted an optimal catalyst featuring a theoretical limiting potential of -1.0516 V, at $\textit{G}_{\text{ads} \ast \text{CO}}$ of 0.0589 eV and $\textit{G}_{\text{ads} \ast \text{OH}}$ of -4.0075 eV, positioned at the right-center of the volcano plot.
-Results from RDS volcano plot indicate that protonation of *CO likely serves as the RDS for CO$_2$RR.
+Results from RDS volcano plot indicate that protonation of *CO likely serves as the RDS for CO\textsubscript{2}RR.
 Consequently, it should be the focal point for future catalyst designs.

### 2024-01-09 paper/main_4.3_validation.tex
major cleanup: flat out dirs as per arxiv request
insert si cross-ref in main
replace math sub/subscript with text

--- 2024-01-05 paper/main_sections/4.3_validation.tex
@@
     \centering
-    \includegraphics[width=0.95\linewidth]{main_sections/figures/figure_4.JPG}
+    \includegraphics[width=0.95\linewidth]{main_fig4_validation.JPG}
     \caption{\textbf{Validation of CNN Predictions.}
-    a-c, The occlusion experiment results for (a)Cr $d_{x^2-y^2}$ orbital of Cr@g-$\mathrm{C_3N_4}$, (b)Co $d_{xy}$ orbital of Co@g-$\mathrm{C_3N_4}$ and (c)Cu $d_{xy}$ orbital of Cu@g-$\mathrm{C_3N_4}$.
+    a-c, The occlusion experiment results for (a)Cr $d_{x^2-y^2}$ orbital of Cr@g-C\textsubscript{3}N\textsubscript{4}, (b)Co $d_{xy}$ orbital of Co@g-C\textsubscript{3}N\textsubscript{4} and (c)Cu $d_{xy}$ orbital of Cu@g-C\textsubscript{3}N\textsubscript{4}.
     Occlusion experiments were conducted on the initial states of CO adsorption process.
-    d-f, Real-space wavefunction visualization for (d)Cr $d_{x^2-y^2}$ orbital of Cr@g-$\mathrm{C_3N_4}$, (e)Co $d_{xy}$ orbital of Co@g-$\mathrm{C_3N_4}$ and (f)Cu $d_{xy}$ orbital of Cu@g-$\mathrm{C_3N_4}$.
+    d-f, Real-space wavefunction visualization for (d)Cr $d_{x^2-y^2}$ orbital of Cr@g-C\textsubscript{3}N\textsubscript{4}, (e)Co $d_{xy}$ orbital of Co@g-C\textsubscript{3}N\textsubscript{4} and (f)Cu $d_{xy}$ orbital of Cu@g-C\textsubscript{3}N\textsubscript{4}.
     Wavefunction visualizations were performed on the final states of CO adsorption process.
     The yellow and aqua colors represent areas of positive and negative Kohn-Sham orbital coefficients, respectively.
-    g-j, Occlusion experiment results for (g)$d_{xy}$ orbital and (h)$d_{xz}$ orbital for Co of Co@g-$\mathrm{C_3N_4}$.
-    COHP analysis for (i)$d_{xy}$ orbital and (j)$d_{xz}$ orbital for Co of Co@g-$\mathrm{C_3N_4}$, performed between Co and all adsorbate atoms in the final states of CO adsorption process.}
+    g-j, Occlusion experiment results for (g)$d_{xy}$ orbital and (h)$d_{xz}$ orbital for Co of Co@g-C\textsubscript{3}N\textsubscript{4}.
+    COHP analysis for (i)$d_{xy}$ orbital and (j)$d_{xz}$ orbital for Co of Co@g-C\textsubscript{3}N\textsubscript{4}, performed between Co and all adsorbate atoms in the final states of CO adsorption process.}
     \label{main_fig4:validation}
@@
 In this work, occlusion experiments involve orbitalwise masking specific eDOS, which are then fed into the CNN model to observe resulting disturbance in adsorption energy.
-A visual representation of this process can be found in Supplementary Figure 21 (TODO:).
+A visual representation of this process can be found in Supplementary \cref{si_fig21:occlusion}.
 Conceptually, this experiment simulates the effect of shielding electronic states, allowing investigation of the potential contribution to adsorption energy from these states.
@@
 
-To validate our method, we conducted occlusion experiments on Cr@g-C$_3$N$_4$, Co@g-C$_3$N$_4$ and Cu@g-C$_3$N$_4$.
+To validate our method, we conducted occlusion experiments on Cr@g-C\textsubscript{3}N\textsubscript{4}, Co@g-C\textsubscript{3}N\textsubscript{4} and Cu@g-C\textsubscript{3}N\textsubscript{4}.
 Each of these supported metals possesses 3d subshells with different electronic configurations: half-filled, partially filled and fully filled, allowing us to test the universality of our approach.
-The results of the occlusion experiment on the supported Cr single atom in Cr@g-C$_3$N$_4$ are given in \cref{main_fig4:validation}a.
+The results of the occlusion experiment on the supported Cr single atom in Cr@g-C\textsubscript{3}N\textsubscript{4} are given in \cref{main_fig4:validation}a.
 The $d_{x^2-y^2}$ orbital emerges as dominant in CO interaction.
@@
 This suggests the $d_{x^2-y^2}$ orbital of supported Co predominantly influence the interaction with CO, and thus shielding electrons from this orbital markedly disturb the adsorption energy.
-Additionally, occlusion experiments were performed on the Co $d_xy$ orbital of Co@g-C$_3$N$_4$ (\cref{main_fig4:validation}b) and the $Cu d_xy$ orbital of Cu@g-C$_3$N$_4$ (\cref{main_fig4:validation}c).
+Additionally, occlusion experiments were performed on the Co $d_xy$ orbital of Co@g-C\textsubscript{3}N\textsubscript{4} (\cref{main_fig4:validation}b) and the $Cu d_xy$ orbital of Cu@g-C\textsubscript{3}N\textsubscript{4} (\cref{main_fig4:validation}c).
 In both cases, the $d_xy$ orbital was identified as the dominant contributor.
@@
 In this research, interactions between the supported metal atom and atoms within a 5 \text{\AA} radius were calculated to understand its bonding environment, as detailed in the Methods section.
-The results of the occlusion experiment on the Co $d_xy$ orbital of Co@g-C$_3$N$_4$, identified as the dominant orbital via occlusion experiments, were compared with the COHP analysis, as shown in \cref{main_fig4:validation}g and \cref{main_fig4:validation}i.
+The results of the occlusion experiment on the Co $d_xy$ orbital of Co@g-C\textsubscript{3}N\textsubscript{4}, identified as the dominant orbital via occlusion experiments, were compared with the COHP analysis, as shown in \cref{main_fig4:validation}g and \cref{main_fig4:validation}i.
 The occlusion experiment pinpointed strong metal-adsorbate interactions at energy levels of -1 eV and -6.3 eV, which were confirmed by the COHP analysis.

### 2024-01-09 paper/main_5_methods.tex
replace math sub/subscript with text

@@
 \subsection{Catalyst models}
-Supported SACs were modelled by anchoring individual metal atoms onto various 2D substrates, including graphitic carbon nitride (g-C$_3$N$_4$), nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, boron nitride, and monolayer C$_2$N.
+Supported SACs were modelled by anchoring individual metal atoms onto various 2D substrates, including graphitic carbon nitride (g-C\textsubscript{3}N\textsubscript{4}), nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, boron nitride, and monolayer C\textsubscript{2}N.
 The specific single metal atoms studied are outlined in Supplementary \cref{si_fig1:ptable}.
@@
 \cite{peterson2010copper} and later confirmed by Jiao et al.
-\cite{jiao2017molecular} for g-C$_3$N$_4$ based SACs, involves the following elementary steps.
+\cite{jiao2017molecular} for g-C\textsubscript{3}N\textsubscript{4} based SACs, involves the following elementary steps.
 Asterisks (*) indicate species adsorbed on the SAC surfaces:
@@
 
-The augmented dataset comprises 12,312 samples, with adsorption energies having a standard deviation of 1.8117 eV and a variance of 3.2821 $\mathrm{eV}^2$.
+The augmented dataset comprises 12,312 samples, with adsorption energies having a standard deviation of 1.8117 eV and a variance of 3.2821 eV\textsubscript{2}.
 Twenty percent of these samples were allocated to the validation set. Throughout the training process, a batch size of 64 was employed to ensure a balanced learning dynamic.

### 2024-01-10 paper/si_3_ml.tex
replace math subscript with text

@@
   This figure delineates the relationship between d-band center and adsorption energies for
-  various species: (a) CO$_2$, (b) COOH, (c) CO, (d) CHO, (e) CH$_2$O, (f) OCH$_3$, (g) O, and (h) OH.
+  various species: (a) CO\textsubscript{2}, (b) COOH, (c) CO, (d) CHO,
+  (e) CH\textsubscript{2}O, (f) OCH\textsubscript{3}, (g) O, and (h) OH.
   Data from all six substrates investigated in this study are included.}
@@
     \hline
-    CO$_2$  & 0.0447 & 0.0336 \\
+    CO\textsubscript{2}   & 0.0447 & 0.0336 \\
     COOH                  & 0.0436 & 0.0581 \\
@@
     CHO                   & 0.0614 & 0.0778 \\
-    CH$_2$O & 0.0553 & 0.0632 \\
-    OCH$_3$ & 0.0605 & 0.0636 \\
+    CH\textsubscript{2}O  & 0.0553 & 0.0632 \\
+    OCH\textsubscript{3}  & 0.0605 & 0.0636 \\
     O                     & 0.1135 & 0.1081 \\

### 2024-01-10 paper/main_4.1_cnn_for_eads.tex
revise section headers
remove extra spacing

@@
-% Results and Discussion Part One: Adsorption energy prediction from eDOS with CNN
+% Results Part One: Adsorption energy prediction from eDOS with CNN
 
-\section{Adsorption energy prediction from electronic density of states with convolutional neural network}
+\section{Results}
+
+\subsection{Adsorption energy prediction from electronic density of states with convolutional neural network}
 
@@
     d-m. Parity plots demonstrating the performance of the CNN model across nine adsorbates:
-    (d)all adsorbates, (e) CO\textsubscript{2}, (f)COOH, (g)CO, (h)CHO, (i) CH\textsubscript{2}O, (j) OCH\textsubscript{3}, (k)O, (l)OH, and (m)H.
+    (d) all adsorbates, (e) CO\textsubscript{2}, (f)COOH, (g)CO, (h)CHO,
+    (i) CH\textsubscript{2}O, (j) OCH\textsubscript{3}, (k)O, (l)OH, and (m)H.
     The augmentation data are not displayed in the plots nor included in MAE evaluations.
@@
 
-Originating from the pioneering work of Hammer and Nørskov \cite{hammer2000theoretical}, the d-band center model has emerged as a successful paradigm for employing descriptor to understand and predict the adsorption behavior on transition metal surfaces.
-To investigate alternative electronic and elementary descriptors that may serve as more suitable substitutes for the d-band center model in the context of SACs, we performed Kendall rank correlation analysis to account for both linearity and non-linearity \cite{kendall1938new}.
+Originating from the pioneering work of Hammer and Nørskov \cite{hammer2000theoretical},
+the d-band center model has emerged as a successful paradigm for employing descriptor to understand and predict the adsorption behavior on transition metal surfaces.
+To investigate alternative electronic and elementary descriptors that may serve as more suitable substitutes for the d-band center model in the context of SACs,
+we performed Kendall rank correlation analysis to account for both linearity and non-linearity \cite{kendall1938new}.
 The correlation coefficient map, as presented in \cref{main_fig2:cnn_for_eads}a, highlighted the d-band center as the most informative descriptor with a Kendall's $\tau$ coefficient of -0.33, and followed by the vacuum level and electronegativity.

### 2024-01-10 paper/main_2_abstract.tex
remove extra spacing
adjust spaces

@@
 \begin{abstract}
+\label{main_sec_abstract}
+
 Single-atom catalysts (SACs) have emerged as pivotal frontiers for catalyzing a myriad of chemical reactions,
@@
 thereby paving the way for systematically designing efficient SACs.
+
 \end{abstract}

### 2024-01-10 paper/si_4_others.tex
fix typo
remove extra spacing
adjust spaces

--- 2024-01-09 paper/si_4_others.tex
@@
 \section{Other additional information}
+\label{si_sec4_env}
 
 \subsection{Additional information on machine learning environment}
+\label{si_sec4.1_ml_env}
 
@@
 \subsection{Additional information on data analysis and visualization environment}
+\label{si_sec4.2_vis_env}
+
 Data analysis and visualization tasks were executed on an Apple MacBook Air featuring an octa-core M2 chip.
@@
 were obtained from the GitHub repository dair-ai/ml-visuals \cite{Saravia_ML_Visuals_2021}.
-Blender was used to create and render the visual representation of the catalyst analysis pipeline shown in \cref{main_fig1:pipeline} of the main text.
+Blender was used to create and render the visual representation of the
+catalyst analysis pipeline shown in \cref{main_fig1:pipeline} of the main text.
 

### 2024-01-10 paper/main_3_introduction.tex
adjust spaces
break some long lines

@@
 \section{Introduction}
+\label{main_sec_intro}
 
@@
     \caption{\textbf{Catalyst Performance Analysis Pipeline Integrating Volcano Plots and CNN.}
-    The figure demonstrates the integrated usage of volcano plots for predictive assessments of existing catalysts and the utility of CNNs to predict and modulate adsorption energies \(E_{\text{ads}}\) using eDOS as input.
+    The figure demonstrates the integrated usage of volcano plots for
+    predictive assessments of existing catalysts and the utility of CNNs
+    to predict and modulate adsorption energies \(E_{\text{ads}}\) using eDOS as input.
     Advanced occlusion and shifting experiments on eDOS are conducted to extract chemical meanings from CNN model.}
@@
 
-Electrochemical CO\textsubscript{2}RR stands as a promising avenue for long-term seasonal energy storage \cite{dinh2018co2} and mitigating excess CO\textsubscript{2} in the atmosphere.
+Electrochemical CO\textsubscript{2}RR stands as a promising avenue for long-term
+seasonal energy storage \cite{dinh2018co2} and mitigating excess CO\textsubscript{2} in the atmosphere.
 
-Despite decades of research, metallic copper remains a leading CO\textsubscript{2}RR electrocatalyst for hydrocarbon production \cite{osella2023co2}, albeit burdened by substantial overpotential and low faradic efficiency and poor operational stability \cite{chen2019identifying, liu2021co2}.
-In this regard, supported SACs have displayed remarkable activity and selectivity across various catalytic reactions \cite{wang2018heterogeneous, yang2018atomically}, leveraging their unique electronic properties and coordination environment.
-To date, experimental studies have primarily focused on two-electron reduction products due to the facile release of gaseous CO \cite{cai2021insights, ju2017understanding, ren2019isolated}.
-Consequently, there is a pressing need to modulate the electronic structure of single-atom sites to enable hydrocarbon production at reduced overpotential.
+Despite decades of research, metallic copper remains a leading CO\textsubscript{2}RR electrocatalyst
+for hydrocarbon production \cite{osella2023co2}, albeit burdened by substantial overpotential
+and low faradic efficiency and poor operational stability \cite{chen2019identifying, liu2021co2}.
+In this regard, supported SACs have displayed remarkable activity and selectivity
+across various catalytic reactions \cite{wang2018heterogeneous, yang2018atomically},
+leveraging their unique electronic properties and coordination environment.
+To date, experimental studies have primarily focused on two-electron reduction products
+due to the facile release of gaseous CO \cite{cai2021insights, ju2017understanding, ren2019isolated}.
+Consequently, there is a pressing need to modulate the electronic structure of single-atom sites
+to enable hydrocarbon production at reduced overpotential.
 
 The challenge towards effective catalysts design lies in understanding the reaction mechanisms.
-Experimental determination of these mechanisms remains challenging due to the complexity of in situ spectroscopic detection of reaction intermediates \cite{zhao2021revisiting}.
+Experimental determination of these mechanisms remains challenging due to
+the complexity of in situ spectroscopic detection of reaction intermediates \cite{zhao2021revisiting}.
 Computational modeling, particularly methods based on quantum mechanics (QM) such as density functional theory (DFT),
-allows for the profiling the energetics of intermediates and unveils structure-activity relationships for identified active sites \cite{feaster2017understanding, carter2008challenges}, contributing to understanding of reaction mechanisms.
-However, the high computational cost of QM methods restricts the accessible catalyst space \cite{jinnouchi2017predicting, cuenya2015nanocatalysis, goldsmith2018machine}.
+allows for the profiling the energetics of intermediates and unveils structure-activity relationships
+for identified active sites \cite{feaster2017understanding, carter2008challenges},
+contributing to understanding of reaction mechanisms.
+However, the high computational cost of QM methods restricts the
+accessible catalyst space \cite{jinnouchi2017predicting, cuenya2015nanocatalysis, goldsmith2018machine}.
 
-In this context, researchers have explored descriptor-based methods to circumvent QM calculations and establish direct correlations between target properties and electronic factors, commonly referred to as descriptors or features.
-Traditional methods of crafting descriptors, as seen in the d-band model of Hammer and Nørskov \cite{hammer1995electronic}, necessitate meticulous selection of chemical properties based on chemical knowledge and are inherently case-dependent \cite{kajita2017universal}.
-Particularly in the case of SACs, the relationship is intricate, rendering manual crafting inadequate \cite{han2021single, thirumalai2018investigating}.
-To streamline this featurization process, we employed convolutional neural networks (CNNs), which autonomously derive a hierarchical representation directly from the electronic density of state (eDOS) \cite{tran2015learning, socher2012convolutional, krizhevsky2012imagenet}.
-This approach accurately maps to the activity space, negating the need for manual crafting of descriptors and providing a more efficient method to understand and establish the structure-mechanism-activity relationship for electrochemical reactions.
+In this context, researchers have explored descriptor-based methods
+to circumvent QM calculations and establish direct correlations
+between target properties and electronic factors, commonly referred to as descriptors or features.
+Traditional methods of crafting descriptors, as seen in the d-band model of Hammer and Nørskov \cite{hammer1995electronic},
+necessitate meticulous selection of chemical properties based on chemical knowledge
+and are inherently case-dependent \cite{kajita2017universal}.
+Particularly in the case of SACs, the relationship is intricate,
+rendering manual crafting inadequate \cite{han2021single, thirumalai2018investigating}.
+To streamline this featurization process, we employed convolutional neural networks (CNNs),
+which autonomously derive a hierarchical representation directly from the electronic density of state (eDOS)
+\cite{tran2015learning, socher2012convolutional, krizhevsky2012imagenet}.
+This approach accurately maps to the activity space, negating the need for manual crafting of descriptors
+and providing a more efficient method to understand and
+establish the structure-mechanism-activity relationship for electrochemical reactions.
 
-In this study, we introduced a catalyst performance analysis pipeline (\cref{main_fig1:pipeline}) integrating a customized CNN model and volcano plots.
-Our CNN model accurately estimated the adsorption energies, the activity descriptor, from the eDOS of 2D materials supported single metal catalysts.
-Evaluations on the adsorption energies of nine intermediates along CO\textsubscript{2}RR and competing hydrogen evolution reaction (HER) as well yielded prediction mean absolute errors (MAEs) at the level of 0.1 eV, which is well aligned with the precision of conventional DFT calculations \cite{kirklin2015open, lejaeghere2016reproducibility, wellendorff2015benchmark}.
+In this study, we introduced a catalyst performance analysis pipeline (\cref{main_fig1:pipeline})
+integrating a customized CNN model and volcano plots.
+Our CNN model accurately estimated the adsorption energies, the activity descriptor,
+from the eDOS of 2D materials supported single metal catalysts.
+Evaluations on the adsorption energies of nine intermediates along CO\textsubscript{2}RR
+and competing hydrogen evolution reaction (HER) as well
+yielded prediction mean absolute errors (MAEs) at the level of 0.1 eV,
+which is well aligned with the precision of conventional DFT calculations
+\cite{kirklin2015open, lejaeghere2016reproducibility, wellendorff2015benchmark}.
 This result validated the capability of current CNN model to accurately capture intricate spatial information from eDOS.
-Building on this, we introduced an orbitalwise eDOS occlusion experiment was adopted afterwards inspired from the occlusion technique widely used in computer vision and pattern recognition applications.
-Systematic eDOS experiment was performed to elucidate orbitalwise contributions to the adsorption energies at different energy levels, which produced consistent outcome from Crystal Orbital Hamilton Population (COHP) analysis and real-space wavefunction visualization.
-All these results justified the proficiency of CNN model on identifying the dominant orbitals for adsorbate-substrate interactions.
-Furthermore, orbital-wise eDOS shifting experiment, exploring the impact of orbital-wise eDOS shifting on the adsorption behavior of studied catalysts were performed.
+Building on this, we introduced an orbitalwise eDOS occlusion experiment was adopted afterwards
+inspired from the occlusion technique widely used in computer vision and pattern recognition applications.
+Systematic eDOS experiment was performed to elucidate orbitalwise contributions to
+the adsorption energies at different energy levels,
+which produced consistent outcome from Crystal Orbital Hamilton Population (COHP) analysis
+and real-space wavefunction visualization.
+All these results justified the proficiency of CNN model on identifying
+the dominant orbitals for adsorbate-substrate interactions.
+Furthermore, orbital-wise eDOS shifting experiment, exploring the impact of orbital-wise eDOS shifting
+on the adsorption behavior of studied catalysts were performed.
 
 Simultaneously, we incorporated the volcano plots into the catalysis performance analysis pipeline.
-Besides offering intuitive analysis of catalyst activities (represented by the elevation of volcanoes), volcano plots points to the directions on how effort can be exerted to identify promising catalyst candidates.
-Built upon scaling relations \cite{peterson2012activity}, we introduced a hybrid-descriptor scheme incorporating both C- and O-centered species.
-The scaling coefficient of determination ($R^2$) was increased by 0.1387 using hybrid descriptor, which demonstrate an improved prediction accuracy compared to the well documented single descriptor based method.
+Besides offering intuitive analysis of catalyst activities (represented by the elevation of volcanoes),
+volcano plots points to the directions on how effort can be exerted to identify promising catalyst candidates.
+Built upon scaling relations \cite{peterson2012activity}, we introduced a hybrid-descriptor scheme
+incorporating both C- and O-centered species.
+The scaling coefficient of determination ($R^2$) was increased by 0.1387 using hybrid descriptor,
+which demonstrate an improved prediction accuracy compared to the well documented single descriptor based method.
 
-In summary, we introduced a catalyst performance analysis pipeline by integrating CNN and volcano plot analysis, using CO\textsubscript{2}RR as an example proof of concept.
+In summary, we introduced a catalyst performance analysis pipeline by
+integrating CNN and volcano plot analysis, using CO\textsubscript{2}RR as an example proof of concept.
 The CNN, which correlates eDOS with activity descriptors, establishes a robust electronic structure-activity relationship.
-Notably, it is capable to predict the influence of eDOS disturbances, caused by either alloying, strain, or defects \cite{norskov2011density, bera2017density, kusada2019emergence}, to modulate the catalytic activity of materials, which will offer insights into the intrinsic mechanism for rationalized catalyst optimization strategies.
-Advancing the current volcano plot method, the involvement of CNN models in catalyst performance analysis pipeline holds enormous promise for advanced exploration of catalysts with superior performance.
+Notably, it is capable to predict the influence of eDOS disturbances,
+caused by either alloying, strain, or defects \cite{norskov2011density, bera2017density, kusada2019emergence},
+to modulate the catalytic activity of materials,
+which will offer insights into the intrinsic mechanism for rationalized catalyst optimization strategies.
+Advancing the current volcano plot method,
+the involvement of CNN models in catalyst performance analysis pipeline holds enormous promise
+for advanced exploration of catalysts with superior performance.

### 2024-01-10 z-non-matplotlib-figures/3D-volcano-plot/main.py
add ref to fig1 mountain (no bib in repo)

@@ -1,5 +1,6 @@
 #!/usr/bin/env python3
 # -*- coding: utf-8 -*-
+# Plotted with: https://github.com/ColCarroll/ridge_map
 
 from pathlib import Path
 

### 2024-01-10 z-non-matplotlib-figures/3D-volcano-plot/src/RidgeMapPlotter.py

@@ -1,5 +1,6 @@
 #!/usr/bin/env python3
 # -*- coding: utf-8 -*-
+# https://github.com/ColCarroll/ridge_map
 
 from ridge_map import FontManager, RidgeMap
 import matplotlib.pyplot as plt

### 2024-01-12 paper/si_4_others.tex
fix table positions
improve table format

@@
 % Supplementary Table 19: Packages in the DL env
-\begin{table}[h]
+\begin{table}[htbp]
   \centering
   \begin{tabular}{llll}
-    \hline
+    \toprule
     Name                & Version & Build                        & Channel     \\
-    \hline
+    \midrule
     conda               & 4.13.0  & py39h06a4308\textunderscore0 & anaconda    \\
@@
     yaml                & 0.2.5   & h7b6447c\textunderscore0     & anaconda    \\
-    \hline
+    \bottomrule
   \end{tabular}
@@
 % Supplementary Table 20: Packages in data analysis and vis env
-\begin{table}[h]
+\begin{table}[htbp]
   \centering
   \begin{tabular}{llll}
-    \hline
+    \toprule
     Name             & Version & Build                    & Channel \\
-    \hline
+    \midrule
     bokeh            & 3.2.2   & pypi\textunderscore0     & pypi    \\
@@
     tensorflow-macos & 2.13.0  & pypi\textunderscore0     & pypi    \\
-    \hline
+    \bottomrule
   \end{tabular}

### 2024-01-12 paper/si_3_ml.tex
remove extra spacing
adjust spaces
text wrap
fix table positions
adjust figure positioning
improve table format

@@
 % SI Figure 18: d-band venter vs adsorption energy scatter plot
-\begin{figure}
+\begin{figure}[htbp]
   \centering
@@
 % SI Figure 19: Pairwise plot of adsorption energy vs key descriptors
-\begin{figure}
+\begin{figure}[htbp]
   \centering
@@
 % Supplementary Table 15: Notations for elementary descriptors and electronic descriptors
-\begin{table}[h]
+\begin{table}[htbp]
   \centering
-  \begin{tabular}{llll}
-    \hline
+  \begin{tabular}{lp{5cm}lp{5cm}}
+    \toprule
     \multicolumn{2}{c}{Elementary Descriptors}       & \multicolumn{2}{c}{Electronic Descriptors}            \\
-    \hline
+    \midrule
     $R$            & atomic radius                   & $\alpha$, $\beta$, $\gamma$  & lattice parameters     \\
@@
     $V$            & number of valence electrons     &                        &                              \\
-    \hline
+    \bottomrule
   \end{tabular}
@@
 \label{si_sec3.3_input_pipeline}
+
 The format of the 2D array for the eDOS is naturally well-suited for use as neural network inputs.
@@
 % SI Figure 20: Representation of the input eDOS data structure
-\begin{figure}
+\begin{figure}[htbp]
   \centering
@@
 % TODO: check adam citation
-\begin{table}[h]
+\begin{table}[htbp]
   \centering
-  \begin{tabular}{lll}
-    \hline
+  \begin{tabular}{llp{5cm}}
+    \toprule
     \textbf{Hyperparameter} & \textbf{Search Space}                             & \textbf{Description}            \\
-    \hline
+    \midrule
     learningRate  & [10\textsuperscript{-4}, 10\textsuperscript{-2}], log scale & Learning rate of Adam\cite{kingma2017adam} optimizer \\
@@
     br\_act       & "tanh", "relu", "sigmoid" & Activation function of fully connected layers in branch           \\
-    \hline
+    \bottomrule
   \end{tabular}
@@
 % TODO: check adam citation
-\begin{table}[h]
+\begin{table}[htbp]
   \centering
-  \begin{tabular}{lll}
-    \hline
+  \begin{tabular}{llp{6cm}}
+    \toprule
     \textbf{Hyperparameter}   & \textbf{Optimal Value} & \textbf{Description}                \\
-    \hline
+    \midrule
     learningRate  & $10^{-3}$ & Learning rate of Adam\cite{kingma2017adam} optimizer                              \\
@@
     br\_act       & "tanh"    & Activation function of fully connected layers in branch      \\
-    \hline
+    \bottomrule
   \end{tabular}
@@
 % Supplementary Table 18: Prediction MAEs of the CNN model
-\begin{table}[h]
+\begin{table}[htbp]
   \centering
   \begin{tabular}{lll}
-    \hline
+    \toprule
     \textbf{Adsorbate}    & \textbf{Original dataset (eV)} & \textbf{Augmented dataset (eV)} \\
-    \hline
+    \midrule
     CO\textsubscript{2}   & 0.0447 & 0.0336 \\
@@
     H                     & 0.0703 & 0.0646 \\
-    \hline
+    \bottomrule
   \end{tabular}
@@
 % SI Figure 21: Illustration of the eDOS occlusion experiment
-\begin{figure}
+\begin{figure}[htbp]
   \centering
@@
 % SI Figure 22: Occlusion experiment with a masker width of 1
-\begin{figure}
+\begin{figure}[htbp]
   \centering
@@
 % SI Figure 23: Occlusion experiment with a masker width of 3
-\begin{figure}
+\begin{figure}[htbp]
   \centering
@@
 % SI Figure 24: Occlusion experiment with a masker width of 5
-\begin{figure}
+\begin{figure}[htbp]
   \centering
@@
 % SI Figure 25: Occlusion experiment with a masker width of 11
-\begin{figure}
+\begin{figure}[htbp]
   \centering
@@
 % SI Figure 26: Occlusion experiment with a masker width of 21
-\begin{figure}
+\begin{figure}[htbp]
   \centering
@@
 % SI Figure 27: Occlusion experiment with a masker width of 31
-\begin{figure}
+\begin{figure}[htbp]
   \centering
@@
 % SI Figure 28: Occlusion experiment with a masker width of 41
-\begin{figure}
+\begin{figure}[htbp]
   \centering
@@
 % SI Figure 29: Occlusion experiment with a masker width of 51
-\begin{figure}
+\begin{figure}[htbp]
   \centering
@@
 % SI Figure 30: Illustration of the eDOS shifting experiment
-\begin{figure}
+\begin{figure}[htbp]
   \centering
@@
 % SI Figure 31: Shifting experiment on p orbital
-\begin{figure}
+\begin{figure}[htbp]
   \centering

### 2024-01-12 paper/si_3_ml.tex
remove headers bold format
tweak citation

@@
 % Supplementary Table 16: The hyperparameter search space
-% TODO: check adam citation
 \begin{table}[htbp]
@@
     \toprule
-    \textbf{Hyperparameter} & \textbf{Search Space}                             & \textbf{Description}            \\
+    Hyperparameter& Search Space              & Description                                                       \\
     \midrule
-    learningRate  & [10\textsuperscript{-4}, 10\textsuperscript{-2}], log scale & Learning rate of Adam\cite{kingma2017adam} optimizer \\
+    learningRate  & [10\textsuperscript{-4}, 10\textsuperscript{-2}], log scale & Learning rate of Adam \cite{kingma2017adam} optimizer \\
     dropoutRate   & [0, 1]                    & Dropout rate                                                      \\
@@
 % Supplementary Table 17: Optimal hyperparameters identified with Hyperband algorithm
-% TODO: check adam citation
 \begin{table}[htbp]
@@
     \toprule
-    \textbf{Hyperparameter}   & \textbf{Optimal Value} & \textbf{Description}                \\
+    Hyperparameter& Optimal Value & Description                                              \\
     \midrule
-    learningRate  & $10^{-3}$ & Learning rate of Adam\cite{kingma2017adam} optimizer                              \\
+    learningRate  & $10^{-3}$ & Learning rate of Adam \cite{kingma2017adam} optimizer                              \\
     dropoutRate   & 0.3       & Dropout rate                                                 \\
@@
     \toprule
-    \textbf{Adsorbate}    & \textbf{Original dataset (eV)} & \textbf{Augmented dataset (eV)} \\
+    Adsorbate             & Original dataset (eV) & Augmented dataset (eV) \\
     \midrule

### 2024-01-14 paper/arxiv/si_3_ml.tex
move into arxiv dir

--- 2024-01-12 paper/si_3_ml.tex
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_fig18_d-band_eads.png}
+  \includegraphics[width=\textwidth]{si_fig18_d-band_eads.png}
   \caption{\textbf{Scatter plot of d-Band Center and Adsorption Energy Relationships.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_fig19_pairwise_eads_des.png}
+  \includegraphics[width=\textwidth]{si_fig19_pairwise_eads_des.png}
   \caption{\textbf{Pairwise Plot of Adsorption Energy and Key Descriptors.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_fig20_input_dos.png}
+  \includegraphics[width=0.3\textwidth]{si_fig20_input_dos.png}
   \caption{\textbf{Schematic representation of the input eDOS data structure.}}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_fig21_occlusion.png}
+  \includegraphics[width=\textwidth]{si_fig21_occlusion.png}
   \caption{\textbf{Illustration of the eDOS occlusion experiment.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_fig22_occl_wid1.png}
+  \includegraphics[width=0.6\textwidth]{si_fig22_occl_wid1.png}
   \caption{\textbf{Occlusion Experiment with a masker width of “1”.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_fig23_occl_wid3.png}
+  \includegraphics[width=0.6\textwidth]{si_fig23_occl_wid3.png}
   \caption{\textbf{Occlusion Experiment with a masker width of “3”.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_fig24_occl_wid5.png}
+  \includegraphics[width=0.6\textwidth]{si_fig24_occl_wid5.png}
   \caption{\textbf{Occlusion Experiment with a masker width of “5”.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_fig25_occl_wid11.png}
+  \includegraphics[width=0.6\textwidth]{si_fig25_occl_wid11.png}
   \caption{\textbf{Occlusion Experiment with a masker width of “11”.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_fig26_occl_wid21.png}
+  \includegraphics[width=0.6\textwidth]{si_fig26_occl_wid21.png}
   \caption{\textbf{Occlusion Experiment with a masker width of “21”.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_fig27_occl_wid31.png}
+  \includegraphics[width=0.6\textwidth]{si_fig27_occl_wid31.png}
   \caption{\textbf{Occlusion Experiment with a masker width of “31”.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_fig28_occl_wid41.png}
+  \includegraphics[width=0.6\textwidth]{si_fig28_occl_wid41.png}
   \caption{\textbf{Occlusion Experiment with a masker width of “41”.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_fig29_occl_wid51.png}
+  \includegraphics[width=0.6\textwidth]{si_fig29_occl_wid51.png}
   \caption{\textbf{Occlusion Experiment with a masker width of “51”.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_fig30_shifting.png}
+  \includegraphics[width=\textwidth]{si_fig30_shifting.png}
   \caption{\textbf{Illustration of the eDOS shifting experiment.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{si_fig31_p_shifting.png}
+  \includegraphics[width=0.75\textwidth]{si_fig31_p_shifting.png}
   \caption{\textbf{Shifting experiment on p orbital.}

### 2024-01-14 paper/arxiv/si_3_ml.tex
replace curly quotes

@@
 In this study, the array adopts a shape of [numSamplings, numOrbitals, numChannels], as illustrated in \cref{si_fig20:input_dos}.
-Here, “numSamplings” represents the number of data points sampled across the energy spectrum,
-“numOrbitals” denotes the number of DOS orbitals,
-and “numChannels” indicates the number of atomic channels.
+Here, "numSamplings" represents the number of data points sampled across the energy spectrum,
+"numOrbitals" denotes the number of DOS orbitals,
+and "numChannels" indicates the number of atomic channels.
 
@@
   \tablefootnote{The same CNN model, trained on the augmented dataset, was used for all predictions.
-  The term “original dataset” refers to evaluations conducted on the original dataset without any augmented data;
+  The term "original dataset" refers to evaluations conducted on the original dataset without any augmented data;
   it does not imply the use of a different CNN model trained solely on the original dataset.
-  Similarly, “augmented dataset” refers to evaluations on the dataset with both original data and augment data,
+  Similarly, "augmented dataset" refers to evaluations on the dataset with both original data and augment data,
   not a distinct model.}
@@
   This figure demonstrates the step-by-step process of the occlusion experiment.
-  The input eDOS array first undergoes zero-padded, and then a masker of width “width” is applied,
+  The input eDOS array first undergoes zero-padded, and then a masker of width "width" is applied,
   resulting in an occlusion array that preserves the shape of the input array.}
@@
   \includegraphics[width=0.6\textwidth]{si_fig22_occl_wid1.png}
-  \caption{\textbf{Occlusion Experiment with a masker width of “1”.}
+  \caption{\textbf{Occlusion Experiment with a masker width of "1".}
   This figure shows an occlusion experiment on the Ge atom in
@@
   \includegraphics[width=0.6\textwidth]{si_fig23_occl_wid3.png}
-  \caption{\textbf{Occlusion Experiment with a masker width of “3”.}
+  \caption{\textbf{Occlusion Experiment with a masker width of "3".}
   This figure shows an occlusion experiment on the Ge atom in
@@
   \includegraphics[width=0.6\textwidth]{si_fig24_occl_wid5.png}
-  \caption{\textbf{Occlusion Experiment with a masker width of “5”.}
+  \caption{\textbf{Occlusion Experiment with a masker width of "5".}
   This figure shows an occlusion experiment on the Ge atom in
@@
   \includegraphics[width=0.6\textwidth]{si_fig25_occl_wid11.png}
-  \caption{\textbf{Occlusion Experiment with a masker width of “11”.}
+  \caption{\textbf{Occlusion Experiment with a masker width of "11".}
   This figure shows an occlusion experiment on the Ge atom in
@@
   \includegraphics[width=0.6\textwidth]{si_fig26_occl_wid21.png}
-  \caption{\textbf{Occlusion Experiment with a masker width of “21”.}
+  \caption{\textbf{Occlusion Experiment with a masker width of "21".}
   This figure shows an occlusion experiment on the Ge atom in
@@
   \includegraphics[width=0.6\textwidth]{si_fig27_occl_wid31.png}
-  \caption{\textbf{Occlusion Experiment with a masker width of “31”.}
+  \caption{\textbf{Occlusion Experiment with a masker width of "31".}
   This figure shows an occlusion experiment on the Ge atom in
@@
   \includegraphics[width=0.6\textwidth]{si_fig28_occl_wid41.png}
-  \caption{\textbf{Occlusion Experiment with a masker width of “41”.}
+  \caption{\textbf{Occlusion Experiment with a masker width of "41".}
   This figure shows an occlusion experiment on the Ge atom in
@@
   \includegraphics[width=0.6\textwidth]{si_fig29_occl_wid51.png}
-  \caption{\textbf{Occlusion Experiment with a masker width of “51”.}
+  \caption{\textbf{Occlusion Experiment with a masker width of "51".}
   This figure shows an occlusion experiment on the Ge atom in

### 2024-01-14 paper/arxiv/main_4.2_volcano_plots.tex
move into arxiv dir
replace curly quotes

--- 2024-01-09 paper/main_4.2_volcano_plots.tex
@@
-% Results and Discussion Part Two: Hybrid descriptors enabled volcano plot for catalyst analysis
+% Results Part Two: Hybrid descriptors enabled volcano plot for catalyst analysis
 
-\section{Hybrid descriptors enabled volcano plot for catalyst analysis}
+\subsection{Hybrid descriptors enabled volcano plot for catalyst analysis}
 
-\begin{figure}
+\begin{figure}[htbp]
     \centering
-    \includegraphics[width=0.75\linewidth]{main_fig3_volcano.JPG}
-    \caption{\textbf{Limiting Potential Volcano Plot and Periodic Table.}
+    \includegraphics[width=\textwidth]{main_fig3_volcano.png}
+    \caption{\textbf{Limiting Potential Volcano Plot and Periodic Table.}}
     a. Limiting potential volcano plot computed from hybrid-descriptor-based linear scaling relations at -0.17 V vs SHE.
@@
 The activity and selectivity volcano plots imply that enhancing theoretical activity could be achieved by decreasing CO affinity while increasing OH affinity with the catalysts.
-This result suggests a perspective: weak binding of CO to the catalyst surface might facilitate the rotation of C-O backbone from the “upright” configuration in *CO to the “horizontal” orientation in *CHO \cite{peterson2010copper},
+This result suggests a perspective: weak binding of CO to the catalyst surface might facilitate the rotation of C-O backbone from the "upright" configuration in *CO to the "horizontal" orientation in *CHO \cite{peterson2010copper},
 and therefore facilitating dynamics and protonation of the *CO species.

### 2024-01-14 paper/arxiv/supp_3_ml.tex
use formal names for submission

--- 2024-01-14 paper/arxiv/si_3_ml.tex
@@
 \subsection{d-band center and adsorption energy relations}
-\label{si_sec3.1_dband_eads}
+\label{supp_sec3.1_dband_eads}
 
@@
   \centering
-  \includegraphics[width=\textwidth]{si_fig18_d-band_eads.png}
+  \includegraphics[width=\textwidth]{supp_fig18_d-band_eads.png}
   \caption{\textbf{Scatter plot of d-Band Center and Adsorption Energy Relationships.}
@@
   Data from all six substrates investigated in this study are included.}
-  \label{si_fig18:dband_vs_eads}
+  \label{supp_fig18:dband_vs_eads}
 \end{figure}
@@
 \subsection{Feature correlation analysis}
-\label{si_sec3.2_feature_corr}
+\label{supp_sec3.2_feature_corr}
 
@@
   \centering
-  \includegraphics[width=\textwidth]{si_fig19_pairwise_eads_des.png}
+  \includegraphics[width=\textwidth]{supp_fig19_pairwise_eads_des.png}
   \caption{\textbf{Pairwise Plot of Adsorption Energy and Key Descriptors.}
@@
   Data from all six substrates investigated in this study are included.}
-  \label{si_fig19:pairwise_eads_des}
+  \label{supp_fig19:pairwise_eads_des}
 \end{figure}
@@
   \caption{Notations for elementary descriptors and electronic descriptors}
-  \label{si_table15:descriptor_notations}
+  \label{supp_table15:descriptor_notations}
 \end{table}
@@
 \subsection{Input pipeline construction}
-\label{si_sec3.3_input_pipeline}
+\label{supp_sec3.3_input_pipeline}
 
 The format of the 2D array for the eDOS is naturally well-suited for use as neural network inputs.
-In this study, the array adopts a shape of [numSamplings, numOrbitals, numChannels], as illustrated in \cref{si_fig20:input_dos}.
+In this study, the array adopts a shape of [numSamplings, numOrbitals, numChannels], as illustrated in \cref{supp_fig20:input_dos}.
 Here, "numSamplings" represents the number of data points sampled across the energy spectrum,
@@
   \centering
-  \includegraphics[width=0.3\textwidth]{si_fig20_input_dos.png}
+  \includegraphics[width=0.3\textwidth]{supp_fig20_input_dos.png}
   \caption{\textbf{Schematic representation of the input eDOS data structure.}}
-  \label{si_fig20:input_dos}
+  \label{supp_fig20:input_dos}
 \end{figure}
@@
 \subsection{Hyperparameter tuning for CNN}
-\label{si_sec3.4_hyperparam}
+\label{supp_sec3.4_hyperparam}
 
@@
   \caption{The hyperparameter search space}
-  \label{si_table16:hyperparam_space}
+  \label{supp_table16:hyperparam_space}
 \end{table}
@@
   \caption{Optimal hyperparameters identified with Hyperband algorithm}
-  \label{si_table17:opt_hyperparam}
+  \label{supp_table17:opt_hyperparam}
 \end{table}
@@
   not a distinct model.}
-  \label{si_table18:cnn_mae}
+  \label{supp_table18:cnn_mae}
 \end{table}
@@
 \subsection{Occlusion experiment}
-\label{si_sec3.5_occlusion}
+\label{supp_sec3.5_occlusion}
 
@@
   \centering
-  \includegraphics[width=\textwidth]{si_fig21_occlusion.png}
+  \includegraphics[width=\textwidth]{supp_fig21_occlusion.png}
   \caption{\textbf{Illustration of the eDOS occlusion experiment.}
@@
   resulting in an occlusion array that preserves the shape of the input array.}
-  \label{si_fig21:occlusion}
+  \label{supp_fig21:occlusion}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{si_fig22_occl_wid1.png}
+  \includegraphics[width=0.6\textwidth]{supp_fig22_occl_wid1.png}
   \caption{\textbf{Occlusion Experiment with a masker width of "1".}
@@
   the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
-  \label{si_fig22:occl_wid1}
+  \label{supp_fig22:occl_wid1}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{si_fig23_occl_wid3.png}
+  \includegraphics[width=0.6\textwidth]{supp_fig23_occl_wid3.png}
   \caption{\textbf{Occlusion Experiment with a masker width of "3".}
@@
   the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
-  \label{si_fig23:occl_wid3}
+  \label{supp_fig23:occl_wid3}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{si_fig24_occl_wid5.png}
+  \includegraphics[width=0.6\textwidth]{supp_fig24_occl_wid5.png}
   \caption{\textbf{Occlusion Experiment with a masker width of "5".}
@@
   the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
-  \label{si_fig24:occl_wid5}
+  \label{supp_fig24:occl_wid5}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{si_fig25_occl_wid11.png}
+  \includegraphics[width=0.6\textwidth]{supp_fig25_occl_wid11.png}
   \caption{\textbf{Occlusion Experiment with a masker width of "11".}
@@
   the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
-  \label{si_fig25:occl_wid11}
+  \label{supp_fig25:occl_wid11}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{si_fig26_occl_wid21.png}
+  \includegraphics[width=0.6\textwidth]{supp_fig26_occl_wid21.png}
   \caption{\textbf{Occlusion Experiment with a masker width of "21".}
@@
   the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
-  \label{si_fig26:occl_wid21}
+  \label{supp_fig26:occl_wid21}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{si_fig27_occl_wid31.png}
+  \includegraphics[width=0.6\textwidth]{supp_fig27_occl_wid31.png}
   \caption{\textbf{Occlusion Experiment with a masker width of "31".}
@@
   the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
-  \label{si_fig27:occl_wid31}
+  \label{supp_fig27:occl_wid31}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{si_fig28_occl_wid41.png}
+  \includegraphics[width=0.6\textwidth]{supp_fig28_occl_wid41.png}
   \caption{\textbf{Occlusion Experiment with a masker width of "41".}
@@
   the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
-  \label{si_fig28:occl_wid41}
+  \label{supp_fig28:occl_wid41}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{si_fig29_occl_wid51.png}
+  \includegraphics[width=0.6\textwidth]{supp_fig29_occl_wid51.png}
   \caption{\textbf{Occlusion Experiment with a masker width of "51".}
@@
   the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
-  \label{si_fig29:occl_wid51}
+  \label{supp_fig29:occl_wid51}
 \end{figure}
@@
 \subsection{Shifting experiment}
-\label{si_sec3.6_shifting}
+\label{supp_sec3.6_shifting}
 
@@
   \centering
-  \includegraphics[width=\textwidth]{si_fig30_shifting.png}
+  \includegraphics[width=\textwidth]{supp_fig30_shifting.png}
   \caption{\textbf{Illustration of the eDOS shifting experiment.}
@@
   assess the disturbance in adsorption energy caused by the shifting operation.}
-  \label{si_fig30:shifting}
+  \label{supp_fig30:shifting}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.75\textwidth]{si_fig31_p_shifting.png}
+  \includegraphics[width=0.75\textwidth]{supp_fig31_p_shifting.png}
   \caption{\textbf{Shifting experiment on p orbital.}
@@
   A positive eDOS shift indicates a shift towards higher energy levels, and vice versa.}
-  \label{si_fig31:p_shifting}
+  \label{supp_fig31:p_shifting}
 \end{figure}

### 2024-01-14 paper/arxiv/supp_4_others.tex
use formal names for submission

--- 2024-01-12 paper/si_4_others.tex
@@
 \section{Other additional information}
-\label{si_sec4_env}
+\label{supp_sec4_env}
 
 \subsection{Additional information on machine learning environment}
-\label{si_sec4.1_ml_env}
+\label{supp_sec4.1_ml_env}
 
@@
   \tablefootnote{The complete list of packages is provided along with the source code.}
-  \label{si_table19:pack_dl_env}
+  \label{supp_table19:pack_dl_env}
 \end{table}
@@
 \subsection{Additional information on data analysis and visualization environment}
-\label{si_sec4.2_vis_env}
+\label{supp_sec4.2_vis_env}
 
@@
 The illustrations of CNN architecture displayed in \cref{main_fig1:pipeline} of the main text,
-as well as \cref{si_fig21:occlusion} and \cref{si_fig30:shifting},
+as well as \cref{supp_fig21:occlusion} and \cref{supp_fig30:shifting},
 were obtained from the GitHub repository dair-ai/ml-visuals \cite{Saravia_ML_Visuals_2021}.
@@
   \tablefootnote{The complete list of packages is provided along with the source code.}
-  \label{si_table20:pack_vis_env}
+  \label{supp_table20:pack_vis_env}
 \end{table}

### 2024-01-14 paper/arxiv/main_4.2_volcano_plots.tex
name formal names for submission

@@
 By integrating both bonding featured descriptors into the hybrid approach, we found the coefficient of determination ($R^2$) was increased by 0.1387.
-Detailed information about the scaling parameters and performance enhancements are provided in Supplementary \cref{si_table13:scaling_params} and Supplementary \cref{si_fig10:r2_hyb_des}.
+Detailed information about the scaling parameters and performance enhancements are provided in Supplementary \cref{supp_table13:scaling_params} and Supplementary \cref{supp_fig10:r2_hyb_des}.
 This improvement to some extent underscored our premise that CO\textsubscript{2}RR intermediates typically exhibit chemical similarities encompassing both O- and C-type descriptors.
@@
 
-Expanding upon the revised scaling relations, we introduce an activity volcano plot and a rate-determining step (RDS) volcano plot for the CO\textsubscript{2}RR process, shown in \cref{main_fig3:volcano}a and Supplementary \cref{si_fig11:rds_volcano}.
-Given that HER is a key competing reaction with CO\textsubscript{2}RR \cite{goyal2020competition}, we also incorporated a selectivity volcano plot, presented in Supplementary \cref{si_fig12:sel_volc}, to offer a comprehensive analysis of catalyst candidates.
+Expanding upon the revised scaling relations, we introduce an activity volcano plot and a rate-determining step (RDS) volcano plot for the CO\textsubscript{2}RR process, shown in \cref{main_fig3:volcano}a and Supplementary \cref{supp_fig11:rds_volcano}.
+Given that HER is a key competing reaction with CO\textsubscript{2}RR \cite{goyal2020competition}, we also incorporated a selectivity volcano plot, presented in Supplementary \cref{supp_fig12:sel_volc}, to offer a comprehensive analysis of catalyst candidates.
 In adherence to Peterson and Nørskov's original framework \cite{peterson2012activity}, our choice of x and y axes descriptors aligned with $\textit{G}_{\text{ads} \ast \text{CO}}$ and $\textit{G}_{\text{ads} \ast \text{OH}}$.
@@
 Notably, the observed selectivity trend paralleled the activity trend, suggesting that catalysts exhibiting high theoretical activity are also resistant to HER side reactions.
-The RDS volcano plot (Supplementary \cref{si_fig11:rds_volcano}) indicated protonation of *CO as the rate-determining step for nearly optimal candidates.
+The RDS volcano plot (Supplementary \cref{supp_fig11:rds_volcano}) indicated protonation of *CO as the rate-determining step for nearly optimal candidates.
 Moreover, the activity volcano plot predicted an optimal catalyst featuring a theoretical limiting potential of -1.0516 V, at $\textit{G}_{\text{ads} \ast \text{CO}}$ of 0.0589 eV and $\textit{G}_{\text{ads} \ast \text{OH}}$ of -4.0075 eV, positioned at the right-center of the volcano plot.
@@
 
-Additionally, we mapped the theoretical limiting potentials of the analyzed catalyst candidates onto periodic tables, shown in \cref{main_fig3:volcano}b and Supplementary \cref{si_fig13:n-gra_ptable} to Supplementary \cref{si_fig17:C2N_ptable}.
+Additionally, we mapped the theoretical limiting potentials of the analyzed catalyst candidates onto periodic tables, shown in \cref{main_fig3:volcano}b and Supplementary \cref{supp_fig13:n-gra_ptable} to Supplementary \cref{supp_fig17:C2N_ptable}.
 Our analyses do not reveal consistent trends within groups or periods, nor did they exhibit evident patterns across substrates.

### 2024-01-14 paper/arxiv/main_4.4_shifting_exp.tex
name formal names for submission

--- 2024-01-09 paper/main_4.4_shifting_exp.tex
@@
-% Results and Discussion Part Four: Shifting experiments for prediction of better catalysts
+% Results Part Four: Shifting experiments for prediction of better catalysts
 
-\section{Validation of CNN predictions}
+\subsection{Shifting experiments for prediction of better catalysts}
 
-\begin{figure}
+\begin{figure}[htbp]
     \centering
-    \includegraphics[width=0.95\linewidth]{main_fig5_shifting.JPG}
+    \includegraphics[width=\textwidth]{main_fig5_shifting.png}
     \caption{\textbf{Shifting Experiments.}
-    Impact of orbitalwise eDOS shifting on CO adsorption energy, as predicted by the CNN model, for single metal atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.
-    The disturbances caused by shifting of (a)entire $d$, (b)$d_{xy}$, (c)$d_{yz}$, (d)$d_{z^2}$, (e)$d_{xz}$ and (f)$d_{x^2-y^2}$ orbitals are illustrated.
+    Impact of orbitalwise eDOS shifting on CO adsorption energy, as predicted by the CNN model,
+    for single metal atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.
+    The disturbances caused by shifting of (a)entire $d$, (b)$d_{xy}$, (c)$d_{yz}$,
+    (d)$d_{z^2}$, (e)$d_{xz}$ and (f)$d_{x^2-y^2}$ orbitals are illustrated.
     The shifting step size corresponds to the energy resolution of the eDOS, which is 0.005 eV in this study.
@@
 
-While CNN models excel in prediction of the activity of catalyst candidates directly from eDOS, volcano plots point out directions leading to better catalysts.
-Exploring potential disturbances to adsorption energies and aiming to shift existing catalyst candidates closer to the peak of the activity volcano plot presents an intriguing avenue of investigation.
-In this work, we introduce an orbitalwise shifting experiment to explore the impact of orbitalwise eDOS shifting on adsorption behavior.
-The experiment involved shifting eDOS along the energy axis, and the CNN model was deployed to predict the resultant disturbance in adsorption energy for each shifting operation.
+While CNN models excel in prediction of the activity of catalyst candidates directly from eDOS,
+volcano plots point out directions leading to better catalysts.
+Exploring potential disturbances to adsorption energies and aiming to shift existing catalyst
+candidates closer to the peak of the activity volcano plot presents an intriguing avenue of investigation.
+In this work, we introduce an orbitalwise shifting experiment to explore
+the impact of orbitalwise eDOS shifting on adsorption behavior.
+The experiment involved shifting eDOS along the energy axis,
+and the CNN model was deployed to predict the resultant disturbance in adsorption energy for each shifting operation.
 Focusing on all Period 4 metal elements examined in this study, we analyzed the effects of eDOS shifting.
-To induce a moderate disturbance, we selected the energy range of -1 to 1 eV, and a shifting resolution of 0.005 eV/step was chosen to align with the eDOS calculation resolution.
+To induce a moderate disturbance, we selected the energy range of -1 to 1 eV,
+and a shifting resolution of 0.005 eV/step was chosen to align with the eDOS calculation resolution.
 
-\cref{main_fig5:shifting} illustrates that supported Ga and Ge, the sole p-block metals in our study, exhibited no response to d orbital shifting.
-This observation is consistent with their lack of d-electrons in their valence shells, reinforcing the reliability of our shifting experiments.
-We also investigated potential disturbance from p orbital shifting, as shown in Supplementary \cref{si_fig31:p_shifting} and found no significant response.
-This implies that Ge@g-C\textsubscript{3}N\textsubscript{4} holds promise as a CO\textsubscript{2}RR electrocatalyst, given its high activity and resilience to electronic structure disturbances.
+\cref{main_fig5:shifting} illustrates that supported Ga and Ge, the sole p-block metals in our study,
+exhibited no response to d orbital shifting.
+This observation is consistent with their lack of d-electrons in their valence shells,
+reinforcing the reliability of our shifting experiments.
+We also investigated potential disturbance from p orbital shifting,
+as shown in Supplementary \cref{supp_fig31:p_shifting} and found no significant response.
+This implies that Ge@g-C\textsubscript{3}N\textsubscript{4} holds promise as a CO\textsubscript{2}RR electrocatalyst,
+given its high activity and resilience to electronic structure disturbances.
 Nevertheless, fine-tuning its performance through eDOS modulation might pose a challenge.
@@
 Interestingly, the adsorption energy consistently shifted towards more positive values, indicating a weakening of the catalyst-adsorbate interaction, regardless of the shifting direction within the investigated energy range.
-This underscores the intricate interplay between the supported metal atom and the substrate, emphasizing the necessity of a tool like the CNN model to predict such disturbances.
-Supported Cr exhibited a contrary response to eDOS shifting, strengthening the interaction with the CO adsorbate regardless of the shifting direction.
-Supported Ti, V, Co and Ni showed weak response to eDOS shifting, suggesting the need for alternative methods beyond manipulating their eDOS to regulate their interactions with CO adsorbate.
+This underscores the intricate interplay between the supported metal atom and the substrate,
+emphasizing the necessity of a tool like the CNN model to predict such disturbances.
+Supported Cr exhibited a contrary response to eDOS shifting, strengthening the
+interaction with the CO adsorbate regardless of the shifting direction.
+Supported Ti, V, Co and Ni showed weak response to eDOS shifting,
+suggesting the need for alternative methods beyond manipulating their eDOS
+to regulate their interactions with CO adsorbate.
 
-In summary, shifting experiments offer a valuable means to predict the potential disturbances in adsorption behavior resulting from eDOS shifting, a task that is challenging to accomplish directly within the DFT framework.
-However, it's important to note that achieving the predicted shifting in actual theoretical or experimental scenarios may not be easily accessible.
-Skillful manipulation of the electronic structure of catalyst candidates would be required, presenting a practical challenge.
-In contrast to prior studies on bulk metals \cite{fung2021machine}, wherein the adsorption energy exhibits a continuous shift with eDOS variations, the response of SACs is notably discrete.
-These responses manifest as isolated peaks throughout the shifting range, attributed to the distinctive structure of SACs.
-Despite this challenge, having a tool that can predict the potential impact of eDOS shifting is advantageous for the theoretical design of SACs.
+In summary, shifting experiments offer a valuable means to predict the potential
+disturbances in adsorption behavior resulting from eDOS shifting,
+a task that is challenging to accomplish directly within the DFT framework.
+However, it's important to note that achieving the predicted shifting
+in actual theoretical or experimental scenarios may not be easily accessible.
+Skillful manipulation of the electronic structure of catalyst candidates would be required,
+presenting a practical challenge.
+In contrast to prior studies on bulk metals \cite{fung2021machine},
+wherein the adsorption energy exhibits a continuous shift with eDOS variations,
+the response of SACs is notably discrete.
+These responses manifest as isolated peaks throughout the shifting range,
+attributed to the distinctive structure of SACs.
+Despite this challenge, having a tool that can predict the potential impact of
+eDOS shifting is advantageous for the theoretical design of SACs.

### 2024-01-14 paper/arxiv/main_4.1_cnn_for_eads.tex
name formal names for submission

--- 2024-01-10 paper/main_4.1_cnn_for_eads.tex
@@
 
-\begin{figure}
+\begin{figure}[htbp]
     \centering
-    \includegraphics[width=0.7\linewidth]{main_fig2_cnn.JPG}
+    \includegraphics[width=\textwidth]{main_fig2_cnn.png}
     \caption{\textbf{CNN for Electronic Density of States.}
@@
     and some electronic and elementary descriptors.
-    Definitions of the notations are provided in Supplementary \cref{si_table15:descriptor_notations}.
+    Definitions of the notations are provided in Supplementary \cref{supp_table15:descriptor_notations}.
     b-c. Architectural of (b)the root and (c)each branch of the CNN model.
@@
 The correlation coefficient map, as presented in \cref{main_fig2:cnn_for_eads}a, highlighted the d-band center as the most informative descriptor with a Kendall's $\tau$ coefficient of -0.33, and followed by the vacuum level and electronegativity.
-However, d-band center alone does not suffice for accurate predictions of intermediate adsorption energy as illustrated in the scatter plot Supplementary \cref{si_fig18:dband_vs_eads}, and therefore, refinements are imperative.
+However, d-band center alone does not suffice for accurate predictions of intermediate adsorption energy as illustrated in the scatter plot Supplementary \cref{supp_fig18:dband_vs_eads}, and therefore, refinements are imperative.
 Unlike bulk transition metal surfaces, where the variations in the d-band centre account for the majority of the adsorption energy variations \cite{norskov2011density, takigawa2016machine}, the unique structure of SACs introduces more variables rather than d-band center that are intrinsically correlated with the variations of adsorption energy.
@@
 This MAE aligns with the established precision of DFT methods, which typically range between 0.1-0.2 eV concerning experimental measurement \cite{wellendorff2015benchmark, kirklin2015open, lejaeghere2016reproducibility}.
-The full list of prediction errors is available in Supplementary \cref{si_table18:cnn_mae}.
+The full list of prediction errors is available in Supplementary \cref{supp_table18:cnn_mae}.
 These results confirm the CNN model's ability to predict adsorption energies from eDOS input.

### 2024-01-14 paper/arxiv/main_5_methods.tex
move into arxiv dir
name formal names for submission

--- 2024-01-09 paper/main_5_methods.tex
@@
 \section{Methods}
+\label{main_sec_methods}
 
@@
 \subsection{Catalyst models}
-Supported SACs were modelled by anchoring individual metal atoms onto various 2D substrates, including graphitic carbon nitride (g-C\textsubscript{3}N\textsubscript{4}), nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, boron nitride, and monolayer C\textsubscript{2}N.
-The specific single metal atoms studied are outlined in Supplementary \cref{si_fig1:ptable}.
+Supported SACs were modelled by anchoring individual metal atoms onto various 2D substrates,
+including graphitic carbon nitride (g-C\textsubscript{3}N\textsubscript{4}), nitrogen-doped graphene,
+graphene with dual-vacancy, black phosphorous, boron nitride, and monolayer C\textsubscript{2}N.
+The specific single metal atoms studied are outlined in Supplementary \cref{supp_fig1:ptable}.
 To prevent interactions between adjacent images along the z-axis, vacuum layers of 15 \text{\AA} were introduced.
@@
 where $\textit{G}$ represents the free energy, $\textit{E}$ denotes electronic energy, $\textit{E}_{\text{ZPE}}$ is the zero-point energy, $\textit{T}$ represents temperature in Kevin, and $\textit{S}$ stands for entropy.
-Detailed information regarding these corrections can be found in Supplementary \cref{si_sec2.3_energies}.
+Detailed information regarding these corrections can be found in Supplementary \cref{supp_sec2.3_energies}.
 
@@
 \subsection{Hybrid descriptor for volcano plots}
-Hybrid descriptors incorporate both descriptors within a single equation, enhancing the accuracy of scaling relationship with minimal computational overhead, as demonstrated in Supplementary \cref{si_fig10:r2_hyb_des} and Supplementary \cref{si_table13:scaling_params}.
-Comprehensive analyses are presented Supplementary \cref{si_sec2.5_scaling}. This leads to the formulation of the scaling relation:
+Hybrid descriptors incorporate both descriptors within a single equation, enhancing the accuracy of scaling relationship with minimal computational overhead, as demonstrated in Supplementary \cref{supp_fig10:r2_hyb_des} and Supplementary \cref{supp_table13:scaling_params}.
+Comprehensive analyses are presented Supplementary \cref{supp_sec2.5_scaling}. This leads to the formulation of the scaling relation:
 \begin{align}
@@
 To identify the optimal set of hyperparameters, we employed Hyperband \cite{li2018hyperband}, a modern and parallelizable bandit-based optimization algorithm.
-The search space for hyperparameters is detailed in Supplementary \cref{si_table16:hyperparam_space}, and the resulting optimal hyperparameters are presented in Supplementary \cref{si_table17:opt_hyperparam}.
+The search space for hyperparameters is detailed in Supplementary \cref{supp_table16:hyperparam_space}, and the resulting optimal hyperparameters are presented in Supplementary \cref{supp_table17:opt_hyperparam}.
 
@@
 \subsection{Occlusion experiments}
-Supplementary \cref{si_fig21:occlusion} visually illustrates the occlusion experiment methodology.
+Supplementary \cref{supp_fig21:occlusion} visually illustrates the occlusion experiment methodology.
 To maintain consistent shapes, zero-padding was applied to the input eDOS arrays.
 Focusing on understanding the influence of metals on adsorption behavior, a masker with dimensions [width, 1, 1] was employed along the metal channel to eliminate cross-orbital interactions.
-Here, "width" denotes the masker width, and detailed explanations for determining the width are provided in Supplementary \cref{si_sec3.5_occlusion}.
+Here, "width" denotes the masker width, and detailed explanations for determining the width are provided in Supplementary \cref{supp_sec3.5_occlusion}.
 Through recursive application of these maskers, variations in predicted adsorption energies from the CNN model were recorded, generating an occlusion array.
@@
 \subsection{Shifting experiments}
-Supplementary \cref{si_fig30:shifting} illustrates the implemented shifting experiment protocol.
+Supplementary \cref{supp_fig30:shifting} illustrates the implemented shifting experiment protocol.
 In this study, the initial electronic density of states underwent controlled shifting along the energy axis.
@@
 The CNN model was implemented using TensorFlow \cite{abadi2016tensorflow}, and hyperparameter optimization was conducted using the Hyperband \cite{li2018hyperband} algorithm via KerasTuner \cite{omalley2019kerastuner}.
-For a more detailed overview of our machine learning setup and data analysis environment, please refer to Supplementary \cref{si_sec4_env}.
+For a more detailed overview of our machine learning setup and data analysis environment, please refer to Supplementary \cref{supp_sec4_env}.

### 2024-01-14 paper/arxiv/main_1_head.tex
move into arxiv dir
fix affiliation order
fix corr author mark
format fixes

--- 2024-01-09 paper/main_1_head.tex
@@
 \title{Convolutional Neural Networks and Volcano Plots:
-Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions}
+Screening and Prediction of Two-Dimensional Single-Atom Catalysts
+for CO\textsubscript{2} Reduction Reactions}
 
@@
 \author[1]{Haoyu Yang}
-\author[3]{Juanli Zhao}
-\author[4]{Qiankun Wang}
-\author[3]{Bin Liu}
-\author[5]{Wei Luo}
+\author[2]{Juanli Zhao}
+\author[3]{Qiankun Wang}
+\author[2]{Bin Liu}
+\author[4]{Wei Luo}
 \author[1,*]{Ziqi Sun}
-\author[2,**]{Ting Liao}
+\author[5,**]{Ting Liao}
 
 % Affiliations
-\affil[1]{School of Chemistry and Physics, Queensland University of Technology, George Street, Brisbane, QLD 4000, Australia}
-\affil[2]{School of Mechanical Medical and Process Engineering, Queensland University of Technology, George Street, Brisbane, QLD 4000, Australia}
+\affil[1]{School of Chemistry and Physics, Queensland University of Technology,
+George Street, Brisbane, QLD 4000, Australia}
+\affil[2]{School of Mechanical Medical and Process Engineering, Queensland University of Technology,
+George Street, Brisbane, QLD 4000, Australia}
 \affil[3]{School of Materials Science and Engineering, Shanghai University, Shanghai, China}
 \affil[4]{School of Computer Science and Engineering, Southeast University, Nanjing, China}
-\affil[5]{State Key Laboratory for Modification of Chemical Fibers and Polymer Materials, College of Materials Science and Engineering, Institute of Functional Materials, Donghua University, Shanghai, 201620 China}
+\affil[5]{College of Materials Science and Engineering, Institute of Functional Materials,
+Donghua University, Shanghai, China}
 \affil[*]{Corresponding author: ziqi.sun@qut.edu.au}
@@
 
-% Make Title
 \maketitle

### 2024-01-14 paper/arxiv/main_4.2_volcano_plots.tex
format fixes
fix caption text

@@
 
+% Figure 3: Limiting Potential Volcano Plot and Periodic Table
 \begin{figure}[htbp]
@@
     \includegraphics[width=\textwidth]{main_fig3_volcano.png}
-    \caption{\textbf{Limiting Potential Volcano Plot and Periodic Table.}}
+    \caption{\textbf{Limiting Potential Volcano Plot and Periodic Table.}
     a. Limiting potential volcano plot computed from hybrid-descriptor-based linear scaling relations at -0.17 V vs SHE.
@@
     Dotted purple lines delineate regions representing rate-determining steps (RDS), with roman numerals denoting the respective RDS for each region.
-    b. Limiting potential periodic table illustrating the theoretical activity of single atom catalysts, where metals are supported on g-C\textsubscript{3}N\textsubscript{4}.
+    b. Limiting potential periodic table illustrating the theoretical activity of single atom catalysts, where metals are supported on g-C\textsubscript{3}N\textsubscript{4}.}
     \label{main_fig3:volcano}

### 2024-01-14 paper/arxiv/main_4.3_validation.tex
name formal names for submission
format fixes
make subfig symbol bold

--- 2024-01-09 paper/main_4.3_validation.tex
@@
-% Results and Discussion Part Three: Validation of CNN predictions
+% Results Part Three: Validation of CNN predictions
 
-\section{Validation of CNN predictions}
+\subsection{Validation of CNN predictions}
 
-\begin{figure}
+% Figure 4: Validation of CNN Predictions
+\begin{figure}[htbp]
     \centering
-    \includegraphics[width=0.95\linewidth]{main_fig4_validation.JPG}
+    \includegraphics[width=\textwidth]{main_fig4_validation.png}
     \caption{\textbf{Validation of CNN Predictions.}
-    a-c, The occlusion experiment results for (a)Cr $d_{x^2-y^2}$ orbital of Cr@g-C\textsubscript{3}N\textsubscript{4}, (b)Co $d_{xy}$ orbital of Co@g-C\textsubscript{3}N\textsubscript{4} and (c)Cu $d_{xy}$ orbital of Cu@g-C\textsubscript{3}N\textsubscript{4}.
+    \textbf{a}-\textbf{c}, The occlusion experiment results for (\textbf{a})Cr
+    $d_{x^2-y^2}$ orbital of Cr@g-C\textsubscript{3}N\textsubscript{4},
+    (\textbf{b})Co $d_{xy}$ orbital of Co@g-C\textsubscript{3}N\textsubscript{4} and
+    (\textbf{c})Cu $d_{xy}$ orbital of Cu@g-C\textsubscript{3}N\textsubscript{4}.
     Occlusion experiments were conducted on the initial states of CO adsorption process.
-    d-f, Real-space wavefunction visualization for (d)Cr $d_{x^2-y^2}$ orbital of Cr@g-C\textsubscript{3}N\textsubscript{4}, (e)Co $d_{xy}$ orbital of Co@g-C\textsubscript{3}N\textsubscript{4} and (f)Cu $d_{xy}$ orbital of Cu@g-C\textsubscript{3}N\textsubscript{4}.
+    \textbf{d}-\textbf{f}, Real-space wavefunction visualization for (\textbf{d})Cr
+    $d_{x^2-y^2}$ orbital of Cr@g-C\textsubscript{3}N\textsubscript{4}, (\textbf{e})Co
+    $d_{xy}$ orbital of Co@g-C\textsubscript{3}N\textsubscript{4} and (\textbf{f})Cu
+    $d_{xy}$ orbital of Cu@g-C\textsubscript{3}N\textsubscript{4}.
     Wavefunction visualizations were performed on the final states of CO adsorption process.
-    The yellow and aqua colors represent areas of positive and negative Kohn-Sham orbital coefficients, respectively.
-    g-j, Occlusion experiment results for (g)$d_{xy}$ orbital and (h)$d_{xz}$ orbital for Co of Co@g-C\textsubscript{3}N\textsubscript{4}.
-    COHP analysis for (i)$d_{xy}$ orbital and (j)$d_{xz}$ orbital for Co of Co@g-C\textsubscript{3}N\textsubscript{4}, performed between Co and all adsorbate atoms in the final states of CO adsorption process.}
+    The yellow and aqua colors represent areas of positive and negative
+    Kohn-Sham orbital coefficients, respectively.
+    \textbf{g}-\textbf{j}, Occlusion experiment results for (\textbf{g})$d_{xy}$ orbital
+    and (\textbf{h})$d_{xz}$ orbital for Co of Co@g-C\textsubscript{3}N\textsubscript{4}.
+    COHP analysis for (\textbf{i})$d_{xy}$ orbital and (\textbf{j})$d_{xz}$ orbital for
+     Co of Co@g-C\textsubscript{3}N\textsubscript{4}, performed between Co and
+     all adsorbate atoms in the final states of CO adsorption process.}
     \label{main_fig4:validation}
@@
 In this work, occlusion experiments involve orbitalwise masking specific eDOS, which are then fed into the CNN model to observe resulting disturbance in adsorption energy.
-A visual representation of this process can be found in Supplementary \cref{si_fig21:occlusion}.
+A visual representation of this process can be found in Supplementary \cref{supp_fig21:occlusion}.
 Conceptually, this experiment simulates the effect of shielding electronic states, allowing investigation of the potential contribution to adsorption energy from these states.

### 2024-01-14 paper/arxiv/main_4.4_shifting_exp.tex
format fixes
make subfig symbol bold

@@
 
+% Figure 5: Shifting Experiments
 \begin{figure}[htbp]
@@
     for single metal atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.
-    The disturbances caused by shifting of (a)entire $d$, (b)$d_{xy}$, (c)$d_{yz}$,
-    (d)$d_{z^2}$, (e)$d_{xz}$ and (f)$d_{x^2-y^2}$ orbitals are illustrated.
-    The shifting step size corresponds to the energy resolution of the eDOS, which is 0.005 eV in this study.
+    The disturbances caused by shifting of (\textbf{a})entire $d$, (\textbf{b})$d_{xy}$,
+    (\textbf{c})$d_{yz}$, (\textbf{d})$d_{z^2}$, (\textbf{e})$d_{xz}$ and
+    (\textbf{f})$d_{x^2-y^2}$ orbitals are illustrated.
+    The shifting step size corresponds to the energy resolution of the eDOS,
+    which is 0.005 eV in this study.
     A positive eDOS shift indicates a shift towards higher energy levels, and vice versa.}

### 2024-01-14 paper/arxiv/main_4.1_cnn_for_eads.tex
format fixes
make subfig symbol bold

@@
 
+% Figure 2: CNN for eDOS
 \begin{figure}[htbp]
@@
     \caption{\textbf{CNN for Electronic Density of States.}
-    a. Kendall rank correlation map illustrating the correlation between adsorption energy
-    and some electronic and elementary descriptors.
-    Definitions of the notations are provided in Supplementary \cref{supp_table15:descriptor_notations}.
-    b-c. Architectural of (b)the root and (c)each branch of the CNN model.
+    \textbf{a}. Kendall rank correlation map illustrating the correlation
+    between adsorption energy and some electronic and elementary descriptors.
+    Definitions of the notations are provided in
+    Supplementary \cref{supp_table15:descriptor_notations}.
+    \textbf{b}-\textbf{c}. Architectural of (\textbf{b})the root and
+    (\textbf{c})each branch of the CNN model.
     The architecture remains consistent across individual branches.
-    d-m. Parity plots demonstrating the performance of the CNN model across nine adsorbates:
-    (d) all adsorbates, (e) CO\textsubscript{2}, (f)COOH, (g)CO, (h)CHO,
-    (i) CH\textsubscript{2}O, (j) OCH\textsubscript{3}, (k)O, (l)OH, and (m)H.
+    \textbf{d}-\textbf{m}. Parity plots demonstrating the performance of the
+    CNN model across nine adsorbates:
+    (\textbf{d}) all adsorbates, (\textbf{e}) CO\textsubscript{2}, (\textbf{f})COOH,
+    (\textbf{g})CO, (\textbf{h})CHO, (\textbf{i}) CH\textsubscript{2}O,
+    (\textbf{j}) OCH\textsubscript{3}, (\textbf{k})O, (\textbf{l})OH, and (\textbf{m})H.
     The augmentation data are not displayed in the plots nor included in MAE evaluations.

### 2024-01-14 paper/arxiv/supp_3_ml.tex
adjust table spaces
make subfig label bold

@@
   This figure delineates the relationship between d-band center and adsorption energies for
-  various species: (a) CO\textsubscript{2}, (b) COOH, (c) CO, (d) CHO,
-  (e) CH\textsubscript{2}O, (f) OCH\textsubscript{3}, (g) O, and (h) OH.
+  various species: (\textbf{a}) CO\textsubscript{2}, (\textbf{b}) COOH, (\textbf{c}) CO,
+  (\textbf{d}) CHO, (\textbf{e}) CH\textsubscript{2}O, (\textbf{f}) OCH\textsubscript{3},
+  (\textbf{g}) O, and (\textbf{h}) OH.
   Data from all six substrates investigated in this study are included.}

### 2024-01-14 paper/arxiv/supp_3_ml.tex
fix quote signs

@@
 In this study, the array adopts a shape of [numSamplings, numOrbitals, numChannels], as illustrated in \cref{supp_fig20:input_dos}.
-Here, "numSamplings" represents the number of data points sampled across the energy spectrum,
-"numOrbitals" denotes the number of DOS orbitals,
-and "numChannels" indicates the number of atomic channels.
+Here, ``numSamplings'' represents the number of data points sampled across the energy spectrum,
+``numOrbitals'' denotes the number of DOS orbitals,
+and ``numChannels'' indicates the number of atomic channels.
 
@@
     root\_fc1     & 256, 512, 1024, 2048      & Output dimensionality of 2\textsuperscript{nd} fully connected layer in root           \\
-    root\_act     & "tanh", "relu", "sigmoid" & Activation function of fully connected layers in root             \\
+    root\_act     & ``tanh'', ``relu'', ``sigmoid'' & Activation function of fully connected layers in root             \\
     kernelSize    & [2, 32]                   & Width of the convolution window                                   \\
@@
     br\_fc1       & 8, 16, 32, 64, 128, 256   & Output dimensionality of 2\textsuperscript{nd} fully connected layer in branch      \\
-    br\_act       & "tanh", "relu", "sigmoid" & Activation function of fully connected layers in branch           \\
+    br\_act       & ``tanh'', ``relu'', ``sigmoid'' & Activation function of fully connected layers in branch           \\
     \bottomrule
@@
     root\_fc1     & 512       & Output dimensionality of 2\textsuperscript{nd} fully connected layer in root   \\
-    root\_act     & "relu"    & Activation function of fully connected layers in root        \\
+    root\_act     & ``relu''    & Activation function of fully connected layers in root        \\
     kernelSize    & 10        & Width of convolution window                                  \\
@@
     br\_fc1       & 128       & Output dimensionality of 2\textsuperscript{nd} fully connected layer in branch \\
-    br\_act       & "tanh"    & Activation function of fully connected layers in branch      \\
+    br\_act       & ``tanh''    & Activation function of fully connected layers in branch      \\
     \bottomrule
@@
   \tablefootnote{The same CNN model, trained on the augmented dataset, was used for all predictions.
-  The term "original dataset" refers to evaluations conducted on the original dataset without any augmented data;
+  The term ``original dataset'' refers to evaluations conducted on the original dataset without any augmented data;
   it does not imply the use of a different CNN model trained solely on the original dataset.
-  Similarly, "augmented dataset" refers to evaluations on the dataset with both original data and augment data,
+  Similarly, ``augmented dataset'' refers to evaluations on the dataset with both original data and augment data,
   not a distinct model.}
@@
   This figure demonstrates the step-by-step process of the occlusion experiment.
-  The input eDOS array first undergoes zero-padded, and then a masker of width "width" is applied,
+  The input eDOS array first undergoes zero-padded, and then a masker of width ``width'' is applied,
   resulting in an occlusion array that preserves the shape of the input array.}
@@
   \includegraphics[width=0.6\textwidth]{supp_fig22_occl_wid1.png}
-  \caption{\textbf{Occlusion Experiment with a masker width of "1".}
+  \caption{\textbf{Occlusion Experiment with a masker width of ``1''.}
   This figure shows an occlusion experiment on the Ge atom in
@@
   \includegraphics[width=0.6\textwidth]{supp_fig23_occl_wid3.png}
-  \caption{\textbf{Occlusion Experiment with a masker width of "3".}
+  \caption{\textbf{Occlusion Experiment with a masker width of ``3''.}
   This figure shows an occlusion experiment on the Ge atom in
@@
   \includegraphics[width=0.6\textwidth]{supp_fig24_occl_wid5.png}
-  \caption{\textbf{Occlusion Experiment with a masker width of "5".}
+  \caption{\textbf{Occlusion Experiment with a masker width of ``5''.}
   This figure shows an occlusion experiment on the Ge atom in
@@
   \includegraphics[width=0.6\textwidth]{supp_fig25_occl_wid11.png}
-  \caption{\textbf{Occlusion Experiment with a masker width of "11".}
+  \caption{\textbf{Occlusion Experiment with a masker width of ``11''.}
   This figure shows an occlusion experiment on the Ge atom in
@@
   \includegraphics[width=0.6\textwidth]{supp_fig26_occl_wid21.png}
-  \caption{\textbf{Occlusion Experiment with a masker width of "21".}
+  \caption{\textbf{Occlusion Experiment with a masker width of ``21''.}
   This figure shows an occlusion experiment on the Ge atom in
@@
   \includegraphics[width=0.6\textwidth]{supp_fig27_occl_wid31.png}
-  \caption{\textbf{Occlusion Experiment with a masker width of "31".}
+  \caption{\textbf{Occlusion Experiment with a masker width of ``31''.}
   This figure shows an occlusion experiment on the Ge atom in
@@
   \includegraphics[width=0.6\textwidth]{supp_fig28_occl_wid41.png}
-  \caption{\textbf{Occlusion Experiment with a masker width of "41".}
+  \caption{\textbf{Occlusion Experiment with a masker width of ``41''.}
   This figure shows an occlusion experiment on the Ge atom in
@@
   \includegraphics[width=0.6\textwidth]{supp_fig29_occl_wid51.png}
-  \caption{\textbf{Occlusion Experiment with a masker width of "51".}
+  \caption{\textbf{Occlusion Experiment with a masker width of ``51''.}
   This figure shows an occlusion experiment on the Ge atom in

### 2024-01-14 paper/arxiv/main_4.2_volcano_plots.tex
make subfig symbol bold
fix quote signs

@@
     \caption{\textbf{Limiting Potential Volcano Plot and Periodic Table.}
-    a. Limiting potential volcano plot computed from hybrid-descriptor-based linear scaling relations at -0.17 V vs SHE.
+    \textbf{a}. Limiting potential volcano plot computed from hybrid-descriptor-based
+    linear scaling relations at -0.17 V vs SHE.
     In the plot, the circle, triangle, square, diamond, plus, and star symbols represent metals supported on g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, BN, and C\textsubscript{2}N, respectively.
     Dotted purple lines delineate regions representing rate-determining steps (RDS), with roman numerals denoting the respective RDS for each region.
-    b. Limiting potential periodic table illustrating the theoretical activity of single atom catalysts, where metals are supported on g-C\textsubscript{3}N\textsubscript{4}.}
+    \textbf{b}. Limiting potential periodic table illustrating the theoretical activity of
+    single atom catalysts, where metals are supported on g-C\textsubscript{3}N\textsubscript{4}.}
     \label{main_fig3:volcano}
@@
 The activity and selectivity volcano plots imply that enhancing theoretical activity could be achieved by decreasing CO affinity while increasing OH affinity with the catalysts.
-This result suggests a perspective: weak binding of CO to the catalyst surface might facilitate the rotation of C-O backbone from the "upright" configuration in *CO to the "horizontal" orientation in *CHO \cite{peterson2010copper},
+This result suggests a perspective: weak binding of CO to the catalyst surface might facilitate the rotation of C-O backbone from the ``upright'' configuration in *CO to the ``horizontal'' orientation in *CHO \cite{peterson2010copper},
 and therefore facilitating dynamics and protonation of the *CO species.

### 2024-01-14 paper/arxiv/main_5_methods.tex
format fixes
fix quote signs

@@
 \begin{align}
-\mu(H^+) + \mu(e^-) = \frac{1}{2}\mu(H_{2(g)}) - eU  \label{main_eq11:che_potential}
+\mu(\mathrm{H}^+) + \mu(e^-) = \frac{1}{2}\mu(\mathrm{H}_{2(\mathrm{g})}) - eU  \label{main_eq11:che_potential}
 \end{align}
@@
 To enhance the generalizability and robustness of the our CNN model, and achieve comprehensive coverage of the chemical space \cite{DBLP:journals/corr/abs-2112-12542}, we applied data augmentation techniques to the initial dataset using the following procedures:
-	- In addition to the designated "initial state" of the adsorption process, where the adsorbate positioned 6.5 \text{\AA} above the supported single metal atom, five intermediate images were interpolated.
+	- In addition to the designated ``initial state'' of the adsorption process, where the adsorbate positioned 6.5 \text{\AA} above the supported single metal atom, five intermediate images were interpolated.
 These images were distributed between the initial and final states at a spacing of 0.5 \text{\AA}, starting from the initial state side.
@@
 Focusing on understanding the influence of metals on adsorption behavior, a masker with dimensions [width, 1, 1] was employed along the metal channel to eliminate cross-orbital interactions.
-Here, "width" denotes the masker width, and detailed explanations for determining the width are provided in Supplementary \cref{supp_sec3.5_occlusion}.
+Here, ``width'' denotes the masker width, and detailed explanations for determining the width are provided in Supplementary \cref{supp_sec3.5_occlusion}.
 Through recursive application of these maskers, variations in predicted adsorption energies from the CNN model were recorded, generating an occlusion array.

### 2024-01-14 paper/arxiv/supp_1_head.tex
fix date and insert author in SI

--- 2024-01-14 paper/arxiv/main_1_head.tex
@@
-% Title and Authors (Affiliations)
-
-% Title
-\title{Convolutional Neural Networks and Volcano Plots:
-Screening and Prediction of Two-Dimensional Single-Atom Catalysts
-for CO\textsubscript{2} Reduction Reactions}
+% SI title
+\title{Supporting Information for:  \\
+Convolutional Neural Networks and Volcano Plots:
+Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions}
 
@@
 
+% Date
+\date{January 15, 2024}
+
 \maketitle

### 2024-01-15 paper/arxiv/main_3_introduction.tex
move into arxiv dir
format fixes
revise figure captions

--- 2024-01-10 paper/main_3_introduction.tex
@@
 
-\begin{figure}
+% Figure 1: Catalyst Performance Analysis Pipeline
+\begin{figure}[htbp]
     \centering
-    \includegraphics[width=0.95\linewidth]{main_fig1_pipeline.JPG}
+    \includegraphics[width=\textwidth]{main_fig1_pipeline.png}
     \caption{\textbf{Catalyst Performance Analysis Pipeline Integrating Volcano Plots and CNN.}
     The figure demonstrates the integrated usage of volcano plots for
-    predictive assessments of existing catalysts and the utility of CNNs
+    predictive assessment of existing catalysts, and the utility of CNNs
     to predict and modulate adsorption energies \(E_{\text{ads}}\) using eDOS as input.
-    Advanced occlusion and shifting experiments on eDOS are conducted to extract chemical meanings from CNN model.}
+    eDOS occlusion and shifting experiments are conducted to extract chemical information from CNN model.}
     \label{main_fig1:pipeline}

### 2024-01-15 paper/arxiv/main_4.2_volcano_plots.tex
revise figure captions

@@
     \textbf{a}. Limiting potential volcano plot computed from hybrid-descriptor-based
-    linear scaling relations at -0.17 V vs SHE.
-    In the plot, the circle, triangle, square, diamond, plus, and star symbols represent metals supported on g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, BN, and C\textsubscript{2}N, respectively.
-    Dotted purple lines delineate regions representing rate-determining steps (RDS), with roman numerals denoting the respective RDS for each region.
+    linear scaling relations at potential of -0.17 V vs SHE.
+    In the plot, the circle, triangle, square, diamond, plus, and star symbols represent
+    metals supported on g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene,
+    graphene with dual-vacancy, black phosphorous, BN, and C\textsubscript{2}N, respectively.
+    Dotted purple lines delineate regions representing rate-determining steps (RDS),
+    with roman numerals denoting the respective RDS for each region.
     \textbf{b}. Limiting potential periodic table illustrating the theoretical activity of
-    single atom catalysts, where metals are supported on g-C\textsubscript{3}N\textsubscript{4}.}
+    single atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.}
     \label{main_fig3:volcano}

### 2024-01-15 paper/arxiv/main_4.1_cnn_for_eads.tex
revise figure captions

@@
     \textbf{a}. Kendall rank correlation map illustrating the correlation
-    between adsorption energy and some electronic and elementary descriptors.
+    between adsorption energy and other electronic and elementary descriptors.
     Definitions of the notations are provided in
     Supplementary \cref{supp_table15:descriptor_notations}.
-    \textbf{b}-\textbf{c}. Architectural of (\textbf{b})the root and
-    (\textbf{c})each branch of the CNN model.
-    The architecture remains consistent across individual branches.
+    \textbf{b}-\textbf{c}. Architectural of (\textbf{b}) the root and
+    (\textbf{c}) each branch of the CNN model.
+    The architecture stays consistent across individual branches.
     \textbf{d}-\textbf{m}. Parity plots demonstrating the performance of the
     CNN model across nine adsorbates:
-    (\textbf{d}) all adsorbates, (\textbf{e}) CO\textsubscript{2}, (\textbf{f})COOH,
-    (\textbf{g})CO, (\textbf{h})CHO, (\textbf{i}) CH\textsubscript{2}O,
-    (\textbf{j}) OCH\textsubscript{3}, (\textbf{k})O, (\textbf{l})OH, and (\textbf{m})H.
-    The augmentation data are not displayed in the plots nor included in MAE evaluations.
+    (\textbf{d}) all adsorbates, (\textbf{e}) CO\textsubscript{2}, (\textbf{f}) COOH,
+    (\textbf{g}) CO, (\textbf{h}) CHO, (\textbf{i}) CH\textsubscript{2}O,
+    (\textbf{j}) OCH\textsubscript{3}, (\textbf{k}) O, (\textbf{l}) OH, and (\textbf{m}) H.
+    The augmentation data are not displayed in these plots, nor included in MAE evaluations.
     Kernel density estimate results are shown along the top and right sides of the main plot,

### 2024-01-15 paper/arxiv/main_4.3_validation.tex
revise figure captions

@@
     \caption{\textbf{Validation of CNN Predictions.}
-    \textbf{a}-\textbf{c}, The occlusion experiment results for (\textbf{a})Cr
-    $d_{x^2-y^2}$ orbital of Cr@g-C\textsubscript{3}N\textsubscript{4},
-    (\textbf{b})Co $d_{xy}$ orbital of Co@g-C\textsubscript{3}N\textsubscript{4} and
-    (\textbf{c})Cu $d_{xy}$ orbital of Cu@g-C\textsubscript{3}N\textsubscript{4}.
-    Occlusion experiments were conducted on the initial states of CO adsorption process.
-    \textbf{d}-\textbf{f}, Real-space wavefunction visualization for (\textbf{d})Cr
-    $d_{x^2-y^2}$ orbital of Cr@g-C\textsubscript{3}N\textsubscript{4}, (\textbf{e})Co
-    $d_{xy}$ orbital of Co@g-C\textsubscript{3}N\textsubscript{4} and (\textbf{f})Cu
-    $d_{xy}$ orbital of Cu@g-C\textsubscript{3}N\textsubscript{4}.
+    \textbf{a}-\textbf{c}, The eDOS occlusion experiment results for
+    (\textbf{a}) Cr of Cr@g-C\textsubscript{3}N\textsubscript{4},
+    (\textbf{b}) Co of Co@g-C\textsubscript{3}N\textsubscript{4} and
+    (\textbf{c}) Cu of Cu@g-C\textsubscript{3}N\textsubscript{4}.
+    eDOS occlusion experiments were conducted on the initial states of CO adsorption process.
+    \textbf{d}-\textbf{f}, Real-space wavefunction visualization for
+    (\textbf{d}) Cr $d_{x^2-y^2}$ orbital of Cr@g-C\textsubscript{3}N\textsubscript{4},
+    (\textbf{e}) Co $d_{xy}$ orbital of Co@g-C\textsubscript{3}N\textsubscript{4} and
+    (\textbf{f}) Cu $d_{xy}$ orbital of Cu@g-C\textsubscript{3}N\textsubscript{4}.
     Wavefunction visualizations were performed on the final states of CO adsorption process.
@@
     Kohn-Sham orbital coefficients, respectively.
-    \textbf{g}-\textbf{j}, Occlusion experiment results for (\textbf{g})$d_{xy}$ orbital
-    and (\textbf{h})$d_{xz}$ orbital for Co of Co@g-C\textsubscript{3}N\textsubscript{4}.
-    COHP analysis for (\textbf{i})$d_{xy}$ orbital and (\textbf{j})$d_{xz}$ orbital for
+    \textbf{g}-\textbf{j}, Occlusion experiment results for (\textbf{g}) $d_{xy}$ orbital
+    and (\textbf{h}) $d_{xz}$ orbital for Co of Co@g-C\textsubscript{3}N\textsubscript{4}.
+    COHP analysis for (\textbf{i}) $d_{xy}$ orbital and (\textbf{j}) $d_{xz}$ orbital for
     Co of Co@g-C\textsubscript{3}N\textsubscript{4}, performed between Co and

### 2024-01-15 paper/arxiv/main_4.4_shifting_exp.tex
revise figure captions

--- 2024-01-14 paper/arxiv/main_4.4_shifting_exp.tex
@@
     for single metal atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.
-    The disturbances caused by shifting of (a)entire $d$, (b)$d_{xy}$, (c)$d_{yz}$,
-    (d)$d_{z^2}$, (e)$d_{xz}$ and (f)$d_{x^2-y^2}$ orbitals are illustrated.
-    The shifting step size corresponds to the energy resolution of the eDOS, which is 0.005 eV in this study.
+    The disturbances caused by shifting of (\textbf{a}) entire $d$, (\textbf{b}) $d_{xy}$,
+    (\textbf{c}) $d_{yz}$, (\textbf{d}) $d_{z^2}$, (\textbf{e}) $d_{xz}$ and
+    (\textbf{f}) $d_{x^2-y^2}$ orbitals are illustrated.
+    The shifting step size corresponds to the energy resolution of the eDOS,
+    and is 0.005 eV in this study.
     A positive eDOS shift indicates a shift towards higher energy levels, and vice versa.}

### 2024-01-15 paper/arxiv/main_4.2_volcano_plots.tex
tweak caption

@@
     with roman numerals denoting the respective RDS for each region.
+    The reaction steps are defined in \cref{main_eq1:co2rr1} to \cref{main_eq8:co2rr8}.
     \textbf{b}. Limiting potential periodic table illustrating the theoretical activity of
-    single atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.}
+    single metal atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.}
     \label{main_fig3:volcano}

### 2024-01-15 paper/arxiv/supp_3_ml.tex
import SI section 2.2

@@
 \label{supp_sec3.2_feature_corr}
+
+\cref{supp_fig19:pairwise_eads_des} displays the pairwise relationships between CO adsorption energy
+and its four most correlated descriptors: d-band center (spin-up) $\delta\epsilon_{\text{d}}\uparrow$,
+lattice parameter $\gamma$, vacuum level $E_\text{vac}$, and electronegativity
+on the Allen scale $\chi_\text{Allen}$, identified by Kendall rank correlation analysis.
+\cref{supp_table15:descriptor_notations} lists notations for elementary descriptors and electronic descriptors.
 

### 2024-01-15 paper/arxiv/main_6_appendix.tex
merge code and data availability

--- 2024-01-09 paper/main_sections/6_tail.tex
@@
 
-\section{Data Availability}
-Essential source data required to replicate the study's results-including VASP input files,
-structure files of SACs, eDOS arrays and the pretrained CNN model-are available on GitHub
-at \url{https://github.com/DanielYang59/cnn4dos} or can be provided by the corresponding authors upon request.
-Due to their substantial size in terabytes, the complete source data is not currently hosted on publicly available repositories but can also be obtained from the corresponding authors upon request.
-
-\section{Code Availability}
-Associated computer code for this study can be accessed on GitHub at \url{https://github.com/DanielYang59/cnn4dos},
-or obtained from the corresponding authors upon request.
+\section{Code and Data Availability}
+Essential source code and data required to replicate the study's results-including VASP input files,
+structure files of SACs, eDOS arrays and the pretrained CNN model-are available on GitHub repository
+at \url{https://github.com/DanielYang59/cnn4dos}, and can be provided by the corresponding authors upon request.
+Due to their substantial size in terabytes, the complete source data (complete VASP output files and such)
+is not currently hosted on publicly available repositories,
+but can be obtained from the corresponding authors upon request.
 
@@
 The QUT eResearch Office provided computational resources and services used in this work.
-This research was undertaken with the assistance of resources and services from the National Computational Infrastructure (NCI), supported by the Australian Government.
-It was also supported by resources provided by the Pawsey Supercomputing Research Centre with funding from the Australian Government and the Government of Western Australia.
-Insights into deep learning methodologies were contributed by Mr. Yanwei Guan from Chongqing University and Mr. Zhipeng He from Assoc. Prof. Chun Ouyang's team at QUT.
-The machine learning and data analysis implementation benefited from resources provided by the GitHub, TensorFlow and Stack Overflow communities.
-Dr. Ryky Nelson from RWTH Aachen University offered valuable guidance on Crystal Orbital Hamilton Population analysis.
+This research was undertaken with the assistance of resources and services from
+the National Computational Infrastructure (NCI), supported by the Australian Government.
+It was also supported by resources provided by the Pawsey Supercomputing Research Centre
+with funding from the Australian Government and the Government of Western Australia.
+Insights into deep learning methodologies were contributed by Mr. Yanwei Guan
+from Chongqing University and Mr. Zhipeng He from Assoc. Prof. Chun Ouyang's team at QUT.
+The machine learning and data analysis implementation benefited from
+resources provided by the GitHub, TensorFlow and Stack Overflow communities.
+Dr. Ryky Nelson from RWTH Aachen University offered valuable guidance on
+Crystal Orbital Hamilton Population analysis.
 
 \section{Author Contributions}
-H.Y. performed DFT calculations, implemented Python code for machine learning methodologies and data analysis,
+H.Y. performed DFT calculations, implemented Python code for
+machine learning methodologies and data analysis,
 and drafted and refined the manuscript.
@@
 Z.S. initiated the research concept, contributed to manuscript revisions, and supervised the overall research.
-T.L. guided DFT calculations and data analysis, offering continuous supervision throughout the research and manuscript drafting.
+T.L. guided DFT calculations and data analysis, offering continuous supervision
+throughout the research and manuscript drafting.
 

### 2024-01-17 paper/arxiv/supp_3_ml.tex
replace tabular with NiceTabular
rewrite table with NiceTabular

@@
   \centering
-  \begin{tabular}{lp{5cm}lp{5cm}}
+  \begin{NiceTabular}
+    [caption = Notations for elementary descriptors and electronic descriptors]
+    {lp{5cm}lp{5cm}}
     \toprule
@@
     \bottomrule
-  \end{tabular}
-  \caption{Notations for elementary descriptors and electronic descriptors}
+  \end{NiceTabular}
   \label{supp_table15:descriptor_notations}
@@
   \centering
-  \begin{tabular}{llp{5cm}}
+  \begin{NiceTabular}
+    [caption = The hyperparameter search space]
+    {llp{5cm}}
     \toprule
@@
     \bottomrule
-  \end{tabular}
-  \caption{The hyperparameter search space}
+  \end{NiceTabular}
   \label{supp_table16:hyperparam_space}
@@
   \centering
-  \begin{tabular}{llp{6cm}}
+  \begin{NiceTabular}
+    [caption = Optimal hyperparameters identified with Hyperband algorithm]
+    {llp{6cm}}
     \toprule
@@
     \bottomrule
-  \end{tabular}
-  \caption{Optimal hyperparameters identified with Hyperband algorithm}
+  \end{NiceTabular}
   \label{supp_table17:opt_hyperparam}
@@
   \centering
-  \begin{tabular}{lll}
+  \begin{NiceTabular}
+    [caption = Prediction mean absolute errors of the CNN model,
+    tabularnote = \textit{Note:} {The same CNN model, trained on the
+    augmented dataset, was used for all predictions. The term ``original dataset''
+    refers to evaluations conducted on the original dataset without any augmented data;
+    it does not imply the use of a different CNN model trained solely on the original dataset.
+    Similarly, ``augmented dataset'' refers to evaluations on the dataset with
+    both original data and augment data, not a distinct model.}]
+    {lll}
     \toprule
@@
     \bottomrule
-  \end{tabular}
-  \caption{Prediction mean absolute errors of the CNN model}
-  \tablefootnote{The same CNN model, trained on the augmented dataset, was used for all predictions.
-  The term ``original dataset'' refers to evaluations conducted on the original dataset without any augmented data;
-  it does not imply the use of a different CNN model trained solely on the original dataset.
-  Similarly, ``augmented dataset'' refers to evaluations on the dataset with both original data and augment data,
-  not a distinct model.}
+  \end{NiceTabular}
+  \caption{}
   \label{supp_table18:cnn_mae}

### 2024-01-17 paper/arxiv/supp_4_others.tex
adjust table spaces
make subfig label bold
replace tabular with NiceTabular
rewrite table with NiceTabular

@@
 courtesy of the Australian National Computational Infrastructure's (NCI) HPC Gadi system.
-The HyperBand algorithm \cite{li2018hyperband}, as implemented in KerasTuner \cite{omalley2019kerastuner} , facilitated the tuning process.
+The HyperBand algorithm \cite{li2018hyperband}, as implemented in
+KerasTuner \cite{omalley2019kerastuner}, facilitated the tuning process.
 
@@
   \centering
-  \begin{tabular}{llll}
+  \begin{NiceTabular}
+    [caption = Core packages in the deep learning environment,
+    tabularnote = \textit{Note:} The complete list of packages is
+    provided along with the source code.]
+    {llll}
     \toprule
@@
     \bottomrule
-  \end{tabular}
-  \caption{Core packages in the deep learning environment}
-  \tablefootnote{The complete list of packages is provided along with the source code.}
+  \end{NiceTabular}
   \label{supp_table19:pack_dl_env}
@@
   \centering
-  \begin{tabular}{llll}
+  \begin{NiceTabular}
+    [caption = Core packages in data analysis and visualization environment,
+    tabularnote = \textit{Note:} The complete list of packages
+    is provided along with the source code.]
+    {llll}
     \toprule
@@
     \bottomrule
-  \end{tabular}
-  \caption{Core packages in data analysis and visualization environment}
-  \tablefootnote{The complete list of packages is provided along with the source code.}
+  \end{NiceTabular}
   \label{supp_table20:pack_vis_env}

### 2024-01-17 paper/arxiv/main_3_introduction.tex
use sentence-style capitalization

@@
     \includegraphics[width=\textwidth]{main_fig1_pipeline.png}
-    \caption{\textbf{Catalyst Performance Analysis Pipeline Integrating Volcano Plots and CNN.}
+    \caption{\textbf{Catalyst performance analysis pipeline integrating volcano plots and CNN.}
     The figure demonstrates the integrated usage of volcano plots for

### 2024-01-17 paper/arxiv/supp_3_ml.tex
continue clean up tables
clean up table formats

--- 2024-01-15 paper/arxiv/supp_3_ml.tex
@@
 \begin{table}[htbp]
-  \centering
-  \begin{tabular}{lp{5cm}lp{5cm}}
+\label{supp_table15:descriptor_notations}
+  \caption{Notations for elementary descriptors and electronic descriptors}
+  \small
+  \begin{tabularx}{\textwidth}{@{}llll@{}}
     \toprule
@@
     \bottomrule
-  \end{tabular}
-  \caption{Notations for elementary descriptors and electronic descriptors}
-  \label{supp_table15:descriptor_notations}
+  \end{tabularx}
 \end{table}
@@
 \begin{table}[htbp]
-  \centering
-  \begin{tabular}{llp{5cm}}
+\label{supp_table16:hyperparam_space}
+  \caption{The hyperparameter search space}
+  \small
+  \begin{tabularx}{\textwidth}{@{}lXX@{}}
     \toprule
@@
     \bottomrule
-  \end{tabular}
-  \caption{The hyperparameter search space}
-  \label{supp_table16:hyperparam_space}
+  \end{tabularx}
 \end{table}
@@
 \begin{table}[htbp]
-  \centering
-  \begin{tabular}{llp{6cm}}
+\label{supp_table17:opt_hyperparam}
+  \caption{Optimal hyperparameters identified with Hyperband algorithm}
+  \small
+  \begin{tabularx}{\textwidth}{@{}lXX@{}}
     \toprule
@@
     \bottomrule
-  \end{tabular}
-  \caption{Optimal hyperparameters identified with Hyperband algorithm}
-  \label{supp_table17:opt_hyperparam}
+  \end{tabularx}
 \end{table}
@@
 \begin{table}[htbp]
-  \centering
-  \begin{tabular}{lll}
+\label{supp_table18:cnn_mae}
+  \caption{Prediction mean absolute errors of the CNN model}
+  \small
+  \begin{tabularx}{\textwidth}{@{}lXX@{}}
     \toprule
@@
     \bottomrule
-  \end{tabular}
-  \caption{Prediction mean absolute errors of the CNN model}
-  \tablefootnote{The same CNN model, trained on the augmented dataset, was used for all predictions.
-  The term ``original dataset'' refers to evaluations conducted on the original dataset without any augmented data;
+  \end{tabularx}
+  \bigskip
+  \small\textit{Note:} The same CNN model, trained on the
+    augmented dataset, was used for all predictions. The term ``original dataset''
+    refers to evaluations conducted on the original dataset without any augmented data;
     it does not imply the use of a different CNN model trained solely on the original dataset.
-  Similarly, ``augmented dataset'' refers to evaluations on the dataset with both original data and augment data,
-  not a distinct model.}
-  \label{supp_table18:cnn_mae}
+    Similarly, ``augmented dataset'' refers to evaluations on the dataset with
+    both original data and augment data, not a distinct model.
 \end{table}

### 2024-01-17 paper/arxiv/supp_4_others.tex
continue clean up tables
clean up table formats

--- 2024-01-14 paper/arxiv/supp_4_others.tex
@@
 \begin{table}[htbp]
-  \centering
-  \begin{tabular}{llll}
+\label{supp_table19:pack_dl_env}
+  \caption{Core packages in the deep learning environment}
+  \small
+  \begin{tabularx}{\textwidth}{@{}l *{3}{X} @{}}
     \toprule
@@
     \bottomrule
-  \end{tabular}
-  \caption{Core packages in the deep learning environment}
-  \tablefootnote{The complete list of packages is provided along with the source code.}
-  \label{supp_table19:pack_dl_env}
+  \end{tabularx}
+  \bigskip
+  \small\textit{Note:} The complete list of packages is
+    provided along with the source code
 \end{table}
@@
 \begin{table}[htbp]
-  \centering
-  \begin{tabular}{llll}
+\label{supp_table20:pack_vis_env}
+  \caption{Core packages in data analysis and visualization environment}
+  \small
+  \begin{tabularx}{\textwidth}{@{}l *{3}{X} @{}}
     \toprule
@@
     \bottomrule
-  \end{tabular}
-  \caption{Core packages in data analysis and visualization environment}
-  \tablefootnote{The complete list of packages is provided along with the source code.}
-  \label{supp_table20:pack_vis_env}
+  \end{tabularx}
+  \bigskip
+  \small\textit{Note:} The complete list of packages
+    is provided along with the source code.
 \end{table}

### 2024-01-17 paper/arxiv/supp_4_others.tex
fix table note format

@@
   \end{tabularx}
-  \bigskip
-  \small\textit{Note:} The complete list of packages is
+
+  \smallskip
+
+  \footnotesize\textit{Note:} The complete list of packages is
     provided along with the source code
@@
   \end{tabularx}
-  \bigskip
-  \small\textit{Note:} The complete list of packages
+
+  \smallskip
+
+  \footnotesize\textit{Note:} The complete list of packages
     is provided along with the source code.

### 2024-01-18 paper/arxiv/supp_3_ml.tex
fix table note format
adjust table sizes
tweak table caption format

@@
 \label{supp_table15:descriptor_notations}
-  \caption{Notations for elementary descriptors and electronic descriptors}
-  \small
-  \begin{tabularx}{\textwidth}{@{}llll@{}}
+  \caption{Notations for elementary descriptors and electronic descriptors.}
+  \resizebox{\textwidth}{!}{%
+    \begin{tabular}{llll}
       \toprule
@@
       \bottomrule
-  \end{tabularx}
+    \end{tabular}
+  }
 \end{table}
@@
 \label{supp_table16:hyperparam_space}
-  \caption{The hyperparameter search space}
-  \small
-  \begin{tabularx}{\textwidth}{@{}lXX@{}}
+  \caption{The hyperparameter search space.}
+  \resizebox{\textwidth}{!}{%
+    \begin{tabular}{lll}
       \toprule
@@
 \label{supp_table17:opt_hyperparam}
-  \caption{Optimal hyperparameters identified with Hyperband algorithm}
-  \small
-  \begin{tabularx}{\textwidth}{@{}lXX@{}}
+  \caption{Optimal hyperparameters identified with Hyperband algorithm.}
+  \resizebox{\textwidth}{!}{%
+    \begin{tabular}{lll}
       \toprule
@@
 \label{supp_table18:cnn_mae}
-  \caption{Prediction mean absolute errors of the CNN model}
+  \caption{Prediction mean absolute errors of the CNN model.}
   \small
@@
   \end{tabularx}
-  \bigskip
-  \small\textit{Note:} The same CNN model, trained on the
+
+  \smallskip
+
+  \footnotesize\textit{Note:} The same CNN model, trained on the
     augmented dataset, was used for all predictions. The term ``original dataset''

### 2024-01-18 paper/arxiv/supp_4_others.tex
tweak table caption format

@@
 \label{supp_table19:pack_dl_env}
-  \caption{Core packages in the deep learning environment}
+  \caption{Core packages in the deep learning environment.}
   \small
@@
   \footnotesize\textit{Note:} The complete list of packages is
-    provided along with the source code
+    provided along with the source code.
 \end{table}
@@
 \label{supp_table20:pack_vis_env}
-  \caption{Core packages in data analysis and visualization environment}
+  \caption{Core packages in data analysis and visualization environment.}
   \small

### 2024-01-19 paper/arxiv/main_1_head.tex
fix date and insert author in SI
update author mark and date
fix affi order

@@
 \author[1,*]{Ziqi Sun}
-\author[5,**]{Ting Liao}
+\author[5,*]{Ting Liao}
 
@@
 George Street, Brisbane, QLD 4000, Australia}
-\affil[2]{School of Mechanical Medical and Process Engineering, Queensland University of Technology,
+\affil[2]{School of Materials Science and Engineering, Shanghai University, Shanghai, China}
+\affil[3]{School of Computer Science and Engineering, Southeast University, Nanjing, China}
+\affil[4]{College of Materials Science and Engineering, Institute of Functional Materials,
+Donghua University, Shanghai, China}
+\affil[5]{School of Mechanical Medical and Process Engineering, Queensland University of Technology,
 George Street, Brisbane, QLD 4000, Australia}
-\affil[3]{School of Materials Science and Engineering, Shanghai University, Shanghai, China}
-\affil[4]{School of Computer Science and Engineering, Southeast University, Nanjing, China}
-\affil[5]{College of Materials Science and Engineering, Institute of Functional Materials,
-Donghua University, Shanghai, China}
 \affil[*]{Corresponding author: ziqi.sun@qut.edu.au}
-\affil[**]{Corresponding author: t3.liao@qut.edu.au}
+\affil[*]{Corresponding author: t3.liao@qut.edu.au}
+
+% Date
+\date{January 19, 2024}
 

### 2024-01-19 paper/arxiv/supp_1_head.tex
update author mark and date
fix affi order

@@
 George Street, Brisbane, QLD 4000, Australia}
-\affil[2]{School of Mechanical Medical and Process Engineering, Queensland University of Technology,
+\affil[2]{School of Materials Science and Engineering, Shanghai University, Shanghai, China}
+\affil[3]{School of Computer Science and Engineering, Southeast University, Nanjing, China}
+\affil[4]{College of Materials Science and Engineering, Institute of Functional Materials,
+Donghua University, Shanghai, China}
+\affil[5]{School of Mechanical Medical and Process Engineering, Queensland University of Technology,
 George Street, Brisbane, QLD 4000, Australia}
-\affil[3]{School of Materials Science and Engineering, Shanghai University, Shanghai, China}
-\affil[4]{School of Computer Science and Engineering, Southeast University, Nanjing, China}
-\affil[5]{College of Materials Science and Engineering, Institute of Functional Materials,
-Donghua University, Shanghai, China}
 \affil[*]{Corresponding author: ziqi.sun@qut.edu.au}
-\affil[**]{Corresponding author: t3.liao@qut.edu.au}
+\affil[*]{Corresponding author: t3.liao@qut.edu.au}
 
 % Date
-\date{January 15, 2024}
+\date{January 19, 2024}
 

### 2024-01-19 paper/arxiv/main_3_introduction.tex
clean up abbreviations

@@
 rendering manual crafting inadequate \cite{han2021single, thirumalai2018investigating}.
-To streamline this featurization process, we employed convolutional neural networks (CNNs),
-which autonomously derive a hierarchical representation directly from the electronic density of state (eDOS)
+To streamline this featurization process, we employed CNNs,
+which autonomously derive a hierarchical representation directly from the eDOS
 \cite{tran2015learning, socher2012convolutional, krizhevsky2012imagenet}.

### 2024-01-19 paper/arxiv/main_4.2_volcano_plots.tex
use sentence-style capitalization
clean up abbreviations

@@
     \includegraphics[width=\textwidth]{main_fig3_volcano.png}
-    \caption{\textbf{Limiting Potential Volcano Plot and Periodic Table.}
+    \caption{\textbf{Limiting potential volcano plot and periodic table.}
     \textbf{a}. Limiting potential volcano plot computed from hybrid-descriptor-based
@@
     graphene with dual-vacancy, black phosphorous, BN, and C\textsubscript{2}N, respectively.
-    Dotted purple lines delineate regions representing rate-determining steps (RDS),
+    Dotted purple lines delineate regions representing rate-determining steps,
     with roman numerals denoting the respective RDS for each region.
@@
 This adaptation arose from the intuition that most CO\textsubscript{2}RR intermediates are featured with both bonding types rather than any single one in dominance.
-By integrating both bonding featured descriptors into the hybrid approach, we found the coefficient of determination ($R^2$) was increased by 0.1387.
+By integrating both bonding featured descriptors into the hybrid approach, we found the $R^2$ was increased by 0.1387.
 Detailed information about the scaling parameters and performance enhancements are provided in Supplementary \cref{supp_table13:scaling_params} and Supplementary \cref{supp_fig10:r2_hyb_des}.

### 2024-01-27 paper/writing-version/main_2_abstract.tex
rename dir

--- 2024-01-10 paper/main_2_abstract.tex
@@
 elude traditional methodologies in searching optimal SAC systems with superior catalytic performance.
-Herein, by integrating multi-branch Convolutional Neural Network (CNN) analysis models to hybrid descriptor based activity volcano plot,
+Herein, by integrating multi-branch Convolutional Neural Network (CNN) analysis models
+to hybrid descriptor based activity volcano plot,
 two-dimensional (2D) SAC system composed of diverse metallic single atoms anchored on six type of 2D supports,
-including g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, BN, and C\textsubscript{2}N,
-are screened for efficient CO\textsubscript{2} reduction reaction (CO\textsubscript{2}RR).
-Starting from establishing a correlation map between the adsorption energies of intermediates and diverse electronic and elementary descriptors, sole singular descriptor lost magic to predict catalytic activity, including d-band center.
-Deep learning method utilizing multi-branch CNN model therefore was employed, using 2D electronic density of states (eDOS) as input to predict adsorption energies.
-Hybrid-descriptor enveloping both C- and O-types of CO\textsubscript{2}RR intermediates was introduced to construct volcano plots and limiting potential periodic table,
+including graphitic carbon nitride (g-C\textsubscript{3}N\textsubscript{4}), nitrogen-doped graphene,
+graphene with dual-vacancy, black phosphorous, boron nitride (BN), and C\textsubscript{2}N,
+are screened for efficient CO\textsubscript{2}RR.
+Starting from establishing a correlation map between the adsorption energies of
+intermediates and diverse electronic and elementary descriptors,
+sole singular descriptor lost magic to predict catalytic activity, including d-band center.
+Deep learning method utilizing multi-branch CNN model therefore was employed,
+using 2D electronic density of states (eDOS) as input to predict adsorption energies.
+Hybrid-descriptor enveloping both C- and O-types of CO\textsubscript{2}RR intermediates
+was introduced to construct volcano plots and limiting potential periodic table,
 aiming for intuitive screening of catalyst candidates for efficient CO\textsubscript{2} reduction to CH\textsubscript{4}.
@@
 orbitalwise eDOS shifting experiments based on CNN model were employed.
-The study involves examining the adsorption energy and, consequently, catalytic activities while varying supported single atoms.
+The study involves examining the adsorption energy and,
+consequently, catalytic activities while varying supported single atoms.
 This work offers a tangible framework to inform both theoretical screening and experimental synthesis,

### 2024-01-27 paper/writing-version/main_4.4_shifting_exp.tex
rename dir

--- 2024-01-15 paper/arxiv/main_4.4_shifting_exp.tex
@@
     \includegraphics[width=\textwidth]{main_fig5_shifting.png}
-    \caption{\textbf{Shifting Experiments.}
+    \caption{\textbf{eDOS shifting experiments.}
     Impact of orbitalwise eDOS shifting on CO adsorption energy, as predicted by the CNN model,

### 2024-01-27 paper/writing-version/main_4.1_cnn_for_eads.tex
rename dir

--- 2024-01-15 paper/arxiv/main_4.1_cnn_for_eads.tex
@@
     \includegraphics[width=\textwidth]{main_fig2_cnn.png}
-    \caption{\textbf{CNN for Electronic Density of States.}
-    \textbf{a}. Kendall rank correlation map illustrating the correlation
+    \caption{\textbf{CNN for electronic density of states.}
+    \textbf{a}. Kendall rank correlation coefficient map illustrating the correlation
     between adsorption energy and other electronic and elementary descriptors.

### 2024-01-27 paper/arxiv-submission/main.tex
copy for cleanup: arxiv submit

% Journal Paper Main Text Header

% Document Class and Packages
\documentclass[a4paper, 12pt, titlepage]{article}

% Import packages
\usepackage{amsmath}
\usepackage{array}  % Required for m{} column type
\usepackage{bookmark}
\usepackage{booktabs}  % For better horizontal lines
\usepackage{caption}  % To customize captions
\usepackage{cleveref}  % Define Figure/Table cross-ref headers
\usepackage{datetime2}
\usepackage{enumitem}
\usepackage{geometry}  % Adjust page geometry if needed
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{natbib}
\usepackage{nicematrix}
\usepackage{tablefootnote}
\usepackage{textcomp}
\usepackage{siunitx}
\usepackage{xr}  % external cross-ref
\usepackage[affil-it]{authblk}
\usepackage[english]{babel}
\usepackage[version=4]{mhchem}

% Define Figure/Table/Equation cross-reference headers
\crefname{figure}{Figure}{Figures}
\crefname{table}{Table}{Tables}
\crefname{equation}{Equation}{Equations}
\captionsetup{labelfont=bf}  % make caption label bold

\externaldocument{supp}  % for cross-ref

\begin{document}
\pdfoutput=1  % declare PDFLaTeX processing

\newpage
\input{main_1_head.tex}  % Title and Author Information
\newpage
\input{main_2_abstract.tex}
\newpage
\input{main_3_introduction.tex}
\newpage
\input{main_4.1_cnn_for_eads.tex}
\input{main_4.2_volcano_plots.tex}
\input{main_4.3_validation.tex}
\input{main_4.4_shifting_exp.tex}
\newpage
\input{main_5_methods.tex}

\appendix
\newpage
\input{main_6_appendix.tex}  % Appendix

% Bibliography
\newpage
\bibliographystyle{plain}
\bibliography{references}

\end{document}

% Notes:
% Table formatted to APA format following: https://tex.stackexchange.com/questions/681466/annotation-for-table-following-the-apa-style

### 2024-01-27 paper/arxiv-submission/main_5_methods.tex
copy for cleanup: arxiv submit

--- 2024-01-14 paper/arxiv/main_5_methods.tex
@@
 Supported SACs were modelled by anchoring individual metal atoms onto various 2D substrates,
-including graphitic carbon nitride (g-C\textsubscript{3}N\textsubscript{4}), nitrogen-doped graphene,
+including g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene,
 graphene with dual-vacancy, black phosphorous, boron nitride, and monolayer C\textsubscript{2}N.

### 2024-01-27 paper/arxiv-submission/main.tex
remove comments from main
merge main sections

@@
-% Journal Paper Main Text Header
-
-% Document Class and Packages
 \documentclass[a4paper, 12pt, titlepage]{article}
 
-% Import packages
+% TODO: remove unused?
 \usepackage{amsmath}
-\usepackage{array}  % Required for m{} column type
+\usepackage{array}
 \usepackage{bookmark}
-\usepackage{booktabs}  % For better horizontal lines
-\usepackage{caption}  % To customize captions
-\usepackage{cleveref}  % Define Figure/Table cross-ref headers
+\usepackage{booktabs}
+\usepackage{caption}
+\usepackage{cleveref}
 \usepackage{datetime2}
 \usepackage{enumitem}
-\usepackage{geometry}  % Adjust page geometry if needed
+\usepackage{geometry}
 \usepackage{graphicx}
@@
 \usepackage{siunitx}
-\usepackage{xr}  % external cross-ref
+\usepackage{xr}
 \usepackage[affil-it]{authblk}
@@
 
-% Define Figure/Table/Equation cross-reference headers
 \crefname{figure}{Figure}{Figures}
@@
 \crefname{equation}{Equation}{Equations}
-\captionsetup{labelfont=bf}  % make caption label bold
+\captionsetup{labelfont=bf}
 
-\externaldocument{supp}  % for cross-ref
+\externaldocument{supp}  % TODO: remove this?
 
 \begin{document}
-\pdfoutput=1  % declare PDFLaTeX processing
+\pdfoutput=1
 
 \newpage
-\input{main_1_head.tex}  % Title and Author Information
+    \title{Convolutional Neural Networks and Volcano Plots:
+    Screening and Prediction of Two-Dimensional Single-Atom Catalysts
+    for CO\textsubscript{2} Reduction Reactions}
+
+    \author[1]{Haoyu Yang}
+    \author[2]{Juanli Zhao}
+    \author[3]{Qiankun Wang}
+    \author[2]{Bin Liu}
+    \author[4]{Wei Luo}
+    \author[1,*]{Ziqi Sun}
+    \author[5,*]{Ting Liao}
+
+    \affil[1]{School of Chemistry and Physics, Queensland University of Technology,
+    George Street, Brisbane, QLD 4000, Australia}
+    \affil[2]{School of Materials Science and Engineering, Shanghai University, Shanghai, China}
+    \affil[3]{School of Computer Science and Engineering, Southeast University, Nanjing, China}
+    \affil[4]{College of Materials Science and Engineering, Institute of Functional Materials,
+    Donghua University, Shanghai, China}
+    \affil[5]{School of Mechanical Medical and Process Engineering, Queensland University of Technology,
+    George Street, Brisbane, QLD 4000, Australia}
+    \affil[*]{Corresponding author: ziqi.sun@qut.edu.au}
+    \affil[*]{Corresponding author: t3.liao@qut.edu.au}
+
+    \date{January 27, 2024}
+\maketitle
+
 \newpage
-\input{main_2_abstract.tex}
+\begin{abstract}
+    Single-atom catalysts (SACs) have emerged as pivotal frontiers for catalyzing a myriad of chemical reactions,
+    yet the diverse combinations of active elements and support materials, the nature of coordination environments,
+    elude traditional methodologies in searching optimal SAC systems with superior catalytic performance.
+    Herein, by integrating multi-branch Convolutional Neural Network (CNN) analysis models
+    to hybrid descriptor based activity volcano plot,
+    two-dimensional (2D) SAC system composed of diverse metallic single atoms anchored on six type of 2D supports,
+    including graphitic carbon nitride (g-C\textsubscript{3}N\textsubscript{4}), nitrogen-doped graphene,
+    graphene with dual-vacancy, black phosphorous, boron nitride (BN), and C\textsubscript{2}N,
+    are screened for efficient CO\textsubscript{2}RR.
+    Starting from establishing a correlation map between the adsorption energies of
+    intermediates and diverse electronic and elementary descriptors,
+    sole singular descriptor lost magic to predict catalytic activity, including d-band center.
+    Deep learning method utilizing multi-branch CNN model therefore was employed,
+    using 2D electronic density of states (eDOS) as input to predict adsorption energies.
+    Hybrid-descriptor enveloping both C- and O-types of CO\textsubscript{2}RR intermediates
+    was introduced to construct volcano plots and limiting potential periodic table,
+    aiming for intuitive screening of catalyst candidates for efficient CO\textsubscript{2} reduction to CH\textsubscript{4}.
+    The eDOS occlusion experiments were performed to unravel individual orbital contribution to adsorption energy.
+    To explore the electronic scale principle governing practical engineering catalytic CO\textsubscript{2}RR activity,
+    orbitalwise eDOS shifting experiments based on CNN model were employed.
+    The study involves examining the adsorption energy and,
+    consequently, catalytic activities while varying supported single atoms.
+    This work offers a tangible framework to inform both theoretical screening and experimental synthesis,
+    thereby paving the way for systematically designing efficient SACs.
+\end{abstract}
+
 \newpage
-\input{main_3_introduction.tex}
+\section{Introduction}
+
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width=\textwidth]{main_fig1_pipeline.png}
+        \caption{\textbf{Catalyst performance analysis pipeline integrating volcano plots and CNN.}
+        The figure demonstrates the integrated usage of volcano plots for
+        predictive assessment of existing catalysts, and the utility of CNNs
+        to predict and modulate adsorption energies \(E_{\text{ads}}\) using eDOS as input.
+        eDOS occlusion and shifting experiments are conducted to extract chemical information from CNN model.}
+        \label{main_fig1:pipeline}
+    \end{figure}
+
+    Electrochemical CO\textsubscript{2}RR stands as a promising avenue for long-term
+    seasonal energy storage \cite{dinh2018co2} and mitigating excess CO\textsubscript{2} in the atmosphere.
+
+    Despite decades of research, metallic copper remains a leading CO\textsubscript{2}RR electrocatalyst
+    for hydrocarbon production \cite{osella2023co2}, albeit burdened by substantial overpotential
+    and low faradic efficiency and poor operational stability \cite{chen2019identifying, liu2021co2}.
+    In this regard, supported SACs have displayed remarkable activity and selectivity
+    across various catalytic reactions \cite{wang2018heterogeneous, yang2018atomically},
+    leveraging their unique electronic properties and coordination environment.
+    To date, experimental studies have primarily focused on two-electron reduction products
+    due to the facile release of gaseous CO \cite{cai2021insights, ju2017understanding, ren2019isolated}.
+    Consequently, there is a pressing need to modulate the electronic structure of single-atom sites
+    to enable hydrocarbon production at reduced overpotential.
+
+    The challenge towards effective catalysts design lies in understanding the reaction mechanisms.
+    Experimental determination of these mechanisms remains challenging due to
+    the complexity of in situ spectroscopic detection of reaction intermediates \cite{zhao2021revisiting}.
+    Computational modeling, particularly methods based on quantum mechanics (QM) such as density functional theory (DFT),
+    allows for the profiling the energetics of intermediates and unveils structure-activity relationships
+    for identified active sites \cite{feaster2017understanding, carter2008challenges},
+    contributing to understanding of reaction mechanisms.
+    However, the high computational cost of QM methods restricts the
+    accessible catalyst space \cite{jinnouchi2017predicting, cuenya2015nanocatalysis, goldsmith2018machine}.
+
+    In this context, researchers have explored descriptor-based methods
+    to circumvent QM calculations and establish direct correlations
+    between target properties and electronic factors, commonly referred to as descriptors or features.
+    Traditional methods of crafting descriptors, as seen in the d-band model of Hammer and Nørskov \cite{hammer1995electronic},
+    necessitate meticulous selection of chemical properties based on chemical knowledge
+    and are inherently case-dependent \cite{kajita2017universal}.
+    Particularly in the case of SACs, the relationship is intricate,
+    rendering manual crafting inadequate \cite{han2021single, thirumalai2018investigating}.
+    To streamline this featurization process, we employed CNNs,
+    which autonomously derive a hierarchical representation directly from the eDOS
+    \cite{tran2015learning, socher2012convolutional, krizhevsky2012imagenet}.
+    This approach accurately maps to the activity space, negating the need for manual crafting of descriptors
+    and providing a more efficient method to understand and
+    establish the structure-mechanism-activity relationship for electrochemical reactions.
+
+    In this study, we introduced a catalyst performance analysis pipeline (\cref{main_fig1:pipeline})
+    integrating a customized CNN model and volcano plots.
+    Our CNN model accurately estimated the adsorption energies, the activity descriptor,
+    from the eDOS of 2D materials supported single metal catalysts.
+    Evaluations on the adsorption energies of nine intermediates along CO\textsubscript{2}RR
+    and competing hydrogen evolution reaction (HER) as well
+    yielded prediction mean absolute errors (MAEs) at the level of 0.1 eV,
+    which is well aligned with the precision of conventional DFT calculations
+    \cite{kirklin2015open, lejaeghere2016reproducibility, wellendorff2015benchmark}.
+    This result validated the capability of current CNN model to accurately capture intricate spatial information from eDOS.
+    Building on this, we introduced an orbitalwise eDOS occlusion experiment was adopted afterwards
+    inspired from the occlusion technique widely used in computer vision and pattern recognition applications.
+    Systematic eDOS experiment was performed to elucidate orbitalwise contributions to
+    the adsorption energies at different energy levels,
+    which produced consistent outcome from Crystal Orbital Hamilton Population (COHP) analysis
+    and real-space wavefunction visualization.
+    All these results justified the proficiency of CNN model on identifying
+    the dominant orbitals for adsorbate-substrate interactions.
+    Furthermore, orbital-wise eDOS shifting experiment, exploring the impact of orbital-wise eDOS shifting
+    on the adsorption behavior of studied catalysts were performed.
+
+    Simultaneously, we incorporated the volcano plots into the catalysis performance analysis pipeline.
+    Besides offering intuitive analysis of catalyst activities (represented by the elevation of volcanoes),
+    volcano plots points to the directions on how effort can be exerted to identify promising catalyst candidates.
+    Built upon scaling relations \cite{peterson2012activity}, we introduced a hybrid-descriptor scheme
+    incorporating both C- and O-centered species.
+    The scaling coefficient of determination ($R^2$) was increased by 0.1387 using hybrid descriptor,
+    which demonstrate an improved prediction accuracy compared to the well documented single descriptor based method.
+
+    In summary, we introduced a catalyst performance analysis pipeline by
+    integrating CNN and volcano plot analysis, using CO\textsubscript{2}RR as an example proof of concept.
+    The CNN, which correlates eDOS with activity descriptors, establishes a robust electronic structure-activity relationship.
+    Notably, it is capable to predict the influence of eDOS disturbances,
+    caused by either alloying, strain, or defects \cite{norskov2011density, bera2017density, kusada2019emergence},
+    to modulate the catalytic activity of materials,
+    which will offer insights into the intrinsic mechanism for rationalized catalyst optimization strategies.
+    Advancing the current volcano plot method,
+    the involvement of CNN models in catalyst performance analysis pipeline holds enormous promise
+    for advanced exploration of catalysts with superior performance.
+
 \newpage
-\input{main_4.1_cnn_for_eads.tex}
-\input{main_4.2_volcano_plots.tex}
-\input{main_4.3_validation.tex}
-\input{main_4.4_shifting_exp.tex}
+\section{Results}
+
+\subsection{Adsorption energy prediction from electronic density of states with convolutional neural network}
+
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width=\textwidth]{main_fig2_cnn.png}
+        \caption{\textbf{CNN for electronic density of states.}
+        \textbf{a}. Kendall rank correlation coefficient map illustrating the correlation
+        between adsorption energy and other electronic and elementary descriptors.
+        Definitions of the notations are provided in
+        Supplementary \cref{supp_table15:descriptor_notations}.
+        \textbf{b}-\textbf{c}. Architectural of (\textbf{b}) the root and
+        (\textbf{c}) each branch of the CNN model.
+        The architecture stays consistent across individual branches.
+        \textbf{d}-\textbf{m}. Parity plots demonstrating the performance of the
+        CNN model across nine adsorbates:
+        (\textbf{d}) all adsorbates, (\textbf{e}) CO\textsubscript{2}, (\textbf{f}) COOH,
+        (\textbf{g}) CO, (\textbf{h}) CHO, (\textbf{i}) CH\textsubscript{2}O,
+        (\textbf{j}) OCH\textsubscript{3}, (\textbf{k}) O, (\textbf{l}) OH, and (\textbf{m}) H.
+        The augmentation data are not displayed in these plots, nor included in MAE evaluations.
+        Kernel density estimate results are shown along the top and right sides of the main plot,
+        representing DFT calculations and CNN model prediction distributions, respectively.}
+        \label{main_fig2:cnn_for_eads}
+    \end{figure}
+
+    Originating from the pioneering work of Hammer and Nørskov \cite{hammer2000theoretical},
+    the d-band center model has emerged as a successful paradigm for employing descriptor to understand and predict the adsorption behavior on transition metal surfaces.
+    To investigate alternative electronic and elementary descriptors that may serve as more suitable substitutes for the d-band center model in the context of SACs,
+    we performed Kendall rank correlation analysis to account for both linearity and non-linearity \cite{kendall1938new}.
+    The correlation coefficient map, as presented in \cref{main_fig2:cnn_for_eads}a, highlighted the d-band center as the most informative descriptor with a Kendall's $\tau$ coefficient of -0.33, and followed by the vacuum level and electronegativity.
+    However, d-band center alone does not suffice for accurate predictions of intermediate adsorption energy as illustrated in the scatter plot Supplementary \cref{supp_fig18:dband_vs_eads}, and therefore, refinements are imperative.
+    Unlike bulk transition metal surfaces, where the variations in the d-band centre account for the majority of the adsorption energy variations \cite{norskov2011density, takigawa2016machine}, the unique structure of SACs introduces more variables rather than d-band center that are intrinsically correlated with the variations of adsorption energy.
+    This finding also interpreted that in some reported prior studies, indicating that depending solely on the d-band center may be insufficient for accurate adsorption energy predictions in the context of SACs \cite{sun2022going, fung2020descriptors, di2022universal, yuan2020descriptor, huang2020rational}.
+    As a result, the development of a method tailored specifically for catalysts like SACs becomes essential.
+
+    In our study, we employ CNN, a renowned deep learning method proficient in capturing spatial hierarchy from matrix-like data, such as the eDOS.
+    Notably, CNN's autonomy from prior knowledge and human intervention during feature extraction renders it more efficient than traditional machine-learning methods.
+    Our approach harnesses the entire 2D eDOS with a multi-branch CNN model.
+    \cref{main_fig2:cnn_for_eads}b and \cref{main_fig2:cnn_for_eads}c delineate the model and its branches.
+    The workflow involves processing the entire 2D eDOS as input, segregating orbitals into branches, and directing the concatenated outputs through another convolutional block, which generates the adsorption energy prediction.
+    Sharing learnable parameters across branches optimizes computational efficiency.
+    By leveraging the CNN model, we predicted adsorption energies from the eDOS of supported single atoms, and validated through parity plots (\cref{main_fig2:cnn_for_eads}d-m).
+    The model predicts adsorption energies across nine species within the CO\textsubscript{2}RR process and competing HER side reaction, attaining an averaged MAE of 0.06 eV.
+    This MAE aligns with the established precision of DFT methods, which typically range between 0.1-0.2 eV concerning experimental measurement \cite{wellendorff2015benchmark, kirklin2015open, lejaeghere2016reproducibility}.
+    The full list of prediction errors is available in Supplementary \cref{supp_table18:cnn_mae}.
+    These results confirm the CNN model's ability to predict adsorption energies from eDOS input.
+    Moreover, they suggest the potential for predicting adsorption energies for SACs using eDOS, although this would demand more sophisticated feature engineering techniques.
+
+    In terms of adsorption energy prediction, the CNN model maintained consistency across diverse elemental compositions and varied adsorption strengths.
+    It handled species containing oxygen, hydrogen, and carbon atoms equally well, spanning an adsorption energy range from 0 to 10 eV.
+    Significantly, after training the CNN model, making predictions (inferences) scales only linearly with system size and demands considerably less computational resources compared to DFT calculations \cite{chandrasekaran2019solving}.
+    Conversely, unlike QM based methods, which could generate reasonably precise energy estimation for individual candidates, CNN relies on extensive datasets to ensure reliable predictions.
+    In our case, the original dataset comprised 2052 samples, leading to a CNN model with a validation MAE of 0.3725 eV.
+    In pursuit of enhanced prediction accuracy, we proposed a data augmentation method detailed in the Methods section.
+    This augmentation resulted in an expanded dataset of 12312 samples, enhancing prediction performance with a reduced validation MAE of 0.1736 eV.
+    Comparatively, our CNN model diverges from prior attempts, notably Fung's pioneer work \cite{fung2021machine}, by requiring only the eDOS of supported single metal atom alone and adsorbate.
+    This revision eliminated the necessity for a complete set of substrate and adsorbate eDOS and significantly reduced computational cost.
+    We foresee the potential in the applicability of our method to diverse species and electrocatalytic reactions, given the availability of comprehensive datasets.
+    The strength of our CNN model lies in its freedom from element- or adsorbate-specific parameters, relying solely on eDOS as input.
+    This adaptability opens up the possibility for its utilization in a wide array of electrocatalytic studies.
+
+\subsection{Hybrid descriptors enabled volcano plot for catalyst analysis}
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=\textwidth]{main_fig3_volcano.png}
+    \caption{\textbf{Limiting potential volcano plot and periodic table.}
+    \textbf{a}. Limiting potential volcano plot computed from hybrid-descriptor-based
+    linear scaling relations at potential of -0.17 V vs SHE.
+    In the plot, the circle, triangle, square, diamond, plus, and star symbols represent
+    metals supported on g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene,
+    graphene with dual-vacancy, black phosphorous, BN, and C\textsubscript{2}N, respectively.
+    Dotted purple lines delineate regions representing rate-determining steps,
+    with roman numerals denoting the respective RDS for each region.
+    The reaction steps are defined in \cref{main_eq1:co2rr1} to \cref{main_eq8:co2rr8}.
+    \textbf{b}. Limiting potential periodic table illustrating the theoretical activity of
+    single metal atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.}
+    \label{main_fig3:volcano}
+\end{figure}
+
+Catalyst activity volcano plots, built upon the scaling relations proposed by Peterson and Nørskov's \cite{peterson2012activity},
+goes beyond assessment of candidatures' energetics only but to provide informative guidance on discovering catalysts candidates with superior performance \cite{balandin1969modern, deutschmann2000heterogeneous}.
+Our endeavor to improve the accuracy of volcano plots leads to the development of the hybrid-descriptor,
+which encompasses both C- and O- bonding types of CO\textsubscript{2}RR intermediates within the scaling relations.
+This adaptation arose from the intuition that most CO\textsubscript{2}RR intermediates are featured with both bonding types rather than any single one in dominance.
+By integrating both bonding featured descriptors into the hybrid approach, we found the $R^2$ was increased by 0.1387.
+Detailed information about the scaling parameters and performance enhancements are provided in Supplementary \cref{supp_table13:scaling_params} and Supplementary \cref{supp_fig10:r2_hyb_des}.
+This improvement to some extent underscored our premise that CO\textsubscript{2}RR intermediates typically exhibit chemical similarities encompassing both O- and C-type descriptors.
+After taking this dual nature into consideration, our hybrid-descriptor method can evaluate the intermediates adsorption energies more accurately.
+Importantly, the introduction of hybrid descriptors is computationally affordable compared to DFT methods,
+as it involves only a set of linear regressions to identify the optimal mixing ratio, as elaborated in the Methods section.
+
+Expanding upon the revised scaling relations, we introduce an activity volcano plot and a rate-determining step (RDS) volcano plot for the CO\textsubscript{2}RR process, shown in \cref{main_fig3:volcano}a and Supplementary \cref{supp_fig11:rds_volcano}.
+Given that HER is a key competing reaction with CO\textsubscript{2}RR \cite{goyal2020competition}, we also incorporated a selectivity volcano plot, presented in Supplementary \cref{supp_fig12:sel_volc}, to offer a comprehensive analysis of catalyst candidates.
+In adherence to Peterson and Nørskov's original framework \cite{peterson2012activity}, our choice of x and y axes descriptors aligned with $\textit{G}_{\text{ads} \ast \text{CO}}$ and $\textit{G}_{\text{ads} \ast \text{OH}}$.
+Further elaboration on how the limiting potentials were evaluated across the volcano plot can be found in the Methods section.
+Among the candidatures explored, Ge@g-C\textsubscript{3}N\textsubscript{4} emerged as the most promising catalyst, demonstrating theoretical activity at a limiting potential of -1.2126 eV.
+Notably, the observed selectivity trend paralleled the activity trend, suggesting that catalysts exhibiting high theoretical activity are also resistant to HER side reactions.
+The RDS volcano plot (Supplementary \cref{supp_fig11:rds_volcano}) indicated protonation of *CO as the rate-determining step for nearly optimal candidates.
+Moreover, the activity volcano plot predicted an optimal catalyst featuring a theoretical limiting potential of -1.0516 V, at $\textit{G}_{\text{ads} \ast \text{CO}}$ of 0.0589 eV and $\textit{G}_{\text{ads} \ast \text{OH}}$ of -4.0075 eV, positioned at the right-center of the volcano plot.
+Results from RDS volcano plot indicate that protonation of *CO likely serves as the RDS for CO\textsubscript{2}RR.
+Consequently, it should be the focal point for future catalyst designs.
+The activity and selectivity volcano plots imply that enhancing theoretical activity could be achieved by decreasing CO affinity while increasing OH affinity with the catalysts.
+This result suggests a perspective: weak binding of CO to the catalyst surface might facilitate the rotation of C-O backbone from the ``upright'' configuration in *CO to the ``horizontal'' orientation in *CHO \cite{peterson2010copper},
+and therefore facilitating dynamics and protonation of the *CO species.
+
+The volcano plot offers an intuitive analysis of the reaction energetics and provides insights into the mechanisms of the reaction.
+While the volcano plot provides a broad overview, it lacks the ability to delve into lower-level explanations rooted in electronic structures, where detailed electronic interactions and specific bonding mechanisms remain beyond its scope.
+Despite its limitations, the volcano plot serves as a useful tool for identifying focal elementary steps in the reaction pathway that demand closer attention during catalyst design.
+It also highlights directions for further catalyst refinement, and can also be integrated with the shifting experiment discussed later to optimize existing catalysts.
+
+Additionally, we mapped the theoretical limiting potentials of the analyzed catalyst candidates onto periodic tables, shown in \cref{main_fig3:volcano}b and Supplementary \cref{supp_fig13:n-gra_ptable} to Supplementary \cref{supp_fig17:C2N_ptable}.
+Our analyses do not reveal consistent trends within groups or periods, nor did they exhibit evident patterns across substrates.
+These observations suggest intricate interactions between supported metal atoms and substrates.
+The absence of straightforward trends underscores the need for nuanced explorations in understanding these interactions like the CNN model.
+
+\subsection{Validation of CNN predictions}
+
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width=\textwidth]{main_fig4_validation.png}
+        \caption{\textbf{Validation of CNN predictions.}
+        \textbf{a}-\textbf{c}, The eDOS occlusion experiment results for
+        (\textbf{a}) Cr of Cr@g-C\textsubscript{3}N\textsubscript{4},
+        (\textbf{b}) Co of Co@g-C\textsubscript{3}N\textsubscript{4} and
+        (\textbf{c}) Cu of Cu@g-C\textsubscript{3}N\textsubscript{4}.
+        eDOS occlusion experiments were conducted on the initial states of CO adsorption process.
+        \textbf{d}-\textbf{f}, Real-space wavefunction visualization for
+        (\textbf{d}) Cr $d_{x^2-y^2}$ orbital of Cr@g-C\textsubscript{3}N\textsubscript{4},
+        (\textbf{e}) Co $d_{xy}$ orbital of Co@g-C\textsubscript{3}N\textsubscript{4} and
+        (\textbf{f}) Cu $d_{xy}$ orbital of Cu@g-C\textsubscript{3}N\textsubscript{4}.
+        Wavefunction visualizations were performed on the final states of CO adsorption process.
+        The yellow and aqua colors represent areas of positive and negative
+        Kohn-Sham orbital coefficients, respectively.
+        \textbf{g}-\textbf{j}, Occlusion experiment results for (\textbf{g}) $d_{xy}$ orbital
+        and (\textbf{h}) $d_{xz}$ orbital for Co of Co@g-C\textsubscript{3}N\textsubscript{4}.
+        COHP analysis for (\textbf{i}) $d_{xy}$ orbital and (\textbf{j}) $d_{xz}$ orbital for
+        Co of Co@g-C\textsubscript{3}N\textsubscript{4}, performed between Co and
+        all adsorbate atoms in the final states of CO adsorption process.}
+        \label{main_fig4:validation}
+    \end{figure}
+
+    Historically, interpretability has posed challenges for deep learning methods, often rendering their inner workings akin to black boxes \cite{zhang2018interpretable, zhang2018visual, savage2022breaking}.
+    The occlusion technique, widely utilized in Computer Vision \cite{zeiler2014visualizing, kortylewski2020combining, wang2020robust}, involves systematically masking sections of the input matrix to assess their impact on the final prediction score.
+    In our work, we introduce an orbitalwise occlusion method to discern individual orbital contribution to adsorption energy within the CNN model, drawing inspiration from Fung's pioneer integration of this technique into eDOS analysis \cite{fung2021machine}.
+    In this work, occlusion experiments involve orbitalwise masking specific eDOS, which are then fed into the CNN model to observe resulting disturbance in adsorption energy.
+    A visual representation of this process can be found in Supplementary \cref{supp_fig21:occlusion}.
+Conceptually, this experiment simulates the effect of shielding electronic states, allowing investigation of the potential contribution to adsorption energy from these states.
+    Additionally, we attempted to extract the planewave coefficients of Kohn-Sham orbital for wavefunction visualization.
+    This validation step was undertaken to confirm the spatial distribution of the orbitals pinpointed by the occlusion experiments.
+
+    To validate our method, we conducted occlusion experiments on Cr@g-C\textsubscript{3}N\textsubscript{4}, Co@g-C\textsubscript{3}N\textsubscript{4} and Cu@g-C\textsubscript{3}N\textsubscript{4}.
+    Each of these supported metals possesses 3d subshells with different electronic configurations: half-filled, partially filled and fully filled, allowing us to test the universality of our approach.
+    The results of the occlusion experiment on the supported Cr single atom in Cr@g-C\textsubscript{3}N\textsubscript{4} are given in \cref{main_fig4:validation}a.
+    The $d_{x^2-y^2}$ orbital emerges as dominant in CO interaction.
+    Shielding electrons centered around -2 eV significantly alter the adsorption energy, indicating the potency of this orbital.
+    The real-space wavefunction visualization in \cref{main_fig4:validation}d corroborates these findings, highlighting the interaction between the $d_{x^2-y^2}$ orbital of single metal atom and the adsorbate.
+    This suggests the $d_{x^2-y^2}$ orbital of supported Co predominantly influence the interaction with CO, and thus shielding electrons from this orbital markedly disturb the adsorption energy.
+    Additionally, occlusion experiments were performed on the Co $d_xy$ orbital of Co@g-C\textsubscript{3}N\textsubscript{4} (\cref{main_fig4:validation}b) and the $Cu d_xy$ orbital of Cu@g-C\textsubscript{3}N\textsubscript{4} (\cref{main_fig4:validation}c).
+    In both cases, the $d_xy$ orbital was identified as the dominant contributor.
+    While identifying the dominant orbital is crucial, these findings also suggest that interactions with adsorbates occurring out-of-plane are influenced by in-plane orbitals as well.
+    Importantly, it becomes evident that d orbitals do not universally impact interactions with adsorbates, emphasizing the need for case-specific discussions.
+
+    To validate the chemical relevance of predictions made by CNN model, we conducted COHP analysis, a theoretical bond-detecting tool used to identify bonding and anti-bonding contributions to band-structure energy \cite{deringer2011crystal}.
+    In this research, interactions between the supported metal atom and atoms within a 5 \text{\AA} radius were calculated to understand its bonding environment, as detailed in the Methods section.
+    The results of the occlusion experiment on the Co $d_xy$ orbital of Co@g-C\textsubscript{3}N\textsubscript{4}, identified as the dominant orbital via occlusion experiments, were compared with the COHP analysis, as shown in \cref{main_fig4:validation}g and \cref{main_fig4:validation}i.
+    The occlusion experiment pinpointed strong metal-adsorbate interactions at energy levels of -1 eV and -6.3 eV, which were confirmed by the COHP analysis.
+    We then investigated the non-dominant Co $d_xz$ orbital, and the COHP analysis highlighted interactions at -1 eV and -6.5 eV, aligning with the findings from the occlusion experiments.
+
+    In summary, orbitalwise occlusion experiments provide chemical interpretations into deep learning models, enhancing their interpretability.
+    Furthermore, these occlusion results are readily understandable to chemists, enabling the identification of orbitalwise contributions to the adsorption process.
+
+    \subsection{Shifting experiments for prediction of better catalysts}
+
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width=\textwidth]{main_fig5_shifting.png}
+        \caption{\textbf{eDOS shifting experiments.}
+        Impact of orbitalwise eDOS shifting on CO adsorption energy, as predicted by the CNN model,
+        for single metal atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.
+        The disturbances caused by shifting of (\textbf{a}) entire $d$, (\textbf{b}) $d_{xy}$,
+        (\textbf{c}) $d_{yz}$, (\textbf{d}) $d_{z^2}$, (\textbf{e}) $d_{xz}$ and
+        (\textbf{f}) $d_{x^2-y^2}$ orbitals are illustrated.
+        The shifting step size corresponds to the energy resolution of the eDOS,
+        and is 0.005 eV in this study.
+        A positive eDOS shift indicates a shift towards higher energy levels, and vice versa.}
+        \label{main_fig5:shifting}
+    \end{figure}
+
+    While CNN models excel in prediction of the activity of catalyst candidates directly from eDOS,
+    volcano plots point out directions leading to better catalysts.
+    Exploring potential disturbances to adsorption energies and aiming to shift existing catalyst
+    candidates closer to the peak of the activity volcano plot presents an intriguing avenue of investigation.
+    In this work, we introduce an orbitalwise shifting experiment to explore
+    the impact of orbitalwise eDOS shifting on adsorption behavior.
+    The experiment involved shifting eDOS along the energy axis,
+    and the CNN model was deployed to predict the resultant disturbance
+    in adsorption energy for each shifting operation.
+    Focusing on all Period 4 metal elements examined in this study, we analyzed the effects of eDOS shifting.
+    To induce a moderate disturbance, we selected the energy range of -1 to 1 eV,
+    and a shifting resolution of 0.005 eV/step was chosen to align with the eDOS calculation resolution.
+
+    \cref{main_fig5:shifting} illustrates that supported Ga and Ge, the sole p-block metals in our study,
+    exhibited no response to d orbital shifting.
+    This observation is consistent with their lack of d-electrons in their valence shells,
+    reinforcing the reliability of our shifting experiments.
+    We also investigated potential disturbance from p orbital shifting,
+    as shown in Supplementary \cref{supp_fig31:p_shifting} and found no significant response.
+    This implies that Ge@g-C\textsubscript{3}N\textsubscript{4} holds promise as a CO\textsubscript{2}RR electrocatalyst,
+    given its high activity and resilience to electronic structure disturbances.
+    Nevertheless, fine-tuning its performance through eDOS modulation might pose a challenge.
+    In contrast, supported Fe, Cu and Zn display strong sensitivity to eDOS shifting.
+    Interestingly, the adsorption energy consistently shifted towards more positive values,
+    indicating a weakening of the catalyst-adsorbate interaction,
+    regardless of the shifting direction within the investigated energy range.
+    This underscores the intricate interplay between the supported metal atom and the substrate,
+    emphasizing the necessity of a tool like the CNN model to predict such disturbances.
+    Supported Cr exhibited a contrary response to eDOS shifting, strengthening the
+    interaction with the CO adsorbate regardless of the shifting direction.
+    Supported Ti, V, Co and Ni showed weak response to eDOS shifting,
+    suggesting the need for alternative methods beyond manipulating their eDOS
+    to regulate their interactions with CO adsorbate.
+
+    In summary, shifting experiments offer a valuable means to predict the potential
+    disturbances in adsorption behavior resulting from eDOS shifting,
+    a task that is challenging to accomplish directly within the DFT framework.
+    However, it's important to note that achieving the predicted shifting
+    in actual theoretical or experimental scenarios may not be easily accessible.
+    Skillful manipulation of the electronic structure of catalyst candidates would be required,
+    presenting a practical challenge.
+    In contrast to prior studies on bulk metals \cite{fung2021machine},
+    wherein the adsorption energy exhibits a continuous shift with eDOS variations,
+    the response of SACs is notably discrete.
+    These responses manifest as isolated peaks throughout the shifting range,
+    attributed to the distinctive structure of SACs.
+    Despite this challenge, having a tool that can predict the potential impact of
+    eDOS shifting is advantageous for the theoretical design of SACs.
+
 \newpage
-\input{main_5_methods.tex}
+\section{Methods}
+
+    \subsection{DFT calculations}
+    Spin-polarized density functional theory calculations were performed using the Vienna Ab initio Simulation Package (VASP) version 5.4.4 \cite{kresse1996efficient, kresse1996efficiency, kresse1993ab} to optimize geometries and determine the electronic structure.
+    The Perdew-Burke-Ernzerhof (PBE) functional \cite{kresse1996efficient} within the generalized gradient approximation (GGA) \cite{perdew1996generalized} was utilized to describe the electron-ion interactions and electronic exchange correlations.
+    Kohn-Shan equations were approached employing a plane-wave basis set with a cut-off energy of 440 eV.
+    Geometry optimizations were performed using $\Gamma$-Centered K-point meshes of ($2\times2\times1$) until the force on each atom fell below 0.02 eV/\(\mathrm{\AA}^{-1}\).
+    Electronic structure calculations utilized denser K-point meshes of ($3\times3\times1$) and employed self-consistent field (SCF) methods.
+
+    \subsection{Catalyst models}
+    Supported SACs were modelled by anchoring individual metal atoms onto various 2D substrates,
+    including g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene,
+    graphene with dual-vacancy, black phosphorous, boron nitride, and monolayer C\textsubscript{2}N.
+    The specific single metal atoms studied are outlined in Supplementary \cref{supp_fig1:ptable}.
+    To prevent interactions between adjacent images along the z-axis, vacuum layers of 15 \text{\AA} were introduced.
+
+    \subsection{CO\textsubscript{2}RR pathway}
+    The C1 production CO\textsubscript{2}RR pathway, as initially described by Peterson et al.
+\cite{peterson2010copper} and later confirmed by Jiao et al.
+\cite{jiao2017molecular} for g-C\textsubscript{3}N\textsubscript{4} based SACs, involves the following elementary steps.
+    Asterisks (*) indicate species adsorbed on the SAC surfaces:
+
+    \begin{align}
+    \ce{CO2 + H+ + e-          &-> \text{*}COOH}      \label{main_eq1:co2rr1}    \\
+    \ce{\text{*}CO + H+ + e-   &-> \text{*}CHO}       \label{main_eq3:co2rr3}    \\
+    \ce{\text{*}COOH + H+ + e- &-> \text{*}CO + H2O}  \label{main_eq2:co2rr2}    \\
+    \ce{\text{*}CHO + H+ + e-  &-> \text{*}CH2O}      \label{main_eq4:co2rr4}    \\
+    \ce{\text{*}CH2O + H+ + e- &-> \text{*}OCH3}      \label{main_eq5:co2rr5}    \\
+    \ce{\text{*}OCH3 + H+ + e- &-> \text{*}O + CH4}   \label{main_eq6:co2rr6}    \\
+    \ce{\text{*}O + H+ + e-    &-> \text{*}OH}        \label{main_eq7:co2rr7}    \\
+    \ce{\text{*}OH + H+ + e-   &-> \text{*} + H2O}    \label{main_eq8:co2rr8}
+    \end{align}
+
+    \subsection{Free energy calculations}
+    Free energies were computed from electronic energies by considering thermal corrections, incorporating normal mode analysis of all degrees of freedom of adsorbates.
+    The free energy $\textit{G}$ was calculated using the formula:
+    \begin{align}
+    G = E + E_{\text{ZPE}} - TS  \label{main_eq9:free_energy}
+    \end{align}
+
+    where $\textit{G}$ represents the free energy, $\textit{E}$ denotes electronic energy, $\textit{E}_{\text{ZPE}}$ is the zero-point energy, $\textit{T}$ represents temperature in Kevin, and $\textit{S}$ stands for entropy.
+    Detailed information regarding these corrections can be found in Supplementary \cref{supp_sec2.3_energies}.
+
+    The computational hydrogen electrode (CHE) model \cite{peterson2010copper, norskov2004origin} was employed to introduce potential dependence.
+    At the reference electrode surface, the reaction
+    \begin{align}
+    \ce{1/2H2_{(g)}  <-> H+ + e-}  \label{main_eq10:che}
+    \end{align}
+    is in equilibrium, allowing the calculation of the chemical potential of the electron-proton pair as:
+    \begin{align}
+    \mu(\mathrm{H}^+) + \mu(e^-) = \frac{1}{2}\mu(\mathrm{H}_{2(\mathrm{g})}) - eU  \label{main_eq11:che_potential}
+    \end{align}
+    For the external potential $\textit{U}$ applied, the change in free energy ($\Delta \textit{G}$) was determined using the equation:
+    \begin{align}
+    \Delta G_n(U) = \Delta G_n(U=0) + neU  \label{main_eq12:ext_potential_che}
+    \end{align}
+    Here, $\mu$ represents chemical potential, $\textit{U}$ signifies the external potential applied, $\textit{n}$ represents the number of proton-electron pairs transferred, and $\textit{e}$ denotes the elementary charge.
+
+    \subsection{Hybrid descriptor for volcano plots}
+    Hybrid descriptors incorporate both descriptors within a single equation, enhancing the accuracy of scaling relationship with minimal computational overhead, as demonstrated in Supplementary \cref{supp_fig10:r2_hyb_des} and Supplementary \cref{supp_table13:scaling_params}.
+    Comprehensive analyses are presented Supplementary \cref{supp_sec2.5_scaling}. This leads to the formulation of the scaling relation:
+    \begin{align}
+    G_{\text{ads}} Z =
+    k[\theta^* G_{\text{ads}} \ce{CO} + (1-\theta^*) G_{\text{ads}} \ce{OH}] + c_Z  \label{main_eq13:scaling_relation}
+    \end{align}
+    Here, $\theta$ represents the mixing ratio of the CO descriptor, $\textit{Z}$ denotes any adsorbate, and $\textit{k}$ and $\textit{c}_{Z}$ are adsorbate-specific scaling parameters.
+    The optimal mixing ratio $\theta$ is determined through iterative exploration across the range, utilizing a step length of 0.01.
+
+    \ref{main_eq13:scaling_relation} could be simplified to a more general form:
+    \begin{align}
+    G_{\text{ads}} Z =
+    a_Z G_{\text{ads}} \ce{CO} + b_Z G_{\text{ads}} \ce{OH} + c_Z  \label{main_eq14:general_scaling_relation}
+    \end{align}
+    Here, $a_Z$, $b_Z$, $c_Z$ are adsorbate-specific parameters.
+
+    Consequently, the limiting potential $\textit{U}_{L}$ is entirely determined by two descriptors through the following equation:
+    \begin{align}
+    U_L = -\frac{\max\{ \Delta G_i \}}{e}  \label{main_eq15:limiting_potential}
+    \end{align}
+    Where $\Delta G_{i}$ represents the free energy change of reaction step i.
+
+    This approach simplifies the theoretical performance assessment of any catalyst within the scope of our research to only two descriptors: $G_{\textit{ads} \, \textit{CO}}$ and $G_{\textit{ads} \, \textit{OH}}$.
+    This method offers a visual representation of the high-dimensional optimization challenge.
+    To aid visualization, a 2D mesh grid is established, enabling vectorized assessments of limiting potentials across the descriptor value ranges.
+    At each grid point, the limiting potential is computed using \cref{main_eq15:limiting_potential}.
+
+    \subsection{CNN architecture and hyperparameter tuning}
+    We designed our CNN architecture drawing inspiration from its successful implementation in tasks involving electrocardiogram signal classification \cite{weimann2021transfer}, as illustrated in \cref{main_fig2:cnn_for_eads}b and \cref{main_fig2:cnn_for_eads}c.
+    This multi-branched CNN comprises nine branches tailored to handle eDOS orbitals while ensuring a reduced memory footprint.
+
+    The effectiveness of neural network models is intricately tied to the choice of hyperparameters.
+    To identify the optimal set of hyperparameters, we employed Hyperband \cite{li2018hyperband}, a modern and parallelizable bandit-based optimization algorithm.
+    The search space for hyperparameters is detailed in Supplementary \cref{supp_table16:hyperparam_space}, and the resulting optimal hyperparameters are presented in Supplementary \cref{supp_table17:opt_hyperparam}.
+
+    \subsection{Data augmentation and CNN model training}
+    To enhance the generalizability and robustness of the our CNN model, and achieve comprehensive coverage of the chemical space \cite{DBLP:journals/corr/abs-2112-12542}, we applied data augmentation techniques to the initial dataset using the following procedures:
+        - In addition to the designated ``initial state'' of the adsorption process, where the adsorbate positioned 6.5 \text{\AA} above the supported single metal atom, five intermediate images were interpolated.
+These images were distributed between the initial and final states at a spacing of 0.5 \text{\AA}, starting from the initial state side.
+        - A diverse set of smearing techniques was employed to determine of partial occupancies $f_{nk}$, including the tetrahedron method \cite{blochl1994improved} and the Gaussian method.
+For the Gaussian method, the smearing width was varied within the range of 0.01 eV to 0.1 eV.
+This careful selection of methods was made to guarantee reliable and consistent predictions of adsorption energies from the model, regardless of the smearing technique used.
+
+    The augmented dataset comprises 12,312 samples, with adsorption energies having a standard deviation of 1.8117 eV and a variance of 3.2821 eV\textsubscript{2}.
+    Twenty percent of these samples were allocated to the validation set. Throughout the training process, a batch size of 64 was employed to ensure a balanced learning dynamic.
+
+    \subsection{eDOS occlusion experiments}
+    Supplementary \cref{supp_fig21:occlusion} visually illustrates the eDOS occlusion experiment methodology.
+    To maintain consistent shapes, zero-padding was applied to the input eDOS arrays.
+    Focusing on understanding the influence of metals on adsorption behavior,
+    a masker with dimensions [width, 1, 1] was employed along the metal channel
+    to eliminate cross-orbital interactions.
+    Here, ``width'' denotes the masker width, and detailed explanations for determining the width
+    are provided in Supplementary \cref{supp_sec3.5_occlusion}.
+    Through recursive application of these maskers, variations in predicted adsorption energies from the CNN model were recorded, generating an occlusion array.
+
+    \subsection{eDOS shifting experiments}
+    Supplementary \cref{supp_fig30:shifting} illustrates the implemented eDOS shifting experiment protocol.
+    In this study, the initial electronic density of states underwent controlled shifting along the energy axis.
+    This protocol ranges from -1 eV to 1 eV, with a step length of 0.005 eV per image.
+    To maintain a uniform energy window, each image underwent cropping and padding procedures.
+    The resulted output arrays took the form of [400, 1] arrays for simultaneous orbital shifting and [400, 9] arrays for individual orbital shifting.
+    The energy range for shifting was chosen to induce a moderate disturbance to adsorption energy.
+
+    \subsection{Chemical bond analysis and real-space wavefunction visualization}
+    COHP analysis was performed using the Local-Orbital Basis Suite Towards Electronic-Structure Reconstruction (LOBSTER) package  \cite{deringer2011crystal, koga1999analytical, nelson2020lobster, maintz2013analytic, dronskowski1993crystal} version 4.1.0, with the GGA-PBE wavefunctions fitted by S.
+Maintz \cite{koga1999analytical, maintz2016lobster}.
+    A Gaussian smearing for energy integration was employed with a broadening width of 0.05 eV.
+    The quantification of bonding strength between the single metal atom and the substrate was achieved through the summation of interactions with neighboring atoms within a range of 0.5 \text{\AA} to 5.0 \text{\AA} from the single metal atom.
+    Orbitals of interest were confirmed through band-structure analysis, and real-space wavefunctions were subsequently visualized using VASPKIT \cite{wang2021vaspkit} and VESTA \cite{momma2008vesta}.
+
+    \subsection{Machine learning and data analysis environment}
+    The CNN model was implemented using TensorFlow \cite{abadi2016tensorflow}, and hyperparameter optimization was conducted using the Hyperband \cite{li2018hyperband} algorithm via KerasTuner \cite{omalley2019kerastuner}.
+    For a more detailed overview of our machine learning setup and data analysis environment, please refer to Supplementary \cref{supp_sec4_env}.
 
@@
 \newpage
-\input{main_6_appendix.tex}  % Appendix
+    \section{Code and Data Availability}
+    Essential source code and data required to replicate the study's results-including VASP input files,
+    structure files of SACs, eDOS arrays and the pretrained CNN model-are available on GitHub repository
+    at \url{https://github.com/DanielYang59/cnn4dos}, and can be provided by the corresponding authors upon request.
+    Due to their substantial size in terabytes, the complete source data (complete VASP output files and such)
+    is not currently hosted on publicly available repositories,
+    but can be obtained from the corresponding authors upon request.
 
-% Bibliography
+    \section{Acknowledgements}
+    The QUT eResearch Office provided computational resources and services used in this work.
+    This research was undertaken with the assistance of resources and services from
+    the National Computational Infrastructure (NCI), supported by the Australian Government.
+    It was also supported by resources provided by the Pawsey Supercomputing Research Centre
+    with funding from the Australian Government and the Government of Western Australia.
+    Insights into deep learning methodologies were contributed by Mr. Yanwei Guan
+    from Chongqing University and Mr. Zhipeng He from Assoc. Prof. Chun Ouyang's team at QUT.
+    The machine learning and data analysis implementation benefited from
+    resources provided by the GitHub, TensorFlow and Stack Overflow communities.
+    Dr. Ryky Nelson from RWTH Aachen University offered valuable guidance on
+    Crystal Orbital Hamilton Population analysis.
+
+    \section{Author Contributions}
+    H.Y. performed DFT calculations, implemented Python code for
+    machine learning methodologies and data analysis,
+    and drafted and refined the manuscript.
+    J.Z. engaged in valuable discussions on DFT calculations.
+    Q.W. provided advice on the computer code revisions.
+    B.L. provided guidance on DFT calculations and offered research supervision.
+    W.L. facilitated resource acquisition and offered research supervision.
+    Z.S. initiated the research concept, contributed to manuscript revisions, and supervised the overall research.
+    T.L. guided DFT calculations and data analysis, offering continuous supervision
+    throughout the research and manuscript drafting.
+
+    \section{Competing Interests}
+    The authors declare no competing interests in relation to this research.
+
 \newpage
@@
 
-% Notes:
-% Table formatted to APA format following: https://tex.stackexchange.com/questions/681466/annotation-for-table-following-the-apa-style
+\typeout{get arXiv to do 4 passes: Label(s) may have changed. Rerun}

### 2024-02-06 paper/arxiv-submission/main.tex
merge supplement sections
remove TODOs
add comment back anyway
add header comment
resolve: Warning: Token not allowed in a PDF string (Unicode): (hyperref)

@@
+% Main
 \documentclass[a4paper, 12pt, titlepage]{article}
 
-% TODO: remove unused?
 \usepackage{amsmath}
@@
 
-\externaldocument{supp}  % TODO: remove this?
+\externaldocument{supplement}
 
@@
 
+% Title, Authors and Affiliations
 \newpage
@@
 
+% Abstract
 \newpage
@@
 
+% Introduction
 \newpage
@@
 
+    % Figure 1: Catalyst Performance Analysis Pipeline
     \begin{figure}[htbp]
@@
 
+% Results Part One: Adsorption energy prediction from eDOS with CNN
 \subsection{Adsorption energy prediction from electronic density of states with convolutional neural network}
 
+    % Figure 2: CNN for eDOS
     \begin{figure}[htbp]
@@
 
+% Results Part Two: Hybrid descriptors enabled volcano plot for catalyst analysis
 \subsection{Hybrid descriptors enabled volcano plot for catalyst analysis}
 
+    % Figure 3: Limiting Potential Volcano Plot and Periodic Table
     \begin{figure}[htbp]
@@
 
+% Results Part Three: Validation of CNN predictions
 \subsection{Validation of CNN predictions}
 
+    % Figure 4: Validation of CNN Predictions
     \begin{figure}[htbp]
@@
 
-    \subsection{Shifting experiments for prediction of better catalysts}
+% Results Part Four: Shifting experiments for prediction of better catalysts
+\subsection{eDOS shifting experiments for prediction of better catalysts}
 
+    % Figure 5: eDOS Shifting Experiments
     \begin{figure}[htbp]
@@
 
+% Methods
 \newpage
@@
 
-    \subsection{CO\textsubscript{2}RR pathway}
+    \subsection{CO\texorpdfstring{\textsubscript{2}}{2}RR pathway}
     The C1 production CO\textsubscript{2}RR pathway, as initially described by Peterson et al.
@@
 
+% Code/Data Availability, Acknowledgements, Author Contributions and Competing Interests
 \appendix
@@
 \end{document}
-
-\typeout{get arXiv to do 4 passes: Label(s) may have changed. Rerun}

### 2024-02-06 paper/arxiv-submission/main.tex
resolve Float too large for page resolve ""
fix "Command \r invalid in math mode"

@@
 \usepackage[version=4]{mhchem}
+
+\DeclareSIUnit\angstrom{\text {Å}}
 
@@
         \centering
-        \includegraphics[width=\textwidth]{main_fig3_volcano.png}
+        \includegraphics[width=0.9\textwidth]{main_fig3_volcano.png}
         \caption{\textbf{Limiting potential volcano plot and periodic table.}
@@
     Kohn-Shan equations were approached employing a plane-wave basis set with a cut-off energy of 440 eV.
-    Geometry optimizations were performed using $\Gamma$-Centered K-point meshes of ($2\times2\times1$) until the force on each atom fell below 0.02 eV/\(\mathrm{\AA}^{-1}\).
+    Geometry optimizations were performed using $\Gamma$-Centered K-point meshes of ($2\times2\times1$) until the force on each atom fell below \SI{0.02}{\electronvolt\per\angstrom}.
     Electronic structure calculations utilized denser K-point meshes of ($3\times3\times1$) and employed self-consistent field (SCF) methods.

### 2024-02-06 paper/arxiv-submission/main.tex
break long lines

@@
     \subsection{DFT calculations}
-    Spin-polarized density functional theory calculations were performed using the Vienna Ab initio Simulation Package (VASP) version 5.4.4 \cite{kresse1996efficient, kresse1996efficiency, kresse1993ab} to optimize geometries and determine the electronic structure.
-    The Perdew-Burke-Ernzerhof (PBE) functional \cite{kresse1996efficient} within the generalized gradient approximation (GGA) \cite{perdew1996generalized} was utilized to describe the electron-ion interactions and electronic exchange correlations.
+    Spin-polarized density functional theory calculations were performed using
+    the Vienna Ab initio Simulation Package (VASP) version 5.4.4 \cite{kresse1996efficient, kresse1996efficiency, kresse1993ab}
+    to optimize geometries and determine the electronic structure.
+    The Perdew-Burke-Ernzerhof (PBE) functional \cite{kresse1996efficient} within
+    the generalized gradient approximation (GGA) \cite{perdew1996generalized}
+    was utilized to describe the electron-ion interactions and electronic exchange correlations.
     Kohn-Shan equations were approached employing a plane-wave basis set with a cut-off energy of 440 eV.
-    Geometry optimizations were performed using $\Gamma$-Centered K-point meshes of ($2\times2\times1$) until the force on each atom fell below \SI{0.02}{\electronvolt\per\angstrom}.
-    Electronic structure calculations utilized denser K-point meshes of ($3\times3\times1$) and employed self-consistent field (SCF) methods.
+    Geometry optimizations were performed using $\Gamma$-Centered K-point meshes of ($2\times2\times1$)
+    until the force on each atom fell below \SI{0.02}{\electronvolt\per\angstrom}.
+    Electronic structure calculations utilized denser K-point meshes of ($3\times3\times1$)
+    and employed self-consistent field (SCF) methods.
 
@@
     \subsection{CO\texorpdfstring{\textsubscript{2}}{2}RR pathway}
-    The C1 production CO\textsubscript{2}RR pathway, as initially described by Peterson et al.
-\cite{peterson2010copper} and later confirmed by Jiao et al.
-\cite{jiao2017molecular} for g-C\textsubscript{3}N\textsubscript{4} based SACs, involves the following elementary steps.
+    The C1 production CO\textsubscript{2}RR pathway, as initially described by Peterson et al. \cite{peterson2010copper}
+    and later confirmed by Jiao et al. \cite{jiao2017molecular} for
+    g-C\textsubscript{3}N\textsubscript{4} based SACs, involves the following elementary steps.
     Asterisks (*) indicate species adsorbed on the SAC surfaces:
@@
     \subsection{Free energy calculations}
-    Free energies were computed from electronic energies by considering thermal corrections, incorporating normal mode analysis of all degrees of freedom of adsorbates.
+    Free energies were computed from electronic energies by considering thermal corrections,
+    incorporating normal mode analysis of all degrees of freedom of adsorbates.
     The free energy $\textit{G}$ was calculated using the formula:
@@
 
-    where $\textit{G}$ represents the free energy, $\textit{E}$ denotes electronic energy, $\textit{E}_{\text{ZPE}}$ is the zero-point energy, $\textit{T}$ represents temperature in Kevin, and $\textit{S}$ stands for entropy.
+    where $\textit{G}$ represents the free energy, $\textit{E}$ denotes electronic energy,
+    $\textit{E}_{\text{ZPE}}$ is the zero-point energy, $\textit{T}$ represents temperature in Kevin,
+    and $\textit{S}$ stands for entropy.
     Detailed information regarding these corrections can be found in Supplementary \cref{supp_sec2.3_energies}.
 
-    The computational hydrogen electrode (CHE) model \cite{peterson2010copper, norskov2004origin} was employed to introduce potential dependence.
+    The computational hydrogen electrode (CHE) model \cite{peterson2010copper, norskov2004origin}
+    was employed to introduce potential dependence.
     At the reference electrode surface, the reaction
@@
     \end{align}
-    For the external potential $\textit{U}$ applied, the change in free energy ($\Delta \textit{G}$) was determined using the equation:
+    For the external potential $\textit{U}$ applied, the change in free energy ($\Delta \textit{G}$)
+    was determined using the equation:
     \begin{align}
@@
     \end{align}
-    Here, $\mu$ represents chemical potential, $\textit{U}$ signifies the external potential applied, $\textit{n}$ represents the number of proton-electron pairs transferred, and $\textit{e}$ denotes the elementary charge.
+    Here, $\mu$ represents chemical potential, $\textit{U}$ signifies the external potential applied,
+    $\textit{n}$ represents the number of proton-electron pairs transferred,
+    and $\textit{e}$ denotes the elementary charge.
 
     \subsection{Hybrid descriptor for volcano plots}
-    Hybrid descriptors incorporate both descriptors within a single equation, enhancing the accuracy of scaling relationship with minimal computational overhead, as demonstrated in Supplementary \cref{supp_fig10:r2_hyb_des} and Supplementary \cref{supp_table13:scaling_params}.
-    Comprehensive analyses are presented Supplementary \cref{supp_sec2.5_scaling}. This leads to the formulation of the scaling relation:
+    Hybrid descriptors incorporate both descriptors within a single equation,
+    enhancing the accuracy of scaling relationship with minimal computational overhead,
+    as demonstrated in Supplementary \cref{supp_fig10:r2_hyb_des} and Supplementary \cref{supp_table13:scaling_params}.
+    Comprehensive analyses are presented Supplementary \cref{supp_sec2.5_scaling}.
+    This leads to the formulation of the scaling relation:
     \begin{align}
@@
     \end{align}
-    Here, $\theta$ represents the mixing ratio of the CO descriptor, $\textit{Z}$ denotes any adsorbate, and $\textit{k}$ and $\textit{c}_{Z}$ are adsorbate-specific scaling parameters.
-    The optimal mixing ratio $\theta$ is determined through iterative exploration across the range, utilizing a step length of 0.01.
+    Here, $\theta$ represents the mixing ratio of the CO descriptor, $\textit{Z}$ denotes any adsorbate,
+    and $\textit{k}$ and $\textit{c}_{Z}$ are adsorbate-specific scaling parameters.
+    The optimal mixing ratio $\theta$ is determined through iterative exploration across the range,
+    utilizing a step length of 0.01.
 
@@
 
-    Consequently, the limiting potential $\textit{U}_{L}$ is entirely determined by two descriptors through the following equation:
+    Consequently, the limiting potential $\textit{U}_{L}$ is entirely determined
+    by two descriptors through the following equation:
     \begin{align}
@@
 
-    This approach simplifies the theoretical performance assessment of any catalyst within the scope of our research to only two descriptors: $G_{\textit{ads} \, \textit{CO}}$ and $G_{\textit{ads} \, \textit{OH}}$.
+    This approach simplifies the theoretical performance assessment of any catalyst
+    within the scope of our research to only two descriptors:
+    $G_{\textit{ads} \, \textit{CO}}$ and $G_{\textit{ads} \, \textit{OH}}$.
     This method offers a visual representation of the high-dimensional optimization challenge.
-    To aid visualization, a 2D mesh grid is established, enabling vectorized assessments of limiting potentials across the descriptor value ranges.
+    To aid visualization, a 2D mesh grid is established, enabling vectorized assessments of
+    limiting potentials across the descriptor value ranges.
     At each grid point, the limiting potential is computed using \cref{main_eq15:limiting_potential}.
@@
     \subsection{CNN architecture and hyperparameter tuning}
-    We designed our CNN architecture drawing inspiration from its successful implementation in tasks involving electrocardiogram signal classification \cite{weimann2021transfer}, as illustrated in \cref{main_fig2:cnn_for_eads}b and \cref{main_fig2:cnn_for_eads}c.
-    This multi-branched CNN comprises nine branches tailored to handle eDOS orbitals while ensuring a reduced memory footprint.
+    We designed our CNN architecture drawing inspiration from its successful implementation in
+    tasks involving electrocardiogram signal classification \cite{weimann2021transfer},
+    as illustrated in \cref{main_fig2:cnn_for_eads}b and \cref{main_fig2:cnn_for_eads}c.
+    This multi-branched CNN comprises nine branches tailored to handle eDOS orbitals
+    while ensuring a reduced memory footprint.
 
     The effectiveness of neural network models is intricately tied to the choice of hyperparameters.
-    To identify the optimal set of hyperparameters, we employed Hyperband \cite{li2018hyperband}, a modern and parallelizable bandit-based optimization algorithm.
-    The search space for hyperparameters is detailed in Supplementary \cref{supp_table16:hyperparam_space}, and the resulting optimal hyperparameters are presented in Supplementary \cref{supp_table17:opt_hyperparam}.
+    To identify the optimal set of hyperparameters, we employed Hyperband \cite{li2018hyperband},
+    a modern and parallelizable bandit-based optimization algorithm.
+    The search space for hyperparameters is detailed in Supplementary \cref{supp_table16:hyperparam_space},
+    and the resulting optimal hyperparameters are presented in Supplementary \cref{supp_table17:opt_hyperparam}.
 
     \subsection{Data augmentation and CNN model training}
-    To enhance the generalizability and robustness of the our CNN model, and achieve comprehensive coverage of the chemical space \cite{DBLP:journals/corr/abs-2112-12542}, we applied data augmentation techniques to the initial dataset using the following procedures:
-        - In addition to the designated ``initial state'' of the adsorption process, where the adsorbate positioned 6.5 \text{\AA} above the supported single metal atom, five intermediate images were interpolated.
-These images were distributed between the initial and final states at a spacing of 0.5 \text{\AA}, starting from the initial state side.
-        - A diverse set of smearing techniques was employed to determine of partial occupancies $f_{nk}$, including the tetrahedron method \cite{blochl1994improved} and the Gaussian method.
+    To enhance the generalizability and robustness of the our CNN model,
+    and achieve comprehensive coverage of the chemical space \cite{DBLP:journals/corr/abs-2112-12542},
+    we applied data augmentation techniques to the initial dataset using the following procedures:
+        - In addition to the designated ``initial state'' of the adsorption process,
+        where the adsorbate positioned 6.5 \text{\AA} above the supported single metal atom,
+        five intermediate images were interpolated.
+        These images were distributed between the initial and final states at a spacing of 0.5 \text{\AA},
+        starting from the initial state side.
+        - A diverse set of smearing techniques was employed to determine of partial occupancies $f_{nk}$,
+        including the tetrahedron method \cite{blochl1994improved} and the Gaussian method.
         For the Gaussian method, the smearing width was varied within the range of 0.01 eV to 0.1 eV.
-This careful selection of methods was made to guarantee reliable and consistent predictions of adsorption energies from the model, regardless of the smearing technique used.
+        This careful selection of methods was made to guarantee reliable and consistent predictions
+        of adsorption energies from the model, regardless of the smearing technique used.
 
-    The augmented dataset comprises 12,312 samples, with adsorption energies having a standard deviation of 1.8117 eV and a variance of 3.2821 eV\textsubscript{2}.
-    Twenty percent of these samples were allocated to the validation set. Throughout the training process, a batch size of 64 was employed to ensure a balanced learning dynamic.
+    The augmented dataset comprises 12,312 samples, with adsorption energies having
+    a standard deviation of 1.8117 eV and a variance of 3.2821 eV\textsubscript{2}.
+    Twenty percent of these samples were allocated to the validation set.
+    Throughout the training process, a batch size of 64 was employed to ensure a balanced learning dynamic.
 
     \subsection{eDOS occlusion experiments}
-    Supplementary \cref{supp_fig21:occlusion} visually illustrates the eDOS occlusion experiment methodology.
-    To maintain consistent shapes, zero-padding was applied to the input eDOS arrays.
-    Focusing on understanding the influence of metals on adsorption behavior,
-    a masker with dimensions [width, 1, 1] was employed along the metal channel
-    to eliminate cross-orbital interactions.
+    Supplementary \cref{supp_fig21:occlusion} visually illustrates the eDOS occlusion
+    experiment methodology. To maintain consistent shapes, zero-padding was applied to the
+    input eDOS arrays. Focusing on understanding the influence of metals on
+    adsorption behavior, a masker with dimensions [width, 1, 1] was employed along
+    the metal channel to eliminate cross-orbital interactions.
     Here, ``width'' denotes the masker width, and detailed explanations for determining the width
     are provided in Supplementary \cref{supp_sec3.5_occlusion}.
-    Through recursive application of these maskers, variations in predicted adsorption energies from the CNN model were recorded, generating an occlusion array.
+    Through recursive application of these maskers, variations in predicted
+    adsorption energies from the CNN model were recorded, generating an occlusion array.
 
@@
     To maintain a uniform energy window, each image underwent cropping and padding procedures.
-    The resulted output arrays took the form of [400, 1] arrays for simultaneous orbital shifting and [400, 9] arrays for individual orbital shifting.
+    The resulted output arrays took the form of [400, 1] arrays for simultaneous orbital shifting
+    and [400, 9] arrays for individual orbital shifting.
     The energy range for shifting was chosen to induce a moderate disturbance to adsorption energy.
@@
     \subsection{Chemical bond analysis and real-space wavefunction visualization}
-    COHP analysis was performed using the Local-Orbital Basis Suite Towards Electronic-Structure Reconstruction (LOBSTER) package  \cite{deringer2011crystal, koga1999analytical, nelson2020lobster, maintz2013analytic, dronskowski1993crystal} version 4.1.0, with the GGA-PBE wavefunctions fitted by S.
-Maintz \cite{koga1999analytical, maintz2016lobster}.
+    COHP analysis was performed using the Local-Orbital Basis Suite Towards
+    Electronic-Structure Reconstruction (LOBSTER) package
+    \cite{deringer2011crystal, koga1999analytical, nelson2020lobster, maintz2013analytic, dronskowski1993crystal} version 4.1.0,
+    with the GGA-PBE wavefunctions fitted by S. Maintz \cite{koga1999analytical, maintz2016lobster}.
     A Gaussian smearing for energy integration was employed with a broadening width of 0.05 eV.
-    The quantification of bonding strength between the single metal atom and the substrate was achieved through the summation of interactions with neighboring atoms within a range of 0.5 \text{\AA} to 5.0 \text{\AA} from the single metal atom.
-    Orbitals of interest were confirmed through band-structure analysis, and real-space wavefunctions were subsequently visualized using VASPKIT \cite{wang2021vaspkit} and VESTA \cite{momma2008vesta}.
+    The quantification of bonding strength between the single metal atom and the substrate
+    was achieved through the summation of interactions with neighboring atoms
+    within a range of 0.5 \text{\AA} to 5.0 \text{\AA} from the single metal atom.
+    Orbitals of interest were confirmed through band-structure analysis,
+    and real-space wavefunctions were subsequently visualized using VASPKIT \cite{wang2021vaspkit}
+    and VESTA \cite{momma2008vesta}.
 
     \subsection{Machine learning and data analysis environment}
-    The CNN model was implemented using TensorFlow \cite{abadi2016tensorflow}, and hyperparameter optimization was conducted using the Hyperband \cite{li2018hyperband} algorithm via KerasTuner \cite{omalley2019kerastuner}.
-    For a more detailed overview of our machine learning setup and data analysis environment, please refer to Supplementary \cref{supp_sec4_env}.
+    The CNN model was implemented using TensorFlow \cite{abadi2016tensorflow},
+    and hyperparameter optimization was conducted using the Hyperband \cite{li2018hyperband} algorithm
+    via KerasTuner \cite{omalley2019kerastuner}.
+    For a more detailed overview of our machine learning setup and data analysis environment,
+    please refer to Supplementary \cref{supp_sec4_env}.
 

### 2024-02-09 paper/journal-submission/cover-letter/cover_letter.tex
add cover letter skeleton

% Cover Letter
\documentclass[a4paper, 12pt]{article}

\usepackage{booktabs}
\usepackage{graphics}
\usepackage{multirow}
\usepackage{tablefootnote}

\begin{document}

\title{Cover Letter for: Convolutional Neural Networks and Volcano Plots:
    Screening and Prediction of Two-Dimensional Single-Atom Catalysts
    for CO\textsubscript{2} Reduction Reactions}

\date{\today}
\maketitle
\newpage

\section{Affiliation and contact information for the corresponding authors}

\begin{table}
    \label{cov_let_table:corr_author_contact}
    \centering
    \begin{tabular}{p{3cm}p{6cm}l}
    \toprule
    Corresponding Author  & Affiliation                                             & Contact Email       \\
    \midrule
    Ting Liao             & School of Mechanical Medical and Process Engineering,
                            Queensland University of Technology, George Street,
                            Brisbane, QLD 4000, Australia                           & t3.liao@qut.edu.au   \\
    Ziqi Sun              & School of Chemistry and Physics,
                            Queensland University of Technology, George Street,
                            Brisbane, QLD 4000, Australia                           & ziqi.sun@qut.edu.au  \\
    \bottomrule
    \end{tabular}
\end{table}

\section{Importance of this work}

\section{Reviewers and exclusion of referees}

TODO: need supervisor input.

\section{Prior discussions with editor}

Authors had no prior discussions with \textit{Nature Communications} editors about this work.

\end{document}
% End of Cover Letter

### 2024-02-09 paper/journal-submission/cover-letter/cover_letter.tex
clean up table
further clean up table
add importance section

@@
 \usepackage{booktabs}
-\usepackage{graphics}
-\usepackage{multirow}
-\usepackage{tablefootnote}
+\usepackage{tabularx}
 
@@
 
-\begin{table}
+\begin{table}[htbp]
 \label{cov_let_table:corr_author_contact}
-    \centering
-    \begin{tabular}{p{3cm}p{6cm}l}
+    \begin{tabularx}{\textwidth}{p{2.5cm}p{6cm}l}
     \toprule
@@
     \bottomrule
-    \end{tabular}
+    \end{tabularx}
 \end{table}
 
-\section{Importance of this work}
+\section{Importance and appropriateness for submission}
+
+\noindent \textbf{High Predictive Accuracy:} \\
+    Our computational model demonstrates accuracy in predicting the adsorption energies
+    of various CO2RR and HER adsorbates on single-atom catalysts (SACs),
+    achieving a mean absolute error (MAE) at the 0.1 eV level.
+    Our eDOS occlusion and shifting experiments elucidate the orbitalwise contributions
+    to adsorption behavior and potential changes resulting from
+    electronic density of states (eDOS) disturbances.
+    The chemical meaningfulness of our predictions is validated through
+    crystal orbital Hamilton population (COHP) analysis. \\
+
+\noindent \textbf{Versatile Predictive Model:} \\
+    Our convolutional neural network (CNN) model offers distinct advantages.
+    Firstly, it does not rely on species-specific parameters,
+    making it applicable beyond CO2RR to a wide range of electrochemical reduction reactions.
+    Secondly, our model requires only the eDOS of supported single metal atoms and adsorbates,
+    eliminating the need for substrate-specific parameters
+    and significantly reducing memory footprint.
+    Additionally, utilizing a multi-branched CNN architecture further reduced
+    the model's memory footprint. \\
+
+\noindent \textbf{Improved Linear Scaling Relations:} \\
+    We present revised linear scaling relations that reduce scaling errors
+    with limited computational overhead.
+    This advancement paves the way for the generation of accurate volcano plots. \\
+
+\noindent \textbf{Efficient Catalyst Screening Pipeline:} \\
+    Our screening pipeline integrates volcano plots to predict directions
+    for optimization, and eDOS shifting experiments to identify methods
+    for achieving predicted volcano plot outcomes.
 
@@
 
-Authors had no prior discussions with \textit{Nature Communications} editors about this work.
+Authors declared no prior discussions with \textit{Nature Communications} editors about this work.
 

### 2024-02-14 cnn4dos/1-model-and-training/1-hyper-tune/check_metrics.py
global ruff mypy format fix

@@ -3,11 +3,10 @@
 
 
 import io
-import keras_tuner
 import sys
 
+import keras_tuner
 from hp_model import hp_model
-
 
 # Main Loop
 if __name__ == "__main__":
@@ -20,8 +19,7 @@ if __name__ == "__main__":
         objective="val_mean_absolute_error",
         directory="hp_search",
         project_name="best_model",
-        )
-
+    )
 
     # Create a StringIO buffer to capture output
     output_buffer = io.StringIO()
@@ -38,7 +36,6 @@ if __name__ == "__main__":
     summary_string = output_buffer.getvalue()
     # Close the buffer
     output_buffer.close()
-
 
     # Parse metrics into dict
     metric_dict = {}

### 2024-02-14 cnn4dos/1-model-and-training/1-hyper-tune/gpu_tuner.sh

@@ -23,4 +23,3 @@ python3 keras-tuner.py > "tuner_$(date +"%Y_%m_%d_%H_%M").log" 2>&1
 
 # Request interactive GPU
 # qsub -I -q gpuvolta -lwd,walltime=1:00:00,ngpus=1,ncpus=12,mem=96GB,jobfs=1GB,storage=gdata/iu57+gdata/v88+gdata/dk92
-

### 2024-02-14 cnn4dos/1-model-and-training/1-hyper-tune/hp_model.py

@@ -21,33 +21,46 @@ def hp_model(hp, input_shape=(4000, 9, 6)):
         # Reshape (None, 4000, 6) to (None, 4000, 1, 6)
         conv_x = tf.keras.layers.Reshape(target_shape=(4000, 1, 6))(branch_input)
 
-
         # Dynamic amount of ConV blocks
         for i in range(hp_branch_numConvBlocks):
             for j in range(hp_branch_primary_numConvLayers):
                 ## Primary ConV blocks
-                conv_x = tf.keras.layers.Conv2D(numFilters, (hp_branch_primary_kernel_size, 1), activation="relu", padding="same")(conv_x)
-
+                conv_x = tf.keras.layers.Conv2D(
+                    numFilters,
+                    (hp_branch_primary_kernel_size, 1),
+                    activation="relu",
+                    padding="same",
+                )(conv_x)
 
             ## Ending ConV block
-            conv_x = tf.keras.layers.Conv2D(numFilters, (hp_branch_ending_kernel_size, 1), (2, 1), activation="relu", padding="same")(conv_x)
+            conv_x = tf.keras.layers.Conv2D(
+                numFilters,
+                (hp_branch_ending_kernel_size, 1),
+                (2, 1),
+                activation="relu",
+                padding="same",
+            )(conv_x)
 
             if hp_branch_include_pooling:
-                conv_x = tf.keras.layers.AveragePooling2D(pool_size=(hp_branch_pool_size, 1), padding="same")(conv_x)
+                conv_x = tf.keras.layers.AveragePooling2D(
+                    pool_size=(hp_branch_pool_size, 1), padding="same"
+                )(conv_x)
 
             conv_x = tf.keras.layers.Dropout(drop_out_rate)(conv_x)
-
 
         ## Flatten and dense
         conv_flat = tf.keras.layers.Flatten()(conv_x)
 
         # Branch output
-        branch_output = tf.keras.layers.Dense(hp_branch_dense_units, activation=hp_branch_dense_activation_func)(conv_flat)
-        branch_output = tf.keras.layers.Dense(hp_branch_dense_units/2, activation=hp_branch_dense_activation_func)(branch_output)
+        branch_output = tf.keras.layers.Dense(
+            hp_branch_dense_units, activation=hp_branch_dense_activation_func
[…]

### 2024-02-14 cnn4dos/1-model-and-training/1-hyper-tune/keras-tuner.py

@@ -2,25 +2,28 @@
 # -*- coding: utf-8 -*-
 
 
+import os
+
 import keras_tuner
 import numpy as np
-import os
+
 os.environ["TF_GPU_THREAD_MODE"] = "gpu_private"
 os.environ["TF_CPP_MIN_LOG_LEVEL"] = "2"
-from pathlib import Path
 import sys
-import tensorflow as tf
 import warnings
-import yaml
+from pathlib import Path
 
+import tensorflow as tf
+import yaml
 from hp_model import hp_model
 from lib.dataset import Dataset
-
 
 # Main Loop
 if __name__ == "__main__":
     # Print GPU info
-    print("Num GPUs Available: ", len(tf.config.experimental.list_physical_devices('GPU')))
+    print(
+        "Num GPUs Available: ", len(tf.config.experimental.list_physical_devices("GPU"))
+    )
     print("Device name: ", tf.test.gpu_device_name())
 
     # Set global random seed
@@ -49,41 +52,53 @@ if __name__ == "__main__":
     epochs = cfg["model_training"]["epochs"]
     sample_size = cfg["model_training"]["sample_size"]
 
-
     # Load features(DOS) and labels from cached file to save time
     if os.path.exists("features.npy") and os.path.exists("labels.npy"):
-        warnings.warn("Warning! features/labels load from cached file. Tags changed after cache generation in config.yaml might not take effect.")
+        warnings.warn(
+            "Warning! features/labels load from cached file. Tags changed after cache generation in config.yaml might not take effect."
+        )
         features = tf.convert_to_tensor(np.load("features.npy"))
         labels = tf.convert_to_tensor(np.load("labels.npy"))
 
         total_sample = labels.shape[0]
-
 
     else:
         # Initiate dataset loader
         dataFetcher = Dataset()
 
         # Load feature
-        dataFetcher.load_feature(feature_dir, substrates, adsorbates, centre_atoms,
-                                states={"is", }, spin=spin,
-                                remove_ghost=remove_ghost,
-                                load_augment=load_augmentation, augmentations=augmentations)
+        dataFetcher.load_feature(
+            feature_dir,
+            substrates,
+            adsorbates,
+            centre_atoms,
+            states={
+                "is",
+            },
+            spin=spin,
+            remove_ghost=remove_ghost,
+            load_augment=load_augmentation,
[…]

### 2024-02-14 cnn4dos/1-model-and-training/1-hyper-tune/lib/dataset.py

@@ -3,10 +3,11 @@
 
 
 import os
+import warnings
+
 import numpy as np
 import pandas as pd
 from sklearn.preprocessing import normalize
-import warnings
 
 
 class Dataset:
@@ -20,11 +21,23 @@ class Dataset:
         adsorbates (list):
 
     """
+
     def __init__(self) -> None:
         pass
 
-
-    def load_feature(self, path, substrates, adsorbates, centre_atoms, states=("is", "fs"), spin="up", load_augment=False, augmentations=None, keysep=":", remove_ghost=False):
+    def load_feature(
+        self,
+        path,
+        substrates,
+        adsorbates,
+        centre_atoms,
+        states=("is", "fs"),
+        spin="up",
+        load_augment=False,
+        augmentations=None,
+        keysep=":",
+        remove_ghost=False,
+    ):
         """Load DOS dataset feature from given list of dirs.
 
         Args:
@@ -75,7 +88,6 @@ class Dataset:
         self.substrates = substrates
         self.adsorbates = adsorbates
 
-
         # Import DOS as numpy array
         feature_data = {}
         for sub in substrates:
@@ -91,11 +103,26 @@ class Dataset:
 
                     # Loop through all directories to load DOS
                     for folder in os.listdir(directory):
-                        if os.path.isdir(os.path.join(directory, folder)) and (os.path.exists(os.path.join(directory, folder, f"dos_up_{centre_atom_index}.npy")) or os.path.exists(os.path.join(directory, folder, f"dos_down_{centre_atom_index}.npy"))):
+                        if os.path.isdir(os.path.join(directory, folder)) and (
+                            os.path.exists(
+                                os.path.join(
+                                    directory, folder, f"dos_up_{centre_atom_index}.npy"
+                                )
+                            )
+                            or os.path.exists(
+                                os.path.join(
+                                    directory,
+                                    folder,
+                                    f"dos_down_{centre_atom_index}.npy",
+                                )
+                            )
+                        ):
                             # Do augmentation distance check for augmented data
-                            if sub.endswith("_aug") and folder.split("_")[-1] not in augmentations:
+                            if (
+                                sub.endswith("_aug")
+                                and folder.split("_")[-1] not in augmentations
+                            ):
                                 continue
-
 
                             # Compile dict key as "{substrate}{keysep}{adsorbate}{keysep}{state}"
                             key = f"{sub}{keysep}{ads}{keysep}{state}{keysep}{folder}"
@@ -103,14 +130,39 @@ class Dataset:
[…]

### 2024-02-14 cnn4dos/1-model-and-training/1-hyper-tune/lib/model.py

@@ -22,25 +22,40 @@ def cnn_for_dos(input_shape, drop_out_rate):
         branch_input = tf.keras.layers.Reshape(target_shape=(4000, 1, 6))(branch_input)
 
         # 1st Conv layer
-        conv_1 = tf.keras.layers.Conv2D(16, (3, 1), activation="relu", padding="same")(branch_input)
-        conv_1 = tf.keras.layers.Conv2D(16, (3, 1), activation="relu", padding="same")(conv_1)
-        conv_1 = tf.keras.layers.Conv2D(16, (8, 1), (2, 1), activation="relu", padding="same")(conv_1)
+        conv_1 = tf.keras.layers.Conv2D(16, (3, 1), activation="relu", padding="same")(
+            branch_input
+        )
+        conv_1 = tf.keras.layers.Conv2D(16, (3, 1), activation="relu", padding="same")(
+            conv_1
+        )
+        conv_1 = tf.keras.layers.Conv2D(
+            16, (8, 1), (2, 1), activation="relu", padding="same"
+        )(conv_1)
         conv_1 = tf.keras.layers.Dropout(drop_out_rate)(conv_1)
 
-
         # 2nd Conv layer
-        conv_2 = tf.keras.layers.Conv2D(16, (3, 1), activation="relu", padding="same")(conv_1)
-        conv_2 = tf.keras.layers.Conv2D(16, (3, 1), activation="relu", padding="same")(conv_2)
-        conv_2 = tf.keras.layers.Conv2D(16, (8, 1), (2, 1), activation="relu", padding="same")(conv_2)
+        conv_2 = tf.keras.layers.Conv2D(16, (3, 1), activation="relu", padding="same")(
+            conv_1
+        )
+        conv_2 = tf.keras.layers.Conv2D(16, (3, 1), activation="relu", padding="same")(
+            conv_2
+        )
+        conv_2 = tf.keras.layers.Conv2D(
+            16, (8, 1), (2, 1), activation="relu", padding="same"
+        )(conv_2)
         conv_2 = tf.keras.layers.Dropout(drop_out_rate)(conv_2)
 
-
         # 3rd Conv layer
-        conv_3 = tf.keras.layers.Conv2D(16, (3, 1), activation="relu", padding="same")(conv_2)
-        conv_3 = tf.keras.layers.Conv2D(16, (3, 1), activation="relu", padding="same")(conv_3)
[…]

### 2024-02-14 cnn4dos/1-model-and-training/1-hyper-tune/lib/record_runtime_info.py

@@ -5,9 +5,10 @@
 import json
 import logging
 import platform
-import psutil
 import socket
 import subprocess
+
+import psutil
 
 
 def record_python_package_ver(logfile="python_package_ver.log"):
@@ -21,7 +22,9 @@ def record_python_package_ver(logfile="python_package_ver.log"):
 
     """
     # Get all installed Python packages
-    result = subprocess.run(["pip", "freeze"], stdout=subprocess.PIPE).stdout.decode('utf-8')
+    result = subprocess.run(["pip", "freeze"], stdout=subprocess.PIPE).stdout.decode(
+        "utf-8"
+    )
 
     # Write results to log file
     with open(logfile, mode="w") as f:
@@ -48,7 +51,7 @@ def record_system_info(logfile="sys_info.log"):
         info["architecture"] = platform.machine()
         info["hostname"] = socket.gethostname()
         info["processor"] = platform.processor()
-        info["ram"] = str(round(psutil.virtual_memory().total / (1024.0 ** 3))) + " GB"
+        info["ram"] = str(round(psutil.virtual_memory().total / (1024.0**3))) + " GB"
     except Exception as e:
         logging.exception(e)
 

### 2024-02-14 cnn4dos/1-model-and-training/2-best-model/lib/dataset.py

@@ -2,10 +2,11 @@
 
 
 import os
+import warnings
+
 import numpy as np
 import pandas as pd
 from sklearn.preprocessing import normalize
-import warnings
 
 
 class Dataset:

### 2024-02-14 cnn4dos/1-model-and-training/2-best-model/plot_cnn_model.py

@@ -1,10 +1,10 @@
 """Plot CNN model architecture."""
 
-
 model_dir = "model"
 
 
 import os
+
 import tensorflow as tf
 
 os.environ["TF_CPP_MIN_LOG_LEVEL"] = "2"

### 2024-02-14 cnn4dos/1-model-and-training/2-best-model/predict_and_evaluate.py

@@ -2,19 +2,19 @@
 # -*- coding: utf-8 -*-
 
 
-import numpy as np
 import os
 
+import numpy as np
+
 os.environ["TF_CPP_MIN_LOG_LEVEL"] = "2"
-from sklearn.metrics import r2_score
 import sys
-import tensorflow as tf
-from tensorflow import keras
 import warnings
+
+import tensorflow as tf
 import yaml
-
 from lib.dataset import Dataset
-
+from sklearn.metrics import r2_score
+from tensorflow import keras
 
 # Main Loop
 if __name__ == "__main__":

### 2024-02-14 cnn4dos/1-model-and-training/2-best-model/save_best_model.py

@@ -1,9 +1,8 @@
 """Save best CNN model."""
 
-
-import keras_tuner
 import os
 
+import keras_tuner
 from hp_model import hp_model
 
 os.environ["TF_CPP_MIN_LOG_LEVEL"] = "3"

### 2024-02-14 cnn4dos/2-model-evaluation/1-plot_parity_for_ALL.py

@@ -1,22 +1,21 @@
 """Plot parity for all adsorbates in a single plot."""
 
-
 model_dir = "../1-model-and-training/2-best-model"
 
 
-from matplotlib import rcParams
-from matplotlib.patches import PathPatch
+import os
+import sys
+from pathlib import Path
+
 import matplotlib.pyplot as plt
 import numpy as np
-import os
-
-from pathlib import Path
 import seaborn as sns
 import statsmodels.api as sm
-from sklearn.metrics import r2_score
-import sys
 import tensorflow as tf
 import yaml
+from matplotlib import rcParams
+from matplotlib.patches import PathPatch
+from sklearn.metrics import r2_score
 
 os.environ["TF_CPP_MIN_LOG_LEVEL"] = "3"
 rcParams["font.family"] = "sans-serif"
@@ -24,7 +23,6 @@ rcParams["font.sans-serif"] = ["Arial"]
 
 sys.path.append(model_dir)
 from lib.dataset import Dataset
-
 
 if __name__ == "__main__":
     # Load configs

### 2024-02-14 cnn4dos/2-model-evaluation/2-plot_parity_for_EACH.py

@@ -1,22 +1,21 @@
 """Plot parity for each adsorbates in individual plots."""
 
-
 model_dir = "../1-model-and-training/2-best-model"
 
 
 import copy
-from matplotlib import rcParams
-from matplotlib.patches import PathPatch
+import os
+import sys
+from pathlib import Path
+
 import matplotlib.pyplot as plt
 import numpy as np
-import os
-
-from pathlib import Path
 import seaborn as sns
 import statsmodels.api as sm
-import sys
 import tensorflow as tf
 import yaml
+from matplotlib import rcParams
+from matplotlib.patches import PathPatch
 
 os.environ["TF_CPP_MIN_LOG_LEVEL"] = "3"
 rcParams["font.family"] = "sans-serif"
@@ -24,7 +23,6 @@ rcParams["font.sans-serif"] = ["Arial"]
 
 sys.path.append(model_dir)
 from lib.dataset import Dataset
-
 
 if __name__ == "__main__":
     # Load configs

### 2024-02-14 cnn4dos/3-occlusion-experiments/main.py

@@ -1,25 +1,24 @@
 """Main for eDOS occlusion experiments."""
 
-
 import os
-from pathlib import Path
-import numpy as np
-from tqdm import tqdm
-import tensorflow as tf
 import sys
+from pathlib import Path
+
+import numpy as np
+import tensorflow as tf
+from tqdm import tqdm
 
 # Modify sys.path for shared components
 root_dir = Path(__file__).parent
 shared_components_dir = root_dir / "../shared_components/src"
 sys.path.append(str(shared_components_dir.resolve()))
 
-from src.occlusionGenerator import occlusionGenerator
-from src.occlusionPlotter import OcclusionPlotter
-from src.utilities import get_fermi_level
-
 from cnnPredictor import CNNPredictor
 from dataLoader import DataLoader
 from dosProcessor import DOSProcessor
+from src.occlusionGenerator import occlusionGenerator
+from src.occlusionPlotter import OcclusionPlotter
+from src.utilities import get_fermi_level
 
 
 def main():

### 2024-02-14 cnn4dos/3-occlusion-experiments/src/occlusionGenerator.py

@@ -1,8 +1,8 @@
 """Generate occlusion arrays."""
 
+import warnings
 
 import numpy as np
-import warnings
 
 
 class occlusionGenerator:

### 2024-02-14 cnn4dos/3-occlusion-experiments/src/occlusionPlotter.py

@@ -1,15 +1,15 @@
 """Occlusion experiments plotter: line mode and heatmap mode."""
 
+import os
+import warnings
+from pathlib import Path
+from typing import Tuple
 
 import matplotlib as mpl
-from matplotlib import rcParams
 import matplotlib.pyplot as plt
 import matplotlib.ticker as ticker
 import numpy as np
-import os
-from pathlib import Path
-import warnings
-from typing import Tuple
+from matplotlib import rcParams
 
 rcParams["font.family"] = "sans-serif"
 rcParams["font.sans-serif"] = ["Arial"]

### 2024-02-14 cnn4dos/3-occlusion-experiments/src/utilities.py

@@ -1,9 +1,9 @@
 """Utilities for eDOS occlusion."""
 
-
-import pandas as pd
 from pathlib import Path
 from typing import Tuple
+
+import pandas as pd
 
 
 def get_properties_from_path(working_dir: Path) -> Tuple[str, str, str, str]:

### 2024-02-14 cnn4dos/4-shifting-experiments/main.py

@@ -1,16 +1,15 @@
 """eDOS shifting experiment main."""
 
-
 import os
+import sys
 from pathlib import Path
+
 import numpy as np
 import tensorflow as tf
-from tqdm import tqdm
-import sys
-
 from src.shiftGenerator import ShiftGenerator
 from src.shiftPlotter import ShiftPlotter
 from src.utilities import get_folders_in_dir
+from tqdm import tqdm
 
 sys.path.append("../shared_components/src")
 from cnnPredictor import CNNPredictor

### 2024-02-14 cnn4dos/4-shifting-experiments/src/shiftGenerator.py

@@ -1,9 +1,9 @@
 """Generate eDOS shifted arrays."""
 
-
-import numpy as np
 import warnings
 from typing import List
+
+import numpy as np
 
 
 class ShiftGenerator:

### 2024-02-14 cnn4dos/4-shifting-experiments/src/shiftPlotter.py

@@ -1,11 +1,11 @@
 """Plot eDOS shifting experiments results."""
 
-
-from matplotlib import rcParams
-import matplotlib.pyplot as plt
-from mendeleev import element
-import numpy as np
 from pathlib import Path
+
+import matplotlib.pyplot as plt
+import numpy as np
+from matplotlib import rcParams
+from mendeleev import element
 
 rcParams["font.family"] = "sans-serif"
 rcParams["font.sans-serif"] = ["Arial"]

### 2024-02-14 cnn4dos/5-volcano-plot/main.py

@@ -1,15 +1,13 @@
 """Volcano plotter main."""
 
-
 import os
 from pathlib import Path
-import yaml
 
+import yaml
 from src.lib.dataLoader import dataLoader
 from src.lib.reactionCalculator import reactionCalculator
 from src.lib.scalingRelation import scalingRelation
 from src.lib.volcanoPlotter import volcanoPlotter
-
 
 if __name__ == "__main__":
     # Load configs
@@ -47,8 +45,8 @@ if __name__ == "__main__":
         descriptors=(descriptor_x, descriptor_y),
         mixing_ratios="AUTO",
         verbose=True,
-        remove_ads_prefix=True
-        )
+        remove_ads_prefix=True,
+    )
 
     # Print linear fitting parameters of free energy
     print(calculator.fitting_paras)
@@ -59,12 +57,14 @@ if __name__ == "__main__":
         adsorbate_energy_file=adsorbate_energy_file,
         reaction_pathway_file=reaction_pathway_file,
         external_potential=external_potential,
-        )
+    )
 
     reaction_scaling_relations = {
-        "CO2RR_CH4": reaction_calculator.calculate_reaction_scaling_relations(name="CO2RR_CH4"),
-        "HER": reaction_calculator.calculate_reaction_scaling_relations(name="HER")
-        }
+        "CO2RR_CH4": reaction_calculator.calculate_reaction_scaling_relations(
+            name="CO2RR_CH4"
+        ),
+        "HER": reaction_calculator.calculate_reaction_scaling_relations(name="HER"),
+    }
 
     # Initialize volcano plotter
     plotter = volcanoPlotter(
@@ -74,28 +74,30 @@ if __name__ == "__main__":
         descriptors=(descriptor_x, descriptor_y),
         adsorption_free_energies=loader.adsorption_free_energy,
         markers=markers,
-        )
+    )
 
     # Generate CO2RR limiting potential volcano plot
     plotter.plot_limiting_potential(
         reaction_name="CO2RR_CH4",
         label_selection=label_selection,
         savename=os.path.join("figures", "limiting_potential_CO2RR_CH4.png"),
-        show=False
-        )
+        show=False,
+    )
 
     # Generate rate determining step plot
     plotter.plot_rds(
         reaction_name="CO2RR_CH4",
         savename=os.path.join("figures", "RDS_CO2RR_CH4.png"),
-        show=False)
+        show=False,
+    )
 
     # Generate selectivity volcano plot
[…]

### 2024-02-14 cnn4dos/5-volcano-plot/src/lib/dataLoader.py

@@ -1,17 +1,17 @@
 """Data loader for volcano plotter."""
 
-
 import json
 import os
+
 import pandas as pd
 
 
 class dataLoader:
     def __init__(self) -> None:
         """Data loader class for volcano plots, load:
-            1. adsorption energy
-            2. reaction pathway
-            3. thermal correction (ZPE, TS) for adsorption energy
+        1. adsorption energy
+        2. reaction pathway
+        3. thermal correction (ZPE, TS) for adsorption energy
 
         """
 
@@ -33,7 +33,9 @@ class dataLoader:
 
         # Import thermal correction file
         df = pd.read_csv(correction_file)
-        thermal_correction_dict = dict(zip(df["Species"], df["Correction"].astype(float)))
+        thermal_correction_dict = dict(
+            zip(df["Species"], df["Correction"].astype(float))
+        )
 
         # Apply thermal correction for each substrate
         self.adsorption_free_energy = {}
@@ -43,7 +45,9 @@ class dataLoader:
             for ads in free_energy_df.columns.values:
                 # Check if all adsorbates have a correction entry
                 if f'*{ads.split("-")[-1]}' not in thermal_correction_dict:
-                    raise ValueError(f"Cannot find thermal correction for {ads.split('-')[-1]}")
+                    raise ValueError(
+                        f"Cannot find thermal correction for {ads.split('-')[-1]}"
+                    )
 
                 # Apply correction by column
                 free_energy_df[ads] += thermal_correction_dict[f'*{ads.split("-")[-1]}']
@@ -69,7 +73,9 @@ class dataLoader:
 
         # Load adsorption energy by substrate
         self.adsorption_energy = {
-            sub: pd.read_csv(os.path.join(path, f"{sub}.csv"), index_col=0).loc[:, adsorbates]  # apply adsorbate filter
+            sub: pd.read_csv(os.path.join(path, f"{sub}.csv"), index_col=0).loc[
+                :, adsorbates
+            ]  # apply adsorbate filter
             for sub in substrates
         }
 
@@ -114,8 +120,24 @@ class dataLoader:
 # Test area
 if __name__ == "__main__":
     test_path = "../../../0-dataset/label_adsorption_energy"
[…]

### 2024-02-14 cnn4dos/5-volcano-plot/src/lib/reactionCalculator.py

@@ -1,18 +1,18 @@
 """Calculate reaction for volcano plotter."""
 
-
 import numpy as np
 
 from .dataLoader import dataLoader
 
 
 class reactionCalculator:
-    def __init__(self,
-                 adsorption_energy_scaling_relation,
-                 adsorbate_energy_file,
-                 reaction_pathway_file,
-                 external_potential=0.0
-                 ):
+    def __init__(
+        self,
+        adsorption_energy_scaling_relation,
+        adsorbate_energy_file,
+        reaction_pathway_file,
+        external_potential=0.0,
+    ):
         """Calculate scaling relations for reaction.
 
         Args:
@@ -137,33 +137,46 @@ class reactionCalculator:
 if __name__ == "__main__":
     # Set args
     path = "../../../0-dataset/label_adsorption_energy"
-    substrates = ["g-C3N4_is", "nitrogen-graphene_is", "vacant-graphene_is", "C2N_is", "BN_is", "BP_is"]
+    substrates = [
+        "g-C3N4_is",
+        "nitrogen-graphene_is",
+        "vacant-graphene_is",
+        "C2N_is",
+        "BN_is",
+        "BP_is",
+    ]
     adsorbates = ["2-COOH", "3-CO", "4-CHO", "5-CH2O", "6-OCH3", "7-O", "8-OH", "11-H"]
 
     # Loading adsorption energy
     from dataLoader import dataLoader
+
     test_loader = dataLoader()
     test_loader.load_adsorption_energy(path, substrates, adsorbates)
 
-    test_loader.calculate_adsorption_free_energy(correction_file="../../data/corrections_thermal.csv")
+    test_loader.calculate_adsorption_free_energy(
+        correction_file="../../data/corrections_thermal.csv"
+    )
 
     # Calculate adsorption energy linear scaling relations
     from scalingRelation import scalingRelation
+
     calculator = scalingRelation(
         adsorption_energy_dict=test_loader.adsorption_free_energy,
         descriptors=("3-CO", "8-OH"),
         mixing_ratios="AUTO",
         verbose=False,
-        remove_ads_prefix=True
-        )
+        remove_ads_prefix=True,
+    )
 
     # Test reaction energy scaling relations calculator
     reaction_calculator = reactionCalculator(
         adsorption_energy_scaling_relation=calculator.fitting_paras,
         adsorbate_energy_file="../../data/energy_adsorbate.csv",
[…]

### 2024-02-14 cnn4dos/5-volcano-plot/src/lib/scalingRelation.py

@@ -1,7 +1,7 @@
 """Calculate adsorption energy linear scaling relations."""
 
-
 import warnings
+
 import numpy as np
 from scipy import stats
 
@@ -53,10 +53,10 @@ class scalingRelation:
             # Test mixing ratio
             mixing_ratio_test_result = {}
             for ratio in range(101):
-                mixing_ratio_test_result[
-                    ratio
-                ] = self.__fit_all_adsorbates_with_given_ratio(
-                    ratios=[ratio, 100 - ratio],
+                mixing_ratio_test_result[ratio] = (
+                    self.__fit_all_adsorbates_with_given_ratio(
+                        ratios=[ratio, 100 - ratio],
+                    )
                 )
 
             # Add mixing ratio test results to attrib

### 2024-02-14 cnn4dos/5-volcano-plot/src/lib/utils.py

@@ -1,14 +1,11 @@
 """Utils for volcano plotter."""
 
-
 import pandas as pd
 
 
 def stack_adsorption_energy_dict(
-    energy_dict,
-    add_prefix_to_rowname=True,
-    remove_prefix_from_colname=False
-    ) -> pd.DataFrame:
+    energy_dict, add_prefix_to_rowname=True, remove_prefix_from_colname=False
+) -> pd.DataFrame:
     """Stack adsorption energies from different substrates vertically.
 
     Args:
@@ -22,7 +19,9 @@ def stack_adsorption_energy_dict(
     # Add substrate name to row index (prep for stacking)
     if add_prefix_to_rowname:
         for key in energy_dict:
-            energy_dict[key] = energy_dict[key].rename(index=lambda x, key=key: f'{key}_{str(x)}')
+            energy_dict[key] = energy_dict[key].rename(
+                index=lambda x, key=key: f"{key}_{str(x)}"
+            )
 
     df = pd.concat(energy_dict.values())
 
@@ -40,21 +39,31 @@ def stack_adsorption_energy_dict(
 if __name__ == "__main__":
     # Set args
     path = "../../../0-dataset/label_adsorption_energy"
-    substrates = ["g-C3N4_is", "nitrogen-graphene_is", "vacant-graphene_is", "C2N_is", "BN_is", "BP_is"]
+    substrates = [
+        "g-C3N4_is",
+        "nitrogen-graphene_is",
+        "vacant-graphene_is",
+        "C2N_is",
+        "BN_is",
+        "BP_is",
+    ]
     adsorbates = ["2-COOH", "3-CO", "4-CHO", "5-CH2O", "6-OCH3", "7-O", "8-OH", "11-H"]
 
     # Loading adsorption energy
     from dataLoader import dataLoader
+
     loader = dataLoader()
     loader.load_adsorption_energy(path, substrates, adsorbates)
 
     # Add thermal correction
-    loader.calculate_adsorption_free_energy(correction_file="../../data/corrections_thermal.csv")
+    loader.calculate_adsorption_free_energy(
+        correction_file="../../data/corrections_thermal.csv"
+    )
 
     # Test stacking adsorption energy dict
     stacked_adsorption_energy = stack_adsorption_energy_dict(
         loader.adsorption_free_energy,
         add_prefix_to_rowname=False,
-        remove_prefix_from_colname=True
-        )
+        remove_prefix_from_colname=True,
+    )
     print(stacked_adsorption_energy)

### 2024-02-14 cnn4dos/5-volcano-plot/src/lib/volcanoPlotter.py

@@ -1,17 +1,16 @@
 """Main plotter for volcano plot."""
 
-
 import math
-import matplotlib as mpl
-from matplotlib import rcParams
-from matplotlib.colors import BoundaryNorm
-from matplotlib.colors import ListedColormap
-from matplotlib.colors import LinearSegmentedColormap
-from matplotlib.lines import Line2D
-import matplotlib.pyplot as plt
-import numpy as np
 import warnings
 from typing import Tuple
+
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+import numpy as np
+from matplotlib import rcParams
+from matplotlib.colors import (BoundaryNorm, LinearSegmentedColormap,
+                               ListedColormap)
+from matplotlib.lines import Line2D
 
 rcParams["font.family"] = "sans-serif"
 rcParams["font.sans-serif"] = ["Arial"]
@@ -27,7 +26,7 @@ class volcanoPlotter:
         adsorption_free_energies,
         dpi=300,
         *args,
-        **kwargs
+        **kwargs,
     ):
         # Update attrib
         self.scaling_relations = scaling_relations
@@ -187,9 +186,7 @@ class volcanoPlotter:
                 "boron nitride ",
                 "black phosphorous",
             ],
-        ).get_frame().set_boxstyle(
-            "Round", pad=0.2, rounding_size=2
-        )
+        ).get_frame().set_boxstyle("Round", pad=0.2, rounding_size=2)
         # use round cornered (ref: https://stackoverflow.com/questions/62972429/how-to-change-legend-edges-from-round-to-sharp-corners)
 
         # Add labels for selected samples
@@ -231,7 +228,10 @@ class volcanoPlotter:
         line_color = "#8F00FF"
         line_style = (
             0,
-            (1, 1.5),  # (offset, (on_off_seq)) (ref: https://matplotlib.org/stable/gallery/lines_bars_and_markers/linestyles.html)
+            (
+                1,
+                1.5,
+            ),  # (offset, (on_off_seq)) (ref: https://matplotlib.org/stable/gallery/lines_bars_and_markers/linestyles.html)
         )
 
         plt.plot(
@@ -277,10 +277,8 @@ class volcanoPlotter:
         plt.text(-0.75, -0.4, "VII", fontsize=font_size)
 
     def __generate_free_energy_change_mesh(
-        self,
-        reaction_name,
-        density=(400, 400)
-        ) -> dict:
+        self, reaction_name, density=(400, 400)
+    ) -> dict:
[…]

### 2024-02-14 cnn4dos/5-volcano-plot/src/test/debug_tools.py

@@ -1,13 +1,13 @@
 """Debug tools for volcano plotter."""
 
-
-import copy
 import contextlib
-import numpy as np
+import copy
 import os
-import pandas as pd
 import sys
 import warnings
+
+import numpy as np
+import pandas as pd
 
 sys.path.append("..")
 from lib.dataLoader import dataLoader
@@ -73,8 +73,7 @@ class volcanoDebugger:
         self.scaling_relations = calculator.fitting_paras
 
     def __calculate_adsorption_energy_from_scaling_relation(
-        self,
-        fitting_paras
+        self, fitting_paras
     ) -> pd.DataFrame:
         """Calculate adsorption (free) energy from scaling relations.
 

### 2024-02-14 cnn4dos/6-COHP_vs_occlusion/main.py

@@ -1,13 +1,13 @@
 """Plot -COHP and occlusion experiment result (Co dxz/dxy orbitals)."""
 
+import warnings
+from pathlib import Path
 
 import matplotlib.pyplot as plt
 import numpy as np
 import pandas as pd
 from matplotlib.gridspec import GridSpec
 from matplotlib.ticker import MaxNLocator
-import warnings
-from pathlib import Path
 
 
 def setup_matplotlib():

### 2024-02-14 cnn4dos/shared_components/calculate_dataset_variance.py

@@ -5,14 +5,14 @@
 training_dir = "../1-model-and-training/1-hyper-tune"
 
 
-import numpy as np
+import sys
 from pathlib import Path
+
+import numpy as np
 import yaml
 
-import sys
 sys.path.append(training_dir)
 from lib.dataset import Dataset
-
 
 if __name__ == "__main__":
     # Load configs
@@ -30,17 +30,22 @@ if __name__ == "__main__":
     augmentations = cfg["species"]["augmentations"]
     spin = cfg["species"]["spin"]
 
-
     # Load dataset
     dataFetcher = Dataset()
 
     ## Load feature
-    dataFetcher.load_feature(feature_dir,
-                             substrates, adsorbates,
-                             centre_atoms,
-                             states={"is", },
-                             spin=spin,
-                             load_augment=load_augmentation, augmentations=augmentations)
+    dataFetcher.load_feature(
+        feature_dir,
+        substrates,
+        adsorbates,
+        centre_atoms,
+        states={
+            "is",
+        },
+        spin=spin,
+        load_augment=load_augmentation,
+        augmentations=augmentations,
+    )
 
     ## Load labels
     dataFetcher.load_label(label_dir)

### 2024-02-14 cnn4dos/shared_components/extract_dos_from_vasprunxml.py

@@ -10,9 +10,10 @@ working_dir = "."
 spin = "up"  # DEBUG
 
 
-import numpy as np
 import os
 from pathlib import Path
+
+import numpy as np
 
 
 def get_total_atom(poscarfile):
@@ -77,6 +78,7 @@ def dos_extractor(folder, spin):
 
     # Import vasprun.xml
     from xml.etree import ElementTree
+
     dos_tree = ElementTree.parse(file)
     dos_root = dos_tree.getroot()
 
@@ -93,7 +95,9 @@ def dos_extractor(folder, spin):
         dos_down = []
 
         # find dos data position
-        for atom in dos_root[8][-2][-1][0][-1]:  # 8-calculation; -2-dos; -1-partial; 0-array; -1-set
+        for atom in dos_root[8][-2][-1][0][
+            -1
+        ]:  # 8-calculation; -2-dos; -1-partial; 0-array; -1-set
             # Spin up
             spin_up_dos = [i.text.strip() for i in atom[0]]
             ## Convert each line to np array
@@ -102,7 +106,9 @@ def dos_extractor(folder, spin):
             # Spin down
             spin_down_dos = [i.text.strip() for i in atom[1]]
             ## Convert each line to np array
-            spin_down_dos = np.array([[float(j) for j in i.split()] for i in spin_down_dos])
+            spin_down_dos = np.array(
+                [[float(j) for j in i.split()] for i in spin_down_dos]
+            )
 
             # Append DOS data to list
             dos_up.append(spin_up_dos)
@@ -114,7 +120,9 @@ def dos_extractor(folder, spin):
 
     # Write DOS to numpy array
     if ispin == "1":
-        return ValueError("None spin polarised analysis currently not supported!")  # DEBUG
+        return ValueError(
+            "None spin polarised analysis currently not supported!"
+        )  # DEBUG
 
     else:  # ISPIN = 2
         if spin in {"up", "both"}:
@@ -127,7 +135,9 @@ def dos_extractor(folder, spin):
 
 if __name__ == "__main__":
     # Check core files (POSCAR and vasprun.xml)
-    if os.path.exists(os.path.join(working_dir, "POSCAR")) and os.path.exists(os.path.join(working_dir, "vasprun.xml")):
+    if os.path.exists(os.path.join(working_dir, "POSCAR")) and os.path.exists(
+        os.path.join(working_dir, "vasprun.xml")
+    ):
[…]

### 2024-02-14 cnn4dos/shared_components/extract_single_atom_DOS.py

@@ -6,16 +6,16 @@ spin = "up"
 working_dir = "."
 
 
-import numpy as np
 import os
 from pathlib import Path
+
+import numpy as np
 
 
 def extract_DOS(source_dir, atom_index, spin="up"):
     # Check args
     assert spin in {"up", "down", "both"}
     assert isinstance(atom_index, int) and atom_index >= 1
-
 
     # Load spin up DOS
     if spin in {"up", "both"}:
@@ -51,5 +51,4 @@ if __name__ == "__main__":
     # Loop through folders in working dir
     if (working_dir / f"dos_{spin}.npy").exists():
         # Extract DOS
-        extract_DOS(source_dir=working_dir,
-                      atom_index=atom_index, spin=spin)
+        extract_DOS(source_dir=working_dir, atom_index=atom_index, spin=spin)

### 2024-02-14 cnn4dos/shared_components/plot_dos.py

@@ -16,10 +16,11 @@ src_dos_name = "example_dos_up.npy"
 orbital_names = ["s", "py", "pz", "px", "dxy", "dyz", "dz2", "dxz", "dx2-y2"]
 
 
+import os
+
 import matplotlib as mpl
 import matplotlib.pyplot as plt
 import numpy as np
-import os
 
 
 def plot_line(x_coords, arr, savedir):
@@ -45,7 +46,7 @@ def plot_line(x_coords, arr, savedir):
 
     # Set x/y axis labels
     ## Ref: https://matplotlib.org/stable/tutorials/text/mathtext.html
-    mpl.rcParams['mathtext.default'] = 'regular'  # do not use Italic as default
+    mpl.rcParams["mathtext.default"] = "regular"  # do not use Italic as default
     fig.supxlabel("E-E$_f$ (eV)", fontsize=18)
     fig.supylabel("DOS (states/eV)", fontsize=18)
 
@@ -64,20 +65,19 @@ if __name__ == "__main__":
     assert isinstance(energy_step, int)
     assert isinstance(e_fermi, (int, float))
 
-
     # Import DOS array
     src_dos = np.load(os.path.join(working_dir, src_dos_name))
 
     # Check DOS array
     if src_dos.shape[1] > 9:
-        print(f"Caution! Expected DOS in shape (NEDOS, orbital), found shape ({src_dos.shape[0]}, {src_dos.shape[1]})")
-
+        print(
+            f"Caution! Expected DOS in shape (NEDOS, orbital), found shape ({src_dos.shape[0]}, {src_dos.shape[1]})"
+        )
 
     # Generate x coordinates
     energy_array = np.linspace(energy_start, energy_end, energy_step)
     ## Subtract fermi level
     energy_array = energy_array - e_fermi
-
 
     # Plot original DOS as line
     plot_line(energy_array, src_dos, savedir=working_dir)

### 2024-02-14 cnn4dos/shared_components/src/cnnPredictor.py

@@ -1,9 +1,11 @@
 #!/bin/usr/python3
 # -*- coding: utf-8 -*-
 
-import tensorflow as tf
-import numpy as np
 from pathlib import Path
+
+import numpy as np
+import tensorflow as tf
+
 
 class CNNPredictor:
 
@@ -20,7 +22,9 @@ class CNNPredictor:
         """
 
         if model_path and loaded_model:
-            raise ValueError("You can either provide a model_path or a loaded_model, not both.")
+            raise ValueError(
+                "You can either provide a model_path or a loaded_model, not both."
+            )
 
         if model_path:
             self.model = tf.keras.models.load_model(Path(model_path) / "model")
@@ -33,7 +37,9 @@ class CNNPredictor:
         else:
             raise ValueError("Either model_path or loaded_model should be provided.")
 
-    def predict(self, dos_array: np.ndarray, adsorbate_dos_array: np.ndarray) -> np.ndarray:
+    def predict(
+        self, dos_array: np.ndarray, adsorbate_dos_array: np.ndarray
+    ) -> np.ndarray:
         """
         Make predictions based on the DOS and adsorbate DOS arrays.
 
@@ -53,12 +59,16 @@ class CNNPredictor:
             raise ValueError("The last dimension (numChannels) of DOS array must be 1.")
 
         if dos_array.shape[:-1] != adsorbate_dos_array.shape[:-1]:
-            raise ValueError("The shapes of dos_array and adsorbate_dos_array must match in the first two dimensions.")
+            raise ValueError(
+                "The shapes of dos_array and adsorbate_dos_array must match in the first two dimensions."
+            )
 
         # Append adsorbate DOS array to DOS array along the numChannels axis
         combined_array = np.concatenate([dos_array, adsorbate_dos_array], axis=-1)
 
         # Make predictions with CNN model
-        predictions = self.model.predict(np.expand_dims(combined_array, axis=0), verbose=0).flatten()
+        predictions = self.model.predict(
+            np.expand_dims(combined_array, axis=0), verbose=0
+        ).flatten()
 
         return predictions

### 2024-02-14 cnn4dos/shared_components/src/dataLoader.py

@@ -1,10 +1,12 @@
 #!/bin/usr/python3
 # -*- coding: utf-8 -*-
 
+import warnings
+from pathlib import Path
+
 import numpy as np
 import yaml
-from pathlib import Path
-import warnings
+
 
 class DataLoader:
 
@@ -28,12 +30,14 @@ class DataLoader:
         if not config_path.exists():
             raise FileNotFoundError(f"The specified file {config_path} does not exist.")
 
-        with open(config_path, 'r') as f:
+        with open(config_path, "r") as f:
             config = yaml.safe_load(f)
 
         return config
 
-    def load_and_preprocess_adsorbate_dos(self, filepath: str, max_adsorbate_channels: int) -> np.ndarray:
+    def load_and_preprocess_adsorbate_dos(
+        self, filepath: str, max_adsorbate_channels: int
+    ) -> np.ndarray:
         """
         Load and preprocess the adsorbate DOS array.
 
@@ -74,7 +78,9 @@ class DataLoader:
             raise ValueError("Number of channels exceeds the maximum allowed.")
         elif numChannels < max_adsorbate_channels:
             pad_width = max_adsorbate_channels - numChannels
-            adsorbate_dos = np.pad(adsorbate_dos, ((0, 0), (0, 0), (0, pad_width)), 'constant')
+            adsorbate_dos = np.pad(
+                adsorbate_dos, ((0, 0), (0, 0), (0, pad_width)), "constant"
+            )
 
         return adsorbate_dos
 
@@ -101,7 +107,9 @@ class DataLoader:
 
         unshifted_dos = np.load(filepath)
         numSamplings, numOrbitals = unshifted_dos.shape
-        unshifted_dos = np.expand_dims(unshifted_dos, axis=-1)  # Reshape to (numSamplings, numOrbitals, 1)
+        unshifted_dos = np.expand_dims(
+            unshifted_dos, axis=-1
+        )  # Reshape to (numSamplings, numOrbitals, 1)
 
         if numOrbitals not in {1, 4, 9, 16}:
             raise ValueError("numOrbitals must be one of {1, 4, 9, 16}")

### 2024-02-14 cnn4dos/shared_components/src/dosProcessor.py

@@ -1,8 +1,10 @@
 #!/bin/usr/python3
 # -*- coding: utf-8 -*-
 
-import numpy as np
 import warnings
+
+import numpy as np
+
 
 class DOSProcessor:
     def __init__(self, dos_array: np.ndarray):
@@ -22,7 +24,9 @@ class DOSProcessor:
         numSamplings, numOrbitals, _ = dos_array.shape
 
         if numSamplings <= 500:
-            warnings.warn("The number of samplings is not greater than 500, please double-check if DOS is in correct shape.")
+            warnings.warn(
+                "The number of samplings is not greater than 500, please double-check if DOS is in correct shape."
+            )
 
         if numOrbitals not in {1, 4, 9, 16}:
             raise ValueError("numOrbitals must be one of {1, 4, 9, 16}")

### 2024-02-14 figures/3D-volcano-plot/main.py

@@ -1,21 +1,18 @@
-"""Create 2D/3D ridge plots."""
-
-# Plotted with: https://github.com/ColCarroll/ridge_map
-
+"""Create 2D/3D ridge plots, with github.com/ColCarroll/ridge_map."""
 
 from pathlib import Path
 
-from src.RidgeMapPlotter import RidgeMapPlotter
+from .src.RidgeMapPlotter import RidgeMapPlotter  # type: ignore
 
 
-def main():
+def main() -> None:
     plotter = RidgeMapPlotter(
         coordinates=(-156.250305, 18.890695, -154.714966, 20.275080),
-        font_url='https://github.com/google/fonts/blob/main/ofl/uncialantiqua/UncialAntiqua-Regular.ttf?raw=true',
+        font_url="https://github.com/google/fonts/blob/main/ofl/uncialantiqua/UncialAntiqua-Regular.ttf?raw=true",
         show_plot=False,
-        cmap='coolwarm',  # https://matplotlib.org/stable/gallery/color/colormap_reference.html
+        cmap="coolwarm",  # https://matplotlib.org/stable/gallery/color/colormap_reference.html
         interpolate=False,
-        )
+    )
 
     # Generate and plot 3D ridge
     plotter.get_3D_data(num_lines=150)
@@ -23,11 +20,8 @@ def main():
 
     # Generate and plot 2D projection
     plotter.get_2D_data(num_lines=150)
-    plotter.plot_2D_projection(
-        filename=Path("figures") / "2D_volcano.png",
-        alpha=1.0
-        )
+    plotter.plot_2D_projection(filename=Path("figures") / "2D_volcano.png", alpha=1.0)
 
 
-if __name__ == '__main__':
+if __name__ == "__main__":
     main()

### 2024-02-14 figures/3D-volcano-plot/src/RidgeMapPlotter.py

@@ -1,57 +1,80 @@
-# https://github.com/ColCarroll/ridge_map
+"""Create 2D/3D ridge plots, with github.com/ColCarroll/ridge_map."""
 
+from pathlib import Path
+from typing import Tuple
 
-from ridge_map import FontManager, RidgeMap
 import matplotlib.pyplot as plt
 import numpy as np
-from pathlib import Path
 import pandas as pd
+from ridge_map import FontManager, RidgeMap  # type: ignore
 
 
 class RidgeMapPlotter:
-    def __init__(self, coordinates, font_url, show_plot=False, cmap='ocean', interpolate=False):
+    def __init__(
+        self,
+        coordinates: Tuple[float, float, float, float],
+        font_url: str,
+        show_plot: bool = False,
+        cmap: str = "ocean",
+        interpolate: bool = False,
+    ) -> None:
         self.font = FontManager(font_url)
         self.rm = RidgeMap(coordinates, font=self.font.prop)
         self.show_plot = show_plot
         self.cmap = plt.get_cmap(cmap)
         self.interpolate = interpolate
 
-    def get_3D_data(self, num_lines):
+    def get_3D_data(self, num_lines: int) -> None:
         self.values_3D = self.rm.get_elevation_data(num_lines=num_lines)
-        self.preprocessed_values_3D = self.rm.preprocess(values=self.values_3D, lake_flatness=2, water_ntile=10, vertical_ratio=250)
+        self.preprocessed_values_3D = self.rm.preprocess(
+            values=self.values_3D, lake_flatness=2, water_ntile=10, vertical_ratio=250
+        )
 
         if self.interpolate:
-            self.preprocessed_values_3D = self._interpolate_with_adjacent_means(self.preprocessed_values_3D)
+            self.preprocessed_values_3D = self._interpolate_with_adjacent_means(
+                self.preprocessed_values_3D
+            )
 
-    def get_2D_data(self, num_lines):
+    def get_2D_data(self, num_lines: int) -> None:
         self.values_2D = self.rm.get_elevation_data(num_lines=num_lines)
-        self.preprocessed_values_2D = self.rm.preprocess(values=self.values_2D, lake_flatness=2, water_ntile=10, vertical_ratio=250)
+        self.preprocessed_values_2D = self.rm.preprocess(
+            values=self.values_2D, lake_flatness=2, water_ntile=10, vertical_ratio=250
+        )
 
         if self.interpolate:
[…]

### 2024-02-14 figures/supporting-information/plot_activity_periodic_table/main.py

@@ -4,6 +4,7 @@
 
 import os
 from pathlib import Path
+
 import yaml
 from src.load_limiting_potential import load_limiting_potential
 from src.plot_periodic_table import plot_periodic_table
@@ -18,26 +19,28 @@ def main():
     substrate = cfg["species"]["substrate"]
     colorbar_range = cfg["plottings"]["colorbar_range"]
 
-
     # Load limiting potential for selected substrate
-    limiting_potential = load_limiting_potential(limiting_potential_file, substrate=substrate,
-                            name_col=data_cols["name"], potential_col=data_cols["limiting_potential"])
-
+    limiting_potential = load_limiting_potential(
+        limiting_potential_file,
+        substrate=substrate,
+        name_col=data_cols["name"],
+        potential_col=data_cols["limiting_potential"],
+    )
 
     # Pass limiting potential to plotter
     os.makedirs("figures", exist_ok=True)
     plot_periodic_table(
-    limiting_potential_dict=limiting_potential,
-    extended=False,  # hide Lu/Lr elements
-    cmap="coolwarm",
-    cbar_height=390,  # colorbar height (should reposition to top right)
-    alpha=0.80,
-    cbar_location=(0, 162),
-    cbar_range=colorbar_range,
-    output_filename=(Path("figures") / f"{substrate}.png").resolve(),
-    show=False
+        limiting_potential_dict=limiting_potential,
+        extended=False,  # hide Lu/Lr elements
+        cmap="coolwarm",
+        cbar_height=390,  # colorbar height (should reposition to top right)
+        alpha=0.80,
+        cbar_location=(0, 162),
+        cbar_range=colorbar_range,
+        output_filename=(Path("figures") / f"{substrate}.png").resolve(),
+        show=False,
     )
 
 
 if __name__ == "__main__":
-   main()
+    main()

### 2024-02-14 figures/supporting-information/plot_activity_periodic_table/src/load_limiting_potential.py

@@ -3,6 +3,7 @@
 
 
 import os
+
 import pandas as pd
 
 
@@ -38,7 +39,6 @@ def load_limiting_potential(path, substrate, name_col=0, potential_col=1):
             names.append(name.split("_")[-1])
             potentials.append(float(row[potential_col]))
 
-
     if not names:
         raise ValueError(f"No match found for substrate {substrate}.")
     else:
@@ -47,5 +47,7 @@ def load_limiting_potential(path, substrate, name_col=0, potential_col=1):
 
 # Test area
 if __name__ == "__main__":
-    load_limiting_potential(path="../../../5-volcano-plot/src/test/debug_results/diff_limiting_potential.csv",
-                            substrate="g-C3N4")
+    load_limiting_potential(
+        path="../../../5-volcano-plot/src/test/debug_results/diff_limiting_potential.csv",
+        substrate="g-C3N4",
+    )

### 2024-02-14 figures/supporting-information/plot_activity_periodic_table/src/plot_periodic_table.py

@@ -7,22 +7,25 @@ This module was taken from: https://github.com/arosen93/ptable_trends, and only 
 """
 
 
+import warnings
+from typing import List
+
+import colorcet
 from bokeh.io import export_png
 from bokeh.io import show as show_
-from bokeh.models import BasicTicker, ColorBar, ColumnDataSource, LinearColorMapper, NumeralTickFormatter
+from bokeh.models import (BasicTicker, ColorBar, ColumnDataSource,
+                          LinearColorMapper, NumeralTickFormatter)
 from bokeh.plotting import figure
 from bokeh.sampledata.periodic_table import elements
 from bokeh.transform import dodge
-import colorcet
 from matplotlib import rcParams
+from matplotlib.cm import ScalarMappable, coolwarm, turbo
 from matplotlib.colors import Normalize, to_hex
-from matplotlib.cm import coolwarm, ScalarMappable, turbo
 from pandas import options
-from typing import List
-import warnings
 
 rcParams["font.family"] = "sans-serif"
 rcParams["font.sans-serif"] = ["Arial"]
+
 
 def plot_periodic_table(
     limiting_potential_dict: dict,
@@ -47,7 +50,6 @@ def plot_periodic_table(
     cbar_location: tuple = (0, 0),  # location of colorbar
     cbar_range: dict = None,
 ) -> figure:
-
     """
     Plot a heatmap over the periodic table of elements.
 
@@ -131,7 +133,6 @@ def plot_periodic_table(
     data_elements = [i.split("-")[-1] for i in limiting_potential_dict.keys()]
     data = list(limiting_potential_dict.values())
 
-
     period_label.append("blank")
     period_label.append("La")
     period_label.append("Ac")
@@ -152,8 +153,7 @@ def plot_periodic_table(
 
     # Define matplotlib and bokeh color map
     color_mapper = LinearColorMapper(
-        palette=bokeh_palette,
-        low=min(data), high=max(data)
+        palette=bokeh_palette, low=min(data), high=max(data)
     )
     norm = Normalize(vmin=min(data), vmax=max(data))
     color_scale = ScalarMappable(norm=norm, cmap=cmap).to_rgba(data, alpha=None)
@@ -226,10 +226,8 @@ def plot_periodic_table(
     )
     p.text(x=x, y=y, text="atomic_number", text_font_size="11pt", **text_props)
 
-
     # Hide grid lines
     p.grid.grid_line_color = None
-
 
     # Add colorbar
[…]

### 2024-02-14 figures/supporting-information/plot_adsorption_energy_correlation/main.py

@@ -2,15 +2,14 @@
 # -*- coding: utf-8 -*-
 
 
+import os
+
 import matplotlib.pyplot as plt
 import numpy as np
-import os
 import seaborn as sns
-
 from src.create_heatmap import corrplot
-from src.generate_corr_matrix import generate_corr_matrix
 from src.format_mol_name import format_mol_name
-
+from src.generate_corr_matrix import generate_corr_matrix
 
 if __name__ == "__main__":
     # Generate correlation matrix
@@ -28,11 +27,18 @@ if __name__ == "__main__":
     plt.figure(figsize=(8, 7))
     corrplot(
         corr_matrix,
-        size_scale=500, marker="s",  # shape of the marker
-        )
+        size_scale=500,
+        marker="s",  # shape of the marker
+    )
 
-    plt.savefig(os.path.join("figures", "Eads_correlation_map.png"), bbox_inches="tight", dpi=300)
+    plt.savefig(
+        os.path.join("figures", "Eads_correlation_map.png"),
+        bbox_inches="tight",
+        dpi=300,
+    )
 
     # Show correlation coefficients
     print(corr_matrix)
-    print(f"Min value across entire dataframe is {corr_matrix.min().min():.4f}. Variance is {np.var(corr_matrix.to_numpy().flatten(), ddof=1)}.")
+    print(
+        f"Min value across entire dataframe is {corr_matrix.min().min():.4f}. Variance is {np.var(corr_matrix.to_numpy().flatten(), ddof=1)}."
+    )

### 2024-02-14 figures/supporting-information/plot_adsorption_energy_correlation/src/create_heatmap.py

@@ -3,11 +3,11 @@ I did not write this module, but took it from somewhere from the Internet.
 Sadly I cannot remember the original author.  --Haoyu Yang.
 """
 
-
 import matplotlib.pyplot as plt
+import numpy as np
 import pandas as pd
 import seaborn as sns
-import numpy as np
+
 plt.rcParams["font.family"] = "Arial"
 
 
@@ -17,69 +17,98 @@ def heatmap(x, y, **kwargs):
         if color_min == color_max:
             return palette[-1]
         else:
-            val_position = float((val - color_min)) / (color_max - color_min)  # position of value in the input range, relative to the length of the input range
-            val_position = min(max(val_position, 0), 1)  # bound the position between 0 and 1
-            ind = int(val_position * (n_colors - 1))  # target index in the color palette
+            val_position = float((val - color_min)) / (
+                color_max - color_min
+            )  # position of value in the input range, relative to the length of the input range
+            val_position = min(
+                max(val_position, 0), 1
+            )  # bound the position between 0 and 1
+            ind = int(
+                val_position * (n_colors - 1)
+            )  # target index in the color palette
             return palette[ind]
 
     def value_to_size(val):
         if size_min == size_max:
             return 1 * size_scale
         else:
-            val_position = (val - size_min) * 0.99 / (size_max - size_min) + 0.01  # position of value in the input range, relative to the length of the input range
-            val_position = min(max(val_position, 0), 1)  # bound the position between 0 and 1
+            val_position = (val - size_min) * 0.99 / (
+                size_max - size_min
+            ) + 0.01  # position of value in the input range, relative to the length of the input range
+            val_position = min(
+                max(val_position, 0), 1
+            )  # bound the position between 0 and 1
 
             return val_position * size_scale
 
-    if 'color' in kwargs:
-        color = kwargs['color']
+    if "color" in kwargs:
+        color = kwargs["color"]
     else:
         color = [1] * len(x)
 
-    if 'palette' in kwargs:
-        palette = kwargs['palette']
[…]

### 2024-02-14 figures/supporting-information/plot_adsorption_energy_correlation/src/format_mol_name.py

@@ -15,14 +15,14 @@ def format_mol_name(string):
         str: formatted name
 
     """
-    pattern = r'\d+'
+    pattern = r"\d+"
     numbers = re.findall(pattern, string)
 
     for num in numbers:
-        num_subscript = ''
+        num_subscript = ""
         for digit in num:
-            num_subscript += f'$_\mathregular{{{digit}}}$'
-        string = string.replace(num, f'{num_subscript}')
+            num_subscript += f"$_\mathregular{{{digit}}}$"
+        string = string.replace(num, f"{num_subscript}")
 
     return string
 

### 2024-02-14 figures/supporting-information/plot_adsorption_energy_correlation/src/generate_corr_matrix.py

@@ -2,8 +2,10 @@
 # -*- coding: utf-8 -*-
 
 
-import yaml
 import sys
+
+import yaml
+
 sys.path.insert(0, "../../5-volcano-plot/src/lib")
 
 from dataLoader import dataLoader
@@ -28,17 +30,18 @@ def generate_corr_matrix(config_file, corr_type="pearson"):
     substrates = cfg["species"]["substrates"]
     adsorbates = cfg["species"]["adsorbates"]
 
-
     # Load adsorption energy of selected species
     loader = dataLoader()
-    loader.load_adsorption_energy(path=adsorption_energy_path, substrates=substrates, adsorbates=adsorbates)
+    loader.load_adsorption_energy(
+        path=adsorption_energy_path, substrates=substrates, adsorbates=adsorbates
+    )
 
     adsorption_energy_dict = loader.adsorption_energy
 
-
     # Stack adsorption energy from different substrates to one DataFrame
-    adsorption_energy_df = stack_adsorption_energy_dict(adsorption_energy_dict, remove_prefix_from_colname=True)
-
+    adsorption_energy_df = stack_adsorption_energy_dict(
+        adsorption_energy_dict, remove_prefix_from_colname=True
+    )
 
     # Calculate Pearson correlation coefficient map
     return adsorption_energy_df.corr(method=corr_type)

### 2024-02-14 figures/supporting-information/plot_d-band-centre_vs_Eads/plot_all.py

@@ -3,13 +3,12 @@
 
 
 import os
-import yaml
 
+import yaml
 from src.dBand import dBand
 from src.list_dos_files import list_dos_files
 from src.load_ads_energy import load_ads_energy
 from src.plot_scatter import plot_scatter
-
 
 if __name__ == "__main__":
     # Load configs
@@ -27,7 +26,6 @@ if __name__ == "__main__":
 
     energy_range = cfg["calculation"]["energy_range"]
 
-
     # Work on all DOS files
     d_band_centres = []
     adsorption_energies = []
@@ -37,11 +35,16 @@ if __name__ == "__main__":
 
     for file in dos_files:
         # Calculate d-band centre
-        calculator = dBand(dosFile=file, fileType="numpy",
-                           fermi_level_dir=fermi_level_dir,
-                           energy_range=energy_range)
+        calculator = dBand(
+            dosFile=file,
+            fileType="numpy",
+            fermi_level_dir=fermi_level_dir,
+            energy_range=energy_range,
+        )
 
-        d_band_centre = calculator.calculate_d_band_centre(merge_suborbitals=True, verbose=False)
+        d_band_centre = calculator.calculate_d_band_centre(
+            merge_suborbitals=True, verbose=False
+        )
 
         # Skip samples without d electron
         if d_band_centre != "NA":
@@ -55,4 +58,11 @@ if __name__ == "__main__":
             colors.append(color_dict[file.split(os.sep)[-4]])
 
     # Create scatter plot
-    plot_scatter(x=d_band_centres, y=adsorption_energies, labels=labels, colors=colors, show=True, savename=os.path.join("figures", "d-band-Eads.png"))
+    plot_scatter(
+        x=d_band_centres,
+        y=adsorption_energies,
+        labels=labels,
+        colors=colors,
+        show=True,
+        savename=os.path.join("figures", "d-band-Eads.png"),
+    )

### 2024-02-14 figures/supporting-information/plot_d-band-centre_vs_Eads/plot_each_ads.py

@@ -3,13 +3,12 @@
 
 
 import os
-import yaml
 
+import yaml
 from src.dBand import dBand
 from src.list_dos_files import list_dos_files
 from src.load_ads_energy import load_ads_energy
 from src.plot_scatter import plot_scatter
-
 
 if __name__ == "__main__":
     # Load configs
@@ -33,21 +32,34 @@ if __name__ == "__main__":
         adsorption_energies = []
         labels = []
         colors = []
-        dos_files = list_dos_files(dos_dir, [ads, ], substrates)
+        dos_files = list_dos_files(
+            dos_dir,
+            [
+                ads,
+            ],
+            substrates,
+        )
 
         for file in dos_files:
             # Calculate d-band centre
-            calculator = dBand(dosFile=file, fileType="numpy",
-                            fermi_level_dir=fermi_level_dir,
-                            energy_range=energy_range)
+            calculator = dBand(
+                dosFile=file,
+                fileType="numpy",
+                fermi_level_dir=fermi_level_dir,
+                energy_range=energy_range,
+            )
 
-            d_band_centre = calculator.calculate_d_band_centre(merge_suborbitals=True, verbose=False)
+            d_band_centre = calculator.calculate_d_band_centre(
+                merge_suborbitals=True, verbose=False
+            )
 
             # Skip samples without d electron
             if d_band_centre != "NA":
                 d_band_centres.append(d_band_centre)
                 # Get adsorption energy
-                adsorption_energies.append(load_ads_energy(file, ads_energy_dir=label_dir))
+                adsorption_energies.append(
+                    load_ads_energy(file, ads_energy_dir=label_dir)
+                )
 
                 labels.append(file.split(os.sep)[-4])
 
@@ -55,4 +67,11 @@ if __name__ == "__main__":
                 colors.append(color_dict[file.split(os.sep)[-4]])
 
         # Create scatter plot
-        plot_scatter(x=d_band_centres, y=adsorption_energies, labels=labels, colors=colors, show=False, savename=os.path.join("figures", f"{ads}.png"))
+        plot_scatter(
+            x=d_band_centres,
+            y=adsorption_energies,
+            labels=labels,
+            colors=colors,
+            show=False,
+            savename=os.path.join("figures", f"{ads}.png"),
+        )

### 2024-02-14 figures/supporting-information/plot_d-band-centre_vs_Eads/src/dBand.py

@@ -3,20 +3,29 @@
 
 
 import os
-import numpy as np
-from .load_fermi_level import load_fermi_level
 import warnings
+
+import numpy as np
+
+from .load_fermi_level import load_fermi_level
 
 
 class dBand:
-    def __init__(self, dosFile, fermi_level_dir, energy_range, fileType="numpy",):
+    def __init__(
+        self,
+        dosFile,
+        fermi_level_dir,
+        energy_range,
+        fileType="numpy",
+    ):
         # Check args
         assert os.path.exists(dosFile)
-        if fileType not in {"numpy", }:
-            raise ValueError(f"DOS file type \"{fileType}\" is currently not supported.")
+        if fileType not in {
+            "numpy",
+        }:
+            raise ValueError(f'DOS file type "{fileType}" is currently not supported.')
         assert isinstance(energy_range, (list, tuple)) and len(energy_range) == 2
         self.energy_range = energy_range
-
 
         # Load DOS from file
         self.__load_dos(dosFile, fileType)
@@ -27,10 +36,8 @@ class dBand:
         # Take d-band DOS
         self.__take_d_band()
 
-
         # Load fermi level
         self.fermi_level = load_fermi_level(dosFile, fermi_level_dir)
-
 
     def __calculate_band_moment(self, single_dos_orbital, energy_array, ordinal):
         """Calculate nth-order band moment.
@@ -45,24 +52,23 @@ class dBand:
         assert isinstance(ordinal, int) and ordinal >= 1
         assert single_dos_orbital.ndim == 1
 
-
         # Calculate band moment
         density = np.copy(single_dos_orbital) ** ordinal
 
-        numerator = np.trapz(y=(density * np.copy(energy_array)),
-                             dx=(energy_array[-1] - energy_array[0]) / energy_array.shape[0]
-                             )
+        numerator = np.trapz(
+            y=(density * np.copy(energy_array)),
+            dx=(energy_array[-1] - energy_array[0]) / energy_array.shape[0],
+        )
 
-        denominator = np.trapz(y=density,
-                               dx=(energy_array[-1] - energy_array[0]) / energy_array.shape[0]
-                               )
+        denominator = np.trapz(
+            y=density, dx=(energy_array[-1] - energy_array[0]) / energy_array.shape[0]
+        )
 
         if numerator * denominator != 0:
             return numerator / denominator
 
         else:
[…]

### 2024-02-14 figures/supporting-information/plot_d-band-centre_vs_Eads/src/list_dos_files.py

@@ -27,7 +27,6 @@ def list_dos_files(dos_dir, adsorbates, substrates, dos_file_name="dos_up_*.npy"
     assert isinstance(adsorbates, list)
     assert isinstance(substrates, list)
 
-
     # Get all DOS files
     dos_files = []
     for sub in substrates:
@@ -35,9 +34,10 @@ def list_dos_files(dos_dir, adsorbates, substrates, dos_file_name="dos_up_*.npy"
             dos_file_pattern = os.path.join(dos_dir, sub, ads, "*", dos_file_name)
             matches = glob.glob(dos_file_pattern)
             if not matches:
-                raise ValueError(f"No matched DOS found for pattern {dos_file_pattern}.")
+                raise ValueError(
+                    f"No matched DOS found for pattern {dos_file_pattern}."
+                )
             dos_files.extend(matches)
-
 
     return dos_files
 
@@ -47,7 +47,16 @@ if __name__ == "__main__":
 
     dos_files = list_dos_files(
         dos_dir="../../0-dataset/feature_DOS",
-        adsorbates=["3-CO_is", ],
-        substrates = ["g-C3N4", "nitrogen-graphene", "vacant-graphene", "C2N", "BN", "BP"],
+        adsorbates=[
+            "3-CO_is",
+        ],
+        substrates=[
+            "g-C3N4",
+            "nitrogen-graphene",
+            "vacant-graphene",
+            "C2N",
+            "BN",
+            "BP",
+        ],
     )
     print(dos_files)

### 2024-02-14 figures/supporting-information/plot_d-band-centre_vs_Eads/src/load_ads_energy.py

@@ -3,6 +3,7 @@
 
 
 import os
+
 import pandas as pd
 
 
@@ -21,16 +22,16 @@ def load_ads_energy(dosFile, ads_energy_dir):
     assert os.path.exists(dosFile)
     assert os.path.isdir(ads_energy_dir)
 
-
     # Unpack DOS file name
     substrate = dosFile.split(os.sep)[-4]
     adsorbate = dosFile.split(os.sep)[-3].split("_")[0]
     state = dosFile.split(os.sep)[-3].split("_")[-1]
     metal = dosFile.split(os.sep)[-2]
 
-
     # Get adsorption energy DataFrame
-    df = pd.read_csv(os.path.join(ads_energy_dir, f"{substrate}_{state}.csv"), index_col=0)
+    df = pd.read_csv(
+        os.path.join(ads_energy_dir, f"{substrate}_{state}.csv"), index_col=0
+    )
 
     return df.loc[metal, adsorbate]
 

### 2024-02-14 figures/supporting-information/plot_d-band-centre_vs_Eads/src/load_fermi_level.py

@@ -3,6 +3,7 @@
 
 
 import os
+
 import pandas as pd
 
 
@@ -20,7 +21,6 @@ def load_fermi_level(dosFile, fermi_level_dir):
     # Check args
     assert os.path.isdir(fermi_level_dir)
 
-
     # Unpack info from DOS file name
     ## substrate name
     substrate = dosFile.split(os.sep)[-4]
@@ -34,10 +34,11 @@ def load_fermi_level(dosFile, fermi_level_dir):
     ## metal name
     metal = dosFile.split(os.sep)[-2]
 
-
     # Load fermi level csv file
     assert os.path.isdir(fermi_level_dir)
-    fermi_level_df = pd.read_csv(os.path.join(fermi_level_dir, f"{substrate}-{state}.csv"), index_col=0)
+    fermi_level_df = pd.read_csv(
+        os.path.join(fermi_level_dir, f"{substrate}-{state}.csv"), index_col=0
+    )
 
     # Locate desired fermi level
     return fermi_level_df.loc[metal, adsorbate]

### 2024-02-14 figures/supporting-information/plot_d-band-centre_vs_Eads/src/plot_scatter.py

@@ -6,7 +6,9 @@ import matplotlib as mpl
 import matplotlib.pyplot as plt
 
 
-def plot_scatter(x, y, labels, colors=None, show=False, savename="d-band-Eads.png", dpi=300):
+def plot_scatter(
+    x, y, labels, colors=None, show=False, savename="d-band-Eads.png", dpi=300
+):
     """Plot scatter for d-band centre vs adsorption energy relationship.
 
     Args:
@@ -27,7 +29,6 @@ def plot_scatter(x, y, labels, colors=None, show=False, savename="d-band-Eads.pn
     else:
         assert len(x) == len(colors)
 
-
     # Create scatter plot
     mpl.rcParams.update(mpl.rcParamsDefault)
     mpl.rcParams["axes.linewidth"] = 2.5
@@ -38,7 +39,6 @@ def plot_scatter(x, y, labels, colors=None, show=False, savename="d-band-Eads.pn
     # Set legend
     plt.legend()
 
-
     # # Set x/y axis labels
     # plt.xlabel("d-Band Centre (eV)", fontsize=18)
     # plt.ylabel("Adsorption Energy (eV)", fontsize=16)
@@ -46,12 +46,11 @@ def plot_scatter(x, y, labels, colors=None, show=False, savename="d-band-Eads.pn
     plt.xlim(-15, 5)
 
     # Set x/y tick label sizes
-    plt.xticks(range(-15, 10, 5),fontsize=18)
+    plt.xticks(range(-15, 10, 5), fontsize=18)
     plt.yticks(fontsize=18)
 
     # Set x/y tick length and thickness
     plt.tick_params("both", length=5, width=2.5, which="major")
-
 
     # Show and save figure
     plt.tight_layout()

### 2024-02-14 figures/supporting-information/plot_d-band-centre_vs_Eads/test/calc_test.py

@@ -1,6 +1,6 @@
-
 import sys
-sys.path.append('../src')
+
+sys.path.append("../src")
 # mport dBand
 import numpy as np
 import pandas as pd
@@ -10,13 +10,14 @@ def __calculate_band_moment(single_dos_orbital, energy_array, ordinal):
     # Calculate band moment
     density = np.copy(single_dos_orbital) ** ordinal
 
-    numerator = np.trapz(y=(density * np.copy(energy_array)),
-                            dx=(energy_array[-1] - energy_array[0]) / energy_array.shape[0]
-                            )
+    numerator = np.trapz(
+        y=(density * np.copy(energy_array)),
+        dx=(energy_array[-1] - energy_array[0]) / energy_array.shape[0],
+    )
 
-    denominator = np.trapz(y=density,
-                            dx=(energy_array[-1] - energy_array[0]) / energy_array.shape[0]
-                            )
+    denominator = np.trapz(
+        y=density, dx=(energy_array[-1] - energy_array[0]) / energy_array.shape[0]
+    )
 
     return numerator / denominator
 
@@ -29,13 +30,11 @@ if __name__ == "__main__":
     energy_array = np.array(df["Energy"])
     d_band_array = np.array(df["d-DOS"])
 
-
     # Calculate d-band centre
     centre = __calculate_band_moment(
         single_dos_orbital=d_band_array,
         energy_array=energy_array,
         ordinal=1,
-
     )
 
     print(centre)

### 2024-02-14 figures/supporting-information/plot_descriptor_kendall_correlation/main.py

@@ -4,10 +4,10 @@
 
 import os
 from pathlib import Path
+
 import yaml
 from src.descriptors import Descriptors
 from src.plot_correlation import plot_correlation
-
 
 if __name__ == "__main__":
     # Load configs
@@ -19,7 +19,6 @@ if __name__ == "__main__":
     electronic_descriptor_file = Path(cfg["path"]["electronic_descriptor_file"])
     descriptor_symbol_dict = cfg["plot"]["descriptor_symbol_dict"]
 
-
     # Load and merge descriptor data
     loader = Descriptors(
         adsorption_energy_file=adsorption_energy_file,
@@ -29,16 +28,19 @@ if __name__ == "__main__":
 
     merged_descriptors = loader.merged_descriptors
 
-
     # Drop metal/substrate columns for correlation map plotting
     merged_descriptors.drop(labels=["metal", "substrate"], axis=1, inplace=True)
-
 
     # Apply standard symbols for descriptor names
     merged_descriptors = merged_descriptors.rename(columns=descriptor_symbol_dict)
     print(merged_descriptors)
 
-
     # Plot Kendall correlation map
     os.makedirs("figures", exist_ok=True)
-    plot_correlation(merged_descriptors, method="kendall", savename=Path("figures") / "kendall_corr.png", show=True, verbose=True)
+    plot_correlation(
+        merged_descriptors,
+        method="kendall",
+        savename=Path("figures") / "kendall_corr.png",
+        show=True,
+        verbose=True,
+    )

### 2024-02-14 figures/supporting-information/plot_descriptor_kendall_correlation/src/descriptors.py

@@ -2,12 +2,18 @@
 # -*- coding: utf-8 -*-
 
 
-import pandas as pd
 from pathlib import Path
+
+import pandas as pd
 
 
 class Descriptors:
-    def __init__(self, adsorption_energy_file, element_descriptor_file, electronic_descriptor_file) -> None:
+    def __init__(
+        self,
+        adsorption_energy_file,
+        element_descriptor_file,
+        electronic_descriptor_file,
+    ) -> None:
         # Load adsorption energy
         self.__load_adsorption_energy(adsorption_energy_file)
 
@@ -17,10 +23,8 @@ class Descriptors:
         # Load electronic descriptors
         self.__load_electronic_descriptor(electronic_descriptor_file)
 
-
         # Merge all descriptors
         self.__merge_descriptors()
-
 
     def __load_adsorption_energy(self, path):
         """Load adsorption energy from csv file.
@@ -32,7 +36,6 @@ class Descriptors:
         assert path.exists()
         self.adsorption_energy = pd.read_csv(path)
 
-
     def __load_element_descriptor(self, path):
         """Load element (elementary) descriptors from csv file.
 
@@ -42,7 +45,6 @@ class Descriptors:
         """
         assert path.exists()
         self.element_descriptor = pd.read_csv(path)
-
 
     def __load_electronic_descriptor(self, path):
         """Load electronic descriptors from csv file.
@@ -54,41 +56,59 @@ class Descriptors:
         assert path.exists()
         self.electronic_descriptor = pd.read_csv(path)
 
-
     def __merge_descriptors(self):
-        """Merge adsorption energy, element descriptors and electronic descriptors.
-
-        """
+        """Merge adsorption energy, element descriptors and electronic descriptors."""
         # Check substrates of adsorption energy and electronic descriptors
-        if not self.adsorption_energy["substrate"].equals(self.electronic_descriptor["substrate"]):
-            raise ValueError("Substrate lists in adsorption energy and electronic descriptors don't match.")
+        if not self.adsorption_energy["substrate"].equals(
+            self.electronic_descriptor["substrate"]
+        ):
+            raise ValueError(
+                "Substrate lists in adsorption energy and electronic descriptors don't match."
+            )
 
         # Check metals of adsorption energy and electronic descriptors
-        if not self.adsorption_energy["metal"].equals(self.electronic_descriptor["metal"]):
-            raise ValueError("Metal lists in adsorption energy and electronic descriptors don't match.")
-
[…]

### 2024-02-14 figures/supporting-information/plot_descriptor_kendall_correlation/src/heatmap_revised.py

@@ -12,11 +12,14 @@ def corrplot(data, size_scale=500, marker="s"):
     corr = pd.melt(data.reset_index(), id_vars="index").replace(np.nan, 0)
     corr.columns = ["x", "y", "value"]
     heatmap(
-        corr["x"], corr["y"], color=corr["value"],
+        corr["x"],
+        corr["y"],
+        color=corr["value"],
         color_range=[-1, 1],
-        #palette=sns.color_palette("coolwarm", 256),
+        # palette=sns.color_palette("coolwarm", 256),
         palette=sns.color_palette("plasma_r", 256),
-        size=corr["value"].abs(), size_range=[0, 1],
+        size=corr["value"].abs(),
+        size_range=[0, 1],
         marker=marker,
         x_order=data.columns,
         y_order=data.columns[::-1],
@@ -30,36 +33,48 @@ def heatmap(x, y, **kwargs):
         if color_min == color_max:
             return palette[-1]
         else:
-            val_position = float((val - color_min)) / (color_max - color_min) # position of value in the input range, relative to the length of the input range
-            val_position = min(max(val_position, 0), 1) # bound the position betwen 0 and 1
-            ind = int(val_position * (n_colors - 1)) # target index in the color palette
+            val_position = float((val - color_min)) / (
+                color_max - color_min
+            )  # position of value in the input range, relative to the length of the input range
+            val_position = min(
+                max(val_position, 0), 1
+            )  # bound the position betwen 0 and 1
+            ind = int(
+                val_position * (n_colors - 1)
+            )  # target index in the color palette
             return palette[ind]
 
     def value_to_size(val):
         if size_min == size_max:
             return 1 * size_scale
         else:
-            val_position = (val - size_min) * 0.99 / (size_max - size_min) + 0.01 # position of value in the input range, relative to the length of the input range
-            val_position = min(max(val_position, 0), 1) # bound the position betwen 0 and 1
+            val_position = (val - size_min) * 0.99 / (
+                size_max - size_min
+            ) + 0.01  # position of value in the input range, relative to the length of the input range
+            val_position = min(
+                max(val_position, 0), 1
[…]

### 2024-02-14 figures/supporting-information/plot_descriptor_kendall_correlation/src/plot_correlation.py

@@ -2,14 +2,16 @@
 # -*- coding: utf-8 -*-
 
 
-from matplotlib import rcParams
 import matplotlib.pyplot as plt
 import pandas as pd
 import seaborn as sns
+from matplotlib import rcParams
+
 from .heatmap_revised import corrplot  # pip install heatmapz
 
 rcParams["font.family"] = "sans-serif"
 rcParams["font.sans-serif"] = ["Arial"]
+
 
 def plot_correlation(dataset, method, savename, show=True, verbose=False):
     """Plot correlation map.
@@ -28,18 +30,17 @@ def plot_correlation(dataset, method, savename, show=True, verbose=False):
 
     # Print correlation data if required
     if verbose:
-        print(f"\"Absolute value\" of {method} correlation coefficients:")
-        print(corr_data.iloc[:,0].abs().sort_values(ascending=False))
-
+        print(f'"Absolute value" of {method} correlation coefficients:')
+        print(corr_data.iloc[:, 0].abs().sort_values(ascending=False))
 
     # Generate correlation plot
     sns.set(color_codes=True, font_scale=1.2)
     plt.figure(figsize=(8, 8))
     corrplot(
         corr_data,
-        size_scale=150, marker="s",
+        size_scale=150,
+        marker="s",
     )
-
 
     # Save and show plot
     plt.savefig(savename, bbox_inches="tight", dpi=600)

### 2024-02-14 figures/supporting-information/plot_pairwise_descriptor_relations/main.py

@@ -4,10 +4,10 @@
 
 import os
 from pathlib import Path
+
 import yaml
 from src.descriptors import Descriptors
 from src.pairplot import PairPlot
-
 
 if __name__ == "__main__":
     # Load configs
@@ -20,21 +20,21 @@ if __name__ == "__main__":
     descriptors = cfg["plot"]["descriptors"]
     descriptor_symbol_dict = cfg["plot"]["descriptor_symbol_dict"]
 
-
     # Load and merge descriptor data
     loader = Descriptors(
         adsorption_energy_file=adsorption_energy_file,
         element_descriptor_file=element_descriptor_file,
-        electronic_descriptor_file=electronic_descriptor_file
-        )
+        electronic_descriptor_file=electronic_descriptor_file,
+    )
 
     merged_descriptors = loader.merged_descriptors
-
 
     # Generate pairwise relations plot
     plotter = PairPlot(data=merged_descriptors)
     os.makedirs("figures", exist_ok=True)
-    plotter.plot_pairplot(descriptors, descriptor_symbol_dict,
-                          savename=Path("figures/pairplot.png"),
-                          show=True
-                          )
+    plotter.plot_pairplot(
+        descriptors,
+        descriptor_symbol_dict,
+        savename=Path("figures/pairplot.png"),
+        show=True,
+    )

### 2024-02-14 figures/supporting-information/plot_pairwise_descriptor_relations/src/descriptors.py

@@ -2,12 +2,18 @@
 # -*- coding: utf-8 -*-
 
 
-import pandas as pd
 from pathlib import Path
+
+import pandas as pd
 
 
 class Descriptors:
-    def __init__(self, adsorption_energy_file, element_descriptor_file, electronic_descriptor_file) -> None:
+    def __init__(
+        self,
+        adsorption_energy_file,
+        element_descriptor_file,
+        electronic_descriptor_file,
+    ) -> None:
         # Load adsorption energy
         self.__load_adsorption_energy(adsorption_energy_file)
 
@@ -17,10 +23,8 @@ class Descriptors:
         # Load electronic descriptors
         self.__load_electronic_descriptor(electronic_descriptor_file)
 
-
         # Merge all descriptors
         self.__merge_descriptors()
-
 
     def __load_adsorption_energy(self, path):
         """Load adsorption energy from csv file.
@@ -32,7 +36,6 @@ class Descriptors:
         assert path.exists()
         self.adsorption_energy = pd.read_csv(path)
 
-
     def __load_element_descriptor(self, path):
         """Load element (elementary) descriptors from csv file.
 
@@ -42,7 +45,6 @@ class Descriptors:
         """
         assert path.exists()
         self.element_descriptor = pd.read_csv(path)
-
 
     def __load_electronic_descriptor(self, path):
         """Load electronic descriptors from csv file.
@@ -54,41 +56,59 @@ class Descriptors:
         assert path.exists()
         self.electronic_descriptor = pd.read_csv(path)
 
-
     def __merge_descriptors(self):
-        """Merge adsorption energy, element descriptors and electronic descriptors.
-
-        """
+        """Merge adsorption energy, element descriptors and electronic descriptors."""
         # Check substrates of adsorption energy and electronic descriptors
-        if not self.adsorption_energy["substrate"].equals(self.electronic_descriptor["substrate"]):
-            raise ValueError("Substrate lists in adsorption energy and electronic descriptors don't match.")
+        if not self.adsorption_energy["substrate"].equals(
+            self.electronic_descriptor["substrate"]
+        ):
+            raise ValueError(
+                "Substrate lists in adsorption energy and electronic descriptors don't match."
+            )
 
         # Check metals of adsorption energy and electronic descriptors
-        if not self.adsorption_energy["metal"].equals(self.electronic_descriptor["metal"]):
-            raise ValueError("Metal lists in adsorption energy and electronic descriptors don't match.")
-
[…]

### 2024-02-14 figures/supporting-information/plot_pairwise_descriptor_relations/src/pairplot.py

@@ -4,6 +4,7 @@
 
 import seaborn as sns
 from matplotlib import rcParams
+
 rcParams["font.family"] = "sans-serif"
 rcParams["font.sans-serif"] = ["Arial"]
 import matplotlib.pyplot as plt
@@ -14,7 +15,6 @@ class PairPlot:
     def __init__(self, data) -> None:
         assert isinstance(data, pd.DataFrame)
         self.data = data
-
 
     def __preprocess_data(self, descriptors):
         """Preprocess data for pairwise plot, including:
@@ -30,18 +30,14 @@ class PairPlot:
         # Drop metal/substrate name columns for plotting
         self.data.drop(labels=["metal", "substrate"], axis=1, inplace=True)
 
-
         # Drop non-numerical columns
         self.data = self.data._get_numeric_data()
-
 
         # Drop lines with missing value
         self.data.dropna(axis=0, inplace=True)
 
-
         # Take selected descriptors only
         self.data = self.data.loc[:, descriptors]
-
 
     def plot_pairplot(self, descriptors, descriptor_symbol_dict, savename, show=False):
         """Generate pairwise relations plot.
@@ -59,22 +55,18 @@ class PairPlot:
         # Preprocess datasheet
         self.__preprocess_data(descriptors=descriptors)
 
-
         # Rename datasheet columns
         self.data = self.data.rename(columns=descriptor_symbol_dict)
 
-
         # Generate pairwise relation plot
-        with sns.plotting_context(rc={"axes.labelsize":32, "axes.linewidth": 2.5}):
-            sns.pairplot(data=self.data,
-
-                         corner=True,
-                         diag_kind="kde",
-                         # diag_kws= {'color': '#82ad32'},  # set diagonal color
-
-                         plot_kws={"s":100, "color": "#9925be", "alpha":0.8}
-                         )
-
+        with sns.plotting_context(rc={"axes.labelsize": 32, "axes.linewidth": 2.5}):
+            sns.pairplot(
+                data=self.data,
+                corner=True,
+                diag_kind="kde",
+                # diag_kws= {'color': '#82ad32'},  # set diagonal color
+                plot_kws={"s": 100, "color": "#9925be", "alpha": 0.8},
+            )
 
         # Save and show figure
         plt.savefig(savename, dpi=300)

### 2024-02-14 figures/supporting-information/test_hybrid_descriptor_ratio/main.py

@@ -2,15 +2,16 @@
 # -*- coding: utf-8 -*-
 
 
-import yaml
 import os
 import sys
+
+import yaml
+
 sys.path.insert(0, "../../5-volcano-plot/src/lib")
 
 from dataLoader import dataLoader
 from scalingRelation import scalingRelation
 from src.plot_mixing_ratio import plot_mixing_ratio
-
 
 if __name__ == "__main__":
     # Load configs
@@ -25,7 +26,6 @@ if __name__ == "__main__":
     descriptor_x = cfg["reaction"]["descriptor_x"]
     descriptor_y = cfg["reaction"]["descriptor_y"]
 
-
     # Loading adsorption energy
     loader = dataLoader()
     loader.load_adsorption_energy(adsorption_energy_path, substrates, adsorbates)
@@ -35,13 +35,14 @@ if __name__ == "__main__":
     # Calculate adsorption energy linear scaling relations
     calculator = scalingRelation(
         adsorption_energy_dict=loader.adsorption_free_energy,
-        descriptors=(descriptor_x, descriptor_y), mixing_ratios="AUTO",
-        verbose=True, remove_ads_prefix=True)
-
+        descriptors=(descriptor_x, descriptor_y),
+        mixing_ratios="AUTO",
+        verbose=True,
+        remove_ads_prefix=True,
+    )
 
     # Get mixing ratio test results
     _mixing_ratio_results = calculator.mixing_ratio_results
-
 
     # Unpack mixing ratio test results to lists
     mixing_ratio_results = {ads: [] for ads in adsorbates}
@@ -50,11 +51,12 @@ if __name__ == "__main__":
         average = []
         for ads in adsorbates:
             if ads not in {descriptor_x, descriptor_y}:
-                mixing_ratio_results[ads].append(_mixing_ratio_results[ratio][ads].rvalue)
+                mixing_ratio_results[ads].append(
+                    _mixing_ratio_results[ratio][ads].rvalue
+                )
                 average.append(_mixing_ratio_results[ratio][ads].rvalue)
 
         average_result.append(sum(average) / len(average))
-
 
     # Plot mixing ratio test for each adsorbate
     for ads in adsorbates:

### 2024-02-14 figures/supporting-information/test_hybrid_descriptor_ratio/src/plot_mixing_ratio.py

@@ -30,7 +30,6 @@ def plot_mixing_ratio(x, y, savename):
 
     plt.xlim([0, 100])
 
-
     plt.tight_layout()
     plt.savefig(savename, dpi=300)
 

### 2024-02-16 cnn4dos/1-model-and-training/1-hyper-tune/check_metrics.py
global pre-commit fixes

@@ -1,12 +1,10 @@
 """Check metrics for an already finished Keras-tuner run."""
 
-
 import io
 import sys
 
 import keras_tuner
 from hp_model import hp_model
-
 
 # Main Loop
 if __name__ == "__main__":

### 2024-02-16 cnn4dos/1-model-and-training/1-hyper-tune/keras-tuner.py

@@ -1,6 +1,5 @@
 """Main runner of Keras-tuner."""
 
-
 import os
 
 import keras_tuner
@@ -16,7 +15,6 @@ import tensorflow as tf
 import yaml
 from hp_model import hp_model
 from lib.dataset import Dataset
-
 
 # Main Loop
 if __name__ == "__main__":

### 2024-02-16 cnn4dos/1-model-and-training/1-hyper-tune/lib/dataset.py

@@ -1,6 +1,5 @@
 """Load and manipulate eDOS dataset for CNN."""
 
-
 import os
 import warnings
 
@@ -95,7 +94,6 @@ class Dataset:
 
             for ads in adsorbates:
                 for state in states:
-
                     # Compile path
                     directory = os.path.join(path, sub, f"{ads}_{state}")
                     assert os.path.isdir(directory)
@@ -190,10 +188,8 @@ class Dataset:
 
         # Skip "none" mode
         if mode != "none":
-
             # Loop through dataset and perform scaling
             for key, arr in self.feature.items():
-
                 # Perform scaling for each channel
                 assert len(arr.shape) == 3  # expect (NEDOS, numOrbitals, numChannels)
                 scaled_arr = []

### 2024-02-16 cnn4dos/1-model-and-training/1-hyper-tune/lib/record_runtime_info.py

@@ -1,6 +1,5 @@
 """Utility script to recording system/Python env information."""
 
-
 import json
 import logging
 import platform

### 2024-02-16 cnn4dos/1-model-and-training/2-best-model/plot_cnn_model.py

@@ -1,6 +1,5 @@
 """Plot CNN model architecture."""
 
-
 import tensorflow as tf
 
 model_dir = "model"

### 2024-02-16 cnn4dos/4-shifting-experiments/src/shiftPlotter.py

@@ -1,6 +1,5 @@
 """Plot eDOS shifting experiments results as heatmap."""
 
-
 from pathlib import Path
 
 import matplotlib.pyplot as plt

### 2024-02-16 cnn4dos/5-volcano-plot/src/lib/scalingRelation.py

@@ -1,6 +1,5 @@
 """Calculate adsorption energy linear scaling relations."""
 
-
 import warnings
 
 import numpy as np

### 2024-02-16 cnn4dos/5-volcano-plot/src/lib/utils.py

@@ -1,6 +1,5 @@
 """Utility scripts for volcano plotter."""
 
-
 import pandas as pd
 
 

### 2024-02-16 cnn4dos/5-volcano-plot/src/lib/volcanoPlotter.py

@@ -1,6 +1,5 @@
 """Main plotter for volcano plot."""
 
-
 import math
 import warnings
 from typing import Tuple
@@ -9,8 +8,7 @@ import matplotlib as mpl
 import matplotlib.pyplot as plt
 import numpy as np
 from matplotlib import rcParams
-from matplotlib.colors import (BoundaryNorm, LinearSegmentedColormap,
-                               ListedColormap)
+from matplotlib.colors import LinearSegmentedColormap
 from matplotlib.lines import Line2D
 
 rcParams["font.family"] = "sans-serif"
@@ -397,10 +395,11 @@ class volcanoPlotter:
         free_energy_change_mesh = self.__generate_free_energy_change_mesh(reaction_name)
 
         # Generate limiting potential mesh
-        self.limiting_potential_mesh, _ = (
-            self.__generate_limiting_potential_and_RDS_mesh(
-                free_energy_change_mesh, reaction_name
-            )
+        (
+            self.limiting_potential_mesh,
+            _,
+        ) = self.__generate_limiting_potential_and_RDS_mesh(
+            free_energy_change_mesh, reaction_name
         )
 
         # Create plt object

### 2024-02-16 cnn4dos/shared_components/extract_single_atom_DOS.py

@@ -1,6 +1,5 @@
 """Extract pDOS from the numpy array of a selected atom."""
 
-
 spin = "up"
 working_dir = "."
 

### 2024-02-16 cnn4dos/shared_components/src/cnnPredictor.py

@@ -1,6 +1,5 @@
 """Infer with pre-trained CNN model."""
 
-
 from pathlib import Path
 
 import numpy as np
@@ -8,7 +7,6 @@ import tensorflow as tf
 
 
 class CNNPredictor:
-
     def __init__(self, model_path=None, loaded_model=None):
         """
         Initialize the CNNPredictor class.

### 2024-02-16 figures/supporting-information/plot_adsorption_energy_correlation/main.py

@@ -1,6 +1,5 @@
 """Plot adsorption energy correlation matrix."""
 
-
 import os
 
 import matplotlib.pyplot as plt
@@ -9,7 +8,6 @@ import seaborn as sns
 from src.create_heatmap import corrplot
 from src.format_mol_name import format_mol_name
 from src.generate_corr_matrix import generate_corr_matrix
-
 
 if __name__ == "__main__":
     # Generate correlation matrix

### 2024-02-16 figures/supporting-information/plot_adsorption_energy_correlation/src/format_mol_name.py

@@ -1,6 +1,5 @@
 """Format molecule names to allow subscripts."""
 
-
 import re
 
 

### 2024-02-16 figures/supporting-information/plot_d-band-centre_vs_Eads/plot_all.py

@@ -1,6 +1,5 @@
 """Plot d-band-center vs adsorption energy relationship for all adsorbates."""
 
-
 import os
 
 import yaml

### 2024-02-16 figures/supporting-information/plot_d-band-centre_vs_Eads/plot_each_ads.py

@@ -1,6 +1,5 @@
 """Plot d-band-center vs adsorption energy relationship for each adsorbate."""
 
-
 import os
 
 import yaml
@@ -8,7 +7,6 @@ from src.dBand import dBand
 from src.list_dos_files import list_dos_files
 from src.load_ads_energy import load_ads_energy
 from src.plot_scatter import plot_scatter
-
 
 if __name__ == "__main__":
     # Load configs

### 2024-02-16 figures/supporting-information/plot_descriptor_kendall_correlation/main.py

@@ -1,13 +1,11 @@
 """Plot descriptior Kendall correlation matrix."""
 
-
 import os
 from pathlib import Path
 
 import yaml
 from src.descriptors import Descriptors
 from src.plot_correlation import plot_correlation
-
 
 if __name__ == "__main__":
     # Load configs

### 2024-02-16 figures/supporting-information/plot_descriptor_kendall_correlation/src/heatmap_revised.py

@@ -1,6 +1,5 @@
 """Plot correlation coefficients as a heatmap matrix."""
 
-
 import matplotlib.pyplot as plt
 import numpy as np
 import pandas as pd
@@ -71,8 +70,9 @@ def heatmap(x, y, **kwargs):
     if "color_range" in kwargs:
         color_min, color_max = kwargs["color_range"]
     else:
-        color_min, color_max = min(color), max(
-            color
+        color_min, color_max = (
+            min(color),
+            max(color),
         )  # Range of values that will be mapped to the palette, i.e. min and max possible correlation
 
     if "size" in kwargs:
@@ -139,7 +139,7 @@ def heatmap(x, y, **kwargs):
         marker=marker,
         s=[value_to_size(v) for v in size],
         c=marker_color,
-        **kwargs_pass_on
+        **kwargs_pass_on,
     )
 
     ax.set_xticks([v for k, v in x_to_num.items()])

### 2024-02-16 figures/supporting-information/plot_descriptor_kendall_correlation/src/plot_correlation.py

@@ -1,6 +1,5 @@
 """Plot the correlation map."""
 
-
 import matplotlib.pyplot as plt
 import pandas as pd
 import seaborn as sns

### 2024-02-16 figures/supporting-information/plot_pairwise_descriptor_relations/main.py

@@ -1,13 +1,11 @@
 """Plot pairwise descriptor relations."""
 
-
 import os
 from pathlib import Path
 
 import yaml
 from src.descriptors import Descriptors
 from src.pairplot import PairPlot
-
 
 if __name__ == "__main__":
     # Load configs

### 2024-02-16 figures/supporting-information/plot_pairwise_descriptor_relations/src/descriptors.py

@@ -1,6 +1,5 @@
 """Load and preprocess descriptor data for plotting."""
 
-
 from pathlib import Path
 
 import pandas as pd

### 2024-02-16 paper/writing-version/supp_3_ml.tex
rename dir
use eDOS over DOS globally

--- 2024-01-18 paper/arxiv/supp_3_ml.tex
@@
 Here, ``numSamplings'' represents the number of data points sampled across the energy spectrum,
-``numOrbitals'' denotes the number of DOS orbitals,
+``numOrbitals'' denotes the number of eDOS orbitals,
 and ``numChannels'' indicates the number of atomic channels.
@@
   \small
-  \begin{tabularx}{\textwidth}{@{}lXX@{}}
+  \center
+  \begin{tabularx}{0.75\textwidth}{@{}lXX@{}}
     \toprule
@@
 
+  \begin{flushright}
+  \begin{minipage}{\textwidth}
     \footnotesize\textit{Note:} The same CNN model, trained on the
@@
       both original data and augment data, not a distinct model.
+  \end{minipage}
+  \end{flushright}
 \end{table}

### 2024-02-16 cnn4dos/1-model-and-training/1-hyper-tune/lib/dataset.py

@@ -9,10 +9,10 @@ from sklearn.preprocessing import normalize
 
 
 class Dataset:
-    """Dataset class for loading and manipulating DOS dataset for Deep Learning.
+    """Dataset class for loading and manipulating eDOS dataset for Deep Learning.
 
     Attributes:
-        feature (dict): DOS feature, key is "{substrate}{keysep}{adsorbate}{keysep}is/fs", value is DOS array
+        feature (dict): eDOS feature, key is "{substrate}{keysep}{adsorbate}{keysep}is/fs", value is eDOS array
         numFeature (int): total number of samples
         featureKeySep (str): separator used in dict keys
         substrates (list):
@@ -36,14 +36,14 @@ class Dataset:
         keysep=":",
         remove_ghost=False,
     ):
-        """Load DOS dataset feature from given list of dirs.
+        """Load eDOS dataset feature from given list of dirs.
 
         Args:
             path (Path): path to dataset dir
             substrates (list): list of substrates to load
             adsorbates (list): list of adsorbates to load
             centre_atoms (dict): centre atom index dict (index starts from 1)
-            filename (str): name of the DOS file under each dir
+            filename (str): name of the eDOS file under each dir
             keysep (str): separator for dir and project name in dataset dict
             states (tuple): list of states, "is" for initial state, "fs" for final state
             spin (str): load spin "up" or "down" DOS, or "both"
@@ -52,9 +52,9 @@ class Dataset:
             remove_ghost (bool): remove ghost state (first point of NEDOS)
 
         Notes:
-            1. DOS array in (NEDOS, orbital) shape
+            1. eDOS array in (NEDOS, orbital) shape
             2. feature dict key is "{substrate}{keysep}{adsorbate}{keysep}is/fs" (is for initial state, fs for final state)
-            3. Spin up DOS should be named "dos_up.npy", down "dos_down.npy"
+            3. Spin up eDOS should be named "dos_up.npy", down "dos_down.npy"
 
         """
         # Check args
@@ -86,7 +86,7 @@ class Dataset:
         self.substrates = substrates
         self.adsorbates = adsorbates
 
-        # Import DOS as numpy array
+        # Import eDOS as numpy array
         feature_data = {}
         for sub in substrates:
             # Get centre atom index from dict
@@ -245,10 +245,10 @@ class Dataset:
         self.label = labels
[…]

### 2024-02-16 cnn4dos/1-model-and-training/2-best-model/lib/dataset.py

@@ -1,4 +1,4 @@
-"""Dataset class for loading and manipulating DOS dataset for CNN."""
+"""Dataset class for loading and manipulating eDOS dataset for CNN."""
 
 
 import os
@@ -10,10 +10,10 @@ from sklearn.preprocessing import normalize
 
 
 class Dataset:
-    """Dataset class for loading and manipulating DOS dataset for Deep Learning.
+    """Dataset class for loading and manipulating eDOS dataset for Deep Learning.
 
     Attributes:
-        feature (dict): DOS feature, key is "{substrate}{keysep}{adsorbate}{keysep}is/fs", value is DOS array
+        feature (dict): eDOS feature, key is "{substrate}{keysep}{adsorbate}{keysep}is/fs", value is eDOS array
         numFeature (int): total number of samples
         featureKeySep (str): separator used in dict keys
         substrates (list):
@@ -37,14 +37,14 @@ class Dataset:
         keysep=":",
         remove_ghost=False,
     ) -> None:
-        """Load DOS dataset feature from given list of dirs.
+        """Load eDOS dataset feature from given list of dirs.
 
         Args:
             path (str): path to dataset dir
             substrates (list): list of substrates to load
             adsorbates (list): list of adsorbates to load
             centre_atoms (dict): centre atom index dict (index starts from 1)
-            filename (str): name of the DOS file under each dir
+            filename (str): name of the eDOS file under each dir
             keysep (str): separator for dir and project name in dataset dict
             states (tuple): list of states, "is" for initial state, "fs" for final state
             spin (str): load spin "up" or "down" DOS, or "both"
@@ -53,9 +53,9 @@ class Dataset:
             remove_ghost (bool): remove ghost state (first point of NEDOS)
 
         Notes:
-            1. DOS array in (NEDOS, orbital) shape
+            1. eDOS array in (NEDOS, orbital) shape
             2. feature dict key is "{substrate}{keysep}{adsorbate}{keysep}is/fs" (is for initial state, fs for final state)
-            3. Spin up DOS should be named "dos_up.npy", down "dos_down.npy"
+            3. Spin up eDOS should be named "dos_up.npy", down "dos_down.npy"
 
         """
         # Check args
@@ -87,7 +87,7 @@ class Dataset:
         self.substrates = substrates
         self.adsorbates = adsorbates
 
-        # Import DOS as numpy array
[…]

### 2024-02-16 cnn4dos/3-occlusion-experiments/main.py

@@ -33,7 +33,7 @@ def main():
         config["occlusion"]["max_adsorbate_channels"],
     )
 
-    # Step 2: Load original DOS in shape (numSamplings, numOrbitals, 1) and remove ghost state
+    # Step 2: Load original eDOS in shape (numSamplings, numOrbitals, 1) and remove ghost state
     unshifted_dos = data_loader.load_unshifted_dos(
         Path(os.getcwd()) / config["occlusion"]["dos_array_name"]
     )

### 2024-02-16 cnn4dos/3-occlusion-experiments/src/occlusionGenerator.py

@@ -24,7 +24,7 @@ class occlusionGenerator:
             dos_array (np.ndarray): The original Density of States (DOS) array.
             occlusion_width (int): The width of the occlusion window. Actual width is `occlusion_width * dos_calculation_resolution`.
             occlusion_step (int): The step size for moving the occlusion window. Actual step size is `occlusion_step * dos_calculation_resolution`.
-            dos_calculation_resolution (float): The resolution for DOS calculations.
+            dos_calculation_resolution (float): The resolution for eDOS calculations.
 
         Raises:
             ValueError: When input values are not as expected.
@@ -94,24 +94,24 @@ class occlusionGenerator:
         self, dos: np.ndarray, orbital_index: int, start_index: int, width: int
     ) -> np.ndarray:
         """
-        Occlude a region in a given DOS array along a specified orbital.
+        Occlude a region in a given eDOS array along a specified orbital.
 
         Args:
-            dos (np.ndarray): The original DOS array.
+            dos (np.ndarray): The original eDOS array.
             orbital_index (int): The index of the orbital to be occluded.
             start_index (int): The starting index for the occlusion.
             width (int): The width of the occlusion region.
 
         Returns:
-            np.ndarray: The occluded DOS array, maintaining the same shape as the original DOS array.
+            np.ndarray: The occluded eDOS array, maintaining the same shape as the original eDOS array.
         """
-        # Zero-padding the DOS array
+        # Zero-padding the eDOS array
         padded_dos = self._apply_padding(np.copy(dos), "pad")
 
-        # Occlude the DOS array
+        # Occlude the eDOS array
         padded_dos[start_index : start_index + width, orbital_index] = 0.0
 
-        # Crop the DOS array to its original shape
+        # Crop the eDOS array to its original shape
         cropped_occluded_dos = self._apply_padding(padded_dos, "crop")
 
         assert dos.shape == cropped_occluded_dos.shape
@@ -119,8 +119,8 @@ class occlusionGenerator:
 
     def generate_occlusion_arrays(self) -> np.ndarray:
         """
-        Generate a series of occlusion DOS arrays, where each array is created
-        by occluding a region in the original DOS array (not going across orbitals).
+        Generate a series of occlusion eDOS arrays, where each array is created
+        by occluding a region in the original eDOS array (not going across orbitals).
 
         Returns:
             np.ndarray: An array of shape (num_occlusions, numOrbitals), each

### 2024-02-16 cnn4dos/3-occlusion-experiments/src/occlusionPlotter.py

@@ -228,7 +228,7 @@ class OcclusionPlotter:
             plt.show()
 
     def plot_line(self, orbitals: list = ["s", "p", "d"], show: bool = False) -> None:
-        """Plot DOS line charts for specified orbitals.
+        """Plot eDOS line charts for specified orbitals.
 
         Args:
             orbitals (list): List of orbitals to plot. Default is ["s", "p", "d"].

### 2024-02-16 cnn4dos/4-shifting-experiments/main.py

@@ -48,7 +48,7 @@ def main():
         print(f"Processing folder {folder.name} ({i + 1} out of {len(folders)})...")
         dos_file_path = folder / config["shifting"]["dos_array_name"]
 
-        # a. Load DOS array with DOSProcessor
+        # a. Load eDOS array with DOSProcessor
         unshifted_dos = data_loader.load_unshifted_dos(dos_file_path)
         dos_processor = DOSProcessor(unshifted_dos)
         processed_dos = dos_processor.remove_ghost_state()
@@ -69,7 +69,7 @@ def main():
             prediction = cnn_predictor.predict(shifted_dos, adsorbate_dos)
             predictions.append(prediction)
 
-        # d. Feed the unshifted DOS array into the CNN model for a reference point
+        # d. Feed the unshifted eDOS array into the CNN model for a reference point
         ref_prediction = cnn_predictor.predict(processed_dos, adsorbate_dos)
 
         # Subtract ref_prediction from each prediction

### 2024-02-16 cnn4dos/4-shifting-experiments/src/shiftGenerator.py

@@ -23,11 +23,11 @@ class ShiftGenerator:
         Initialize the ShiftGenerator.
 
         Args:
-            dos_array (np.ndarray): The pre-processed DOS array of shape (numSamplings, numOrbitals, 1).
+            dos_array (np.ndarray): The pre-processed eDOS array of shape (numSamplings, numOrbitals, 1).
             shifting_range (list): A list containing the start and end of the shifting range.
             shifting_step (float): The step length for each shift.
             shifting_orbitals (list): A list containing the indices of the orbitals to be shifted.
-            dos_calculation_resolution (float): The energy resolution along the numSamplings axis of the DOS array.
+            dos_calculation_resolution (float): The energy resolution along the numSamplings axis of the eDOS array.
 
         Raises:
             ValueError: If the shape of dos_array is not as expected, or if shifting parameters are not valid.
@@ -90,10 +90,10 @@ class ShiftGenerator:
 
     def generate_shifted_arrays(self) -> List[np.ndarray]:
         """
-        Generate a series of shifted DOS arrays.
+        Generate a series of shifted eDOS arrays.
 
         Returns:
-            list: A list of shifted DOS arrays.
+            list: A list of shifted eDOS arrays.
         """
         start, end = self.shifting_range
         shift_values = np.arange(start, end + self.shift_step, self.shift_step)

### 2024-02-16 cnn4dos/shared_components/extract_dos_from_vasprunxml.py

@@ -33,7 +33,7 @@ def get_total_atom(poscarfile):
 
 
 def dos_extractor(folder, spin):
-    """Extractor DOS from vasprun.xml from given folder.
+    """Extractor eDOS from vasprun.xml from given folder.
 
     Args:
         folder (str): name of folder to work on.
@@ -78,7 +78,7 @@ def dos_extractor(folder, spin):
     # Decide if spin polarized from "ISPIN" tag
     ispin = read_ispin_from_vaspxml(dos_root)
 
-    # Begin to export DOS data from vasprun.xml
+    # Begin to export eDOS data from vasprun.xml
     if ispin == "1":
         return ValueError("None spin polarised analysis currently not supported!")
 
@@ -103,7 +103,7 @@ def dos_extractor(folder, spin):
                 [[float(j) for j in i.split()] for i in spin_down_dos]
             )
 
-            # Append DOS data to list
+            # Append eDOS data to list
             dos_up.append(spin_up_dos)
             dos_down.append(spin_down_dos)
 
@@ -111,7 +111,7 @@ def dos_extractor(folder, spin):
         dos_up = np.array(dos_up)
         dos_down = np.array(dos_down)
 
-    # Write DOS to numpy array
+    # Write eDOS to numpy array
     if ispin == "1":
         return ValueError(
             "None spin polarised analysis currently not supported!"
@@ -134,7 +134,7 @@ if __name__ == "__main__":
         # Get total number of atoms from POSCAR
         atom_num = get_total_atom(os.path.join(working_dir, "POSCAR"))
 
-        # Run DOS extractor
+        # Run eDOS extractor
         dos_extractor(working_dir, spin=spin)
 
     else:

### 2024-02-16 cnn4dos/shared_components/extract_single_atom_DOS.py

@@ -17,24 +17,24 @@ def extract_DOS(source_dir, atom_index, spin="up"):
 
     # Load spin up DOS
     if spin in {"up", "both"}:
-        # Load source DOS array
+        # Load source eDOS array
         source_arr = np.load(source_dir / "dos_up.npy")
 
-        # Extract selected atom DOS (spd only)
+        # Extract selected atom eDOS (spd only)
         target_arr = source_arr[atom_index - 1, :, 1:10]
 
-        # Write new DOS array
+        # Write new eDOS array
         np.save((source_dir / f"dos_up_{atom_index}.npy"), target_arr)
 
     # Load spin down DOS
     if spin in {"down", "both"}:
-        # Load source DOS array
+        # Load source eDOS array
         source_arr = np.load(source_dir / "dos_down.npy")
 
-        # Extract selected atom DOS (spd only)
+        # Extract selected atom eDOS (spd only)
         target_arr = source_arr[atom_index - 1, :, 1:10]
 
-        # Write new DOS array
+        # Write new eDOS array
         np.save((source_dir / f"dos_down_{atom_index}.npy"), target_arr)
 
 

### 2024-02-16 cnn4dos/shared_components/plot_dos.py

@@ -1,4 +1,4 @@
-"""Visualize extracted DOS array, expect shape (NEDOS, numOrbitals)."""
+"""Visualize extracted eDOS array, expect shape (NEDOS, numOrbitals)."""
 
 e_fermi = 0  # WARNING!
 
@@ -19,10 +19,10 @@ import numpy as np
 
 
 def plot_line(x_coords, arr, savedir):
-    """Plot DOS as lines.
+    """Plot eDOS as lines.
 
     Args:
-        arr (np.ndarray): DOS array to be plotted, expect shape in (NEDOS, orbital)
+        arr (np.ndarray): eDOS array to be plotted, expect shape in (NEDOS, orbital)
         savedir (str): directory where generated figure will be stored
 
     """
@@ -60,13 +60,13 @@ if __name__ == "__main__":
     assert isinstance(energy_step, int)
     assert isinstance(e_fermi, (int, float))
 
-    # Import DOS array
+    # Import eDOS array
     src_dos = np.load(os.path.join(working_dir, src_dos_name))
 
-    # Check DOS array
+    # Check eDOS array
     if src_dos.shape[1] > 9:
         print(
-            f"Caution! Expected DOS in shape (NEDOS, orbital), found shape ({src_dos.shape[0]}, {src_dos.shape[1]})"
+            f"Caution! Expected eDOS in shape (NEDOS, orbital), found shape ({src_dos.shape[0]}, {src_dos.shape[1]})"
         )
 
     # Generate x coordinates
@@ -74,5 +74,5 @@ if __name__ == "__main__":
     ## Subtract fermi level
     energy_array = energy_array - e_fermi
 
-    # Plot original DOS as line
+    # Plot original eDOS as line
     plot_line(energy_array, src_dos, savedir=working_dir)

### 2024-02-16 cnn4dos/shared_components/src/cnnPredictor.py

@@ -39,11 +39,11 @@ class CNNPredictor:
         self, dos_array: np.ndarray, adsorbate_dos_array: np.ndarray
     ) -> np.ndarray:
         """
-        Make predictions based on the DOS and adsorbate DOS arrays.
+        Make predictions based on the eDOS and adsorbate eDOS arrays.
 
         Args:
-            dos_array (np.ndarray): The processed DOS array of shape (numSamplings, numOrbitals, 1).
-            adsorbate_dos_array (np.ndarray): The processed adsorbate DOS array of shape (numSamplings, numOrbitals, max_adsorbate_channels).
+            dos_array (np.ndarray): The processed eDOS array of shape (numSamplings, numOrbitals, 1).
+            adsorbate_dos_array (np.ndarray): The processed adsorbate eDOS array of shape (numSamplings, numOrbitals, max_adsorbate_channels).
 
         Returns:
             np.ndarray: The prediction array.
@@ -54,14 +54,14 @@ class CNNPredictor:
 
         # Check shapes
         if dos_array.shape[-1] != 1:
-            raise ValueError("The last dimension (numChannels) of DOS array must be 1.")
+            raise ValueError("The last dimension (numChannels) of eDOS array must be 1.")
 
         if dos_array.shape[:-1] != adsorbate_dos_array.shape[:-1]:
             raise ValueError(
                 "The shapes of dos_array and adsorbate_dos_array must match in the first two dimensions."
             )
 
-        # Append adsorbate DOS array to DOS array along the numChannels axis
+        # Append adsorbate eDOS array to eDOS array along the numChannels axis
         combined_array = np.concatenate([dos_array, adsorbate_dos_array], axis=-1)
 
         # Make predictions with CNN model

### 2024-02-16 cnn4dos/shared_components/src/dataLoader.py

@@ -37,21 +37,21 @@ class DataLoader:
         self, filepath: str, max_adsorbate_channels: int
     ) -> np.ndarray:
         """
-        Load and preprocess the adsorbate DOS array.
+        Load and preprocess the adsorbate eDOS array.
 
         Args:
             filepath (str): The path to the .npy file.
             max_adsorbate_channels (int): Maximum number of channels for adsorbate_DOS.
 
         Returns:
-            np.ndarray: The preprocessed adsorbate DOS array of shape (numSamplings, numOrbitals, max_adsorbate_channels).
+            np.ndarray: The preprocessed adsorbate eDOS array of shape (numSamplings, numOrbitals, max_adsorbate_channels).
 
         Raises:
             FileNotFoundError: If the specified file does not exist.
             ValueError: If numOrbitals is not in {1, 4, 9, 16} or numChannels exceeds max_adsorbate_channels.
 
         Note:
-            The original shape of the adsorbate DOS array in the file should be (numChannels, numSamplings, numOrbitals).
+            The original shape of the adsorbate eDOS array in the file should be (numChannels, numSamplings, numOrbitals).
         """
         filepath = Path(filepath)
         if not filepath.exists():
@@ -84,20 +84,20 @@ class DataLoader:
 
     def load_unshifted_dos(self, filepath: str) -> np.ndarray:
         """
-        Load the unshifted DOS array.
+        Load the unshifted eDOS array.
 
         Args:
-            filepath (str): The path to the .npy file containing the unshifted DOS array.
+            filepath (str): The path to the .npy file containing the unshifted eDOS array.
 
         Returns:
-            np.ndarray: The preprocessed DOS array of shape (numSamplings, numOrbitals, numChannels=1).
+            np.ndarray: The preprocessed eDOS array of shape (numSamplings, numOrbitals, numChannels=1).
 
         Raises:
             FileNotFoundError: If the specified file does not exist.
             ValueError: If numOrbitals is not in {1, 4, 9, 16}.
 
         Note:
-            The original shape of the DOS array in the file should be (numSamplings, numOrbitals).
+            The original shape of the eDOS array in the file should be (numSamplings, numOrbitals).
         """
         filepath = Path(filepath)
         if not filepath.exists():

### 2024-02-16 cnn4dos/shared_components/src/dosProcessor.py

@@ -8,23 +8,23 @@ import numpy as np
 class DOSProcessor:
     def __init__(self, dos_array: np.ndarray):
         """
-        Initialize the DOSProcessor with a pre-loaded DOS array.
+        Initialize the DOSProcessor with a pre-loaded eDOS array.
 
         Args:
-            dos_array (np.ndarray): A pre-loaded DOS array with shape (numSamplings, numOrbitals, 1).
+            dos_array (np.ndarray): A pre-loaded eDOS array with shape (numSamplings, numOrbitals, 1).
 
         Raises:
-            TypeError: If the given DOS array is not a numpy array.
-            ValueError: If the shape of the given DOS array is not as expected, or if numSamplings <= 500, or if numOrbitals not in {1, 4, 9, 16}.
+            TypeError: If the given eDOS array is not a numpy array.
+            ValueError: If the shape of the given eDOS array is not as expected, or if numSamplings <= 500, or if numOrbitals not in {1, 4, 9, 16}.
         """
         if not isinstance(dos_array, np.ndarray):
-            raise TypeError("The given DOS array must be a numpy array.")
+            raise TypeError("The given eDOS array must be a numpy array.")
 
         numSamplings, numOrbitals, _ = dos_array.shape
 
         if numSamplings <= 500:
             warnings.warn(
-                "The number of samplings is not greater than 500, please double-check if DOS is in correct shape."
+                "The number of samplings is not greater than 500, please double-check if eDOS is in correct shape."
             )
 
         if numOrbitals not in {1, 4, 9, 16}:
@@ -40,7 +40,7 @@ class DOSProcessor:
             remove_ghost (bool, optional): If True, sets the first values (index 0) along the numOrbitals axis to 0.0.
 
         Returns:
-            np.ndarray: DOS array with ghost states removed, if specified. Shape remains (numSamplings, numOrbitals, 1).
+            np.ndarray: eDOS array with ghost states removed, if specified. Shape remains (numSamplings, numOrbitals, 1).
         """
         if remove_ghost:
             self.dos_array[0, :] = 0.0

### 2024-02-16 figures/supporting-information/plot_d-band-centre_vs_Eads/plot_all.py

@@ -24,7 +24,7 @@ if __name__ == "__main__":
 
     energy_range = cfg["calculation"]["energy_range"]
 
-    # Work on all DOS files
+    # Work on all eDOS files
     d_band_centres = []
     adsorption_energies = []
     labels = []

### 2024-02-16 figures/supporting-information/plot_d-band-centre_vs_Eads/plot_each_ads.py

@@ -25,7 +25,7 @@ if __name__ == "__main__":
     energy_range = cfg["calculation"]["energy_range"]
 
     for ads in adsorbates:
-        # Work on all DOS files
+        # Work on all eDOS files
         d_band_centres = []
         adsorption_energies = []
         labels = []

### 2024-02-16 figures/supporting-information/plot_d-band-centre_vs_Eads/src/dBand.py

@@ -25,7 +25,7 @@ class dBand:
         assert isinstance(energy_range, (list, tuple)) and len(energy_range) == 2
         self.energy_range = energy_range
 
-        # Load DOS from file
+        # Load eDOS from file
         self.__load_dos(dosFile, fileType)
 
         self.nedos = self.dos_array.shape[0]
@@ -69,7 +69,7 @@ class dBand:
             return "NA"  # metals without d electrons
 
     def __calculate_band_centre(self, single_dos_orbital, energy_array):
-        """Calculate band centre of a single DOS orbital.
+        """Calculate band centre of a single eDOS orbital.
 
         Args:
             single_dos_orbital (np.ndarray): merged five orbitals of d-band
@@ -85,7 +85,7 @@ class dBand:
             "Legacy d-band centre calculation method is deprecated. Please use moment-based method."
         )
 
-        # Check DOS shape
+        # Check eDOS shape
         assert single_dos_orbital.ndim == 1
 
         # Calculate band centre
@@ -102,17 +102,17 @@ class dBand:
         return numerator / denominator
 
     def __load_dos(self, dosFile, fileType):
-        """Load DOS file to numpy array, expecting DOS in shape (NEDOS, numOrbitals).
+        """Load eDOS file to numpy array, expecting eDOS in shape (NEDOS, numOrbitals).
 
         Args:
-            dosFile (str): path to DOS file
-            fileType (str): DOS file type
+            dosFile (str): path to eDOS file
+            fileType (str): eDOS file type
 
         Attrib:
-            dos_array (np.ndarray): DOS array in shape (NEDOS, numOrbitals)
+            dos_array (np.ndarray): eDOS array in shape (NEDOS, numOrbitals)
 
         """
-        # Load DOS file
+        # Load eDOS file
         if fileType == "numpy":
             dos_array = np.load(dosFile)
 
@@ -120,29 +120,29 @@ class dBand:
             # Covert to numpy array (if fileType isn't numpy array)
             pass
 
-        # Check DOS array shape
+        # Check eDOS array shape
         numOrbitals = dos_array.shape[1]
         if numOrbitals not in {1, 4, 9, 16}:
             raise ValueError(
-                f'Illegal number of DOS orbitals "{numOrbitals}" found! Expecting DOS in shape (NEDOS, numOrbitals).'
[…]

### 2024-02-16 figures/supporting-information/plot_d-band-centre_vs_Eads/src/load_ads_energy.py

@@ -6,10 +6,10 @@ import pandas as pd
 
 
 def load_ads_energy(dosFile, ads_energy_dir):
-    """Load adsorption energy from DOS file name.
+    """Load adsorption energy from eDOS file name.
 
     Args:
-        dosFile (str): DOS file name
+        dosFile (str): eDOS file name
         ads_energy_dir (str): adsorption energy directory
 
     Returns:
@@ -20,7 +20,7 @@ def load_ads_energy(dosFile, ads_energy_dir):
     assert os.path.exists(dosFile)
     assert os.path.isdir(ads_energy_dir)
 
-    # Unpack DOS file name
+    # Unpack eDOS file name
     substrate = dosFile.split(os.sep)[-4]
     adsorbate = dosFile.split(os.sep)[-3].split("_")[0]
     state = dosFile.split(os.sep)[-3].split("_")[-1]

### 2024-03-20 paper/arxiv-submission/main.tex
try to fix "Bibliography not compatible with author-year citations"
fix bibtex
separate content from build details
fix si title page
remove appendix section
global ruff mypy format fix
migrate to windows subsystem for linux
switch to pdf for figures

@@
 % Main
-\documentclass[a4paper, 12pt, titlepage]{article}
-
-\usepackage{amsmath}
-\usepackage{array}
-\usepackage{bookmark}
-\usepackage{booktabs}
-\usepackage{caption}
-\usepackage{cleveref}
-\usepackage{datetime2}
-\usepackage{enumitem}
-\usepackage{geometry}
-\usepackage{graphicx}
-\usepackage{hyperref}
-\usepackage{multirow}
-\usepackage{natbib}
-\usepackage{nicematrix}
-\usepackage{tablefootnote}
-\usepackage{textcomp}
-\usepackage{siunitx}
-\usepackage{xr}
-\usepackage[affil-it]{authblk}
-\usepackage[english]{babel}
-\usepackage[version=4]{mhchem}
-
-\DeclareSIUnit\angstrom{\text {Å}}
-
-\crefname{figure}{Figure}{Figures}
-\crefname{table}{Table}{Tables}
-\crefname{equation}{Equation}{Equations}
-\captionsetup{labelfont=bf}
-
-\externaldocument{supplement}
-
-\begin{document}
-\pdfoutput=1
 
@@
 
-    \date{January 27, 2024}
+\date{}
 \maketitle
@@
     consequently, catalytic activities while varying supported single atoms.
-    This work offers a tangible framework to inform both theoretical screening and experimental synthesis,
+    This work offers a tangible framework to guide both theoretical screening and experimental synthesis,
     thereby paving the way for systematically designing efficient SACs.
@@
     which autonomously derive a hierarchical representation directly from the eDOS
-    \cite{tran2015learning, socher2012convolutional, krizhevsky2012imagenet}.
+    \cite{tran2015learning, socher2012convolutional, NIPS2012_c399862d}.
     This approach accurately maps to the activity space, negating the need for manual crafting of descriptors
@@
 % Code/Data Availability, Acknowledgements, Author Contributions and Competing Interests
-\appendix
+\setcounter{section}{0}
+\renewcommand{\thesection}{\Alph{section}}
+
 \newpage
@@
 
-\newpage
-\bibliographystyle{plain}
-\bibliography{references}
-
-\end{document}
+% End of Main

### 2024-03-20 paper/journal-submission/main.tex
switch to pdf for figures

--- 2024-03-20 paper/arxiv-submission/main.tex
@@
         \centering
-        \includegraphics[width=\textwidth]{main_fig1_pipeline.png}
+        \includegraphics[width=\textwidth]{main_fig1_pipeline.pdf}
         \caption{\textbf{Catalyst performance analysis pipeline integrating volcano plots and CNN.}
@@
         \centering
-        \includegraphics[width=\textwidth]{main_fig2_cnn.png}
+        \includegraphics[width=\textwidth]{main_fig2_cnn.pdf}
         \caption{\textbf{CNN for electronic density of states.}
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{main_fig3_volcano.png}
+        \includegraphics[width=0.9\textwidth]{main_fig3_volcano.pdf}
         \caption{\textbf{Limiting potential volcano plot and periodic table.}
@@
         \centering
-        \includegraphics[width=\textwidth]{main_fig4_validation.png}
+        \includegraphics[width=\textwidth]{main_fig4_validation.pdf}
         \caption{\textbf{Validation of CNN predictions.}
@@
         \centering
-        \includegraphics[width=\textwidth]{main_fig5_shifting.png}
+        \includegraphics[width=\textwidth]{main_fig5_shifting.pdf}
         \caption{\textbf{eDOS shifting experiments.}
@@
     \section{Acknowledgements}
+    We acknowledge funding support from the Australian Research Council
+    (FT160100281, FT180100387, DP200103568, DP230101625).
     The QUT eResearch Office provided computational resources and services used in this work.

### 2024-03-20 paper/journal-submission/supplement.tex
switch to pdf for figures

% Supplementary Information

% Title
\begin{center}
  \Large{Supporting Information for:  \\
  Convolutional Neural Networks and Volcano Plots:
  Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions}
\end{center}

% SI Section One: Additional details on DFT calculations
\newpage
\section{Additional details on DFT calculations}

\subsection{Catalyst models}
\label{supp_sec2.1_catalysts}

Representative structures for each substrate are depicted in \cref{supp_fig2:Ge_g-C3N4} through \cref{supp_fig7:Al-C2N}. For the adsorption process, the initial state is defined by positioning the optimized adsorbates at a distance of 6.5 \text{\AA} from the single-metal atoms supported on the substrate, oriented along the z-axis.

% SI Figure 1: Periodic table of investigated metals
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig1_ptable.pdf}
  \caption{\textbf{Periodic table of investigated metals.}
  Periodic table highlighting investigated elements: transition metals in blue, metalloids in purple, and other metals in orange.}
  \label{supp_fig1:ptable}
\end{figure}

% SI Figure 2: Structure of Ge atom supported on g-C3N4
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig2_Ge_g-C3N4.pdf}
  \caption{\textbf{Structure of single germanium atom supported on graphitic nitride.}
  (\textbf{a}) View along the z-axis and (\textbf{b}) view along the x-axis
  of the Ge@g-C\textsubscript{3}N\textsubscript{4} structure.
  In the illustrations, silver spheres represent N atoms, brown spheres
  signify C atoms, and purple sphere indicates Ge atom.}
  \label{supp_fig2:Ge_g-C3N4}
\end{figure}

% SI Figure 3: Structure of Cr atom supported on nitrogen-doped graphene
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig3_Cr-n-gra.pdf}
  \caption{\textbf{Structure of single chromium atom supported on nitrogen-doped graphene.}
  (\textbf{a}) View along the z-axis and (\textbf{b}) view along the x-axis
  of the Cr@nitrogen-doped-graphene structure.
  In the illustrations, silver spheres represent N atoms, brown spheres
  signify C atoms, and indigo sphere indicates Cr atom.}
  \label{supp_fig3:Cr-n-gra}
\end{figure}

% SI Figure 4: Structure of Os atom supported on graphene with dual-vacancy
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig4_Os-gra-vac.pdf}
  \caption{\textbf{Structure of single osmium atom supported on graphene with dual-vacancy.}
  (\textbf{a}) View along the z-axis and (\textbf{b}) view along the x-axis
  of the Os@graphene-with-dual-vacancy structure.
  In the illustrations, brown spheres signify C atoms, and light yellow sphere
  indicates Os atom.}
  \label{supp_fig4:Os-gra-vac}
\end{figure}

% SI Figure 5: Structure of Cr atom supported on black phosphorous
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig5_Cr-BP.pdf}
  \caption{\textbf{Structure of single chromium atom supported on black phosphorous.}
  (\textbf{a}) View along the z-axis and (\textbf{b}) view along the x-axis
  of the Cr@black phosphorous structure.
  In the illustrations, light purple spheres represent P atoms, and indigo sphere
  indicates Cr atom.}
  \label{supp_fig5:Cr-BP}
\end{figure}

% SI Figure 6: Structure of Y atom supported on boron nitride
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig6_Y-BN.pdf}
  \caption{\textbf{Structure of single yttrium atom supported on boron nitride.}
  (\textbf{a}) View along the z-axis and (\textbf{b}) view along the x-axis
  of the Y@boron-nitride structure.
  In the illustrations, silver spheres represent N atoms, green spheres
  signify B atoms, and light green sphere indicates Y atom.}
  \label{supp_fig6:Y-BN}
\end{figure}

% SI Figure 7: Structure of Al atom supported on C2N
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig7_Al-C2N.pdf}
  \caption{\textbf{Structure of single aluminum atom supported on C\textsubscript{2}N.}
  (\textbf{a}) View along the z-axis and (\textbf{b}) view along the x-axis
  of the Al@C\textsubscript{2}N structure.
  In the illustrations, silver spheres represent N atoms, brown spheres
  signify C atoms, and blue sphere indicates Al atom.}
  \label{supp_fig7:Al-C2N}
\end{figure}

\subsection[CO2RR pathways]{CO\textsubscript{2}RR pathways}
\label{supp_sec2.2_co2rr_paths}

In this study, we explored three reaction pathways that have been previously documented in the literature \cite{durand2011structure, nie2014reaction, peterson2010copper}, as depicted in \cref{supp_fig8:co2rr_paths}.
The adsorption configuration of the *CHO intermediate is pivotal in each of these pathways for determining the reaction mechanism in the CO\textsubscript{2}RR process.
We calculated the energies associated with the *CHO intermediate for catalysts
supported on g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene, and dual-vacancy graphene-under each mechanism.
These calculations are summarized in \cref{supp_table1:e_3_co2rr_paths}.
Our results indicate that Pathway 1 is the most energetically favorable for most catalysts we investigated.
Therefore, to streamline our analysis, we focused exclusively on Mechanism 1 across all catalysts examined.

% SI Figure 8: Three investigated CO2RR pathways
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\textwidth]{supp_fig8_co2rr_paths.pdf}
  \caption{\textbf{Three investigated CO\textsubscript{2}RR pathways \cite{durand2011structure, nie2014reaction, peterson2010copper} investigated in this work.}}
  \label{supp_fig8:co2rr_paths}
\end{figure}

% Supplementary Table 1: DFT-calculated energies for protonated *CO intermediate for 3 pathways
\begin{table}[htbp]
\label{supp_table1:e_3_co2rr_paths}
  \caption{DFT-calculated energies in eV for protonated *CO intermediate
    for three investigated CO\textsubscript{2}RR pathways.}
  \resizebox{\textwidth}{!}{%
    \begin{tabular}{l *{9}{l}}
      \toprule
      \multirow{2}{*}{Metal}
      & \multicolumn{3}{c}{g-C\textsubscript{3}N\textsubscript{4}}
      & \multicolumn{3}{c}{nitrogen-doped graphene}
      & \multicolumn{3}{c}{graphene with dual-vacancy}  \\ \cline{2-10}
      & Pathway-1 & Pathway-2 & Pathway-3
      & Pathway-1 & Pathway-2 & Pathway-3
      & Pathway-1 & Pathway-2 & Pathway-3  \\
      \midrule
      Al & \textbf{-499.3494} & -497.8343 & -499.3005 & \textbf{-670.3489} & -668.5142 & -670.3093 & -667.2538 & -666.6725 & \textbf{-667.2665} \\
      Co & -502.5946 & -501.1257 & \textbf{-502.6139} & -672.8847 & -670.8013 & \textbf{-672.9020} & \textbf{-671.6284} & -670.4388 & -671.3827 \\
      Cr & -505.6012 & -504.2022 & \textbf{-505.6029} & -675.3126 & -674.1640 & \textbf{-675.3480} & \textbf{-673.4283} & -672.1919 & -673.3818 \\
      Cu & \textbf{-495.8913} & -493.6853 & -495.8820 & \textbf{-666.9894} & -664.9810 & -666.9705 & -666.9876 & -664.7684 & \textbf{-667.1395} \\
      Fe & \textbf{-501.3325} & -499.3969 & -501.3221 & -673.8242 & -672.0887 & \textbf{-673.8478} & \textbf{-672.7810} & -671.5694 & -672.4960 \\
      Ga & -498.2365 & -496.3967 & \textbf{-498.2912} & \textbf{-667.3963} & -665.4677 & -667.3482 & -665.7780 & -664.8573 & \textbf{-665.8030} \\
      Ge & -500.2052 & -497.9780 & \textbf{-500.2156} & \textbf{-668.1785} & -666.3484 & -668.1463 & \textbf{-667.7387} & -665.7394 & -667.7324 \\
      Mn & \textbf{-502.6355} & -500.8006 & -502.6294 & -674.6848 & -672.9574 & \textbf{-674.7030} & -673.2243 & -672.6495 & \textbf{-673.2361} \\
      Ni & \textbf{-500.4085} & -498.5165 & -500.3985 & \textbf{-670.0979} & -667.9544 & -670.0832 & -670.1619 & -668.3684 & \textbf{-670.1756} \\
      Sc & -503.4428 & -501.6129 & \textbf{-503.4437} & \textbf{-673.9590} & -671.7624 & -673.3818 & \textbf{-670.0841} & -668.1044 & -669.6050 \\
      Ti & -503.7848 & -502.6148 & \textbf{-503.8033} & \textbf{-675.1006} & -673.2417 & -674.6257 & \textbf{-672.7127} & -670.6787 & -672.2491 \\
      V  & \textbf{-503.6115} & -502.6188 & -503.5956 & \textbf{-675.0533} & -674.0394 & -675.0136 & \textbf{-673.1855} & -671.5382 & -673.1583 \\
      Zn & \textbf{-493.9854} & -491.5010 & -493.9743 & \textbf{-664.9935} & -663.0932 & -664.9758 & -663.7735 & -661.8097 & \textbf{-663.7959} \\
      Ag & \textbf{-494.4055} & -492.4511 & -494.3905 & -664.6322 & -662.9060 & \textbf{-664.6353} & -664.3972 & -662.3588 & \textbf{-665.0570} \\
      Cd & \textbf{-493.3084} & -491.1781 & -493.2951 & \textbf{-663.8832} & -661.6272 & -663.8653 & -661.8518 & -659.9601 & \textbf{-661.8631} \\
      In & -498.5272 & -496.6593 & \textbf{-498.5908} & \textbf{-666.3968} & -663.7707 & -666.3845 & -663.6532 & -661.5581 & \textbf{-663.6913} \\
      Mo & \textbf{-504.5248} & -503.3763 & -504.5148 & -675.3472 & -674.7118 & \textbf{-675.4389} & -674.7186 & -672.9335 & \textbf{-674.7397} \\
      Nb & -505.3967 & -504.7113 & \textbf{-505.3982} & \textbf{-676.0492} & -674.1997 & -675.4107 & \textbf{-674.6606} & -672.8268 & -674.5488 \\
      Pd & -500.0370 & -498.3310 & \textbf{-500.0455} & \textbf{-669.0243} & -667.0759 & -669.0205 & \textbf{-669.1169} & -667.3223 & -669.1119 \\
      Rh & \textbf{-499.2225} & -497.3162 & -499.2170 & -672.7920 & -670.7853 & \textbf{-672.8099} & \textbf{-671.4286} & -670.3036 & -671.4181 \\
      Ru & \textbf{-503.9986} & -502.1908 & -503.9640 & -674.0273 & -672.4060 & \textbf{-674.0339} & \textbf{-672.9956} & -672.1332 & -672.9909 \\
      Sb & \textbf{-497.3836} & -495.1348 & -497.3442 & \textbf{-666.7198} & -664.9611 & -666.7190 & -666.8632 & -664.8131 & \textbf{-666.8670} \\
      Sn & \textbf{-499.4952} & -497.2007 & -499.1116 & \textbf{-667.1459} & -665.3835 & -667.0999 & \textbf{-665.9821} & -663.8277 & -665.9755 \\
      Tc & \textbf{-503.0602} & -501.1754 & -503.0532 & -674.4342 & -673.8164 & \textbf{-674.4559} & -674.0615 & -672.9747 & \textbf{-674.0738} \\
      Y  & \textbf{-503.9232} & -502.0670 & -503.8988 & \textbf{-673.7620} & -671.6132 & -673.2241 & -669.4633 & -668.0403 & \textbf{-669.5030} \\
      Zr & \textbf{-505.2907} & -503.9148 & -505.1817 & \textbf{-675.6874} & -673.5456 & -675.0519 & \textbf{-673.1694} & -671.1993 & -672.8072 \\
      Au & \textbf{-497.0784} & -495.1720 & -497.0175 & \textbf{-665.1479} & -663.3239 & -665.1370 & -666.4185 & -664.2892 & \textbf{-666.5182} \\
      Bi & \textbf{-496.9946} & -494.7679 & -496.9934 & -665.9563 & -664.2409 & \textbf{-666.0512} & \textbf{-665.0896} & -663.2974 & -665.0887 \\
      Hf & \textbf{-506.4837} & -504.9734 & -506.4777 & \textbf{-677.3077} & -675.1797 & -676.6502 & \textbf{-674.7209} & -672.6650 & -674.2149 \\
      Hg & \textbf{-491.0035} & -488.7951 & -490.9728 & \textbf{-661.2458} & -659.2406 & -661.2398 & -661.7192 & -659.8398 & \textbf{-661.7300} \\
      Ir & \textbf{-503.0227} & -501.1368 & -503.0217 & -673.9926 & -672.0068 & \textbf{-674.0087} & \textbf{-673.5129} & -672.6725 & -673.4975 \\
      Os & -504.7648 & -502.9878 & \textbf{-504.8105} & -675.2098 & -673.6653 & \textbf{-675.2235} & \textbf{-674.9483} & -674.1970 & -674.9223 \\
      Pb & \textbf{-499.1183} & -497.1173 & -499.0544 & -666.4446 & -664.6897 & \textbf{-666.4625} & \textbf{-664.0200} & -662.2222 & -664.0123 \\
      Pt & \textbf{-499.3356} & -497.5110 & -499.3215 & -670.3996 & -668.2412 & \textbf{-670.4147} & \textbf{-671.1408} & -669.2725 & -671.1370 \\
      Re & \textbf{-504.1830} & -502.4735 & -504.1746 & \textbf{-675.7670} & -675.0715 & -675.7486 & \textbf{-675.8701} & -674.9245 & -675.8233 \\
      Ta & -506.6180 & -505.7793 & \textbf{-506.6241} & \textbf{-677.7222} & -675.9907 & -677.0911 & \textbf{-676.4371} & -674.5434 & -676.4262 \\
      Tl & \textbf{-497.9559} & -496.1578 & -497.9382 & -664.5047 & -662.7051 & \textbf{-664.5051} & -662.6279 & -660.6086 & \textbf{-662.6317}\\
      W  & \textbf{-505.8134} & -504.9085 & -505.8030 & -676.5304 & -676.1384 & \textbf{-676.9965} & \textbf{-676.7669} & -675.4895 & -676.7356 \\
      \bottomrule
    \end{tabular}
  }

  \smallskip

  \footnotesize\textit{Note:} Energies of the most stable configurations are highlighted in bold.
\end{table}

\subsection{DFT energies and energy corrections}
\label{supp_sec2.3_energies}

% Supplementary Table 2: Free energies for isolated species.
\begin{table}[htbp]
\label{supp_table2:species_free_energies}
  \caption{Free energies at 298.15 K for isolated species.}
  \center
  \small
  \begin{tabularx}{0.5\textwidth}{@{}lXr@{}}
    \toprule
    Species               & Free Energy (eV)  \\
    \midrule
    CO\textsubscript{2}   & -23.3140          \\
    CO                    & -15.3336          \\
    CH\textsubscript{4}   & -23.4639          \\
    H\textsubscript{2}    & -6.9315           \\
    H\textsubscript{2}O   & -14.3239          \\
    COOH                  & -24.3963          \\
    CHO                   & -17.0983          \\
    CH\textsubscript{2}O  & -22.1607          \\
    OCH\textsubscript{3}  & -24.5075          \\
    O                     & -1.9007           \\
    OH                    & -7.7303           \\
    \bottomrule
  \end{tabularx}

  \smallskip

  \begin{flushright}
  \begin{minipage}{\textwidth}
    \footnotesize\textit{Note:} VASPKIT \cite{wang2021vaspkit} was employed to calculate free energies.
  \end{minipage}
  \end{flushright}
\end{table}

% Supplementary Table 3: Free energy corrections for adsorbed intermediates
\begin{table}[htbp]
\label{supp_table3:ads_e_correction}
  \caption{Free energy corrections at 298.15 K for adsorbed intermediates.}
  \centering
  \small
  \begin{tabularx}{0.5\textwidth}{@{}lXr@{}}
    \toprule
    Species                & Free energy correction (eV)  \\
    \midrule
    *CO\textsubscript{2}   &  0.0864                      \\
    *COOH                  &  0.3693                      \\
    *CO                    &  0.0111                      \\
    *CHO                   &  0.2716                      \\
    *CH\textsubscript{2}O  &  0.5595                      \\
    *OCH\textsubscript{3}  &  0.8738                      \\
    *O                     & -0.0193                      \\
    *OH                    &  0.1993                      \\
    *H                     &  0.1533                      \\
    \bottomrule
  \end{tabularx}

  \smallskip

  \begin{flushright}  % justify footnote
  \begin{minipage}{\textwidth}
    \footnotesize\textit{Note:} {Free energy corrections were obtained by averaging the
      DFT-computed corrections, which include zero-point energy and entropy, across three substrates:
      g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene, and dual-vacancy graphene.}
  \end{minipage}
  \end{flushright}
\end{table}

% Supplementary Table 4: DFT calculated final state energies for adsorbates supported on g-c3n4
\begin{table}[htbp]
\label{supp_table4:e_g-c3n4}
  \caption{DFT calculated final state energies in eV for adsorbates
    supported on g-C\textsubscript{3}N\textsubscript{4}.}
  \resizebox{\textwidth}{!}{%
    \begin{tabular}{l *{9}{l}}
      \toprule
      Metal & *CO\textsubscript{2} & *COOH    & *CO       & *CHO
      & *CH\textsubscript{2}O  & *OCH\textsubscript{3}  & *O        & *OH       & *H        \\
      \midrule
      Al & -481.2292 & -504.7972 & -508.6897 & -496.4490 & -500.7640 & -503.7935 & -509.9998 & -488.6623 & -485.4855 \\
      Co & -483.2039 & -507.0765 & -510.0453 & -500.1329 & -503.9316 & -507.0552 & -510.9052 & -489.9487 & -486.6194 \\
      Cr & -486.7813 & -509.9599 & -513.3962 & -502.1493 & -505.7125 & -509.8851 & -514.1702 & -493.7457 & -489.9202 \\
      Cu & -477.5955 & -502.5914 & -505.9613 & -495.6511 & -498.0502 & -502.4590 & -506.2829 & -484.3166 & -481.9683 \\
      Fe & -482.0576 & -507.1508 & -510.2918 & -500.1101 & -502.1626 & -506.0115 & -511.2543 & -490.0116 & -486.4067 \\
      Ga & -480.8854 & -503.9317 & -506.4938 & -495.7379 & -498.7813 & -503.1345 & -507.5029 & -486.1702 & -483.4575 \\
      Ge & -481.5807 & -504.6467 & -508.4204 & -496.4421 & -500.5712 & -504.0218 & -509.4116 & -488.4168 & -485.2680 \\
      Mn & -483.7690 & -508.5410 & -511.6514 & -500.6279 & -502.6739 & -508.6433 & -512.8569 & -491.2239 & -488.1082 \\
      Ni & -482.0061 & -505.1988 & -508.4173 & -498.5054 & -501.0040 & -504.8945 & -508.6266 & -487.3684 & -484.8272 \\
      Sc & -483.9963 & -509.3147 & -512.9882 & -501.4505 & -505.2024 & -509.4054 & -514.5969 & -493.4105 & -489.2632 \\
      Ti & -484.2282 & -509.6510 & -512.8528 & -502.0410 & -505.3761 & -509.9729 & -514.0700 & -493.6478 & -489.2234 \\
      V  & -484.1990 & -508.6926 & -512.3009 & -501.6777 & -504.4297 & -509.3618 & -513.4561 & -493.8569 & -488.9474 \\
      Zn & -475.2375 & -500.3556 & -504.4103 & -492.4144 & -496.5426 & -499.4232 & -504.6297 & -482.6782 & -481.0438 \\
      Ag & -476.7049 & -501.6430 & -504.5861 & -493.9138 & -496.7220 & -500.9477 & -504.5408 & -482.6604 & -481.2659 \\
      Cd & -475.1288 & -500.1854 & -503.4108 & -491.8954 & -495.6486 & -499.4959 & -503.6209 & -483.3427 & -479.8278 \\
      In & -481.1330 & -504.1653 & -506.4422 & -496.0016 & -498.6643 & -503.3286 & -507.3780 & -485.6281 & -483.1445 \\
      Mo & -484.2892 & -509.4263 & -512.9103 & -503.0025 & -505.5534 & -509.6730 & -513.0136 & -493.5700 & -489.4994 \\
      Nb & -485.4055 & -510.7952 & -514.0380 & -503.5663 & -506.3671 & -511.1572 & -514.7845 & -495.5118 & -490.2111 \\
      Pd & -481.5399 & -504.7593 & -508.5173 & -498.0817 & -501.1620 & -504.0892 & -508.1976 & -486.1551 & -483.9553 \\
      Rh & -479.8884 & -505.2422 & -508.6754 & -498.7129 & -501.4594 & -504.5254 & -508.9536 & -487.8771 & -485.0738 \\
      Ru & -483.8526 & -507.5120 & -511.5881 & -500.6857 & -504.1497 & -506.8934 & -510.9524 & -490.6690 & -488.0169 \\
      Sb & -478.5169 & -502.9708 & -506.5211 & -494.8740 & -498.9453 & -502.5347 & -507.2111 & -486.4448 & -483.4418 \\
      Sn & -481.4238 & -504.4677 & -507.8470 & -496.2883 & -499.9258 & -503.6685 & -508.8152 & -487.6963 & -484.6351 \\
      Tc & -482.7091 & -507.9652 & -512.1064 & -501.9896 & -504.6034 & -508.3486 & -511.4777 & -492.0381 & -488.0897 \\
      Y  & -484.6612 & -509.8564 & -513.6851 & -501.9522 & -505.8238 & -509.8344 & -515.2400 & -493.4038 & -489.6506 \\
      Zr & -485.4694 & -511.1852 & -514.3901 & -503.1958 & -506.9346 & -511.5864 & -515.6720 & -496.3037 & -490.4785 \\
      Au & -479.1941 & -502.3245 & -506.9013 & -495.6782 & -499.0711 & -501.6877 & -506.5462 & -484.6198 & -483.6909 \\
      Bi & -478.2695 & -502.8490 & -506.2055 & -494.6965 & -498.5557 & -502.3398 & -506.7999 & -485.7536 & -483.1348 \\
      Hf & -486.5155 & -512.4535 & -515.5965 & -504.3393 & -508.1599 & -512.8332 & -517.2187 & -496.4195 & -491.7486 \\
      Hg & -472.8730 & -500.0491 & -502.1889 & -491.7544 & -494.1224 & -499.2181 & -501.8365 & -480.3761 & -479.2046 \\
      Ir & -483.7878 & -507.2024 & -510.6763 & -500.2051 & -503.2948 & -506.5209 & -509.8509 & -490.9790 & -487.3503 \\
      Os & -484.9279 & -508.6427 & -512.5954 & -501.8541 & -505.2080 & -507.8334 & -511.8734 & -491.0155 & -489.0898 \\
      Pb & -481.3587 & -504.4450 & -507.5634 & -496.2379 & -499.6114 & -503.5822 & -508.1698 & -486.8476 & -484.2646 \\
      Pt & -481.1676 & -504.3670 & -508.2170 & -499.0073 & -500.9446 & -504.2695 & -508.1465 & -487.3508 & -484.6644 \\
      Re & -483.6421 & -508.9474 & -512.8388 & -502.8952 & -505.3651 & -509.1168 & -512.6374 & -493.0621 & -489.2811 \\
      Ta & -486.3299 & -512.1371 & -515.1895 & -504.6585 & -507.5888 & -512.5295 & -516.0165 & -497.0134 & -490.5695 \\
      Tl & -480.7357 & -503.7632 & -505.9937 & -495.5894 & -497.7724 & -503.0564 & -506.7919 & -484.0732 & -482.3846 \\
      W  & -485.2596 & -510.8145 & -514.28   & -504.2714 & -506.7988 & -511.0643 & -514.2358 & -494.4330 & -490.6506 \\
      \bottomrule
    \end{tabular}
  }
\end{table}

% Supplementary Table 5: DFT calculated final state energies for adsorbates supported on n-doped graphene
\begin{table}[htbp]
\label{supp_table5:e_n_gra}
    \caption{DFT calculated final state energies in eV for adsorbates supported on nitrogen-doped graphene.}
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{l *{9}{l}}
        \toprule
        Metal & *CO\textsubscript{2} & *COOH    & *CO       & *CHO
        & *CH\textsubscript{2}O  & *OCH\textsubscript{3}  & *O        & *OH       & *H        \\
        \midrule
        Al	& -652.7589	&-675.7997	&-679.7595	&-668.0296	&-671.7596	&-676.2161	&-681.1311	&-658.7849	&-656.4702 \\
        Co	& -654.3280 &-677.5394	&-681.2518	&-670.0860  &-673.9208	&-676.7761	&-680.7219	&-659.1714	&-657.8777 \\
        Cr	& -657.0479	&-680.2074	&-683.7982	&-673.0760  &-676.1859	&-679.4701	&-684.5295	&-664.7306	&-660.4141 \\
        Cu	& -650.2181	&-673.3928	&-675.5873	&-665.2174	&-668.0662	&-672.5797	&-675.7047	&-653.5770  &-652.1010 \\
        Fe	& -655.4034	&-678.5897	&-682.1186	&-671.9101	&-674.7438	&-677.8515	&-682.1216	&-661.5422	&-658.7383 \\
        Ga	& -649.9563	&-672.9807	&-676.9763	&-664.9727	&-669.0739	&-672.8536	&-677.7169	&-655.5345	&-653.9243 \\
        Ge	& -651.0391	&-674.1655	&-677.2582	&-665.9255	&-669.5282	&-673.3438	&-678.1585	&-657.4964	&-654.3444 \\
        Mn	& -656.5635	&-679.7128	&-683.1092	&-672.6753	&-675.6877	&-679.0710  &-683.3898	&-663.1584	&-659.7760 \\
        Ni	& -653.1461	&-676.3270  &-678.5166	&-668.1448	&-671.1502	&-675.5454	&-678.5411	&-656.3929	&-655.1238 \\
        Sc	& -655.2274	&-678.9985	&-682.8810  &-670.9489	&-674.9850  &-679.1986	&-684.3192	&-662.2442	&-659.0243 \\
        Ti	& -655.5937	&-680.2412	&-683.5514	&-671.9689	&-675.9724	&-680.4589	&-685.1366	&-665.2871	&-659.7132 \\
        V	  & -656.0751	&-680.2584	&-683.5739	&-672.6281	&-676.0229	&-680.5926	&-684.9400	&-665.6038	&-659.9017 \\
        Zn	& -648.2316	&-671.3824	&-674.1973	&-663.2623	&-666.3990 	&-670.5613	&-674.5436	&-652.2900  &-650.9227 \\
        Ag	& -646.9759	&-670.2666	&-673.2766	&-663.1058	&-665.7601	&-669.7801	&-673.0113	&-651.0760  &-649.9287 \\
        Cd	& -646.1687	&-669.2620  &-672.8043	&-661.4439	&-664.9473	&-668.8180  &-672.9588	&-650.7684	&-649.7670 \\
        In	& -648.6726	&-671.7218	&-675.3788	&-663.4885	&-667.5183	&-670.7536	&-675.8630  &-653.8535	&-652.4757 \\
        Mo	& -655.7944	&-680.2966	&-683.6262	&-672.7667	&-676.3955	&-680.6291	&-684.8234	&-665.8138	&-659.8169 \\
        Nb	& -656.0277	&-680.8814	&-684.2662	&-672.5576	&-676.9139	&-681.4203	&-685.7720  &-666.2363	&-660.3734 \\
        Pd	& -652.2091	&-675.3967	&-677.2760  &-667.1855	&-669.8609	&-674.6033	&-677.3498	&-655.1080  &-654.0027 \\
        Rh	& -653.6928	&-676.9529	&-680.9755	&-669.5137	&-673.6394	&-676.2879	&-680.2104	&-658.6953	&-657.6908 \\
        Ru	& -654.5425	&-678.2124	&-681.9561	&-672.0589	&-674.6177	&-678.0945	&-681.9008	&-661.3838	&-658.6572 \\
        Sb	& -649.9262	&-672.9182	&-675.6457	&-664.7128	&-667.9159	&-672.0849	&-675.8420 	&-655.1699	&-652.4240 \\
        Sn	& -650.5072	&-673.6118	&-675.7767	&-665.3842	&-668.0544	&-672.7597	&-676.5046	&-655.8947	&-652.9261 \\
        Tc	& -655.4025	&-679.3044	&-682.7454	&-672.5785	&-676.3294	&-679.4840  &-683.3209	&-664.2323	&-659.2703 \\
        Y	  & -655.2660 &-679.0430	&-682.7571	&-670.8208	&-674.7780  &-679.0775	&-684.1210  &-661.8034	&-658.8885 \\
        Zr	& -655.9118	&-680.6859	&-684.1920  &-672.1497	&-676.4014	&-680.7930  &-685.7940  &-665.4878	&-660.4163 \\
        Au	& -648.3344	&-671.3969	&-673.1469	&-663.1955	&-665.5964	&-670.5800	&-673.6092	&-651.2436	&-649.7275 \\
        Bi	& -649.1484	&-672.1225	&-675.1630  &-663.9594	&-667.2981	&-671.4617	&-675.6926	&-654.7684	&-651.8907 \\
        Hf	& -657.3364	&-682.3019	&-685.8119	&-673.6603	&-678.0090  &-682.4001	&-687.4607	&-666.9550  &-662.0651 \\
        Hg	& -644.7368	&-667.9224	&-671.2200	&-659.6906	&-663.5208	&-667.0466	&-670.9016	&-648.8944	&-648.3755 \\
        Ir	& -654.8564	&-678.1079	&-682.2865	&-670.9826	&-674.9484	&-677.4097	&-681.3088	&-660.1543	&-658.9895 \\
        Os	& -655.6722	&-679.5364	&-683.3240  &-673.4289	&-675.9254	&-679.4423	&-683.1300	&-663.0791	&-659.9901 \\
        Pb	& -649.8843	&-672.9588	&-674.5856	&-664.7553	&-667.1174	&-672.0886	&-675.8823	&-653.6827	&-651.5940 \\
        Pt	& -653.3281	&-676.5221	&-678.6094	&-668.2951	&-671.2463	&-675.7317	&-678.4334	&-656.4419	&-655.4733 \\
        Re	& -656.3492	&-680.7664	&-683.9596	&-673.9732	&-676.5164	&-681.0627	&-684.8096	&-665.9526	&-660.5620 \\
        Ta	& -657.1988	&-682.6048	&-685.8231	&-674.1666	&-678.5029	&-682.9709	&-687.2294	&-667.7321	&-661.8794 \\
        Tl	& -648.1346	&-671.1831	&-673.2953	&-662.9610  &-665.6240  &-670.3512	&-673.4567	&-651.7909	&-650.4750 \\
        W	  & -657.0204	&-682.0186	&-685.3735	&-674.3843	&-678.2483	&-682.4377	&-686.3613	&-667.4547	&-661.5686 \\
        \bottomrule
      \end{tabular}
    }
\end{table}

% Supplementary Table 6: DFT calculated final state energies for adsorbates supported on graphene with dual-vac
\begin{table}[htbp]
\label{supp_table6:e_vac_gra}
  \caption{DFT calculated final state energies in eV for adsorbates supported on graphene with dual-vacancy.}
  \resizebox{\textwidth}{!}{%
    \begin{tabular}{l *{9}{c}}
      \toprule
      Metal & *CO\textsubscript{2} & *COOH    & *CO       & *CHO
      & *CH\textsubscript{2}O  & *OCH\textsubscript{3}  & *O        & *OH       & *H        \\
      \midrule
      Al & -650.3496 & -673.3468 & -676.2273 & -665.6303 & -668.4112 & -672.5763 & -677.4453 & -655.0864 & -653.0166 \\
      Co & -652.5157 & -675.5864 & -679.3861 & -669.0614 & -672.8955 & -675.8508 & -679.5268 & -658.7929 & -655.9377 \\
      Cr & -655.0421 & -678.1256 & -681.8470 & -671.1282 & -674.2868 & -679.1554 & -683.4111 & -663.3554 & -658.4913 \\
      Cu & -649.8187 & -672.9161 & -674.9327 & -664.8190 & -669.0819 & -672.1515 & -674.7438 & -652.8789 & -653.6953 \\
      Fe & -653.7964 & -677.0127 & -680.3412 & -670.0219 & -673.9525 & -676.7631 & -681.1346 & -660.9239 & -656.9759 \\
      Ga & -649.0340 & -672.0433 & -674.9630 & -663.8505 & -667.2101 & -671.2541 & -675.5229 & -653.2086 & -651.8693 \\
      Ge & -651.0133 & -674.2532 & -677.2272 & -666.0554 & -669.5660 & -673.4485 & -677.8152 & -655.7843 & -654.2731 \\
      Mn & -654.8183 & -678.0584 & -681.5834 & -670.9593 & -674.0994 & -677.9260 & -682.6048 & -662.5702 & -658.1064 \\
      Ni & -651.5295 & -674.6692 & -677.8941 & -667.2937 & -670.7325 & -673.9392 & -677.5204 & -656.1026 & -655.6559 \\
      Sc & -652.1630 & -675.5777 & -678.6101 & -667.5024 & -670.7255 & -675.4361 & -680.0287 & -658.0834 & -654.6913 \\
      Ti & -654.2548 & -677.9326 & -681.1516 & -670.0780 & -673.2830 & -677.9113 & -682.6933 & -661.1957 & -657.4040 \\
      V  & -654.6939 & -678.0200 & -681.8606 & -670.8517 & -674.2298 & -679.2097 & -683.4928 & -663.1639 & -658.4619 \\
      Zn & -646.9805 & -670.1676 & -672.2508 & -662.0849 & -664.7199 & -669.3791 & -672.6028 & -650.3134 & -648.8961 \\
      Ag & -647.4840 & -670.5954 & -672.4765 & -662.3757 & -665.1014 & -669.8199 & -672.2893 & -650.2207 & -651.5223 \\
      Cd & -645.2038 & -668.3897 & -670.2685 & -660.2502 & -662.7479 & -667.5994 & -670.6023 & -648.2958 & -646.9658 \\
      In & -646.8189 & -669.9379 & -673.1820 & -661.7351 & -665.3833 & -669.1524 & -673.5557 & -651.3730 & -650.2004 \\
      Mo & -656.2058 & -679.7202 & -683.2424 & -672.3832 & -675.6459 & -679.9903 & -684.8002 & -664.6331 & -659.9673 \\
      Nb & -656.1010 & -679.4842 & -683.3623 & -672.0587 & -675.6683 & -679.5996 & -684.8935 & -664.2634 & -659.9617 \\
      Pd & -650.5405 & -673.6524 & -677.0119 & -666.0816 & -669.7529 & -672.9394 & -676.5341 & -655.1586 & -654.8764 \\
      Rh & -652.7998 & -675.8992 & -679.6974 & -669.1468 & -672.2062 & -676.2142 & -679.9592 & -659.4214 & -656.7388 \\
      Ru & -654.8166 & -678.0140 & -681.6090 & -671.1415 & -674.0502 & -677.9828 & -682.4415 & -662.4653 & -658.2092 \\
      Sb & -649.9882 & -673.0639 & -675.9906 & -664.8414 & -668.3621 & -672.2685 & -676.6274 & -655.1055 & -653.1345 \\
      Sn & -648.5997 & -671.7246 & -675.2765 & -663.7120 & -667.5399 & -670.8850 & -675.8484 & -653.8138 & -652.4041 \\
      Tc & -655.8173 & -679.2476 & -682.6345 & -672.1709 & -675.0076 & -679.2729 & -683.7569 & -664.1434 & -659.2908 \\
      Y  & -652.1517 & -675.4891 & -678.6682 & -667.4644 & -670.6934 & -675.1478 & -680.0013 & -658.3045 & -654.7163 \\
      Zr & -654.8760 & -678.4572 & -681.6839 & -670.6090 & -673.8291 & -678.4537 & -683.1390 & -661.4741 & -657.9892 \\
      Au & -649.3963 & -672.5116 & -674.3660 & -664.2836 & -667.3357 & -671.7273 & -674.1359 & -652.0358 & -653.1138 \\
      Bi & -648.8651 & -672.0004 & -673.7920 & -663.7934 & -666.2170 & -671.1801 & -674.0672 & -652.8628 & -650.9149 \\
      Hf & -656.1155 & -679.7805 & -683.2130 & -671.9925 & -675.3123 & -679.9256 & -684.7502 & -662.8630 & -659.4860 \\
      Hg & -645.0948 & -668.2801 & -669.9749 & -660.1062 & -662.5696 & -667.4822 & -670.2672 & -647.8582 & -646.7652 \\
      Ir & -654.4999 & -677.8310 & -681.7312 & -671.1936 & -674.7821 & -678.1749 & -681.9532 & -661.9662 & -658.5262 \\
      Os & -656.3635 & -679.8433 & -683.4557 & -673.1036 & -675.9479 & -679.6710 & -684.4704 & -664.7281 & -660.0873 \\
      Pb & -647.8007 & -670.9491 & -673.2996 & -662.7392 & -665.6502 & -670.1373 & -673.5969 & -651.6692 & -650.4432 \\
      Pt & -652.4961 & -675.6092 & -678.9183 & -668.2053 & -671.6867 & -674.8876 & -678.4355 & -657.4936 & -656.2759 \\
      Re & -657.2440 & -681.0777 & -684.5183 & -673.9603 & -676.8950 & -681.2383 & -685.8328 & -666.1615 & -661.2885 \\
      Ta & -657.4068 & -681.0711 & -685.1062 & -673.5947 & -677.3738 & -681.6985 & -686.7561 & -666.0327 & -661.7361 \\
      Tl & -645.7286 & -668.8734 & -671.7205 & -660.7259 & -664.0001 & -668.1110 & -672.0305 & -649.7198 & -648.7563 \\
      W  & -657.5901 & -681.6722 & -685.1010 & -674.1028 & -677.7828 & -682.4493 & -686.6385 & -666.9364 & -661.8641 \\
      \bottomrule
    \end{tabular}
  }
\end{table}

% Supplementary Table 7: ZPE for adsorbates supported on g-c3n4
\begin{table}[htbp]
\label{supp_table7:zpe_g-c3n4}
  \caption{Zero-point energies in eV for relaxed adsorbates supported
    on g-C\textsubscript{3}N\textsubscript{4} at 298.15 K.}
  \resizebox{\textwidth}{!}{%
    \begin{tabular}{l *{9}{l}}
      \toprule
      Metal & *CO\textsubscript{2} & *COOH & *CO & *CHO
      & *CH\textsubscript{2}O & *OCH\textsubscript{3} & *O & *OH    & *H     \\
      \midrule
      Al & 0.2905 & 0.6130 & 0.1743 & 0.4606 & 0.7456 & 1.0974 & 0.0629 & 0.3521 & 0.1925 \\
      Co & 0.3038 & 0.5895 & 0.2051 & 0.4186 & 0.6269 & 1.0663 & 0.0571 & 0.3248 & 0.1507 \\
      Cr & 0.3140 & 0.5964 & 0.1640 & 0.4374 & 0.7725 & 1.0779 & 0.0670 & 0.3286 & 0.1626 \\
      Cu & 0.3157 & 0.6016 & 0.2045 & 0.4498 & 0.7797 & 1.0751 & 0.0494 & 0.3332 & 0.1577 \\
      Fe & 0.3088 & 0.5859 & 0.1931 & 0.4437 & 0.7720 & 1.0726 & 0.0599 & 0.3326 & 0.1550 \\
      Ga & 0.3102 & 0.6131 & 0.1448 & 0.4665 & 0.7186 & 1.0680 & 0.0608 & 0.3202 & 0.1813 \\
      Ge & 0.3091 & 0.6069 & 0.1396 & 0.4540 & 0.7269 & 1.0881 & 0.0581 & 0.3506 & 0.1904 \\
      Mn & 0.3022 & 0.5876 & 0.1733 & 0.4333 & 0.7637 & 1.0622 & 0.0687 & 0.3219 & 0.1432 \\
      Ni & 0.3023 & 0.5934 & 0.2074 & 0.4546 & 0.7662 & 1.0623 & 0.0542 & 0.3313 & 0.1611 \\
      Sc & 0.2880 & 0.6039 & 0.1771 & 0.4544 & 0.7473 & 1.0806 & 0.0657 & 0.3156 & 0.1480 \\
      Ti & 0.3044 & 0.6088 & 0.1889 & 0.4664 & 0.7863 & 1.0862 & 0.0796 & 0.3417 & 0.1590 \\
      V  & 0.3081 & 0.6005 & 0.2031 & 0.4408 & 0.7868 & 1.0882 & 0.0792 & 0.3388 & 0.1660 \\
      Zn & 0.3243 & 0.6080 & 0.1729 & 0.4601 & 0.7277 & 1.0832 & 0.0514 & 0.3468 & 0.1726 \\
      Ag & 0.3167 & 0.5993 & 0.1815 & 0.4457 & 0.7264 & 1.0590 & 0.0390 & 0.3304 & 0.1576 \\
      Cd & 0.3242 & 0.6007 & 0.1533 & 0.4502 & 0.7292 & 1.0604 & 0.0983 & 0.3322 & 0.1439 \\
      In & 0.3116 & 0.5687 & 0.1399 & 0.4025 & 0.7158 & 1.0551 & 0.0523 & 0.3315 & 0.1141 \\
      Mo & 0.3109 & 0.6071 & 0.2163 & 0.4441 & 0.7970 & 1.0825 & 0.0765 & 0.3312 & 0.1851 \\
      Nb & 0.3101 & 0.5971 & 0.2013 & 0.4340 & 0.7960 & 1.0908 & 0.0798 & 0.3329 & 0.1598 \\
      Pd & 0.3148 & 0.6091 & 0.1996 & 0.4778 & 0.7402 & 1.0777 & 0.0525 & 0.3425 & 0.1508 \\
      Rh & 0.3064 & 0.6180 & 0.2215 & 0.4654 & 0.7649 & 1.0844 & 0.0615 & 0.3643 & 0.1946 \\
      Ru & 0.3060 & 0.6201 & 0.2104 & 0.4668 & 0.7761 & 1.0800 & 0.0663 & 0.3421 & 0.2026 \\
      Sb & 0.3050 & 0.6244 & 0.1461 & 0.4696 & 0.7473 & 1.1052 & 0.0689 & 0.3676 & 0.2043 \\
      Sn & 0.3115 & 0.5941 & 0.1441 & 0.4373 & 0.7202 & 1.0761 & 0.0591 & 0.3397 & 0.1601 \\
      Tc & 0.3170 & 0.6102 & 0.2178 & 0.4543 & 0.7890 & 1.0807 & 0.0698 & 0.3442 & 0.2008 \\
      Y  & 0.2768 & 0.5949 & 0.1712 & 0.4467 & 0.7278 & 1.0780 & 0.0573 & 0.3206 & 0.1349 \\
      Zr & 0.2939 & 0.6068 & 0.1888 & 0.4631 & 0.7737 & 1.0875 & 0.0744 & 0.3155 & 0.1592 \\
      Au & 0.3123 & 0.6245 & 0.2147 & 0.4761 & 0.7312 & 1.0845 & 0.0527 & 0.3432 & 0.2066 \\
      Bi & 0.3076 & 0.6148 & 0.1485 & 0.4612 & 0.7392 & 1.0935 & 0.0611 & 0.3554 & 0.1893 \\
      Hf & 0.2928 & 0.6104 & 0.1880 & 0.4658 & 0.7769 & 1.0954 & 0.0765 & 0.3218 & 0.1728 \\
      Hg & 0.3220 & 0.6221 & 0.1486 & 0.4707 & 0.7338 & 1.0809 & 0.0541 & 0.3469 & 0.1924 \\
      Ir & 0.3127 & 0.6311 & 0.2271 & 0.4818 & 0.7530 & 1.0740 & 0.1084 & 0.3314 & 0.2142 \\
      Os & 0.3122 & 0.6260 & 0.2258 & 0.4796 & 0.7531 & 1.0911 & 0.0670 & 0.3501 & 0.2154 \\
      Pb & 0.3152 & 0.5834 & 0.1401 & 0.4239 & 0.7113 & 1.0486 & 0.0513 & 0.3043 & 0.1352 \\
      Pt & 0.3144 & 0.6361 & 0.2225 & 0.4908 & 0.7569 & 1.0921 & 0.0603 & 0.3672 & 0.2058 \\
      Re & 0.3171 & 0.6175 & 0.2213 & 0.4665 & 0.8021 & 1.0985 & 0.0780 & 0.3597 & 0.2032 \\
      Ta & 0.3099 & 0.5977 & 0.2000 & 0.4414 & 0.7993 & 1.0880 & 0.0847 & 0.3410 & 0.1780 \\
      Tl & 0.3114 & 0.5614 & 0.1389 & 0.3494 & 0.7105 & 1.0410 & 0.0246 & 0.3210 & 0.0951 \\
      W  & 0.3146 & 0.6059 & 0.2160 & 0.4456 & 0.8033 & 1.0886 & 0.0725 & 0.3387 & 0.1834 \\
      \bottomrule
    \end{tabular}
  }
\end{table}

% Supplementary Table 8: Entropy corrections for adsorbate@g-C3N4
\begin{table}[htbp]
\label{supp_table8:s_g-c3n4}
  \caption{Entropy corrections ($-T \cdot S$) in eV for relaxed
    adsorbates supported on g-C\textsubscript{3}N\textsubscript{4} at 298.15 K.}
  \resizebox{\textwidth}{!}{%
    \begin{tabular}{l *{9}{l}}
      \toprule
      Metal & *CO\textsubscript{2} & *COOH& *CO     & *CHO
      & *CH\textsubscript{2}O& *OCH\textsubscript{3}& *O      & *OH     & *H      \\
      \midrule
      Al & -0.2195 & -0.2476 & -0.1874 & -0.1939 & -0.2359 & -0.1759 & -0.0894 & -0.1010 & -0.0124 \\
      Co & -0.2359 & -0.2665 & -0.1544 & -0.1572 & -0.1755 & -0.2095 & -0.1078 & -0.1510 & -0.0341 \\
      Cr & -0.1862 & -0.2605 & -0.2075 & -0.2069 & -0.1478 & -0.1733 & -0.0790 & -0.1437 & -0.0221 \\
      Cu & -0.3098 & -0.2403 & -0.1655 & -0.1803 & -0.1647 & -0.2378 & -0.0977 & -0.1375 & -0.0297 \\
      Fe & -0.2184 & -0.2028 & -0.1676 & -0.1797 & -0.1742 & -0.2640 & -0.0815 & -0.1285 & -0.0215 \\
      Ga & -0.2602 & -0.2558 & -0.2291 & -0.1881 & -0.1252 & -0.2576 & -0.0897 & -0.1441 & -0.0182 \\
      Ge & -0.1978 & -0.2423 & -0.1635 & -0.1802 & -0.2104 & -0.2364 & -0.1178 & -0.1052 & -0.0087 \\
      Mn & -0.2142 & -0.2678 & -0.1863 & -0.2059 & -0.1788 & -0.2752 & -0.0808 & -0.1425 & -0.0261 \\
      Ni & -0.2460 & -0.1948 & -0.1592 & -0.1224 & -0.1275 & -0.2506 & -0.0997 & -0.1384 & -0.0224 \\
      Sc & -0.2227 & -0.2369 & -0.1843 & -0.1667 & -0.1817 & -0.2035 & -0.0728 & -0.1416 & -0.0226 \\
      Ti & -0.1978 & -0.2263 & -0.1685 & -0.1389 & -0.1414 & -0.1795 & -0.0578 & -0.1013 & -0.0195 \\
      V  & -0.2603 & -0.2511 & -0.1452 & -0.2028 & -0.1360 & -0.2374 & -0.0612 & -0.1082 & -0.0186 \\
      Zn & -0.2928 & -0.2543 & -0.1909 & -0.1959 & -0.2202 & -0.2331 & -0.0910 & -0.1185 & -0.0228 \\
      Ag & -0.2458 & -0.2428 & -0.1910 & -0.1890 & -0.3097 & -0.2421 & -0.1060 & -0.1392 & -0.0276 \\
      Cd & -0.2961 & -0.2561 & -0.2368 & -0.2023 & -0.2076 & -0.2630 & -0.0270 & -0.1408 & -0.0337 \\
      In & -0.1978 & -0.2895 & -0.1071 & -0.1840 & -0.1338 & -0.2826 & -0.1011 & -0.1386 & -0.0405 \\
      Mo & -0.1912 & -0.2310 & -0.1310 & -0.1680 & -0.1269 & -0.2228 & -0.0641 & -0.1496 & -0.0155 \\
      Nb & -0.1896 & -0.2540 & -0.1460 & -0.1924 & -0.1290 & -0.2147 & -0.0575 & -0.1177 & -0.0261 \\
      Pd & -0.2405 & -0.2385 & -0.1649 & -0.1740 & -0.2538 & -0.2201 & -0.0900 & -0.1143 & -0.0518 \\
      Rh & -0.2408 & -0.2385 & -0.1355 & -0.1734 & -0.1853 & -0.2247 & -0.0863 & -0.0866 & -0.0222 \\
      Ru & -0.2197 & -0.2304 & -0.1450 & -0.1769 & -0.1655 & -0.1574 & -0.0832 & -0.1294 & -0.0138 \\
      Sb & -0.2354 & -0.2277 & -0.1320 & -0.1793 & -0.2211 & -0.1961 & -0.0616 & -0.0808 & -0.0090 \\
      Sn & -0.2606 & -0.2544 & -0.2227 & -0.2021 & -0.3045 & -0.2568 & -0.0787 & -0.1171 & -0.0160 \\
      Tc & -0.1875 & -0.2373 & -0.1347 & -0.1733 & -0.1485 & -0.2301 & -0.0697 & -0.1007 & -0.0121 \\
      Y  & -0.2557 & -0.2528 & -0.1929 & -0.1886 & -0.2130 & -0.2081 & -0.0824 & -0.1393 & -0.0285 \\
      Zr & -0.2083 & -0.2325 & -0.1624 & -0.1459 & -0.1574 & -0.2014 & -0.0640 & -0.1556 & -0.0208 \\
      Au & -0.1901 & -0.2267 & -0.1484 & -0.1846 & -0.2939 & -0.2307 & -0.0857 & -0.1271 & -0.0138 \\
      Bi & -0.2366 & -0.2392 & -0.1915 & -0.1899 & -0.2361 & -0.1986 & -0.0683 & -0.0934 & -0.0100 \\
      Hf & -0.2043 & -0.2219 & -0.1618 & -0.1418 & -0.1489 & -0.1981 & -0.0610 & -0.1414 & -0.0163 \\
      Hg & -0.2980 & -0.2371 & -0.2812 & -0.1995 & -0.3039 & -0.2465 & -0.0878 & -0.1245 & -0.0175 \\
      Ir & -0.2097 & -0.2290 & -0.1261 & -0.1803 & -0.1913 & -0.2221 & -0.0377 & -0.1379 & -0.0159 \\
      Os & -0.1795 & -0.2235 & -0.1294 & -0.1519 & -0.1609 & -0.2027 & -0.0680 & -0.1093 & -0.0124 \\
      Pb & -0.2546 & -0.2691 & -0.1666 & -0.2165 & -0.2641 & -0.2520 & -0.1007 & -0.1097 & -0.0257 \\
      Pt & -0.2411 & -0.2029 & -0.1496 & -0.1593 & -0.2009 & -0.2246 & -0.0950 & -0.0937 & -0.0137 \\
      Re & -0.1869 & -0.2262 & -0.1293 & -0.1697 & -0.1266 & -0.2165 & -0.0644 & -0.0953 & -0.0146 \\
      Ta & -0.1872 & -0.2532 & -0.1523 & -0.1847 & -0.1265 & -0.1798 & -0.0535 & -0.1040 & -0.0177 \\
      Tl & -0.2599 & -0.2833 & -0.1807 & -0.1538 & -0.2422 & -0.1501 & -0.0126 & -0.1338 & -0.0533 \\
      W  & -0.1791 & -0.2368 & -0.1335 & -0.1723 & -0.1225 & -0.2253 & -0.0673 & -0.1180 & -0.0201 \\
      \bottomrule
    \end{tabular}
  }
\end{table}

% Supplementary Table 9: ZPE for adsorbates supported on N-doped graphene
\begin{table}[htbp]
\label{supp_table9:zpe_n_gra}
  \caption{Zero-point energies in eV for relaxed adsorbates
    supported on nitrogen-doped graphene at 298.15 K.}
  \resizebox{\textwidth}{!}{%
    \begin{tabular}{l *{9}{c}}
      \toprule
      Metal & *CO\textsubscript{2} & *COOH & *CO & *CHO
      & *CH\textsubscript{2}O & *OCH\textsubscript{3} & *O & *OH    & *H     \\
      \midrule
      Al & 0.3093 & 0.6024 & 0.1683 & 0.4395 & 0.7509 & 1.0855 & 0.0552 & 0.3401 & 0.1864 \\
      Co & 0.3140 & 0.6247 & 0.2044 & 0.4787 & 0.7345 & 1.0615 & 0.0606 & 0.3315 & 0.2006 \\
      Cr & 0.3108 & 0.5983 & 0.2007 & 0.4410 & 0.7211 & 1.0824 & 0.0828 & 0.3253 & 0.1625 \\
      Cu & 0.3145 & 0.5943 & 0.1460 & 0.4377 & 0.7196 & 1.0160 & 0.0407 & 0.3104 & 0.1523 \\
      Fe & 0.3117 & 0.6148 & 0.2195 & 0.4634 & 0.7877 & 1.0678 & 0.0703 & 0.3163 & 0.1858 \\
      Ga & 0.3129 & 0.6080 & 0.1561 & 0.4537 & 0.7495 & 1.0826 & 0.0573 & 0.3420 & 0.1897 \\
      Ge & 0.3131 & 0.6206 & 0.1402 & 0.4629 & 0.7281 & 1.1014 & 0.0686 & 0.3538 & 0.2110 \\
      Mn & 0.3120 & 0.6111 & 0.2128 & 0.4601 & 0.8078 & 1.0640 & 0.0793 & 0.3148 & 0.2040 \\
      Ni & 0.3110 & 0.6059 & 0.1485 & 0.4602 & 0.7283 & 1.0467 & 0.0402 & 0.3168 & 0.1620 \\
      Sc & 0.2741 & 0.5910 & 0.1620 & 0.4456 & 0.7019 & 1.0758 & 0.0575 & 0.3166 & 0.1338 \\
      Ti & 0.2920 & 0.6020 & 0.1781 & 0.4525 & 0.7593 & 1.0831 & 0.0731 & 0.2981 & 0.1481 \\
      V  & 0.2984 & 0.6055 & 0.1865 & 0.4609 & 0.7756 & 1.0843 & 0.0786 & 0.3171 & 0.1525 \\
      Zn & 0.3143 & 0.5928 & 0.1554 & 0.4357 & 0.7116 & 1.0521 & 0.0394 & 0.3248 & 0.1640 \\
      Ag & 0.3127 & 0.5862 & 0.1862 & 0.4307 & 0.7518 & 1.0419 & 0.0356 & 0.3231 & 0.1308 \\
      Cd & 0.3055 & 0.5910 & 0.1518 & 0.4402 & 0.7312 & 1.0524 & 0.0366 & 0.3189 & 0.1483 \\
      In & 0.3096 & 0.5986 & 0.1414 & 0.4477 & 0.7152 & 1.0724 & 0.0437 & 0.3300 & 0.1609 \\
      Mo & 0.2949 & 0.6111 & 0.1914 & 0.4728 & 0.7806 & 1.0887 & 0.0795 & 0.3253 & 0.1500 \\
      Nb & 0.2946 & 0.5996 & 0.1767 & 0.4601 & 0.7874 & 1.0896 & 0.0742 & 0.3048 & 0.1515 \\
      Pd & 0.3122 & 0.5993 & 0.1444 & 0.4490 & 0.7303 & 1.0342 & 0.0300 & 0.3047 & 0.1558 \\
      Rh & 0.3115 & 0.6288 & 0.1969 & 0.4826 & 0.7388 & 1.0867 & 0.0602 & 0.3453 & 0.2025 \\
      Ru & 0.3152 & 0.6122 & 0.2180 & 0.4569 & 0.7918 & 1.0947 & 0.0698 & 0.3483 & 0.1873 \\
      Sb & 0.3115 & 0.5874 & 0.1397 & 0.4349 & 0.7184 & 1.0467 & 0.0646 & 0.3351 & 0.1752 \\
      Sn & 0.3112 & 0.6002 & 0.1400 & 0.4367 & 0.7239 & 1.0836 & 0.0568 & 0.3359 & 0.1710 \\
      Tc & 0.3053 & 0.6110 & 0.2105 & 0.4251 & 0.7934 & 1.0870 & 0.0807 & 0.3496 & 0.1741 \\
      Y  & 0.2709 & 0.5835 & 0.1580 & 0.4307 & 0.7059 & 1.0703 & 0.0500 & 0.3200 & 0.1226 \\
      Zr & 0.2719 & 0.5963 & 0.1723 & 0.4430 & 0.7327 & 1.0846 & 0.0669 & 0.3176 & 0.1472 \\
      Au & 0.3137 & 0.5480 & 0.1442 & 0.3577 & 0.7209 & 0.9864 & 0.0174 & 0.2881 & 0.1027 \\
      Bi & 0.3111 & 0.5778 & 0.1378 & 0.4190 & 0.7133 & 1.0475 & 0.0550 & 0.3241 & 0.1533 \\
      Hf & 0.2699 & 0.6002 & 0.1714 & 0.4452 & 0.7372 & 1.0904 & 0.0687 & 0.3242 & 0.1569 \\
      Hg & 0.3113 & 0.6082 & 0.1397 & 0.4569 & 0.7258 & 1.0720 & 0.0412 & 0.3304 & 0.1625 \\
      Ir & 0.3132 & 0.6309 & 0.2106 & 0.4856 & 0.7390 & 1.0888 & 0.0626 & 0.3456 & 0.2022 \\
      Os & 0.3156 & 0.6148 & 0.2179 & 0.4592 & 0.7971 & 1.0984 & 0.0768 & 0.3463 & 0.1812 \\
      Pb & 0.3116 & 0.5352 & 0.1385 & 0.3677 & 0.7147 & 1.0532 & 0.0474 & 0.3172 & 0.1302 \\
      Pt & 0.3139 & 0.6134 & 0.1439 & 0.4671 & 0.7359 & 1.0406 & 0.0482 & 0.3114 & 0.1736 \\
      Re & 0.3035 & 0.6045 & 0.2095 & 0.4566 & 0.7995 & 1.0957 & 0.0846 & 0.3493 & 0.1818 \\
      Ta & 0.2751 & 0.6019 & 0.1869 & 0.4630 & 0.7724 & 1.0937 & 0.0751 & 0.3060 & 0.1669 \\
      Tl & 0.3131 & 0.5988 & 0.1402 & 0.4439 & 0.7193 & 1.0169 & 0.0573 & 0.3244 & 0.1506 \\
      W  & 0.2889 & 0.6117 & 0.1927 & 0.4777 & 0.7852 & 1.0941 & 0.0810 & 0.3273 & 0.1832 \\
      \bottomrule
    \end{tabular}
  }
\end{table}

% Supplementary Table 10: Entropy corrections for adsorbate@N-doped graphene
\begin{table}[htbp]
\label{supp_table10:s_n_gra}
  \caption{Entropy corrections ($-T \cdot S$) in eV for relaxed
    adsorbates supported on nitrogen-doped graphene at 298.15 K.}
  \resizebox{\textwidth}{!}{%
    \begin{tabular}{l *{9}{l}}
      \toprule
      Metal & *CO\textsubscript{2} & *COOH& *CO     & *CHO
      & *CH\textsubscript{2}O& *OCH\textsubscript{3}& *O      & *OH     & *H      \\
      \midrule
      Al & -0.1981 & -0.2564 & -0.1979 & -0.1424 & -0.2051 & -0.1839 & -0.0794 & -0.1211 & -0.0113 \\
      Co & -0.2358 & -0.2213 & -0.1589 & -0.1584 & -0.2025 & -0.2223 & -0.0701 & -0.0817 & -0.0123 \\
      Cr & -0.2593 & -0.1973 & -0.1568 & -0.2037 & -0.2291 & -0.1679 & -0.0569 & -0.0875 & -0.0228 \\
      Cu & -0.2457 & -0.2636 & -0.2132 & -0.2040 & -0.1267 & -0.2137 & -0.1188 & -0.1711 & -0.0226 \\
      Fe & -0.1936 & -0.2385 & -0.1356 & -0.1758 & -0.1985 & -0.1910 & -0.0647 & -0.0892 & -0.0172 \\
      Ga & -0.2565 & -0.1937 & -0.1600 & -0.2025 & -0.2139 & -0.1766 & -0.0727 & -0.1269 & -0.0126 \\
      Ge & -0.2469 & -0.2413 & -0.1027 & -0.1937 & -0.1687 & -0.1551 & -0.0690 & -0.1091 & -0.0080 \\
      Mn & -0.1929 & -0.2402 & -0.1409 & -0.1736 & -0.1949 & -0.2011 & -0.0563 & -0.1631 & -0.0160 \\
      Ni & -0.1239 & -0.2440 & -0.2027 & -0.1785 & -0.2318 & -0.1792 & -0.0929 & -0.1520 & -0.0170 \\
      Sc & -0.1938 & -0.2647 & -0.1418 & -0.2024 & -0.2291 & -0.2139 & -0.0790 & -0.1516 & -0.0293 \\
      Ti & -0.2093 & -0.2423 & -0.1798 & -0.1640 & -0.1765 & -0.1433 & -0.0692 & -0.1462 & -0.0262 \\
      V  & -0.2112 & -0.2373 & -0.1734 & -0.1578 & -0.1642 & -0.0767 & -0.0621 & -0.1522 & -0.0273 \\
      Zn & -0.2567 & -0.2001 & -0.2491 & -0.2135 & -0.1581 & -0.1396 & -0.1091 & -0.1668 & -0.0211 \\
      Ag & -0.2600 & -0.2035 & -0.1802 & -0.2231 & -0.1723 & -0.1531 & -0.1293 & -0.1487 & -0.0596 \\
      Cd & -0.2615 & -0.2042 & -0.1827 & -0.2185 & -0.2727 & -0.2094 & -0.1192 & -0.1850 & -0.0320 \\
      In & -0.1886 & -0.2021 & -0.1593 & -0.2221 & -0.1949 & -0.2061 & -0.1158 & -0.1603 & -0.0238 \\
      Mo & -0.2049 & -0.2075 & -0.1659 & -0.1327 & -0.1650 & -0.2041 & -0.0605 & -0.1258 & -0.0437 \\
      Nb & -0.2072 & -0.2300 & -0.1145 & -0.1439 & -0.1403 & -0.2086 & -0.0684 & -0.1863 & -0.0251 \\
      Pd & -0.1843 & -0.2620 & -0.1476 & -0.2000 & -0.1645 & -0.2057 & -0.1131 & -0.1688 & -0.0223 \\
      Rh & -0.2986 & -0.2220 & -0.1669 & -0.1667 & -0.1953 & -0.1423 & -0.0693 & -0.1229 & -0.0149 \\
      Ru & -0.1998 & -0.1779 & -0.1375 & -0.1827 & -0.1455 & -0.2017 & -0.0653 & -0.1103 & -0.0202 \\
      Sb & -0.1938 & -0.1984 & -0.1084 & -0.2024 & -0.1970 & -0.0996 & -0.0780 & -0.1183 & -0.0109 \\
      Sn & -0.1931 & -0.2040 & -0.1708 & -0.2214 & -0.1801 & -0.2006 & -0.0911 & -0.1474 & -0.0185 \\
      Tc & -0.2038 & -0.2277 & -0.1483 & -0.1505 & -0.1515 & -0.1810 & -0.0569 & -0.1008 & -0.0234 \\
      Y  & -0.1994 & -0.2704 & -0.1507 & -0.1605 & -0.2919 & -0.2162 & -0.0981 & -0.1548 & -0.0344 \\
      Zr & -0.2233 & -0.2608 & -0.1845 & -0.1849 & -0.2016 & -0.2144 & -0.0776 & -0.1500 & -0.0242 \\
      Au & -0.1872 & -0.1923 & -0.2237 & -0.1738 & -0.1907 & -0.2639 & -0.1497 & -0.1276 & -0.0301 \\
      Bi & -0.1978 & -0.2736 & -0.1731 & -0.1581 & -0.2369 & -0.0995 & -0.0937 & -0.1386 & -0.0171 \\
      Hf & -0.2235 & -0.2562 & -0.1836 & -0.1839 & -0.1987 & -0.2082 & -0.0759 & -0.1417 & -0.0211 \\
      Hg & -0.1907 & -0.1929 & -0.1053 & -0.0955 & -0.1765 & -0.2558 & -0.1157 & -0.1694 & -0.0357 \\
      Ir & -0.2967 & -0.2218 & -0.1486 & -0.1659 & -0.2038 & -0.2134 & -0.0723 & -0.1326 & -0.0200 \\
      Os & -0.1948 & -0.2462 & -0.1422 & -0.1945 & -0.1448 & -0.2046 & -0.0598 & -0.1205 & -0.0322 \\
      Pb & -0.1979 & -0.2320 & -0.1108 & -0.2414 & -0.1437 & -0.2639 & -0.1126 & -0.1465 & -0.0238 \\
      Pt & -0.1770 & -0.2479 & -0.1481 & -0.1915 & -0.2820 & -0.2030 & -0.0791 & -0.1666 & -0.0228 \\
      Re & -0.1958 & -0.2535 & -0.1508 & -0.1867 & -0.1462 & -0.2483 & -0.0561 & -0.1018 & -0.0249 \\
      Ta & -0.2078 & -0.2197 & -0.1675 & -0.1373 & -0.1542 & -0.2084 & -0.0698 & -0.1979 & -0.0195 \\
      Tl & -0.2573 & -0.2043 & -0.1719 & -0.2270 & -0.1288 & -0.2326 & -0.0688 & -0.1876 & -0.0332 \\
      W  & -0.2007 & -0.2007 & -0.1642 & -0.1194 & -0.1565 & -0.2032 & -0.0607 & -0.1275 & -0.0202 \\
      \bottomrule
    \end{tabular}
  }
\end{table}

% Supplementary Table 11: ZPE for adsorbates supported on graphene with dual-vac
\begin{table}[htbp]
\label{supp_table11:zpe_vac_gra}
  \caption{Zero-point energies in eV for relaxed adsorbates
    supported on graphene with dual-vacancy at 298.15 K.}
  \resizebox{\textwidth}{!}{%
    \begin{tabular}{l *{9}{l}}
      \toprule
      Metal & *CO\textsubscript{2} & *COOH & *CO & *CHO
      & *CH\textsubscript{2}O & *OCH\textsubscript{3}          & *O     & *OH    & *H     \\
      \midrule
      Al & 0.3140 & 0.5988 & 0.1888 & 0.4386 & 0.7218 & 1.0769 & 0.0472 & 0.3366 & 0.1729 \\
      Co & 0.3080 & 0.6179 & 0.2173 & 0.4899 & 0.7928 & 1.0616 & 0.0573 & 0.3458 & 0.1726 \\
      Cr & 0.3318 & 0.5862 & 0.1957 & 0.4277 & 0.8826 & 1.0733 & 0.0792 & 0.3294 & 0.1560 \\
      Cu & 0.3140 & 0.6023 & 0.1769 & 0.5229 & 0.7172 & 1.0131 & 0.0323 & 0.3298 & 0.2857 \\
      Fe & 0.3177 & 0.6110 & 0.2083 & 0.5038 & 0.7828 & 1.0802 & 0.0776 & 0.3515 & 0.1987 \\
      Ga & 0.3126 & 0.6056 & 0.1492 & 0.4494 & 0.7196 & 1.0788 & 0.0446 & 0.3370 & 0.1810 \\
      Ge & 0.3138 & 0.6171 & 0.1471 & 0.4657 & 0.7196 & 1.0935 & 0.0540 & 0.3514 & 0.2028 \\
      Mn & 0.3167 & 0.6141 & 0.2050 & 0.4803 & 0.8009 & 1.0809 & 0.0756 & 0.3411 & 0.1594 \\
      Ni & 0.3134 & 0.6251 & 0.1942 & 0.4571 & 0.7230 & 1.0738 & 0.0496 & 0.3521 & 0.2877 \\
      Sc & 0.3229 & 0.5874 & 0.1668 & 0.4367 & 0.7358 & 1.0673 & 0.0533 & 0.3129 & 0.1288 \\
      Ti & 0.3240 & 0.6049 & 0.1749 & 0.4562 & 0.7202 & 1.0694 & 0.0670 & 0.3143 & 0.1559 \\
      V  & 0.2937 & 0.6042 & 0.1933 & 0.4593 & 0.8437 & 1.0745 & 0.0753 & 0.3319 & 0.1687 \\
      Zn & 0.3123 & 0.5888 & 0.1564 & 0.4317 & 0.7111 & 1.0363 & 0.0324 & 0.3157 & 0.1363 \\
      Ag & 0.3172 & 0.5984 & 0.1399 & 0.4312 & 0.7199 & 1.0034 & 0.0258 & 0.3141 & 0.2932 \\
      Cd & 0.3120 & 0.5796 & 0.1487 & 0.4176 & 0.7144 & 1.0198 & 0.0278 & 0.3084 & 0.1280 \\
      In & 0.3134 & 0.5973 & 0.1458 & 0.4443 & 0.7170 & 1.0666 & 0.0418 & 0.3236 & 0.1610 \\
      Mo & 0.3052 & 0.5923 & 0.1942 & 0.4668 & 0.7718 & 1.0844 & 0.0745 & 0.3350 & 0.1755 \\
      Nb & 0.2952 & 0.6071 & 0.1862 & 0.4605 & 0.7505 & 1.0749 & 0.0721 & 0.3274 & 0.1717 \\
      Pd & 0.3151 & 0.6191 & 0.1872 & 0.4609 & 0.7187 & 1.0525 & 0.0397 & 0.3371 & 0.2963 \\
      Rh & 0.2870 & 0.6096 & 0.2076 & 0.4297 & 0.7850 & 1.0628 & 0.0604 & 0.3590 & 0.2678 \\
      Ru & 0.3000 & 0.6040 & 0.2097 & 0.4645 & 0.7812 & 1.0710 & 0.0790 & 0.3319 & 0.1758 \\
      Sb & 0.3122 & 0.6143 & 0.1436 & 0.4604 & 0.7258 & 1.0938 & 0.0608 & 0.3481 & 0.1912 \\
      Sn & 0.3132 & 0.6077 & 0.1493 & 0.4550 & 0.7182 & 1.0807 & 0.0517 & 0.3338 & 0.1770 \\
      Tc & 0.3051 & 0.6025 & 0.2086 & 0.4585 & 0.7777 & 1.0690 & 0.0799 & 0.3285 & 0.2898 \\
      Y  & 0.3219 & 0.5847 & 0.1632 & 0.4299 & 0.7245 & 1.0646 & 0.0557 & 0.3182 & 0.1164 \\
      Zr & 0.3213 & 0.5966 & 0.1669 & 0.4527 & 0.7200 & 1.0620 & 0.0568 & 0.3151 & 0.1510 \\
      Au & 0.3172 & 0.5927 & 0.1448 & 0.4677 & 0.7261 & 0.9827 & 0.0291 & 0.2904 & 0.2898 \\
      Bi & 0.3108 & 0.6062 & 0.1406 & 0.4521 & 0.7185 & 1.0309 & 0.0528 & 0.3289 & 0.1696 \\
      Hf & 0.3241 & 0.5981 & 0.1713 & 0.4543 & 0.7236 & 1.0751 & 0.0586 & 0.3142 & 0.1550 \\
      Hg & 0.3130 & 0.5763 & 0.1421 & 0.3959 & 0.7161 & 0.9951 & 0.0177 & 0.2917 & 0.1258 \\
      Ir & 0.3054 & 0.6129 & 0.2147 & 0.4199 & 0.7939 & 1.0680 & 0.0712 & 0.3603 & 0.1863 \\
      Os & 0.3033 & 0.6068 & 0.2155 & 0.4695 & 0.7674 & 1.0779 & 0.0823 & 0.3330 & 0.1401 \\
      Pb & 0.3118 & 0.6044 & 0.1424 & 0.4518 & 0.7199 & 1.0740 & 0.0502 & 0.3250 & 0.1623 \\
      Pt & 0.3124 & 0.6242 & 0.1985 & 0.4680 & 0.7263 & 1.0514 & 0.0477 & 0.3406 & 0.2725 \\
      Re & 0.3033 & 0.6034 & 0.2108 & 0.4601 & 0.7864 & 1.0807 & 0.0780 & 0.3317 & 0.2191 \\
      Ta & 0.2938 & 0.6078 & 0.1872 & 0.4601 & 0.7707 & 1.0754 & 0.0732 & 0.3243 & 0.1783 \\
      Tl & 0.3091 & 0.5948 & 0.1424 & 0.4406 & 0.7123 & 1.0568 & 0.0342 & 0.3173 & 0.1569 \\
      W  & 0.3066 & 0.6062 & 0.1912 & 0.3984 & 0.8010 & 1.0777 & 0.0787 & 0.3333 & 0.1815 \\
      \bottomrule
    \end{tabular}
  }
\end{table}

% Supplementary Table 12: Entropy corrections for adsorbate@graphene with dual-vac
\begin{table}[htbp]
\label{supp_table12:s_vac_gra}
  \caption{Entropy corrections ($-T \cdot S$) in eV for relaxed
    adsorbates supported on graphene with dual-vacancy at 298.15 K.}
  \resizebox{\textwidth}{!}{%
    \begin{tabular}{l *{9}{l}}
      \toprule
        Metal & *CO\textsubscript{2} & *COOH& *CO     & *CHO
        & *CH\textsubscript{2}O& *OCH\textsubscript{3}& *O      & *OH     & *H      \\
        \midrule
        Al & -0.2501 & -0.2622 & -0.1799 & -0.2106 & -0.3101 & -0.2050 & -0.0980 & -0.1303 & -0.0165 \\
        Co & -0.1962 & -0.2352 & -0.1529 & -0.1520 & -0.1515 & -0.0821 & -0.0427 & -0.1165 & -0.0376 \\
        Cr & -0.2178 & -0.2281 & -0.1603 & -0.2297 & -0.0849 & -0.0961 & -0.0623 & -0.1200 & -0.0250 \\
        Cu & -0.1907 & -0.2528 & -0.1276 & -0.1239 & -0.1974 & -0.2279 & -0.0711 & -0.1357 & -0.0044 \\
        Fe & -0.2328 & -0.2473 & -0.0848 & -0.1300 & -0.1611 & -0.1248 & -0.0629 & -0.0996 & -0.0292 \\
        Ga & -0.1842 & -0.2577 & -0.2003 & -0.2061 & -0.1912 & -0.2332 & -0.0956 & -0.1395 & -0.0145 \\
        Ge & -0.2491 & -0.1850 & -0.1442 & -0.1942 & -0.1974 & -0.1522 & -0.0886 & -0.1119 & -0.0101 \\
        Mn & -0.2384 & -0.2493 & -0.1559 & -0.1654 & -0.1993 & -0.1304 & -0.0599 & -0.1090 & -0.0275 \\
        Ni & -0.2497 & -0.2279 & -0.1683 & -0.1836 & -0.2402 & -0.2254 & -0.1159 & -0.1027 & -0.0021 \\
        Sc & -0.2252 & -0.1996 & -0.1449 & -0.2023 & -0.2586 & -0.2259 & -0.1128 & -0.1670 & -0.0322 \\
        Ti & -0.2137 & -0.2297 & -0.1918 & -0.1703 & -0.2184 & -0.2455 & -0.0745 & -0.1598 & -0.0186 \\
        V  & -0.2319 & -0.2441 & -0.1693 & -0.1713 & -0.0933 & -0.0952 & -0.0673 & -0.1171 & -0.0164 \\
        Zn & -0.1971 & -0.2071 & -0.1798 & -0.2147 & -0.1577 & -0.2074 & -0.1203 & -0.1637 & -0.0293 \\
        Ag & -0.2465 & -0.2579 & -0.1696 & -0.1739 & -0.1930 & -0.2345 & -0.0117 & -0.1000 & -0.0038 \\
        Cd & -0.1963 & -0.2145 & -0.2124 & -0.2350 & -0.2120 & -0.2341 & -0.1338 & -0.1754 & -0.0354 \\
        In & -0.2567 & -0.2013 & -0.1464 & -0.1558 & -0.2003 & -0.1995 & -0.1043 & -0.1065 & -0.0228 \\
        Mo & -0.2106 & -0.2086 & -0.1656 & -0.1746 & -0.1628 & -0.2038 & -0.0668 & -0.1129 & -0.0144 \\
        Nb & -0.2307 & -0.2394 & -0.1752 & -0.1660 & -0.1679 & -0.1668 & -0.0688 & -0.1288 & -0.0138 \\
        Pd & -0.3134 & -0.2362 & -0.1751 & -0.1707 & -0.1779 & -0.0819 & -0.0677 & -0.1222 & -0.0039 \\
        Rh & -0.2128 & -0.2468 & -0.1542 & -0.1986 & -0.1595 & -0.0720 & -0.0949 & -0.0933 & -0.0021 \\
        Ru & -0.2275 & -0.2613 & -0.1426 & -0.1760 & -0.1693 & -0.0786 & -0.0577 & -0.1332 & -0.0175 \\
        Sb & -0.1891 & -0.1940 & -0.2266 & -0.1526 & -0.2398 & -0.2284 & -0.0788 & -0.1157 & -0.0132 \\
        Sn & -0.2529 & -0.1968 & -0.2028 & -0.2165 & -0.1898 & -0.1845 & -0.0886 & -0.1568 & -0.0170 \\
        Tc & -0.2158 & -0.2603 & -0.1459 & -0.1731 & -0.1578 & -0.0973 & -0.0574 & -0.1222 & -0.0647 \\
        Y  & -0.2962 & -0.2657 & -0.1496 & -0.2075 & -0.2598 & -0.2231 & -0.1096 & -0.1662 & -0.0384 \\
        Zr & -0.1548 & -0.2417 & -0.1360 & -0.1770 & -0.2745 & -0.2015 & -0.0919 & -0.1551 & -0.0185 \\
        Au & -0.2413 & -0.2076 & -0.2877 & -0.1138 & -0.2448 & -0.2634 & -0.0095 & -0.1447 & -0.0041 \\
        Bi & -0.1970 & -0.2006 & -0.2337 & -0.1648 & -0.1315 & -0.2394 & -0.0927 & -0.1399 & -0.0183 \\
        Hf & -0.2728 & -0.2398 & -0.1920 & -0.1784 & -0.2711 & -0.3070 & -0.0834 & -0.1620 & -0.0186 \\
        Hg & -0.1953 & -0.2848 & -0.1710 & -0.1987 & -0.2065 & -0.1285 & -0.1491 & -0.1469 & -0.0370 \\
        Ir & -0.2144 & -0.1796 & -0.1476 & -0.1609 & -0.1474 & -0.0751 & -0.0699 & -0.0953 & -0.0258 \\
        Os & -0.2163 & -0.2409 & -0.1420 & -0.1599 & -0.1776 & -0.0816 & -0.0565 & -0.1218 & -0.0724 \\
        Pb & -0.1964 & -0.2001 & -0.2339 & -0.1644 & -0.1894 & -0.1890 & -0.0888 & -0.1086 & -0.0227 \\
        Pt & -0.1825 & -0.2340 & -0.1657 & -0.1759 & -0.2307 & -0.1921 & -0.0612 & -0.1216 & -0.0022 \\
        Re & -0.2117 & -0.2566 & -0.1472 & -0.1661 & -0.1530 & -0.1479 & -0.0619 & -0.1223 & -0.0261 \\
        Ta & -0.2269 & -0.2462 & -0.1744 & -0.1715 & -0.1696 & -0.1787 & -0.0694 & -0.1428 & -0.0135 \\
        Tl & -0.1981 & -0.2044 & -0.2304 & -0.2198 & -0.2048 & -0.2595 & -0.1146 & -0.1764 & -0.0256 \\
        W  & -0.2006 & -0.2433 & -0.1670 & -0.1453 & -0.1295 & -0.1025 & -0.0613 & -0.1185 & -0.0157 \\
        \bottomrule
    \end{tabular}
  }
\end{table}

\subsection{Correlation analysis of adsorption energies}
\label{supp_sec2.4_corr_analysis}

\cref{supp_fig9:corr_eads} presents a Pearson correlation map that illustrates the relationships between the adsorption energies of various intermediates. This analysis encompasses all six substrates under consideration. The mean Pearson correlation coefficient is 0.6023 with a variance of 0.0109, signifying a robust correlation between the adsorption energies of different intermediates, accompanied by low variability.

% SI Figure 9: Pearson correlation map for Eads of adsorbates for all substrates
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.7\textwidth]{supp_fig9_corr_eads.pdf}
  \caption{\textbf{Pearson correlation map for adsorption energies of various adsorbates for all six substrates.}}
  \label{supp_fig9:corr_eads}
\end{figure}

\subsection{The scaling relation scheme and the hybrid scaling relation}
\label{supp_sec2.5_scaling}

In line with the scaling relation framework proposed by Abild-Pedersen et al. \cite{abild2007scaling},
and later applied to the CO\textsubscript{2} reduction to methane process by Peterson \& Nørskov \cite{peterson2012activity},
adsorbates in the CO\textsubscript{2}RR process can be categorized into C-centered or O-centered species.
In each group, a representative species is designated as the ``descriptor'', allowing approximating the adsorption energies of other species within the same group using scaling relations.
The following equations capture this relationship:

\begin{align}
  G_{\text{ads}}X &= a_X \cdot G_{\text{ads}}{\text{CO}} + c_X
  && \text{(where  $X$ = COOH, CHO, CH\textsubscript{2}O)}  \label{supp_eq1:scaling_relation_x_co}  \\
  G_{\text{ads}}Y &= a_Y \cdot G_{\text{ads}}{\text{OH}} + c_Y
  && \text{(where  $Y$ = O, OCH\textsubscript{3})}          \label{supp_eq2:scaling_relation_y_oh}
\end{align}

Here, CO and OH serve as descriptors for C-centered ($X$) and O-centered ($Y$) groups, respectively, and $a_{\mathrm{X}}, c_{\mathrm{X}}, a_{\mathrm{Y}}, c_{\mathrm{Y}}$ are species-specific scaling parameters.
The scaling relations simplify the adsorption energy landscape to a two-dimensional space, thereby enabling visualization.

However, it's crucial to note that in the CO\textsubscript{2}RR process, most species are not solely C- or O-centered.
Thus, it becomes advantageous to incorporate both types of species in the scaling relation.
Building upon the hybrid scaling relation introduced in the main text, the free energy change ($\Delta\mathit{G}$) for any given reaction step can be readily calculated using \cref{main_eq14:general_scaling_relation} from the main text.
Consider the generic reaction step:
\begin{align}
  \ce{\text{*}A + H+ + e- -> \text{*}B}  \label{supp_eq3:generic_reaction}
\end{align}

The free energy change $\Delta\mathit{G}$ is defined as:
\begin{align}
  \Delta G = G(\text{*}\mathrm{B}) - G(\text{*}\mathrm{A}) - G(\mathrm{H}^+) - G(e^-)  \label{supp_eq4:free_energy_change}
\end{align}

Focusing on any reaction step delineated by \cref{main_eq1:co2rr1} to \cref{main_eq8:co2rr8} in the main text,
\cref{main_eq15:limiting_potential} shows that limiting potential $U_{\mathrm{L}}$ at a specific external potential $U$ is fully determined by the adsorption energies of two descriptors.
For instance, for the reaction described by \cref{main_eq2:co2rr2}:
\begin{align}
  \Delta G &= G(\text{*COOH}) - G(\text{*}) - G(\text{CO}_2) - G(\text{H}^+) - G(\text{e}^-)  \\
  &= G(\text{COOH}) + G(\text{*}) + G_{\text{ads}}\text{COOH} -
  G(\text{*}) - G(\text{CO}_2) -G(\text{H}^+) - G(\text{e}^-) \\
  &= G_{\text{ads}}\text{COOH} + G(\text{COOH}) - G(\text{CO}_2) -G(\text{H}^+) - G(\text{e}^-)  \label{supp_eq5:exp_reaction}
\end{align}

From adsorption energy linear relations, we have:
\begin{align}
  G_{ads}{\mathrm{COOH}} = a_{\text{COOH}} \cdot G_{ads}{\mathrm{CO}} +
  b_{\text{COOH}} \cdot G_{ads}{\mathrm{OH}} + c_{\text{COOH}}  \label{supp_eq6:eads}
\end{align}

which then reduces Supplementary \cref{supp_eq5:exp_reaction} to:
\begin{align}
  \begin{split}
    \Delta G = &(a_{\text{COOH}} \cdot G_{\text{ads}}{\mathrm{CO}} +
    b_{\text{COOH}} \cdot G_{\text{ads}}{\mathrm{OH}}) + \\
    &[c_{\text{COOH}} + G(\mathrm{COOH}) -
    G(\mathrm{CO}_2) - G(\mathrm{H}^+) - G(\mathrm{e}^-)]  \label{supp_eq7:reduced_eads}
  \end{split}
\end{align}
In this case, the first term depends solely on the descriptors, while the second term remains constant at a given potential $U$.

% Supplementary Table 13: Eads scaling relation params from hybrid descriptor method
\begin{table}[htbp]
\label{supp_table13:scaling_params}
  \caption{Adsorption free energy scaling relation parameters
    determined by the hybrid descriptor method.}
  \center
  \small
  \begin{tabularx}{0.75\textwidth}{@{}l *{3}{X} @{}}
    \toprule
    Adsorbate             & $a_Z$   & $b_Z$   & $c_Z$    \\
    \midrule
    COOH                  & 0.4032  & 0.5132  &  0.0899  \\
    CHO                   & 0.5977  & 0.3664  & -2.6763  \\
    CH\textsubscript{2}O  & 0.5011  & 0.5011  & -0.9806  \\
    OCH\textsubscript{3}  & 0.0532  & 1.0114  &  0.8489  \\
    O                     & 0.3758  & 1.2580  &  0.0910  \\
    H                     & 0.3164  & 0.3568  & -0.6764  \\
    \bottomrule
  \end{tabularx}

  \smallskip

  \begin{flushright}
    \begin{minipage}{\textwidth}
      \footnotesize\textit{Note:} $a_{Z}$, $b_{Z}$ and $c_{Z}$ correspond
      to coefficients for $G_{\text{ads}}\text{CO}$, $G_{\text{ads}}\text{OH}$
      and constant terms, where $Z$ stands for the adsorbed species of interest.
  \end{minipage}
  \end{flushright}
\end{table}

% SI Figure 10: Improvement in R2 from hybrid-descriptor method
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig10_r2_hyb_des.pdf}
  \caption{\textbf{$R^2$ improvement from hybrid-descriptor method.}
  Improvement in the coefficient of determination ($R^2$) with x-axis
  as CO ratio in CO/OH hybrid descriptors.
  (\textbf{a}) averaged $R^2$ and those of (\textbf{b}) CO\textsubscript{2},
  (\textbf{c}) COOH,
  (\textbf{d}) CHO, (\textbf{e}) CH\textsubscript{2}O, (\textbf{f})
  OCH\textsubscript{3}, (\textbf{g}) O and (\textbf{h}) H are shown.}
  \label{supp_fig10:r2_hyb_des}
\end{figure}

% Supplementary Table 14: Performance comparison of hybrid/single descriptors
\begin{table}[htbp]
\label{supp_table14:hybrid_des_perf}
  \caption{Performance comparison of hybrid descriptor and single
    descriptor for linear scaling relations.}
  \small
  \center
  \begin{tabularx}{0.75\textwidth}{@{}l *{3}{X} @{}}
    \toprule
    \multirow{2}{*}{Adsorbate} & Hybrid Descriptor $R^2$ & Single Descriptor $R^2$ & \multirow{2}{*}{$R^2$} \\
                               & (Optimal CO Ratio)      & Reference Species       &                        \\
    \midrule
    CO\textsubscript{2}   & 0.8083 (57\%)  & 0.7368 (CO)  & 0.0715  \\
    COOH                  & 0.9500 (44\%)  & 0.8113 (CO)  & 0.1387  \\
    CHO                   & 0.9146 (62\%)  & 0.8541 (CO)  & 0.0605  \\
    CH\textsubscript{2}O  & 0.9299 (50\%)  & 0.8226 (CO)  & 0.1073  \\
    OCH\textsubscript{3}  & 0.9936 (5\%)   & 0.9929 (OH)  & 0.0007  \\
    O                     & 0.8974 (23\%)  & 0.8825 (OH)  & 0.0149  \\
    H                     & 0.8303 (47\%)  & 0.7617 (OH)  & 0.0686  \\
    \bottomrule
  \end{tabularx}
\end{table}

\subsection{Volcano plots}
\label{supp_sec2.6_volcano}

In addition to the selectivity volcano plot featured in the main text, we provide a comprehensive plot capturing all rate-determining steps for CO\textsubscript{2}RR in \cref{supp_fig11:rds_volcano}. A separate plot focusing on selectivity over HER is also presented in \cref{supp_fig12:sel_volc}.

% SI Figure 11: CO2RR rate determining step volcano plot
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig11_rds_volcano.pdf}
  \caption{\textbf{CO\textsubscript{2}RR rate determining step volcano plot.}
  This graph illustrates the rate-determining step associated with each region within the CO\textsubscript{2}RR process.}
  \label{supp_fig11:rds_volcano}
\end{figure}

% SI Figure 12: CO2RR selectivity volcano plot
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig12_sel_volc.pdf}
  \caption{\textbf{CO\textsubscript{2}RR selectivity volcano plot.}
  Selectivity volcano plot computed from linear scaling relations.
  In the plot, the circle, triangle, square, diamond, plus, and star symbols correspond to
  metals supported on g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene, graphene with dual-vacancy,
  black phosphorous, BN, and C\textsubscript{2}N, respectively.}
  \label{supp_fig12:sel_volc}
\end{figure}

\subsection{Activity periodic tables}
\label{supp_sec2.7_ptable}

% SI Figure 13: Limiting potential periodic table for nitrogen-doped graphene
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig13_n-gra_ptable.pdf}
  \caption{\textbf{Limiting potential periodic table for nitrogen-doped graphene.}}
  \label{supp_fig13:n-gra_ptable}
\end{figure}

% SI Figure 14: Limiting potential periodic table for graphene with dual-vacancy
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig14_gra-vac_ptable.pdf}
  \caption{\textbf{Limiting potential periodic table for graphene with dual-vacancy.}}
  \label{supp_fig14:gra-vac_ptable}
\end{figure}

% SI Figure 15: Limiting potential periodic table for black phosphorus
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig15_BP_ptable.pdf}
  \caption{\textbf{Limiting potential periodic table for black phosphorus.}}
  \label{supp_fig15:BP_ptable}
\end{figure}

% SI Figure 16: Limiting potential periodic table for boron nitride
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig16_BN_ptable.pdf}
  \caption{\textbf{Limiting potential periodic table for boron nitride.}}
  \label{supp_fig16:BN_ptable}
\end{figure}

% SI Figure 17: Limiting potential periodic table for monolayer C2N
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig17_C2N_ptable.pdf}
  \caption{\textbf{Limiting potential periodic table for monolayer C\textsubscript{2}N.}}
  \label{supp_fig17:C2N_ptable}
\end{figure}

\newpage
% SI Section Two: Additional details on Machine Learning

\section{Additional details on machine learning method}

\subsection{d-band center and adsorption energy relations}
\label{supp_sec3.1_dband_eads}

% SI Figure 18: d-band venter vs adsorption energy scatter plot
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig18_d-band_eads.pdf}
  \caption{\textbf{Scatter plot of d-Band Center and Adsorption Energy Relationships.}
  This figure delineates the relationship between d-band center and adsorption energies for
  various species: (\textbf{a}) CO\textsubscript{2}, (\textbf{b}) COOH, (\textbf{c}) CO,
  (\textbf{d}) CHO, (\textbf{e}) CH\textsubscript{2}O, (\textbf{f}) OCH\textsubscript{3},
  (\textbf{g}) O, and (\textbf{h}) OH.
  Data from all six substrates investigated in this study are included.}
  \label{supp_fig18:dband_vs_eads}
\end{figure}

\subsection{Feature correlation analysis}
\label{supp_sec3.2_feature_corr}

\cref{supp_fig19:pairwise_eads_des} displays the pairwise relationships between CO adsorption energy
and its four most correlated descriptors: d-band center (spin-up) $\delta\epsilon_{\text{d}}\uparrow$,
lattice parameter $\gamma$, vacuum level $E_\text{vac}$, and electronegativity
on the Allen scale $\chi_\text{Allen}$, identified by Kendall rank correlation analysis.
\cref{supp_table15:descriptor_notations} lists notations for elementary descriptors and electronic descriptors.

% SI Figure 19: Pairwise plot of adsorption energy vs key descriptors
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig19_pairwise_eads_des.pdf}
  \caption{\textbf{Pairwise Plot of Adsorption Energy and Key Descriptors.}
  This chart displays the pairwise relationships between CO adsorption energy and
  its four most correlated descriptors: d-band center (spin-up) $\delta\epsilon_{\text{d}}\uparrow$,
  lattice parameter $\gamma$, vacuum level $E_\text{vac}$, and electronegativity
  on the Allen scale $\chi_\text{Allen}$, identified by Kendall rank correlation analysis.
  Data from all six substrates investigated in this study are included.}
  \label{supp_fig19:pairwise_eads_des}
\end{figure}

% Supplementary Table 15: Notations for elementary descriptors and electronic descriptors
\begin{table}[htbp]
\label{supp_table15:descriptor_notations}
  \caption{Notations for elementary descriptors and electronic descriptors.}
  \resizebox{\textwidth}{!}{%
    \begin{tabular}{llll}
      \toprule
      \multicolumn{2}{c}{Elementary Descriptors}       & \multicolumn{2}{c}{Electronic Descriptors}            \\
      \midrule
      $R$            & atomic radius                   & $\alpha$, $\beta$, $\gamma$  & lattice parameters     \\
      $E_\text{ea}$  & electron affinity               & $\Phi_{\text{DFT}}$    & DFT calculated work function \\
      $\Phi$         & work function                   & $E_\text{vac}$         & vacuum level                 \\
      $\chi_\text{Allen}$, $\chi_\text{P}$, $\chi_\text{RevP}$
      & \parbox[t]{4cm}{electronegativity in Allen, Pauling and revised Pauling scales}
      & $E_\text{g}$, $E_\text{g}\uparrow$, $E_\text{g}\uparrow$
      & \parbox[t]{4cm}{average, spin-up and spin-down band gaps}                                              \\
      $A_\text{r}$   & relative atomic mass            & $e_\text{d}$           & number of d-electrons        \\
      $E_\text{i}$   & ionization energy & $\delta\epsilon_{\text{d}}\uparrow$  & d-band centre (spin-up)      \\
      $G$            & group number                    & $W_\text{d}$           & d-band width                 \\
      $P$            & period number                   & $e_{\text{Bader}}$     & Bader charge                 \\
      $V$            & number of valence electrons     &                        &                              \\
      \bottomrule
    \end{tabular}
  }
\end{table}

\subsection{Input pipeline construction}
\label{supp_sec3.3_input_pipeline}

The format of the 2D array for the eDOS is naturally well-suited for use as neural network inputs.
In this study, the array adopts a shape of [numSamplings, numOrbitals, numChannels], as illustrated in \cref{supp_fig20:input_dos}.
Here, ``numSamplings'' represents the number of data points sampled across the energy spectrum,
``numOrbitals'' denotes the number of DOS orbitals,
and ``numChannels'' indicates the number of atomic channels.

% SI Figure 20: Representation of the input eDOS data structure
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.3\textwidth]{supp_fig20_input_dos.pdf}
  \caption{\textbf{Schematic representation of the input eDOS data structure.}}
  \label{supp_fig20:input_dos}
\end{figure}

For practical purposes, certain spatial hierarchies are expected to remain invariant,
such as the energy range over which the eDOS is sampled.
In this work, we maintain a consistent energy range of -14 eV to 6 eV,
sampled at a density of 50 \si{\text{points} \cdot \text{eV}^{-1}}.
In addition to maintaining a fixed energy range,
the following steps are taken to standardize the input eDOS data:
  1.	For atoms lacking d-electrons, the eDOS is zero-padded.
  2.	f-orbital eDOS data are excluded.
  3.	The eDOS of adsorbates is zero-padded along the Channels axis to align with the adsorbate that contains the maximum number of atoms, which, in this study, is the *OCH\textsubscript{3} species. This padded eDOS is then appended to the metal eDOS.

As a result of these preprocessing steps, the input eDOS arrays consistently have a shape of [4000, 9, 6].
This corresponds to 4000 sampling points across the energy range, 9 eDOS orbitals, and 6 atomic channels.

\subsection{Hyperparameter tuning for CNN}
\label{supp_sec3.4_hyperparam}

% Supplementary Table 16: The hyperparameter search space
\begin{table}[htbp]
\label{supp_table16:hyperparam_space}
  \caption{The hyperparameter search space.}
  \resizebox{\textwidth}{!}{%
    \begin{tabular}{lll}
      \toprule
      Hyperparameter& Search Space              & Description                                                       \\
      \midrule
      learningRate  & [10\textsuperscript{-4}, 10\textsuperscript{-2}], log scale & Learning rate of Adam \cite{kingma2017adam} optimizer \\
      dropoutRate   & [0, 1]                    & Dropout rate                                                      \\
      root\_fc0     & 128, 256, 512             & Output dimensionality of 1\textsuperscript{st} fully connected layer in root           \\
      root\_fc1     & 256, 512, 1024, 2048      & Output dimensionality of 2\textsuperscript{nd} fully connected layer in root           \\
      root\_act     & ``tanh'', ``relu'', ``sigmoid'' & Activation function of fully connected layers in root             \\
      kernelSize    & [2, 32]                   & Width of the convolution window                                   \\
      numFilters    & [8, 64]                   & Number of filters in the convolution                              \\
      numConvLayers & [1, 16]                   & Number of convolution layers                                      \\
      numConvBlocks & [1, 16]                   & Number of convolution blocks                                      \\
      br\_fc0       & 16, 32, 64, 128, 256, 512 & Output dimensionality of 1\textsuperscript{st} fully connected layer in branch      \\
      br\_fc1       & 8, 16, 32, 64, 128, 256   & Output dimensionality of 2\textsuperscript{nd} fully connected layer in branch      \\
      br\_act       & ``tanh'', ``relu'', ``sigmoid'' & Activation function of fully connected layers in branch           \\
      \bottomrule
    \end{tabular}
  }
\end{table}

% Supplementary Table 17: Optimal hyperparameters identified with Hyperband algorithm
\begin{table}[htbp]
\label{supp_table17:opt_hyperparam}
  \caption{Optimal hyperparameters identified with Hyperband algorithm.}
  \resizebox{\textwidth}{!}{%
    \begin{tabular}{lll}
      \toprule
      Hyperparameter& Optimal Value & Description                                              \\
      \midrule
      learningRate  & $10^{-3}$ & Learning rate of Adam \cite{kingma2017adam} optimizer                              \\
      dropoutRate   & 0.3       & Dropout rate                                                 \\
      root\_fc0     & 256       & Output dimensionality of 1\textsuperscript{st} fully connected layer in root   \\
      root\_fc1     & 512       & Output dimensionality of 2\textsuperscript{nd} fully connected layer in root   \\
      root\_act     & ``relu''    & Activation function of fully connected layers in root        \\
      kernelSize    & 10        & Width of convolution window                                  \\
      numFilters    & 17        & Number of filters in the convolution                         \\
      numConvLayers & 3         & Number of convolution layers                                 \\
      numConvBlocks & 1         & Number of convolution blocks                                 \\
      br\_fc0       & 256       & Output dimensionality of 1\textsuperscript{st} fully connected layer in branch \\
      br\_fc1       & 128       & Output dimensionality of 2\textsuperscript{nd} fully connected layer in branch \\
      br\_act       & ``tanh''    & Activation function of fully connected layers in branch      \\
      \bottomrule
    \end{tabular}
  }
\end{table}

% Supplementary Table 18: Prediction MAEs of the CNN model
\begin{table}[htbp]
\label{supp_table18:cnn_mae}
  \caption{Prediction mean absolute errors of the CNN model.}
  \small
  \center
  \begin{tabularx}{0.75\textwidth}{@{}lXX@{}}
    \toprule
    Adsorbate             & Original dataset (eV)  & Augmented dataset (eV)  \\
    \midrule
    CO\textsubscript{2}   & 0.0447                 & 0.0336                  \\
    COOH                  & 0.0436                 & 0.0581                  \\
    CO                    & 0.0402                 & 0.0402                  \\
    CHO                   & 0.0614                 & 0.0778                  \\
    CH\textsubscript{2}O  & 0.0553                 & 0.0632                  \\
    OCH\textsubscript{3}  & 0.0605                 & 0.0636                  \\
    O                     & 0.1135                 & 0.1081                  \\
    OH                    & 0.0547                 & 0.0602                  \\
    H                     & 0.0703                 & 0.0646                  \\
    \bottomrule
  \end{tabularx}

  \smallskip

  \begin{flushright}
  \begin{minipage}{\textwidth}
    \footnotesize\textit{Note:} The same CNN model, trained on the
      augmented dataset, was used for all predictions. The term ``original dataset''
      refers to evaluations conducted on the original dataset without any augmented data;
      it does not imply the use of a different CNN model trained solely on the original dataset.
      Similarly, ``augmented dataset'' refers to evaluations on the dataset with
      both original data and augment data, not a distinct model.
  \end{minipage}
  \end{flushright}
\end{table}

\subsection{Occlusion experiment}
\label{supp_sec3.5_occlusion}

% SI Figure 21: Illustration of the eDOS occlusion experiment
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig21_occlusion.pdf}
  \caption{\textbf{Illustration of the eDOS occlusion experiment.}
  This figure demonstrates the step-by-step process of the occlusion experiment.
  The input eDOS array first undergoes zero-padded, and then a masker of width ``width'' is applied,
  resulting in an occlusion array that preserves the shape of the input array.}
  \label{supp_fig21:occlusion}
\end{figure}

% SI Figure 22: Occlusion experiment with a masker width of 1
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig22_occl_wid1.pdf}
  \caption{\textbf{Occlusion Experiment with a masker width of ``1''.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig22:occl_wid1}
\end{figure}

% SI Figure 23: Occlusion experiment with a masker width of 3
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig23_occl_wid3.pdf}
  \caption{\textbf{Occlusion Experiment with a masker width of ``3''.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig23:occl_wid3}
\end{figure}

% SI Figure 24: Occlusion experiment with a masker width of 5
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig24_occl_wid5.pdf}
  \caption{\textbf{Occlusion Experiment with a masker width of ``5''.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig24:occl_wid5}
\end{figure}

% SI Figure 25: Occlusion experiment with a masker width of 11
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig25_occl_wid11.pdf}
  \caption{\textbf{Occlusion Experiment with a masker width of ``11''.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig25:occl_wid11}
\end{figure}

% SI Figure 26: Occlusion experiment with a masker width of 21
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig26_occl_wid21.pdf}
  \caption{\textbf{Occlusion Experiment with a masker width of ``21''.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig26:occl_wid21}
\end{figure}

% SI Figure 27: Occlusion experiment with a masker width of 31
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig27_occl_wid31.pdf}
  \caption{\textbf{Occlusion Experiment with a masker width of ``31''.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig27:occl_wid31}
\end{figure}

% SI Figure 28: Occlusion experiment with a masker width of 41
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig28_occl_wid41.pdf}
  \caption{\textbf{Occlusion Experiment with a masker width of ``41''.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig28:occl_wid41}
\end{figure}

% SI Figure 29: Occlusion experiment with a masker width of 51
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{supp_fig29_occl_wid51.pdf}
  \caption{\textbf{Occlusion Experiment with a masker width of ``51''.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{supp_fig29:occl_wid51}
\end{figure}

\subsection{Shifting experiment}
\label{supp_sec3.6_shifting}

% SI Figure 30: Illustration of the eDOS shifting experiment
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig30_shifting.pdf}
  \caption{\textbf{Illustration of the eDOS shifting experiment.}
  This figure illustrates the sequential stages of the shifting experiment.
  Initially, the input eDOS array is shifted along the Energy axis.
  Subsequently, it undergoes zero-padding and cropping,
  ensuring a consistent shape based on the shifting direction, to match the input eDOS array.
  The resulting shifted array is then processed by the CNN model to
  assess the disturbance in adsorption energy caused by the shifting operation.}
  \label{supp_fig30:shifting}
\end{figure}

% SI Figure 31: Shifting experiment on p orbital
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.75\textwidth]{supp_fig31_p_shifting.pdf}
  \caption{\textbf{Shifting experiment on p orbital.}
  Effect of orbital shifting on CO adsorption energy, predicted by the CNN model,
  for single metal atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.
  The perturbations caused by shifting of entire p orbital are presented.
  The shifting step size corresponds to the energy resolution of the eDOS, set at 0.005 eV in this study.
  A positive eDOS shift indicates a shift towards higher energy levels, and vice versa.}
  \label{supp_fig31:p_shifting}
\end{figure}

\newpage
% SI Section Three: Other Additional Information

\section{Other additional information}
\label{supp_sec4_env}

\subsection{Additional information on machine learning environment}
\label{supp_sec4.1_ml_env}

The hyperparameter optimization for the proposed CNN model was performed using NVIDIA\textsuperscript{\textregistered} V100 Tensor Core GPUs,
courtesy of the Australian National Computational Infrastructure's (NCI) HPC Gadi system.
The HyperBand algorithm \cite{li2018hyperband}, as implemented in
KerasTuner \cite{omalley2019kerastuner}, facilitated the tuning process.

% Supplementary Table 19: Packages in the DL env
\begin{table}[htbp]
\label{supp_table19:pack_dl_env}
  \caption{Core packages in the deep learning environment.}
  \small
  \center
  \begin{tabularx}{0.9\textwidth}{@{}l *{3}{X} @{}}
    \toprule
    Name                 & Version  & Build                         & Channel      \\
    \midrule
    conda                & 4.13.0   & py39h06a4308\textunderscore0  & anaconda     \\
    cuda-nvcc            & 11.8.89  & 0                             & nvidia       \\
    cuda-toolkit         & 11.8.0   & 0                             & nvidia       \\
    cudatoolkit          & 11.6.0   & habf752d\textunderscore9      & nvidia       \\
    ipykernel            & 6.9.1    & py39h06a4308\textunderscore0  & anaconda     \\
    ipython              & 7.34.0   & pypi\textunderscore0          & pypi         \\
    jupyter\_client      & 7.2.2    & py39h06a4308\textunderscore0  & anaconda     \\
    jupyterlab           & 3.4.4    & py39h06a4308\textunderscore0  & anaconda     \\
    keras                & 2.9.0    & pypi\textunderscore0          & pypi         \\
    keras-preprocessing  & 1.1.2    & pypi\textunderscore0          & pypi         \\
    keras-tuner          & 1.3.5    &                               & pypi         \\
    matplotlib           & 3.5.1    & py39h06a4308\textunderscore1  & anaconda     \\
    numpy                & 1.22.4   & pypi\textunderscore0          & pypi         \\
    pandas               & 1.3.4    & py39h8c16a72\textunderscore0  & anaconda     \\
    python               & 3.9.12   & h12debd9\textunderscore1      & anaconda     \\
    scikit-learn         & 1.1.1    & py39h6a678d5\textunderscore0  & anaconda     \\
    scipy                & 1.8.1    & py39hddc5342\textunderscore3  & conda-forge  \\
    tensorboard          & 2.9.1    & pypi\textunderscore0          & pypi         \\
    tensorflow           & 2.9.3    & pypi\textunderscore0          & pypi         \\
    tensorflow-gpu       & 2.9.3    & pypi\textunderscore0          & pypi         \\
    xlrd                 & 2.0.1    & pyhd3eb1b0\textunderscore0    & anaconda     \\
    yaml                 & 0.2.5    & h7b6447c\textunderscore0      & anaconda     \\
    \bottomrule
  \end{tabularx}

  \smallskip

  \begin{flushright}
  \begin{minipage}{\textwidth}
    \footnotesize\textit{Note:} The complete list of packages is
      provided along with the source code.
  \end{minipage}
  \end{flushright}
\end{table}

\subsection{Additional information on data analysis and visualization environment}
\label{supp_sec4.2_vis_env}

Data analysis and visualization tasks were executed on an Apple MacBook Air featuring an octa-core M2 chip.
For accuracy, the TensorFlow-Metal plugin for Mac-based GPU acceleration was deliberately excluded,
as it could potentially yield erroneous CNN model predictions.

The illustrations of CNN architecture displayed in \cref{main_fig1:pipeline} of the main text,
as well as \cref{supp_fig21:occlusion} and \cref{supp_fig30:shifting},
were obtained from the GitHub repository dair-ai/ml-visuals \cite{Saravia_ML_Visuals_2021}.
Blender was used to create and render the visual representation of the
catalyst analysis pipeline shown in \cref{main_fig1:pipeline} of the main text.

% Supplementary Table 20: Packages in data analysis and vis env
\begin{table}[htbp]
\label{supp_table20:pack_vis_env}
  \caption{Core packages in data analysis and visualization environment.}
  \small
  \center
  \begin{tabularx}{0.9\textwidth}{@{}l *{3}{X} @{}}
    \toprule
    Name              & Version  & Build                     & Channel  \\
    \midrule
    bokeh             & 3.2.2    & pypi\textunderscore0      & pypi     \\
    colorcet          & 3.0.1    & pypi\textunderscore0      & pypi     \\
    heatmapz          & 0.0.4    & pypi\textunderscore0      & pypi     \\
    keras             & 2.13.1   & pypi\textunderscore0      & pypi     \\
    keras-tuner       & 1.3.5    & pypi\textunderscore0      & pypi     \\
    matplotlib        & 3.7.2    & pypi\textunderscore0      & pypi     \\
    numpy             & 1.24.3   & pypi\textunderscore0      & pypi     \\
    pandas            & 2.0.3    & pypi\textunderscore0      & pypi     \\
    python            & 3.11.4   & hb885b13\textunderscore0  &          \\
    pyyaml            & 6.0.1    & pypi\textunderscore0      & pypi     \\
    scikit-learn      & 1.3.0    & pypi\textunderscore0      & pypi     \\
    scipy             & 1.11.1   & pypi\textunderscore0      & pypi     \\
    seaborn           & 0.12.2   & pypi\textunderscore0      & pypi     \\
    tensorboard       & 2.13.0   & pypi\textunderscore0      & pypi     \\
    tensorflow        & 2.13.0   & pypi\textunderscore0      & pypi     \\
    tensorflow-macos  & 2.13.0   & pypi\textunderscore0      & pypi     \\
    \bottomrule
  \end{tabularx}

  \smallskip

  \begin{flushright}
  \begin{minipage}{\textwidth}
    \footnotesize\textit{Note:} The complete list of packages
      is provided along with the source code.
  \end{minipage}
  \end{flushright}
\end{table}

% End of Supplementary Information

### 2024-03-22 paper/journal-submission/supplement.tex
add authors in SI title page

@@
 % Title
-\begin{center}
-  \Large{Supporting Information for:  \\
+\title{Supporting Information for:  \\
 Convolutional Neural Networks and Volcano Plots:
 Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions}
-\end{center}
+
+\author[1]{Haoyu Yang}
+\author[2]{Juanli Zhao}
+\author[3]{Qiankun Wang}
+\author[2]{Bin Liu}
+\author[4]{Wei Luo}
+\author[1,*]{Ziqi Sun}
+\author[5,*]{Ting Liao}
+
+\affil[1]{School of Chemistry and Physics, Queensland University of Technology,
+George Street, Brisbane, QLD 4000, Australia}
+\affil[2]{School of Materials Science and Engineering, Shanghai University, Shanghai, China}
+\affil[3]{School of Computer Science and Engineering, Southeast University, Nanjing, China}
+\affil[4]{College of Materials Science and Engineering, Institute of Functional Materials,
+Donghua University, Shanghai, China}
+\affil[5]{School of Mechanical Medical and Process Engineering, Queensland University of Technology,
+George Street, Brisbane, QLD 4000, Australia}
+\affil[*]{Corresponding author: ziqi.sun@qut.edu.au}
+\affil[*]{Corresponding author: t3.liao@qut.edu.au}
+
+\date{}
+\maketitle
 
